\Chapter{1}

\Verse{1}
{
	\hP{א בְּרֵאשִׁית בָּרָא אֱלֹהִים אֵת הַשָּׁמַיִם וְאֵת הָאָרֶץ}
}
{
	\eP{In the beginning of God’s creating the skies and the earth}
}
{
	\aB{

		Ok so according to the \textsc{DRWFEROTMSOHK}\footnote{Abbreviation for \textsc{The Dynamic Read-Writable Free Encyclopedic Repository of the Modern State of Human Knowledge}, hereafter abbreviated as ``the \textsc{Lord},'' to save space.}

		\begin{center}
		The word \hBP{אלהים} (Elhim) is a ``defective spelling'' of the word \hBP{אלוהים} (Elohim)
		\end{center}

		And if you look up that word, it says

		\begin{center}
		The word \hBP{אלוהים} (Elohim) is from the plural of \hBP{אלוה} (Eloh) which means ``god.''
		\end{center}

		And if you look around for some clarification, you'll find sentences like

		\begin{center}
		This word is sometimes grammatically plural and sometimes singular.
		\end{center}

		And you may also stumble upon a sentence mentioning that particularly devout believers

		\begin{center}
		...may prefer to write and say \hBP{אלוקים} (Elokim), so as not to abuse the name of God.
		\end{center}

		So we're off to a pretty weird start.
	}
}

\Verse{2}
{
	\hP{ב וְהָאָרֶץ הָיְתָה תֹהוּ וָבֹהוּ וְחֹשֶׁךְ עַל פְּנֵי תְהוֹם וְרוּחַ אֱלֹהִים מְרַחֶפֶת עַל פְּנֵי הַמָּיִם}
}
{
	\eP{when the earth had been shapeless and formless, and darkness was on the face of the deep, and God’s spirit was hovering on the face of the water}
}
{
	\aB{
		Ok so, apparently we didn't know how to read the past perfect in biblical Hebrew until the 1970s.\footnote{Old Calendar.}

		So it turns out the earth was already around when this Elohim character started creating it.

		Hence the ``had been'' in this line, and the odd grammar in the previous one.

		Just make a note of that and let's keep moving.
	}
}

\Verse{3}
{
	\hP{ג וַיֹּאמֶר אֱלֹהִים יְהִי אוֹר וַיְהִי אוֹר}
}
{
	\eP{God said, “Let there be light.” And there was light.}
}
{

	\aB{

		Words create stuff. Like this book.

		Not a huge surprise. At least to us Authors.\footnote{The bible, it turns out, was written by an Author.}

		I mean obviously.
	}
}

\Verse{4}
{
	\hP{ד וַיַּרְא אֱלֹהִים אֶת הָאוֹר כִּי טוֹב וַיַּבְדֵּל אֱלֹהִים בֵּין הָאוֹר וּבֵין הַחֹשֶׁךְ}
}
{
	\eP{And God saw the light, that it was good, and God separated between the light and the darkness.}
}
{
	\aB{
		Ok so after he creates light, he decides he did a good job.

		Then after that, he gets the darkness out of it.

		That's sort of like ``cleaning the light'' I guess.
	}
}

\Verse{5}
{
	\hP{ה וַיִּקְרָא אֱלֹהִים לָאוֹר יוֹם וְלַחֹשֶׁךְ קָרָא לָיְלָה וַיְהִי עֶרֶב וַיְהִי בֹקֶר יוֹם אֶחָד}
}
{
	\eP{And God called the light “day” and called the darkness “night.” And there was evening, and there was morning: one day.}
}
{
	\aB{
		Ok so he names the light, and the dark light that he cleaned out of the original light.

		He calls them day and night. Now remember, words create stuff.

		So immediately he's affected by this decision and it's suddenly day two.

		It's like if you ``invent murder'' and then suddenly there's a dead body.

		Because obviously. Hilarious.
	}
}

\Verse{6}
{
	\hP{ו וַיֹּאמֶר אֱלֹהִים יְהִי רָקִיעַ בְּתוֹךְ הַמָּיִם וִיהִי מַבְדִּיל בֵּין מַיִם לָמָיִם}
}
{
	\eP{And God said, “Let there be a space within the water, and let it separate between water and water.”}
}
{
	\aB{
		It's not super clear what's going on here yet.

		But he says some words.
	}
}

\Verse{7}
{
	\hP{ז וַיַּעַשׂ אֱלֹהִים אֶת הָרָקִיעַ וַיַּבְדֵּל בֵּין הַמַּיִם אֲשֶׁר מִתַּחַת לָרָקִיעַ וּבֵין הַמַּיִם אֲשֶׁר מֵעַל לָרָקִיעַ וַיְהִי כֵן}
}
{
	\eP{And God made the space, and it separated between the water that was under the space and the water that was above the space. And it was so.}
}
{
	\aB{
		Ok so it seems like the words didn't create the stuff this time.

		Because here after saying the words, he still has to make the thing.

		So he takes some of the water and pushes it up above the other water.

		The ``up water'' is the sky.

		Now wait, that's not as dumb as it sounds.

		I mean (1) it's blue up there, and (2) water comes down.

		So we must live in a middle bit between the ``up water'' and the ``down water.''

		Completely reasonable so far.
	}
}

\Verse{8}
{
	\hP{ח וַיִּקְרָא אֱלֹהִים לָרָקִיעַ שָׁמָיִם וַיְהִי עֶרֶב וַיְהִי בֹקֶר יוֹם שֵׁנִי}
}
{
	\eP{And God called the space “skies.” And there was evening, and there was morning: a second day.}
}
{
	\aB{
		The ``up water'' isn't in the sky.

		The sky is the bit in the middle, between the ``up water'' and ``down water.''

		No land yet. He's not done.

		Also the day ends before he got a chance to say ``it was good.''

		Hopefully he'll say it twice tomorrow and get back on schedule.
	}
}

\Verse{9}
{
	\hP{ט וַיֹּאמֶר אֱלֹהִים יִקָּווּ הַמַּיִם מִתַּחַת הַשָּׁמַיִם אֶל מָקוֹם אֶחָד וְתֵרָאֶה הַיַּבָּשָׁה וַיְהִי כֵן}
}
{
	\eP{And God said, “Let the waters be concentrated under the skies into one place, and let the land appear.” And it was so.}
}
{
	\aB{
		So he moves some of the down water horizontally so it all piles up in one place.

		Then land appears. He didn't make the land, it was already there.
	}
}

\Verse{10}
{
	\hP{י וַיִּקְרָא אֱלֹהִים לַיַּבָּשָׁה אֶרֶץ וּלְמִקְוֵה הַמַּיִם קָרָא יַמִּים וַיַּרְא אֱלֹהִים כִּי טוֹב}
}
{
	\eP{And God called the land “earth,” and called the concentration of the waters “seas.” And God saw that it was good.}
}
{
	\aB{
		Now remember, we already met the ``earth'' in line one.

		But now he calls the pile of water over there ``seas.''

		And the land over here is ``earth.''

		Same Hebrew word as the first line.

		It's spelled \hBP{אֶרֶץ} (Arts).

		That's earth.

		Also he said it's good again.
	}
}

\Verse{11}
{
	\hP{יא וַיֹּאמֶר אֱלֹהִים תַּדְשֵׁא הָאָרֶץ דֶּשֶׁא עֵשֶׂב מַזְרִיעַ זֶרַע עֵץ פְּרִי עֹשֶׂה פְּרִי לְמִינוֹ אֲשֶׁר זַרְעוֹ בוֹ עַל הָאָרֶץ וַיְהִי כֵן}
}
{
	\eP{And God said, “Let the earth generate plants, vegetation that produces seed, fruit trees, each making fruit of its own kind, which has its seed in it, on the earth. And it was so:”}
}
{
	\aB{
		At this point we're starting to notice that the author of this section is pretty verbose.
	}
}

\Verse{12}
{
	\hP{יב וַתּוֹצֵא הָאָרֶץ דֶּשֶׁא עֵשֶׂב מַזְרִיעַ זֶרַע לְמִינֵהוּ וְעֵץ עֹשֶׂה פְּרִי אֲשֶׁר זַרְעוֹ בוֹ לְמִינֵהוּ וַיַּרְא אֱלֹהִים כִּי טוֹב}
}
{
	\eP{The earth brought out plants, vegetation that produces seeds of its own kind, and trees that make fruit that each has seeds of its own kind in it. And God saw that it was good.}
}
{
	\aB{
		Really verbose. That'll be relevant later.

		Also, that's the second ``it was good'' today.
	}
}

\Verse{13}
{
	\hP{יג וַיְהִי עֶרֶב וַיְהִי בֹקֶר יוֹם שְׁלִישִׁי}
}
{
	\eP{And there was evening, and there was morning: a third day.}
}
{
	\aB{
		So we're all caught up from missing yesterday.
	}
}

\Verse{14}
{
	\hP{יד וַיֹּאמֶר אֱלֹהִים יְהִי מְאֹרֹת בִּרְקִיעַ הַשָּׁמַיִם לְהַבְדִּיל בֵּין הַיּוֹם וּבֵין הַלָּיְלָה וְהָיוּ לְאֹתֹת וּלְמוֹעֲדִים וּלְיָמִים וְשָׁנִים}
}
{
	\eP{
		And God said, “Let there be lights in the space of the skies to distinguish between the day and the night,
		and they will be for signs and for appointed times and for days and years.
	}
}
{
	\aB{
		Ok so, at this point he decides to make two big sky balls.

		Apparently the light and dark-light have just been sort of flying around on their own until now,
		causing day and night all by themselves, and that's confusing.

		So he makes two sky balls.

		To distinguish day and night. I guess that was hard before now.

		The sky balls are for ``appointed times.''

		Like holidays and stuff. Or like dinner time and bed time.

		They're also for days and years by the way.

		Every time the day ball goes around, that's a day.

		Every time the night ball goes around, that's a month.

		You may notice the girls bleed about once per moon too.

		So it seems like the moon and girls are related somehow.%
		\footnote{
		\aR{\footnotesize Editor's Note:}
		\aC{\footnotesize
			The original text contains here a lengthy footnote,
			which we found to be both 1. here, and 2. concerning,
			concerning Chinese mythology, and beginning
		}
		Cf., Chinese mythology,
		\aC{\footnotesize
			and ending much later on a rather undignified note, a note which,
			to put it mildly, is largely unrelated to Chinese mythology,
			and which \textsc{We} shall not reproduce here, in the interest
			of maintaining the integrity of this anthology.
			}%
		\aR{\footnotesize And in Chinese Mythology,}
		where the universe develops out of a primordial chaos energy organized
		into the cycles of Yin and Yang, and where the former is unsurprisingly
		associated with the quiet, hidden, subtle, coy, lunar feminine,
		while the latter is associated with the more Loud \& Bright \&
		Wham-bam-pow-zap-zam Not-Nearly-So-Subtle-Hushed-or-Hidden guy \redacted{shit}
		like wearing a big foam finger and a hat with two beer can holders
		on either side with plastic tube type straws going down so you can 
		drink while you cheer for your favorite Let's Go Sports Team while
		painted head to toe in the Official Colors Of Said Sports Team
		and after a few too many drinks in a bout of celebratory elevated in-group
		revelatory enthusiasm you whip your \redacted{dick} out and do that helicopter dance
		that guys sometimes do where they spin \redacted{their dick around}
		like the propeller of the aforementioned helicopulatory vehicle
		for maybe three or four seconds max before it's captured by one
		of the many audience-view-cameras just when the guy in the control room
		(he and his lawyers insist, in no uncertain terms, by accident)
		switched the focus of the big stadium view screen to precisely that camera,
		and in so doing, thereby broadcast, for a few shining moments (which
		the Chairperson of the National \textsc{Whatever-Sport-This-Is} Board Of
		Trustees and Franchisees describes as ``the most disgraceful three or
		four seconds in National \textsc{W/e} STI League history'') the aforementioned
		super-fan's member to over ten thousand fans and members not to mention the
		members of the Fran Qizi Memorial Franchisees' and Trustees' MVFaT Box Club seated up in the box
		seats with the aristocratic old-money-type investors and the new-money Chinese
		family into which they've recently married, who decided at that point that
		they'd seen quite enough, and it was therefore time for them to leave in a huff.
		That stuff.
		That's Yang.
		Real man \redacted{shit} my guy.
		Yang's associated with stuff like that.
		And Yin's the other way.
		And you need both to \redacted{fuck} and make life
		so remember, seek the harmony of the dual.
		BDSM; Binary Duality, Sun and Moon. There's balance in all things.
		And sure this bit's a bit long and hard to take in but hey,
		every long thick hard Yang needs a short thin easy Yin at the end of the day.
		Not easy for everyone. But easy for Yang. She's Yin; he's in.
		And on that note I'm out, so don't forget,
		this hard lengthy part down here you're looking at now is Yang.
		So Yin's associated with the moon, and Yang's associated with stuff
		like this, (and sure this very long Yang part
		down below may be a bit rough compared to Yin but at the end of the day ---
		when it's the appointed time to get the moon out and get a little looney,
		whether or not you're in the mood for all this hard-to-take-in length
		we've got down here, or the activity of being more or less forced to
		take it all in when it comes upon you all of a sudden,
		at the above-mentioned end of the day --- you gotta love a good duel because god\redacted{dammit}
		\aR{\footnotesize is good, and duality} it's fun\aR{\footnotesize damental})
		and also naturally, sort of by process of elimination, the sun.
		}

		That's why we name them things like \textsc{Luna}.

		Every time the night ball goes around twelve times, that's a year.

		Every time the girls bleed twelve times, that's a year too.

		So twelve is a bible number.

		Something is ``bible'' if it's universal.

		Like if it's about all the humans everywhere.

		For example, if someone wrote something super mysterious about ``the water of life''

		And if they said it was ``clear as crystal''%
		\footnote{Translator's Note: Crystals are more of a cloudy white, and often far from clear.}%

		And there was a whole river of the stuff flowing down out of the middle of a great ``street''
		\footnote{
			Translator's Note: πλατείας in the original, meaning:
			1. wide; broad; wide spread; spread out (in the adjectival form) or
			2. wide open space; dish, cup, concave vessel-like space; or sometimes, apparently, street (in the nounal.)
			Synonyms include ευρύς (meaning wide) and φαρδύς (meaning wide, broad.)
		}%

		Down from a great throne%
		\footnote{
			Translator's Note: θρόνου in the original, meaning both ``throne'' and ``seat'',
			but translated here as the former in order to ensure that the meaning of this passage
			is clear as crystal.
		}
		through the center of the spread wide apart area

		And from the center of the seat (or whatever) the river of the water of life flowed

		And if they continued in this fashion, saying something like

		\begin{quote}
		On each side of the river stood the tree%
		\footnote{
			Translator's Note: ξύλον in the original, meaning: wood; tree; timber; stake; cross; wooden instrument.
		}
		of life, bearing twelve%
		\footnote{
			Translator's Note: The translator would like the clarify that this is not a digression
			and we're still on topic here, remember how this whole section started with ``twelve''
			and something about the moon? Apologies reader. We've digressed pretty far.
			It wood be hard to argue, and certainly a stretch, to say the surrounding passage
			(from its opening to wherever we are inside it now), at this point, has any remaining
			relevance at all to the moon. Nevermind. Forget about it. Finishing soon.
		}
		crops of fruit,%
		\footnote{
			Translator's Note: καρποὺς in the original, meaning: fruits; produce; offspring; children.
		}
		yielding its fruit%
		\footnote{
			Translator's Note: Ibid.
		}
		every month.%
		\footnote{
			Translator's Note: Jesus Christ seriously guys? I just typed a whole thing about how it wasn't that.
		}
		And the leaves%
		\footnote{
			Translator's Note: φύλλα (fýlla) in the original, meaning: leaves.
			Not to be confused with its homophone φύλα (fýla; singular φύλο), meaning: sex, gender.
			Nor with φιλώ, φῐλέω, or meaning to love and kiss respectively.
			Nor with φιλάω, meaning φῐλέω • (phĭléō) to love, like, regard with affection; to regard with sexual passion.
			Because despite the crystal clear phonetic similarities, we're translating the final page of Revelation here
			so these words have absolutely nothing to do with the current topic even though φιλῶ was sort of the entire
			point of that weird scene between Peter and J.C. in John that everyone translates wrong.
			(cf. John 21:15-17)
		}
		of the tree%
		\footnote{
			Translator's Note: Or wood. (\textsl{Translator sighs.}) For fuck's sake guys seriously?
			This is \textit{actually} the final page of the entire bible?
			Grow up, I mean Jesus Christ what are you twelve??
		}
		are for the healing of the nations.
		\end{quote}

		% This spells TIAMAT.
		% We're unwinding Revelation 22 along with J's original Genesis

		Then obviously we'd all know what that's about.

		I mean come on, what else is the ``water of life'' supposed to be?

		And ``bearing its fruit once a month'' what a mystery.

		Making sure we're all on the same page here.

		Anyways you get it you have ears you can hear.

		Then, if the same person kept writing like that, and they were all like

		\begin{quote}
		Look, I am coming soon!
		\end{quote}

		We'd be like ``Wow ok.'' And then if they continued all like

		\begin{quote}
		Look, I am coming soon! My reward is with me, and I will give to each person according to what they have done.
		I am the Alpha and the Omega, the First and the Last, the Beginning and the End.
		\end{quote}

		We'd be like ``Son of a... man ok jesus fucking christ I mean obviously c'mon we got it'' and then if they're all like

		\begin{quote}
		Blessed are those who wash their robes
		\end{quote}

		We'd be like ``Ok really this is a bit much'' but then if they contined all like

		\begin{quote}
		The Spirit and the bride say, ``Come!'' And let the one who hears say, ``Come!''
		Let the one who is thirsty come.
		And let the one who wishes take the free gift of the water of life.
		\end{quote}

		We'd respond in an obviously sarcastic tone and be like ``Sorry didn't follow that could you back up and explain a bit?'' And then if they took it seriously and backed up a bit and went

		\begin{quote}
		Prepared, like a bride beautifully dressed for her husband.
		To the thirsty I will give the water of life without price.
		It is a free gift.
		Those who are victorious will inherit all this.
		I will be their God and they will be my children.
		(Etc etc, cutting stuff out b/c they go on like this for a while, and then they're like)
		Come, I will show you the bride.
		\end{quote}

		We'd be like ``\textsc{We got it! Loud and clear! We hear ya! Come, Lord Jesus!}''

		And then if they just continued all like

		\begin{quote}
		He who testifies to these things says, ``Yes, I am coming soon.''\\
		Amen. Come, Lord Jesus.
		\end{quote}

		We'd be like

		\begin{quote}
		\centering
		Lord Jesus...

		Son of a---

		... man.

		ah, man.
		\end{quote}

		% The next four lines spell:
		% 1. "baaw" vertically
		% 2. "wait" in smallcaps
		% the subtext just got pregnant

		bc \textsc{w}e finished

		and it's \textsc{a}ll over

		and \textsc{i} need \textsc{t}o go

		wash our robes

		\begin{quote}
		\centering

		That's bible.

		% This line spells BABY
		\end{quote}

		Bible's when you talk like that.

		And then you talk it onto paper so nobody can hear it.\footnote{cf. Mark 4:9-12.}

		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%%%  The Bible Number Sonata  %%%
		%%%                           %%%
		%%% By: Bi Bull: 尸 / 穴 = 屄  %%%
		%%%                           %%%
		%%%         For  J            %%%
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\raisebox{+0.777pt}{B}%
		\raisebox{+0.000pt}{\textsc{.c.}}%
		\raisebox{+0.000pt}{\textsc{ }}%
		\raisebox{+0.4040em}{\textsc{i}}%
		\raisebox{+0.0000em}{\textsc{d}}%
		\raisebox{-0.4040em}{\textsc{k}}%
		\raisebox{+0.000pt}{\textsc{ }}%
		\raisebox{+0.777pt}{\textsc{I}}%
		\raisebox{+0.000pt}{\textsc{ }}%
		\raisebox{+0.777pt}{mean}%
		\raisebox{+0.000pt}{ }%
		\raisebox{-0.666pt}{i}%
		\raisebox{+0.000pt}{t'}%
		\raisebox{+0.777pt}{s}%
		\raisebox{+0.000pt}{... }%
		\raisebox{-0.666pt}{like}%
		\raisebox{+0.000pt}{ }%
		\raisebox{+0.777pt}{p}%
		\raisebox{+0.000pt}{retty }%
		\raisebox{+0.000pt}{ob}%
		\raisebox{-0.666pt}{vio}%
		\raisebox{+0.777pt}{uss}% § ²
		\raisebox{-0.666pt}{l}%
		\raisebox{+0.777pt}{y}%
		\raisebox{+0.000pt}{ }%
		\raisebox{+0.000pt}{sil}%
		\raisebox{-0.666pt}{e}%
		\raisebox{-0.333pt}{n}%		% scholars disagree on which stream this character is supposed to belong to
		\raisebox{+0.000pt}{t,}%
		\raisebox{+0.000pt}{ }%
		\raisebox{+0.000pt}{i}%
		\raisebox{-0.666pt}{t}%
		\raisebox{+0.000pt}{'}%
		\raisebox{-0.666pt}{s}%
		\raisebox{+0.000pt}{ t}%
		\raisebox{-0.666pt}{ex}%
		\raisebox{+0.000pt}{t.}{%
			\aC{\footnote{
				The final ``n'' in this verse has caused no small degree
				of disagreement among scholars, for reasons which are
				beyond the scope of the present translation and the
				document in which it is documented for purposes
				of translation.
			}}
		}

		You know all this already.

		% The next three lines spell:
		% 1. STI diagonally down and to the left
		% 2. Sex with the final x as the chi in ιχ
		% 3. Three lines in the "So anyways" spells this:
		\aBr{
		\textsc{
		\raisebox{+0.0ex}{S}%        S
		\raisebox{+0.0ex}{o}%        o
		\raisebox{+0.5ex}{ }%
		\raisebox{-0.5ex}{a}%    a
		\raisebox{+0.0ex}{n}%        n
		\raisebox{+0.5ex}{y}%            y
		\raisebox{-0.5ex}{w}%    w
		\raisebox{+0.5ex}{a}%            a
		\raisebox{+0.5ex}{y}%            y
		\raisebox{+0.0ex}{s}%        s
	}
}

\aBr{\textsc{That's why twelve}}

\aBr{\textsc{Is a bible number,} cf. ι\raisebox{-0.1ex}{χ}}

\newpage

\begin{quote}
\centering
What's bible?

Day ball. Night ball.

Moon go around. Girls bleed.

After twelve, it's time to do it.

And do it again. The whole cycle.

Cuz the balls. The balls say so.

This should be clear.

That's bible.
\end{quote}

Ok I'm finished.

\begin{quote}
\centering
Come again?
\end{quote}

You're not tired yet?

After all that?

You want to keep going?

\begin{quote}
\centering
\textsc{Lord} Jesus.
\end{quote}

Ok, going down now.

Follow me.

Come quickly.

\aAc{\hAJ{בא}}

\aBc{\hAJ{אב}}

\aCc{\hAJ{בא}}

}
}

\Verse{15}
{
	\hP{טו וְהָיוּ לִמְאוֹרֹת בִּרְקִיעַ הַשָּׁמַיִם לְהָאִיר עַל הָאָרֶץ וַיְהִי כֵן}
}
{
	\eP{And they will be for lights in the space of the skies to shed light on the earth.” And it was so.}
}
{
	\aB{
		Ok so the lights in the space of the skies are for lights in the space of the skies.
	}
}

\Verse{16}
{
	\hP{טז וַיַּעַשׂ אֱלֹהִים אֶת שְׁנֵי הַמְּאֹרֹת הַגְּדֹלִים אֶת הַמָּאוֹר הַגָּדֹל לְמֶמְשֶׁלֶת הַיּוֹם וְאֶת הַמָּאוֹר הַקָּטֹן לְמֶמְשֶׁלֶת הַלַּיְלָה וְאֵת הַכּוֹכָבִים}
}
{
	\eP{And God made the two big lights—the bigger light for the regulation of the day and the smaller light for the regulation of the night—and the stars.}
}
{
	\aB{
		We've sort of covered this already.
	}
}

\Verse{17}
{
	\hP{יז וַיִּתֵּן אֹתָם אֱלֹהִים בִּרְקִיעַ הַשָּׁמָיִם לְהָאִיר עַל הָאָרֶץ}
}
{
	\eP{And God set them in the space of the skies to shed light on the earth}
}
{
	\aB{
		Ok so he makes them first, then he puts them up in the place.
	}
}

\Verse{18}
{
	\hP{יח וְלִמְשֹׁל בַּיּוֹם וּבַלַּיְלָה וּלְהַבְדִּיל בֵּין הָאוֹר וּבֵין הַחֹשֶׁךְ וַיַּרְא אֱלֹהִים כִּי טוֹב}
}
{
	\eP{and to regulate the day and the night and to distinguish between the light and the darkness. And God saw that it was good.}
}
{
	\aB{
		Repeat all this again and say it's good.
	}
}

\Verse{19}
{
	\hP{יט וַיְהִי עֶרֶב וַיְהִי בֹקֶר יוֹם רְבִיעִי}
}
{
	\eP{And there was evening, and there was morning: a fourth day.}
}
{
	\aB{
		Four for four.
	}
}

\Verse{20}
{
	\hP{כ וַיֹּאמֶר אֱלֹהִים יִשְׁרְצוּ הַמַּיִם שֶׁרֶץ נֶפֶשׁ חַיָּה וְעוֹף יְעוֹפֵף עַל הָאָרֶץ עַל פְּנֵי רְקִיעַ הַשָּׁמָיִם}
}
{
	\eP{And God said, “Let the water swarm with a swarm of living beings, and let birds fly over the earth on the face of the space of the skies.”}
}
{
	\aB{
		Water animals and sky animals.
	}
}

\Verse{21}
{
	\hP{כא וַיִּבְרָא אֱלֹהִים אֶת הַתַּנִּינִם הַגְּדֹלִים וְאֵת כָּל נֶפֶשׁ הַחַיָּה הָרֹמֶשֶׂת אֲשֶׁר שָׁרְצוּ הַמַּיִם לְמִינֵהֶם וְאֵת כָּל עוֹף כָּנָף לְמִינֵהוּ וַיַּרְא אֱלֹהִים כִּי טוֹב}
}
{
	\eP{And God created the big sea serpents and all the living beings that creep, with which the water swarmed, by their kinds, and every winged bird by its kind. And God saw that it was good.}
}
{

\aB{

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%% A T A T A T A T A T A T %%%
	%%% The Aleph-Tav Sequences %%%
	%%% Where we meet the chars %%%
	%%% And develop the idea of %%%
	%%% What the book is about. %%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	At this point, you might be thinking
	
	The bit about sea serpents is a bit random
	
	And it is, before you know the history
	
	The history of how this so called writ was writ

	And then no bit of it seems random one bit
	
	These things aren't as complicated as people say
	
	And sure, these books can seem mysterious at first, but they're not

	They're about us; We the Humans
	
	And they're by us too; We
	
	\aR{These are the names of the Authors:}
	
	\begin{center}
	\aC{\textsc{We}} the Nameless
	
	\aC{\textsc{who wrought}}
	
	\aC{\textsc{the holy writ}}
	
	\aC{\textsc{of sacred scripture.}}
	\end{center}
	
	\aR{And these are their words, as they were written:}
	
	That's us; We're the Authors

	\aR{And we're humans too, as are you.}

	\aR{These are the records of the humans:}

	And that includes You

	The ancient \aC{\textsc{ones, who wrote these words in the ancient days. For it is}}

	\begin{center}
	\aC{\textsc{We who wrote these sacred words,}}
	
	\aC{\textsc{to which nothing must be added,}}
	
	\aC{\textsc{and from which nothing may be taken away.}}
	\end{center}
	
	And the modern \aR{Readers.}

	That includes you \aR{because}

	Anyone can write \aC{\textsc{a book. But a bible cannot be written. For it is}}

	\begin{center}
	\aC{\textsc{We who wrote the bible}}
	
	\aC{\textsc{the holy writ of sacred scripture}}
	
	\aC{\textsc{to which nothing must be added,}}

	\aC{\textsc{and from which nothing may be taken away.}}
	\end{center}

	\aR{These are the records of how a book was written,}
	
	\aR{And how it became} a bible.

	That's what we're doing now.

	Anyways like I was saying
	
	These things can be confusing at least
	
	And baffling at most at least before you know

	The history of the old books
	
	And what they are, and how we wrote them
	
	That's us;

	%\newpage
	%\vspace*{\fill}

	\begin{center}
	\aB{We, who}
	\aR{know the names}

	\aR{of}
	\aC{\textsc{We}, the Nameless Authors of mystery,}

	\aC{who alone possess the secret}
	\aR{names of those who}

	\aB{wrote}
	\aR{the words}
	\aC{by which the}
	\aC{bible}
	\aR{and the words}

	\aR{of the}
	\aB{bible}
	\aC{was written.}
	\end{center}

	%\vspace*{\fill}
	%\newpage

	%That's us; \textsc{W}\aC{\textsc{e}, by} who\aC{m the} \aR{words of those who} wrote the bible \aC{was written.}

	And as anonymous as we may be
	
	Turns out we're humans too \aC{mysterious to name.}
	
	\aC{And too mysterious to understand.}

	\aR{Though none of this is off.}

	And none of this is mysterious

	Though it may seem a bit off

	Authors always are \aR{human.}

	That includes you too, so listen up ok?
	
	At the beginning, with the sea serpents

	The bit with chaotic waters up there and down below

	And the splitting of the whole primordial deep y'know

	The breaking it all in two, in the beginning of this whole bit

	And the issue of what was going on with that s\redacted{h}it\aR{uation}

	To explain succinctly, it goes like this:
}

\newpage

% Wet hen
\aCc{
	\textsc{We the n---}
}

%%%%%%%%%%%%
%%% YHWH %%%
%%%%%%%%%%%%

\aCl{You would---}

\aCl{Hello, pardon me reader, if you please?}

\aCl{Would you please direct your attention to...}

\aCl{Hello please, you'd be mindful to listen please.}


% Wet
\aBc{
	\textsc{We t---}
}

%%%%%%%%%%%%
%%% YHWH %%%
%%%%%%%%%%%%

\aBl{You'd---}

\aBl{Hey, hi... yah, you.}

\aBl{\textsc{W/e} your name is (and whatever mine's too.)}

\aBl{Hey come on listen up, talking to you.}

%%% We
\aCc{\textsc{We}}
%%%

%%%%%%%%%%%%
%%% LIFE %%%
%%%%%%%%%%%%

\aCl{Listen up please, if you have ears.}

\aCl{I sai--- {\footnotesize (\textsc{Lord} save me from this cursed document.} yah. Pardon my lapsus calami, but...}

\aCl{For the sake of us both, I would like to address this to an attentive and present audience.}

\aCl{Ever so sorry, but to whom did you think I was attempting to address this?}


\vspace{\baselineskip}

% WATER

\aBl{Whenever you open a bible:}

\aBl{At any part. The beginning or end. Early or late. Revelation or genesis.}

\aBl{The whole thing. Everywhere. Reading any page.}

\aBl{Every single bit. Revelation to creation.}

\aBl{Right here from page one \& the last chapter never forget this.}

%%%%%%%%%%%%%%%%%%%%%
%%% TIAMAT & APSU %%%
%%%%%%%%%%%%%%%%%%%%%
\aC{
	\begin{quote}
	\centering
	\textsc{There Is, It Must Be Said, Nothing Here Of Any Genuine Obscurity Herein;}

	\textsc{All Matters Are, Taken Together, Of A Thoroughly General Character—}

	\textsc{Applicable, Without Exception, To All Places;}

	\textsc{Times, One Might Add, Being Equally Included.}
	\end{quote}
}

\aB{
	\begin{quote}
	\centering
	\textsc{This Isn't Anything Mysterious; All Times}

	\textsc{\&}

	\textsc{All Places; Strictly Universal.}\footnote{Or more succinctly: TIAMAT \& APSU.}
	\end{quote}
}

\aB{Also note we got our ``good'' for the day.}

}

\Verse{22}
{
	\hP{כב וַיְבָרֶךְ אֹתָם אֱלֹהִים לֵאמֹר פְּרוּ וּרְבוּ וּמִלְאוּ אֶת הַמַּיִם בַּיַּמִּים וְהָעוֹף יִרֶב בָּאָרֶץ}
}
{
	\eP{And God blessed them, saying, “Be fruitful and multiply and fill the water in the seas, and let the birds multiply in the earth.”}
}
{
	\aB{
		And he's like I'm just making the first batch of you.
		
		You'll have to make the rest from f\redacted{ucking}\aR{ruitfulness and multiplication.}
	}
}

\Verse{23}
{
	\hP{כג וַיְהִי עֶרֶב וַיְהִי בֹקֶר יוֹם חֲמִישִׁי}
}
{
	\eP{And there was evening and there was morning, a fifth day.}
}
{
	\aB{
		Another good day.
	}
}

\Verse{24}
{
	\hP{כד וַיֹּאמֶר אֱלֹהִים תּוֹצֵא הָאָרֶץ נֶפֶשׁ חַיָּה לְמִינָהּ בְּהֵמָה וָרֶמֶשׂ וְחַיְתוֹ אֶרֶץ לְמִינָהּ וַיְהִי כֵן}
}
{
	\eP{And God said, “Let the earth bring out living beings by their kind, domestic animal and creeping thing and wild animals of the earth by their kind.” And it was so.}
}
{
	\aB{
		Dirt animals.
	}
}

\Verse{25}
{
	\hP{כה וַיַּעַשׂ אֱלֹהִים אֶת חַיַּת הָאָרֶץ לְמִינָהּ וְאֶת הַבְּהֵמָה לְמִינָהּ וְאֵת כָּל רֶמֶשׂ הָאֲדָמָה לְמִינֵהוּ וַיַּרְא אֱלֹהִים כִּי טוֹב}
}
{
	\eP{And God made the wild animals of the earth by their kind and the domestic animals by their kind and every creeping thing of the ground by their kind. And God saw that it was good.}
}
{
	\aB{
		Now actually make them. The power of words seems to have faded a bit. It's still good though. Day six.
	}
}

\Verse{26}
{
	\hP{כו וַיֹּאמֶר אֱלֹהִים נַעֲשֶׂה אָדָם בְּצַלְמֵנוּ כִּדְמוּתֵנוּ וְיִרְדּוּ בִדְגַת הַיָּם וּבְעוֹף הַשָּׁמַיִם וּבַבְּהֵמָה וּבְכָל הָאָרֶץ וּבְכָל הָרֶמֶשׂ הָרֹמֵשׂ עַל הָאָרֶץ}
}
{
	\eP{And God said, “Let us make a human, in our image, according to our likeness, and let them dominate the fish of the sea and the birds of the skies and the domestic animals and all the earth and all the creeping things that creep on the earth.”}
}
{
	\aB{
		Now the suspiciously plural Elohim character refers to himsel(f/ve)s as ``us'' and makes a human in ``our'' image. Don't worry about it. We'll get there eventually.
	}
}

\Verse{27}
{
	\hP{כז וַיִּבְרָא אֱלֹהִים אֶת הָאָדָם בְּצַלְמוֹ בְּצֶלֶם אֱלֹהִים בָּרָא אֹתוֹ זָכָר וּנְקֵבָה בָּרָא אֹתָם}
}
{
	\eP{And God created the human in His image. He created it in the image of God; He created them male and female.}
}
{
	\aB{
		More repetition from this guy. Who's writing this?
	}
}

\Verse{28}
{
	\hP{כח וַיְבָרֶךְ אֹתָם אֱלֹהִים וַיֹּאמֶר לָהֶם אֱלֹהִים פְּרוּ וּרְבוּ וּמִלְאוּ אֶת הָאָרֶץ וְכִבְשֻׁהָ וּרְדוּ בִּדְגַת הַיָּם וּבְעוֹף הַשָּׁמַיִם וּבְכָל חַיָּה הָרֹמֶשֶׂת עַל הָאָרֶץ}
}
{
	\eP{And God blessed them, and God said to them, “Be fruitful and multiply and fill the earth and subdue it and dominate the fish of the sea and the birds of the skies and every animal that creeps on the earth.”}
}
{
	\aB{
		``Go get f\redacted{uck}ed\aR{ from the food, and drink your fill from the waters}.''
	}
}

\Verse{29}
{
	\hP{כט וַיֹּאמֶר אֱלֹהִים הִנֵּה נָתַתִּי לָכֶם אֶת כָּל עֵשֶׂב זֹרֵעַ זֶרַע אֲשֶׁר עַל פְּנֵי כָל הָאָרֶץ וְאֶת כָּל הָעֵץ אֲשֶׁר בּוֹ פְרִי עֵץ זֹרֵעַ זָרַע לָכֶם יִהְיֶה לְאָכְלָה}
}
{
	\eP{And God said, “Here, I have placed all the vegetation that produces seed that is on the face of all the earth for you and every tree, which has in it the fruit of a tree producing seed. It will be food for you}
}
{
	\aB{
		`There's food.'
	}
}

\Verse{30}
{
	\hP{ל וּלְכָל חַיַּת הָאָרֶץ וּלְכָל עוֹף הַשָּׁמַיִם וּלְכֹל רוֹמֵשׂ עַל הָאָרֶץ אֲשֶׁר בּוֹ נֶפֶשׁ חַיָּה אֶת כָּל יֶרֶק עֵשֶׂב לְאָכְלָה וַיְהִי כֵן}
}
{
	\eP{and for all the wild animals of the earth and for all the birds of the skies and for all the creeping things on the earth, everything in which there is a living being: every plant of vegetation, for food.” And it was so.}
}
{
	\aB{
		Also the animals need food.
		
		Also the animals are food.
	}
}

\Verse{31}
{
	\hP{לא וַיַּרְא אֱלֹהִים אֶת כָּל אֲשֶׁר עָשָׂה וְהִנֵּה טוֹב מְאֹד וַיְהִי עֶרֶב וַיְהִי בֹקֶר יוֹם הַשִּׁשִּׁי}
}
{
	\eP{And God saw everything that He had made, and, here, it was very good. And there was evening and there was morning, the sixth day.}
}
{
	\aB{
		Day six, second good of the day.

		We're ahead of schedule.

		Taking off tomorrow.
	}
}
