\Chapter{4}

\Verse{1}
{
	\hOther{}
}
{
	\eOther{
		4

¹ And the human had known Eve, his T: woman, and she became pregnant and
gave birth to Cain and said, “I’ve created a man with YHWH.”\\
	}
}
{
}

\Verse{2}
{
	\hOther{}
}
{
	\eOther{
		And she went on to give birth to his brother, Abel. And Abel was a
shepherd of flocks, and Cain was a worker of ground.\\
	}
}
{
}

\Verse{3}
{
	\hOther{}
}
{
	\eOther{
		And it was at the end of some days, and Cain brought an offering to
YHWH from the fruit of the ground.\\
	}
}
{
}

\Verse{4}
{
	\hOther{}
}
{
	\eOther{
		And Abel brought, as well, from the firstborn of his flock and their
fat. And YHWH paid attention to Abel and his offering\\
	}
}
{
}

\Verse{5}
{
	\hOther{}
}
{
	\eOther{
		and did not pay attention to Cain and his offering. And Cain was very
upset, and his face was fallen.\\
	}
}
{
}

\Verse{6}
{
	\hOther{}
}
{
	\eOther{
		And YHWH said to Cain, “Why are you upset, and why has your face
fallen?”\\
	}
}
{
}

\Verse{7}
{
	\hOther{}
}
{
	\eOther{
		Is it not that if you do well you’ll be raised, and if you don’t do
well then sin crouches at the threshold? And its desire will be for you.
And you’ll dominate it.”\\
	}
}
{
}

\Verse{8}
{
	\hOther{}
}
{
	\eOther{
		And Cain said to his brother Abel. And it was while they were in the
field, and Cain rose against Abel his brother and killed him.\\
	}
}
{
}

\Verse{9}
{
	\hOther{}
}
{
	\eOther{
		And YHWH said to Cain, “Where is Abel your brother?”

And he said, “I don’t know. Am I my brother’s watchman?”\\
	}
}
{
}

\Verse{10}
{
	\hOther{}
}
{
	\eOther{
		And He said, “What have you done? The sound! Your brother’s blood is
crying to me from the ground!\\
	}
}
{
}

\Verse{11}
{
	\hOther{}
}
{
	\eOther{
		And now you’re cursed from the ground that opened its mouth to take
your brother’s blood from your hand.\\
	}
}
{
}

\Verse{12}
{
	\hOther{}
}
{
	\eOther{
		When you work the ground it won’t continue to give its potency to you.
You’ll be a roamer and rover in the earth.”\\
	}
}
{
}

\Verse{13}
{
	\hOther{}
}
{
	\eOther{
		And Cain said to YHWH, “My crime is greater than I can bear.\\
	}
}
{
}

\Verse{14}
{
	\hOther{}
}
{
	\eOther{
		Here, you’ve expelled me from the face of the ground today and I’ll be
hidden from your presence, and I’ll be a roamer and rover in the earth,
and anyone who finds me will kill me.”\\
	}
}
{
}

\Verse{15}
{
	\hOther{}
}
{
	\eOther{
		And YHWH said to him, “Therefore: anyone who kills Cain, he’ll be
avenged sevenfold.” And YHWH set a sign for Cain so that anyone who
finds him would not strike him.\\
	}
}
{
}

\Verse{16}
{
	\hOther{}
}
{
	\eOther{
		And Cain went out from YHWH’s presence and lived in the land of
roving, east of Eden.\\
	}
}
{
}

\Verse{17}
{
	\hOther{}
}
{
	\eOther{
		And Cain knew his wife, and she became pregnant and gave birth to
Enoch. And he was a builder of a city, and he called the name of the
city like the name of his son: Enoch.\\
	}
}
{
}

\Verse{18}
{
	\hOther{}
}
{
	\eOther{
		And Irad was born to Enoch, and Irad fathered Mehuya-el, and Mehuya-el
fathered Metusha-el, and Me-tusha-el fathered Lamech.\\
	}
}
{
}

\Verse{19}
{
	\hOther{}
}
{
	\eOther{
		And Lamech took two wives. The one’s name was Adah, and the second’s
name was Zillah.\\
	}
}
{
}

\Verse{20}
{
	\hOther{}
}
{
	\eOther{
		And Adah gave birth to Yabal. He was father of tent-dweller and
cattleman.\\
	}
}
{
}

\Verse{21}
{
	\hOther{}
}
{
	\eOther{
		And his brother’s name was Yubal. He was father of every player of
lyre and pipe.\\
	}
}
{
}

\Verse{22}
{
	\hOther{}
}
{
	\eOther{
		And Zillah, too, gave birth to Tubal-Cain, forger of every implement
of bronze and iron. And Tubal-Cain’s sister was Naamah.\\
	}
}
{
}

\Verse{23}
{
	\hOther{}
}
{
	\eOther{
		And Lamech said to his wives:

Adah and Zillah, listen to my voice,

Wives of Lamech, hear what I say.

For I’ve killed a man for a wound to me

And a boy for a hurt to me,\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		For Cain will be avenged sevenfold

And Lamech seventy-seven.\\
	}
}
{
}

\Verse{25}
{
	\hR{}
}
{
	\eR{
		And Adam knew his wife again, and she gave birth to a son, and she
called his name Seth “because God put another seed for me in place of
Abel because Cain killed him.”\\
	}
}
{
}

\Verse{26}
{
	\hR{}
}
{
	\eR{
		And a son was born to Seth, him as well, and he called his name Enosh.
Then it was begun to invoke the name YHWH.\\
	}
}
{
}

