\Chapter{6}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		6

¹ And it was when humankind began to multiply on the face of the ground
and daughters were born to them:\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		and the sons of God saw the daughters of humankind, that they were
attractive, and they took women, from all they chose.\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said, “My spirit won’t stay in humankind forever, since
they’re also flesh; and their days shall be a hundred twenty years.”\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		The Nephilim were in the earth in those days and after that as well,
when the sons of God came to the daughters of humankind, and they gave
birth by them. They were the heroes who were of old, people of renown.\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		And YHWH saw that human bad was multiplied in the earth, and every
inclination of their heart’s thoughts was only bad all the day.\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And YHWH regretted that He had made humankind in the earth.

And He was grieved to His heart.\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said, “I’ll wipe out the human whom I’ve created from the face
of the earth, from human to animal to creeping thing, and to the bird of
the skies, because I regret that I made them.”\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		But Noah had found favor in YHWH’s eyes.\\
	}
}
{
}

\Verse{9}
{
	\hR{}
}
{
	\eR{
		NOAH

⁹ These are the records of Noah: Noah was a virtuous man. He was
unblemished in his generations. Noah walked with God.\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And Noah fathered three sons: Shem, Ham, and Yaphet.\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And the earth was corrupted before God, and the earth was filled with
violence.\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And God saw the earth; and, here, it was corrupted, because all flesh
had corrupted its way on the earth.\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And God said to Noah, “The end of all flesh has come before me,
because the earth is filled with violence because of them. And here: I’m
destroying them with the earth.\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		Make yourself an ark of gopher wood, make rooms with the ark, and
pitch it outside and inside with pitch.\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And this is how you shall make it: three hundred cubits the length of
the ark, fifty cubits its width, and thirty cubits its height.\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		You shall make a window for the ark, and you shall finish it to a
cubit from the top, and you shall make the ark’s entrance in its side.
You shall make lower, second, and third stories for it.\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And I, here: I’m bringing the flood, water on the earth, to destroy
all flesh in which is the breath of life from under the skies.
Everything that is in the earth will expire.\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And I shall establish my covenant with you. And you’ll come to the
ark, you and your sons and your wife and your sons’ wives with you.\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And of all the living, of all flesh, you shall bring two of each to
the ark to keep alive with you. They shall be male and female.\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		Of the birds by their kind and of the domestic animals by their kind,
of all the creeping things of the ground by their kind, two of each will
come to you to keep alive.\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And you, take some of every food that will be eaten and gather it to
you, and it will be for you and for them for food.”\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And Noah did it. According to everything that God commanded him, he
did so.\\
	}
}
{
}

