\Chapter{18}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		And YHWH appeared to him at the oaks of Mamre. And he was sitting at
the tent entrance in the heat of the day,\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		and he raised his eyes and saw, and here were three people standing
over him. And he saw and ran toward them from the tent entrance and
bowed to the ground.\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		And he said, “My Lord, if I’ve found favor in your eyes don’t pass on
from your servant.\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		Let a little water be gotten, and wash your feet and relax under a
tree,\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		and let me get a bit of bread, and satisfy your heart. Afterward you’ll
pass on, for that’s why you’ve passed by your servant.”

And they said, “Do that, as you’ve spoken.”\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And Abraham hurried to the tent, to Sarah, and said, “Hurry, three
measures of fine flour. Knead it and make cakes.”\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		And Abraham ran to the herd and took a calf, tender and good, and he
gave it to a servant, and he hurried to prepare it.\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		And he took curds and milk and the calf that he had prepared and placed
them in front of them, and he was standing over them under the tree, and
they ate.\\
	}
}
{
}

\Verse{9}
{
	\hJ{}
}
{
	\eJ{
		And they said to him, “Where is Sarah, your wife?”

And he said, “Here in the tent.”\\
	}
}
{
}

\Verse{10}
{
	\hJ{}
}
{
	\eJ{
		And He said, “I shall come back to you at the time of life, and, here,
Sarah, your wife, will have a son.”

And Sarah was listening at the tent entrance, which was behind him.\\
	}
}
{
}

\Verse{11}
{
	\hJ{}
}
{
	\eJ{
		And Abraham and Sarah were old, well along in days; Sarah had stopped
having the way of women.\\
	}
}
{
}

\Verse{12}
{
	\hJ{}
}
{
	\eJ{
		And Sarah laughed inside her and said, “After I’ve become worn out am
I to have pleasure?! And my lord is old!”\\
	}
}
{
}

\Verse{13}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said to Abraham, “Why is this? Sarah laughed, saying, ‘Shall
I indeed give birth? And I am old!’ Is anything too wondrous for YHWH?\\
	}
}
{
}

\Verse{14}
{
	\hJ{}
}
{
	\eJ{
		At the appointed time I’ll come back to you, at the time of life, and
Sarah will have a son.”\\
	}
}
{
}

\Verse{15}
{
	\hJ{}
}
{
	\eJ{
		And Sarah lied, saying, “I didn’t laugh,” because she was afraid.

And He said, “No, but you did laugh.”\\
	}
}
{
}

\Verse{16}
{
	\hJ{}
}
{
	\eJ{
		And the people got up from there and gazed at the sight of Sodom, and
Abraham was going with them to send them off.\\
	}
}
{
}

\Verse{17}
{
	\hJ{}
}
{
	\eJ{
		And YHWH had said, “Shall I conceal what I’m doing from Abraham,\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		since Abraham will become a big and powerful nation, and all the
nations of the earth will be blessed through him?\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		For I’ve known him for the purpose that he’ll command his children and
his house after him, and they’ll observe YHWH’s way, to do virtue and
judgment, and for the purpose of YHWH’s bringing upon Abraham what He
spoke about him.”\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said, “The cry of Sodom and Gomorrah: how great it is. And
their sin: how very heavy it is.\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		Let me go down, and I’ll see if they’ve done, all told, like the cry
that has come to me. And if not, let me know.”\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		And the people turned from there and went to Sodom.

And Abraham was still standing before YHWH,\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		and Abraham came over and said, “Will you also annihilate the virtuous
with the wicked?\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		Maybe there are fifty virtuous people within the city. Will you also
annihilate and not sustain the place for the fifty virtuous who are in
it?\\
	}
}
{
}

\Verse{25}
{
	\hJ{}
}
{
	\eJ{
		Far be it from you to do a thing like this, to kill virtuous with
wicked—and it will be the same for the virtuous and the wicked—far be it
from you. Will the judge of all the earth not do justice?”\\
	}
}
{
}

\Verse{26}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said, “If I find in Sodom fifty virtuous people within the
city, then I’ll sustain the whole place for their sake.”\\
	}
}
{
}

\Verse{27}
{
	\hJ{}
}
{
	\eJ{
		And Abraham answered, and he said, “Here I’ve undertaken to speak to
my Lord, and I’m dust and ashes.\\
	}
}
{
}

\Verse{28}
{
	\hJ{}
}
{
	\eJ{
		Maybe the fifty virtuous people will be short by five. Will you
destroy the whole city for the five?”

And He said, “I won’t destroy if I find forty-five there.”\\
	}
}
{
}

\Verse{29}
{
	\hJ{}
}
{
	\eJ{
		And he went on again to speak to Him and said, “Maybe forty will be
found there.”

And He said, “I won’t do it for the sake of the forty.”\\
	}
}
{
}

\Verse{30}
{
	\hJ{}
}
{
	\eJ{
		And he said, “May my Lord not be angry, and let me speak. Maybe thirty
will be found there.”

And He said, “I won’t do it if I find thirty there.”\\
	}
}
{
}

\Verse{31}
{
	\hJ{}
}
{
	\eJ{
		And he said, “Here I’ve undertaken to speak to my Lord. Maybe twenty
will be found there.”

And He said, “I won’t destroy for the sake of the twenty.”\\
	}
}
{
}

\Verse{32}
{
	\hJ{}
}
{
	\eJ{
		And he said, “May my Lord not be angry, and let me speak just this one
time. Maybe ten will be found there.”

And He said there, “I won’t destroy for the sake of the ten.”\\
	}
}
{
}

\Verse{33}
{
	\hJ{}
}
{
	\eJ{
		And YHWH went when He had finished speaking to Abraham, and Abraham
went back to his place.\\
	}
}
{
}

