\Chapter{23}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		SARAH’S LIFE

23

¹ And Sarah’s life was a hundred years and twenty years and seven years:
the years of Sarah’s life.\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		And Sarah died in Kiriath Arba—it is Hebron—in the land of Canaan. And
Abraham came to grieve for Sarah and to weep for her.\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And Abraham got up from in front of his dead, and he spoke to the
children of Heth, saying,\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		“I’m an alien and a visitor with you. Give me a possession for a tomb
with you so I may bury my dead from in front of me.”\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And the children of Heth answered Abraham, saying to him,\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		“Listen to us, my lord. You’re a chieftain of God among us. Bury your
dead in the choice of our tombs. Not a man of us will hold back his tomb
from you, from burying your dead.”\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And Abraham got up and bowed to the people of the land, to the children
of Heth,\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		and he spoke with them, saying, “If it’s acceptable to you to bury my
dead from in front of me, listen to me, and intercede for me with
Ephron, son of Zohar,\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		that he’ll give me the cave of Machpelah which he has, that is at the
edge of his field. For full price let him give it to me among you as a
possession for a tomb.”\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And Ephron was sitting among the children of Heth, and Ephron, the
Hittite, answered Abraham in the ears of the children of Heth, for all
who were coming to his city’s gate, saying,\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		“No, sir. Listen to me: I’ve given the field to you, and I’ve given
the cave that’s in it to you. I’ve given it to you before the eyes of
the children of my people. Bury your dead.”\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And Abraham bowed in front of the people of the land,\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		and he spoke to Ephron in the ears of the people of the land, saying,
“Just if you’ll listen to me: I’ve given the money for the field. Take
it from me so I may bury my dead there.”\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And Ephron answered Abraham, saying to him,\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		“Sir, listen to me. Land worth four hundred shekels of silver: what’s
that between me and you?! And bury your dead.”\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And Abraham listened to Ephron, and Abraham weighed out to Ephron the
money that he had spoken in the ears of the children of Heth: four
hundred shekels of silver, at the merchant’s current rate.\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And Ephron’s field that was in Machpelah, which faces Mamre, the field
and the cave that was in it and every tree that was in the field, that
was in all of its border all around, was established\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		for Abraham as a purchase in the eyes of the children of Heth, among
all who were coming to his city’s gate.\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And after that Abraham buried Sarah, his wife, at the cave of the
field of Machpelah, facing Mamre—it is Hebron—in the land of Canaan.\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And the field and the cave that was in it were established for Abraham
as a possession for a tomb from the children of Heth.\\
	}
}
{
}

