\Chapter{27}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		27

¹ And it was when Isaac was old and his eyes were too dim for seeing: and
he called Esau, his older son, and said to him, “My son.”

And he said to him, “I’m here.”\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		And he said, “Here, I’ve become old. I don’t know the day of my death.\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		And now, take up your implements: your quiver and your bow, and go out
to the field and hunt me some game\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		and make me the kind of delicacies that I love and bring them to me and
let me eat, so my soul will bless you before I die.”\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		And Rebekah was listening as Isaac was speaking to Esau, his son. And
Esau went to the field to hunt game to bring.\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And Rebekah said to Jacob, her son, saying, “Here I’ve heard your
father speaking to Esau, your brother, saying,\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		‘Bring me game and make me delicacies so I may eat, and I’ll bless you
in the presence of YHWH before my death.’\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		And now, my son, listen to my voice, to what I’m commanding you.\\
	}
}
{
}

\Verse{9}
{
	\hJ{}
}
{
	\eJ{
		Go to the flock and take two good goat kids for me from there, and I’ll
make them the kind of delicacies that your father loves.\\
	}
}
{
}

\Verse{10}
{
	\hJ{}
}
{
	\eJ{
		And bring them to your father, and he’ll eat, so he’ll bless you
before his death.”\\
	}
}
{
}

\Verse{11}
{
	\hJ{}
}
{
	\eJ{
		And Jacob said to Rebekah, his mother, “Here, Esau, my brother, is a
hairy man and I’m a smooth man.\\
	}
}
{
}

\Verse{12}
{
	\hJ{}
}
{
	\eJ{
		Maybe my father will feel me, and I’ll be like a trickster in his
eyes, and I’ll bring a curse on me and not a blessing.”\\
	}
}
{
}

\Verse{13}
{
	\hJ{}
}
{
	\eJ{
		And his mother said to him, “Let your curse be on me, my son; just
listen to my voice and go take them for me.”\\
	}
}
{
}

\Verse{14}
{
	\hJ{}
}
{
	\eJ{
		And he went and took and brought them to his mother, and his mother
made the kind of delicacies that his father loved.\\
	}
}
{
}

\Verse{15}
{
	\hJ{}
}
{
	\eJ{
		And Rebekah took the finest clothes of Esau, her older son, that were
with her in the house and put them on Jacob, her younger son,\\
	}
}
{
}

\Verse{16}
{
	\hJ{}
}
{
	\eJ{
		and put the skins of the goat kids on his hands and on the smooth part
of his neck.\\
	}
}
{
}

\Verse{17}
{
	\hJ{}
}
{
	\eJ{
		And she put the delicacies and the bread that she’d made in the hand
of Jacob, her son.\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		And he came to his father.

And he said, “My father.”

And he said, “I’m here. Who are you, my son?”\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		And Jacob said to his father, “I’m Esau, your firstborn. I did as you
spoke to me. Get up, sit, and eat some of my game so your soul will
bless me.”\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		And Isaac said to his son, “What’s this? You were quick to find it, my
son.”

And he said, “Because YHWH your God made it happen for me.”\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		And Isaac said to Jacob, “Come over, and I’ll feel you, my son: is
this you, my son Esau, or not?”\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		And Jacob came over to Isaac, his father, and he felt him. And he
said, “The voice is the voice of Jacob, and the hands are the hands of
Esau.”\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		And he did not recognize him because his hands were hairy like the
hands of Esau, his brother, and he blessed him.\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		And he said, “Is this you, my son Esau?”

And he said, “I am.”\\
	}
}
{
}

\Verse{25}
{
	\hJ{}
}
{
	\eJ{
		And he said, “Bring it over to me and let me eat some of my son’s game
so that my soul will bless you. And he brought it over to him, and he
ate; and he brought him wine, and he drank.\\
	}
}
{
}

\Verse{26}
{
	\hJ{}
}
{
	\eJ{
		And Isaac, his father, said to him, “Come over and kiss me, my son.”\\
	}
}
{
}

\Verse{27}
{
	\hJ{}
}
{
	\eJ{
		And he came over and kissed him, and he smelled the aroma of his
clothes and blessed him and said, “See, my son’s aroma is like the aroma
of a field that YHWH has blessed.\\
	}
}
{
}

\Verse{28}
{
	\hJ{}
}
{
	\eJ{
		And may God give you from the dew of the skies and from the fat of the
earth and much grain and wine.\\
	}
}
{
}

\Verse{29}
{
	\hJ{}
}
{
	\eJ{
		May peoples serve you and nations bow to you. Be your brothers’
superior, and may your mother’s sons bow to you. May those who curse you
be cursed and those who bless you be blessed.”\\
	}
}
{
}

\Verse{30}
{
	\hJ{}
}
{
	\eJ{
		And it was as Isaac finished blessing Jacob, and it was: Jacob had
just gone out from the presence of Isaac, his father!—and Esau, his
brother, came from his hunting.\\
	}
}
{
}

\Verse{31}
{
	\hJ{}
}
{
	\eJ{
		And he, too, had made delicacies and brought them to his father. And
he said to his father, “Let my father get up and eat some of his son’s
game so you yourself will bless me.”\\
	}
}
{
}

\Verse{32}
{
	\hJ{}
}
{
	\eJ{
		And Isaac, his father, said to him, “Who are you?”

And he said, “I’m your son, your firstborn, Esau.”\\
	}
}
{
}

\Verse{33}
{
	\hJ{}
}
{
	\eJ{
		And Isaac trembled—a very big trembling. And he said, “Who then is the
one who hunted game and brought it to me, and I ate some of it all
before you came, and I blessed him? He will in fact be blessed.”\\
	}
}
{
}

\Verse{34}
{
	\hJ{}
}
{
	\eJ{
		When Esau heard his father’s words he cried—a very big and bitter cry.
And he said to his father, “Bless me, also me, my father.”\\
	}
}
{
}

\Verse{35}
{
	\hJ{}
}
{
	\eJ{
		And he said, “Your brother came with deception, and he took your
blessing.”\\
	}
}
{
}

\Verse{36}
{
	\hJ{}
}
{
	\eJ{
		And he said, “Was his name really called Jacob! And he’s usurped me
two times now. He’s taken my birthright, and, here, now he’s taken my
blessing.” And he said, “Haven’t you saved a blessing for me?”\\
	}
}
{
}

\Verse{37}
{
	\hJ{}
}
{
	\eJ{
		And Isaac answered, and he said to Esau, “Here I’ve made him your
superior, and I’ve given all his brothers as servants, and I’ve endowed
him with grain and wine. And for you: where, what, will I do, my son?”\\
	}
}
{
}

\Verse{38}
{
	\hJ{}
}
{
	\eJ{
		And Esau said to his father, “Is it one blessing that you have, my
father? Bless me, also me, my father.” And Esau raised his voice and
wept.\\
	}
}
{
}

\Verse{39}
{
	\hJ{}
}
{
	\eJ{
		And Isaac, his father, answered, and he said to him, “Here, away from
the fat of the earth will be your home, and from the dew of the skies
from above.\\
	}
}
{
}

\Verse{40}
{
	\hJ{}
}
{
	\eJ{
		And you’ll live by your sword. And you’ll serve your brother. And it
will be that when you get dominion you’ll break his yoke from your
neck.”\\
	}
}
{
}

\Verse{41}
{
	\hJ{}
}
{
	\eJ{
		And Esau despised Jacob because of the blessing with which his father
blessed him, and Esau said in his heart, “The days of mourning for my
father will be soon, and then I’ll kill Jacob, my brother.”\\
	}
}
{
}

\Verse{42}
{
	\hJ{}
}
{
	\eJ{
		And the words of Esau, her older son, were told to Rebekah, and she
sent and called to Jacob, her younger son, and said to him, “Here, Esau,
your brother, consoles himself regarding you with the idea of killing
you.\\
	}
}
{
}

\Verse{43}
{
	\hJ{}
}
{
	\eJ{
		And now, my son, listen to my voice and get up, flee to Laban, my
brother, at Haran\\
	}
}
{
}

\Verse{44}
{
	\hJ{}
}
{
	\eJ{
		and live with him for a number of days until your brother’s fury will
turn back,\\
	}
}
{
}

\Verse{45}
{
	\hJ{}
}
{
	\eJ{
		until your brother’s anger turns back from you and he forgets what you
did to him. And I’ll send and take you from there. Why should I be
bereaved of the two of you as well in one day?”\\
	}
}
{
}

\Verse{46}
{
	\hP{}
}
{
	\eP{
		And Rebekah said to Isaac, “I’m disgusted with my life because of the
daughters of Heth! If Jacob takes a wife from the daughters of Heth like
these daughters of the land, why do I have a life!”\\
	}
}
{
}

