\Chapter{29}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		29

¹ And Jacob lifted his feet and went to the land of the people of the
east.\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		And he looked, and here was a well in the field, and here were three
flocks of sheep lying by it, because they watered the flocks from that
well, and the stone on the mouth of the well was big,\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		and all the flocks would be gathered there, and they would roll the
stone from the mouth of the well and would water the sheep and then
would put the stone back in its place on the mouth of the well.\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		4And Jacob said to them, “My brothers, where are you from?”

And they said, “We’re from Haran.”\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		And he said to them, “Do you know Laban, son of Nahor?”

And they said, “We know.”\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And he said to them, “Is he well?”

And they said, “Well. And here’s Rachel, his daughter, coming with the
sheep.”\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		And he said, “Here, it will still be daytime for a long time, not the
time for gathering the livestock. Water the sheep and go, pasture them.”\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		And they said, “We can’t until all the flocks will be gathered and
they’ll roll the stone from the mouth of the well, and then we’ll water
the sheep.”\\
	}
}
{
}

\Verse{9}
{
	\hJ{}
}
{
	\eJ{
		He was still speaking with them, and Rachel came with her father’s
sheep, because she was a shepherdess.\\
	}
}
{
}

\Verse{10}
{
	\hJ{}
}
{
	\eJ{
		And it was when Jacob saw Rachel, daughter of Laban, his mother’s
brother, and the sheep of Laban, his mother’s brother: and he went over
and rolled the stone from the mouth of the well and watered the sheep of
Laban, his mother’s brother.\\
	}
}
{
}

\Verse{11}
{
	\hJ{}
}
{
	\eJ{
		And Jacob kissed Rachel and raised his voice and wept.\\
	}
}
{
}

\Verse{12}
{
	\hJ{}
}
{
	\eJ{
		And Jacob told Rachel that he was her father’s kin and that he was
Rebekah’s son, and she ran and told her father.\\
	}
}
{
}

\Verse{13}
{
	\hJ{}
}
{
	\eJ{
		And it was, when Laban heard the news of Jacob, his sister’s son, that
he ran to him and embraced him and kissed him and brought him to his
house. And he told Laban all these things.\\
	}
}
{
}

\Verse{14}
{
	\hJ{}
}
{
	\eJ{
		And Laban said to him, “You are indeed my bone and my flesh.” And he
stayed with him a month.\\
	}
}
{
}

\Verse{15}
{
	\hJ{}
}
{
	\eJ{
		And Laban said to Jacob, “Is it right because you’re my brother that
you should work for me for free? Tell me what your pay should be.”\\
	}
}
{
}

\Verse{16}
{
	\hJ{}
}
{
	\eJ{
		And Laban had two daughters. The older one’s name was Leah, and the
younger one’s name was Rachel.\\
	}
}
{
}

\Verse{17}
{
	\hJ{}
}
{
	\eJ{
		And Leah’s eyes were tender, and Rachel had an attractive figure and
was beautiful.\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		And Jacob loved Rachel.

And he said, “I’ll work for you seven years for Rachel, your younger
daughter.”\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		And Laban said, “Better for me to give her to you than for me to give
her to another man. Live with me.”\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		And Jacob worked seven years for Rachel, and they were like a few days
in his eyes because of his loving her.\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		And Jacob said to Laban, “Give me my wife, because my days have been
completed, and let me come to her.”\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		And Laban gathered all the people of the place and made a feast.\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		And it was in the evening, and he took Leah, his daughter, and brought
her to him. And he came to her.\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		And Laban gave her his maid Zilpah—to Leah, his daughter, as a maid.\\
	}
}
{
}

\Verse{25}
{
	\hJ{}
}
{
	\eJ{
		And it was in the morning, and here she was: Leah! And he said to
Laban, “What is this you’ve done to me? Didn’t I work with you for
Rachel? And why have you deceived me?”\\
	}
}
{
}

\Verse{26}
{
	\hJ{}
}
{
	\eJ{
		And Laban said, “It’s not done like that in our place, to give the
younger one before the firstborn.\\
	}
}
{
}

\Verse{27}
{
	\hJ{}
}
{
	\eJ{
		Complete this week, and this one will be given to you as well—for the
work that you’ll do with me: another seven years.”\\
	}
}
{
}

\Verse{28}
{
	\hJ{}
}
{
	\eJ{
		And Jacob did so; and he completed this week, and he gave him Rachel,
his daughter, for a wife.\\
	}
}
{
}

\Verse{29}
{
	\hJ{}
}
{
	\eJ{
		And Laban gave his maid Bilhah to Rachel, his daughter—to her as a
maid.\\
	}
}
{
}

\Verse{30}
{
	\hJ{}
}
{
	\eJ{
		And he also came to Rachel. And he also loved Rachel more than Leah.
And he worked with him another seven years.\\
	}
}
{
}

\Verse{31}
{
	\hJ{}
}
{
	\eJ{
		And YHWH saw that Leah was hated, and He opened her womb, and Rachel
was infertile.\\
	}
}
{
}

\Verse{32}
{
	\hJ{}
}
{
	\eJ{
		And Leah became pregnant and gave birth to a son and called his name
Reuben because she said, “Because YHWH looked at my suffering, so that
now my man will love me.”\\
	}
}
{
}

\Verse{33}
{
	\hJ{}
}
{
	\eJ{
		And she became pregnant again and gave birth to a son and said,
“Because YHWH listened because I was hated and gave me this one, too.”
And she called his name Simeon.\\
	}
}
{
}

\Verse{34}
{
	\hJ{}
}
{
	\eJ{
		And she became pregnant again and gave birth to a son, and she said,
“Now, this time my man will become bound to me because I’ve given birth
to three sons for him.” On account of this his name was called Levi.\\
	}
}
{
}

\Verse{35}
{
	\hJ{}
}
{
	\eJ{
		And she became pregnant again and gave birth to a son and said, “This
time I’ll praise YHWH.” On account of this she called his name Judah.
And she stopped giving birth.\\
	}
}
{
}

