\Chapter{31}

\Verse{1}
{
	\hE{}
}
{
	\eE{
		31

¹ And he heard Laban’s sons’ words, saying, “Jacob has taken everything
that was our father’s, and he has made all this wealth from what was our
father’s.”\\
	}
}
{
}

\Verse{2}
{
	\hE{}
}
{
	\eE{
		And Jacob saw Laban’s face; and, here, he was not like the day before
yesterday with him.\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said to Jacob, “Go back to your fathers’ land and to your
birthplace, and I’ll be with you.”\\
	}
}
{
}

\Verse{4}
{
	\hE{}
}
{
	\eE{
		And Jacob sent and called Rachel and Leah to the field, to his flock,\\
	}
}
{
}

\Verse{5}
{
	\hE{}
}
{
	\eE{
		and said to them, “I see your father’s face, that he’s not like the day
before yesterday to me. And my father’s God has been with me,\\
	}
}
{
}

\Verse{6}
{
	\hE{}
}
{
	\eE{
		and you know that I served your father with all my might,\\
	}
}
{
}

\Verse{7}
{
	\hE{}
}
{
	\eE{
		and your father has toyed with me and changed my pay ten times, and God
hasn’t let him do bad with me.\\
	}
}
{
}

\Verse{8}
{
	\hE{}
}
{
	\eE{
		If he would say this: ‘The speckled will be your pay’, then all the
flock gave birth to speckled. And if he would say this: ‘The streaked
will be your pay’, then all the flock gave birth to streaked.\\
	}
}
{
}

\Verse{9}
{
	\hE{}
}
{
	\eE{
		And God has delivered your father’s livestock and given them to me.\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		And it was at the time of the flock’s being in heat, and I raised my
eyes and saw in a dream: and here were the he-goats that were going up
on the flock: streaked, speckled, and spotted.\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		“And an angel of God said to me in the dream, ‘Jacob.’

“And I said, ‘I’m here.’\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		“And he said, ‘Raise your eyes and see all the he-goats that are going
up on the flock: streaked, speckled, and spotted. Because I’ve seen
everything that Laban is doing to you.\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		I am the God at Beth-El, where you anointed a pillar, where you made a
vow to me. Now get up, go from this land, and go back to the land of
your birth.’”\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		And Rachel and Leah answered, and they said to him, “Do we still have
a portion and legacy in our father’s house?\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		Aren’t we thought of as foreigners by him, because he sold us and has
eaten up our money as well?!\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		Because all the wealth that God has delivered from our father: it’s
ours and our children’s. And now, do everything that that God has said
to you.”\\
	}
}
{
}

\Verse{17}
{
	\hOther{}
}
{
	\eOther{
		And Jacob got up and carried his children and his wives on the camels.\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And he drove all his cattle and all his property that he had acquired,
the cattle that were in his possession that he had acquired in Paddan
Aram, to come to Isaac, his father, at the land of Canaan.\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		And Laban had gone to shear his flock. And Rachel stole the teraphim
that her father had.\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		And Jacob stole the heart of Laban, the Aramean, by not telling him
that he was fleeing.\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		And he fled, he and everyone he had, and he got up and crossed the
river and set his face toward the mountain of Gilead.\\
	}
}
{
}

\Verse{22}
{
	\hE{}
}
{
	\eE{
		And it was told to Laban on the third day that Jacob had fled.\\
	}
}
{
}

\Verse{23}
{
	\hE{}
}
{
	\eE{
		And he took his brothers with him and pursued him seven days’ journey
and caught up to him in the mountain of Gilead.\\
	}
}
{
}

\Verse{24}
{
	\hE{}
}
{
	\eE{
		And God came to Laban, the Aramean, in a night dream and said to him,
“Watch yourself in case you speak with Jacob: from good to bad.”\\
	}
}
{
}

\Verse{25}
{
	\hE{}
}
{
	\eE{
		And Laban caught up to Jacob, and Jacob had set up his tent in the
mountain, and Laban set up with his brothers in the mountain of Gilead.\\
	}
}
{
}

\Verse{26}
{
	\hE{}
}
{
	\eE{
		And Laban said to Jacob, “What have you done, that you’ve stolen my
heart and driven off my daughters like prisoners by the sword?\\
	}
}
{
}

\Verse{27}
{
	\hE{}
}
{
	\eE{
		Why did you hide so as to flee, and you stole from me, and you didn’t
tell me? And I would have sent you off with happiness and with songs and
with a drum and with a lyre.\\
	}
}
{
}

\Verse{28}
{
	\hE{}
}
{
	\eE{
		And you didn’t permit me to kiss my sons and my daughters. Now you’ve
been foolish to do this.\\
	}
}
{
}

\Verse{29}
{
	\hE{}
}
{
	\eE{
		The god at my hand has the means to do bad to you. But your father’s
God said to me yesterday saying, ‘Watch yourself from speaking with
Jacob: from good to bad.’\\
	}
}
{
}

\Verse{30}
{
	\hE{}
}
{
	\eE{
		And now, you went, because you longed for your father’s house. Why did
you steal my gods?”\\
	}
}
{
}

\Verse{31}
{
	\hE{}
}
{
	\eE{
		And Jacob answered, and he said to Laban, “Because I was afraid.
Because I said, ‘In case you’ll seize your daughters from me.’\\
	}
}
{
}

\Verse{32}
{
	\hE{}
}
{
	\eE{
		Let the one with whom you’ll find your gods not live. In front of our
brothers, recognize and take what of yours is with me.” And Jacob did
not know that Rachel had stolen them.\\
	}
}
{
}

\Verse{33}
{
	\hE{}
}
{
	\eE{
		And Laban came in Jacob’s tent and Leah’s tent and the two maids’
tent, and he did not find them. And he came out from Leah’s tent and
came in Rachel’s tent.\\
	}
}
{
}

\Verse{34}
{
	\hE{}
}
{
	\eE{
		And Rachel had taken the teraphim and put them in the camel’s saddle
and sat on them. And Laban felt around the whole tent and did not find
them.\\
	}
}
{
}

\Verse{35}
{
	\hE{}
}
{
	\eE{
		And she said to her father, “Let it not offend in my lord’s eyes that
I’m not able to get up before you, because I have the way of women.” And
he searched and did not find the teraphim.\\
	}
}
{
}

\Verse{36}
{
	\hE{}
}
{
	\eE{
		And Jacob was angered, and he quarreled with Laban, and Jacob
answered, and he said to Laban, “What is my offense? What is my sin,
that you blazed after me,\\
	}
}
{
}

\Verse{37}
{
	\hE{}
}
{
	\eE{
		that you felt around all my belongings? What did you find out of all
of your house’s belongings? Set it here, in front of my brothers and
your brothers, and let them judge between the two of us.\\
	}
}
{
}

\Verse{38}
{
	\hE{}
}
{
	\eE{
		This twenty years I’ve been with you, your ewes and your she-goats
haven’t lost their offspring, and I haven’t eaten your flock’s rams.\\
	}
}
{
}

\Verse{39}
{
	\hE{}
}
{
	\eE{
		I haven’t brought you one torn up. I would miss it: you would ask it
from my hand, be it stolen by day or stolen by night.\\
	}
}
{
}

\Verse{40}
{
	\hE{}
}
{
	\eE{
		I was … In the daytime heat ate me up, and ice in the night. And my
sleep fled from my eyes.\\
	}
}
{
}

\Verse{41}
{
	\hE{}
}
{
	\eE{
		This twenty years I’ve had in your house: I worked for you fourteen
years for your two daughters and six years for your flock, and you
changed my pay ten times.\\
	}
}
{
}

\Verse{42}
{
	\hE{}
}
{
	\eE{
		If I hadn’t had my father’s God, the God of Abraham and Awe of Isaac,
by now you would have sent me away empty-handed. God saw my degradation
and my hands’ exhaustion, and He pointed it out last night.”\\
	}
}
{
}

\Verse{43}
{
	\hE{}
}
{
	\eE{
		And Laban answered, and he said to Jacob, “The daughters are my
daughters, and the sons are my sons, and the flock is my flock, and
everything that you see: it’s mine. But what shall I do to my daughters,
to these, today, or to their children to whom they’ve given birth?\\
	}
}
{
}

\Verse{44}
{
	\hE{}
}
{
	\eE{
		So now, come and let’s make a covenant, I and you, and let it be a
witness between me and you.”\\
	}
}
{
}

\Verse{45}
{
	\hE{}
}
{
	\eE{
		And Jacob took a stone and set it up as a pillar,\\
	}
}
{
}

\Verse{46}
{
	\hE{}
}
{
	\eE{
		and Jacob said to his brothers, “Collect stones.” And they took stones
and made a pile and ate there at the pile.\\
	}
}
{
}

\Verse{47}
{
	\hE{}
}
{
	\eE{
		And Laban called it ygar shdta’, and Jacob
called it gal-‘d.\\
	}
}
{
}

\Verse{48}
{
	\hE{}
}
{
	\eE{
		And Laban said, “This pile is a witness between me and you today.” On
account of this he called its name Gal-Ed.\\
	}
}
{
}

\Verse{49}
{
	\hE{}
}
{
	\eE{
		(⁴⁹ And Mizpah, because he said, “May YHWH observe between me and you
when one is hidden from the other.”)\\
	}
}
{
}

\Verse{50}
{
	\hE{}
}
{
	\eE{
		“If you degrade my daughters and if you take wives in addition to my
daughters, no man is with us. See: God is witness between me and you.”\\
	}
}
{
}

\Verse{51}
{
	\hE{}
}
{
	\eE{
		And Laban said to Jacob, “Here is this pile, and here is the pillar
that I’ve cast between me and you.\\
	}
}
{
}

\Verse{52}
{
	\hE{}
}
{
	\eE{
		This pile is a witness, and the pillar is a witness that I won’t cross
this pile to you and you won’t cross this pile and this pillar to me for
bad.\\
	}
}
{
}

\Verse{53}
{
	\hE{}
}
{
	\eE{
		Let Abraham’s God and Nahor’s gods, their father’s gods, judge between
us.”

And Jacob swore by the Awe of his father, Isaac.\\
	}
}
{
}

\Verse{54}
{
	\hE{}
}
{
	\eE{
		And Jacob made a sacrifice in the mountain and called his brothers to
eat bread, and they ate bread and spent the night in the mountain.\\
	}
}
{
}

