\Chapter{33}

\Verse{1}
{
	\hE{}
}
{
	\eE{
		33

¹ And Jacob raised his eyes and looked, and here was Esau coming, and
four hundred men with him. And he divided the children among Leah and
Rachel and the two maids;\\
	}
}
{
}

\Verse{2}
{
	\hE{}
}
{
	\eE{
		and he placed the maids and their children first, and Leah and her
children following, and Rachel and Joseph following,\\
	}
}
{
}

\Verse{3}
{
	\hE{}
}
{
	\eE{
		and he passed in front of them. And he bowed to the ground seven times
until he came up to his brother.\\
	}
}
{
}

\Verse{4}
{
	\hE{}
}
{
	\eE{
		And Esau ran to him and embraced him and fell on his neck and kissed
him. And they wept.\\
	}
}
{
}

\Verse{5}
{
	\hE{}
}
{
	\eE{
		And he raised his eyes and saw the women and the children, and he said,
“Who are these whom you have?”

And he said, “The children with whom God has graced your servant.”\\
	}
}
{
}

\Verse{6}
{
	\hE{}
}
{
	\eE{
		And the maids came over, they and their children, and bowed.\\
	}
}
{
}

\Verse{7}
{
	\hE{}
}
{
	\eE{
		And Leah and her children, too, came over, and they bowed. And then
Joseph and Rachel came over, and they bowed.\\
	}
}
{
}

\Verse{8}
{
	\hE{}
}
{
	\eE{
		And he said, “Who is all this camp of yours that I met?”

And he said, “To find favor in my lord’s eyes.”\\
	}
}
{
}

\Verse{9}
{
	\hE{}
}
{
	\eE{
		And Esau said, “I have a great deal, my brother. Let what’s yours be
yours.”\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		And Jacob said, “Don’t. If I’ve found favor in your eyes, then you’ll
take my offering from my hand, because on account of this I’ve seen your
face—like seeing God’s face!—and you’ve accepted me.\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		Take my blessing that’s been brought to you, because God has been
gracious to me and because I have everything.” And he pressed him, and
he took it.\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		And he said, “Let’s travel, and let’s go. And let me go alongside
you.”\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		And he said to him, “My lord knows that the children are weak and the
nursing sheep and oxen are with me, and they’ll drive them one day and
all the sheep will die.\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		Let my lord pass on in front of his servant; and I, let me move along
at my pace required by the task that’s before me and required by the
children until I come to my lord at Seir.”\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		And Esau said, “Let me set with you some of the people who are with
me.”

And he said, “Why have I found favor in my lord’s eyes?”\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		And Esau went back on his way to Seir that day,\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		and Jacob traveled to Sukkot. And he built a house for himself and
made booths for his cattle. On account of this he called the place’s
name Sukkot.\\
	}
}
{
}

\Verse{18}
{
	\hE{}
}
{
	\eE{
		And Jacob came, safe, to the city of Shechem, which was in the land of
Canaan, when he was coming from Paddan Aram, and camped in front of the
city.\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		And he bought the section of field in which he pitched his tent from
the hand of the sons of Hamor, father of Shechem, for a hundred qesita.\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		And he set up an altar there and called it “El, God of Israel.”\\
	}
}
{
}

