\Chapter{35}

\Verse{1}
{
	\hE{}
}
{
	\eE{
		35

¹ And God said to Jacob, “Get up. Go up to Beth-El and live there and
make an altar there to God, who appeared to you when you were fleeing
from Esau, your brother.”\\
	}
}
{
}

\Verse{2}
{
	\hE{}
}
{
	\eE{
		And Jacob said to his house and to everyone who was with him, “Put away
the foreign gods that are among you and be purified and change your
clothes;\\
	}
}
{
}

\Verse{3}
{
	\hE{}
}
{
	\eE{
		and let’s get up and go up to Beth-El, and I’ll make an altar there to
God, who answered me in a day of my trouble, and He was with me in the
way that I went.”\\
	}
}
{
}

\Verse{4}
{
	\hE{}
}
{
	\eE{
		And they gave all the foreign gods that were in their hand and the
rings that were in their ears to Jacob, and Jacob stashed them under the
oak that was by Shechem.\\
	}
}
{
}

\Verse{5}
{
	\hE{}
}
{
	\eE{
		And they traveled, and God’s terror was on the cities that were around
them, and they did not pursue the children of Jacob.\\
	}
}
{
}

\Verse{6}
{
	\hE{}
}
{
	\eE{
		And Jacob came to Luz, which is in the land of Canaan—it is Beth-El—he
and all the people who were with him.\\
	}
}
{
}

\Verse{7}
{
	\hE{}
}
{
	\eE{
		And he built an altar there and called the place El of Beth-El because
God was revealed to him there when he was fleeing from his brother.\\
	}
}
{
}

\Verse{8}
{
	\hE{}
}
{
	\eE{
		And Deborah, Rebekah’s nurse, died and was buried beneath Beth-El,
beneath an oak, and he called its name Oak of Weeping.\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And God appeared to Jacob again when he was coming from Paddan Aram,
and He blessed him.\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And God said to him, “Your name is Jacob. Your name will not be called
Jacob anymore, but rather Israel will be your name.” And He called his
name Israel.\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And God said to him, “I am El Shadday Be fruitful and multiply. A
nation and a community of nations will be from you, and kings will come
out from your hips.\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And the land that I gave to Abraham and to Isaac: I’ll give it to you,
and I’ll give the land to your seed after you.”\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And God went up from on him in the place where He had spoken with him.\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And Jacob set up a pillar in the place where He had spoken with him, a
stone pillar, and he poured a libation on it and spilled oil on it.\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And Jacob called the name of the place where God had spoken to him
there Beth-El.\\
	}
}
{
}

\Verse{16}
{
	\hR{}
}
{
	\eR{
		And they traveled from Beth-El, and there was still the span of the
land to come to Ephrat, and Rachel gave birth, and she had difficulty in
her labor.\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		And it was when she was having difficulty in her labor, and the
midwife said to her, “Don’t be afraid, because this, too, is a son for
you.”\\
	}
}
{
}

\Verse{18}
{
	\hE{}
}
{
	\eE{
		And it was as her soul was going out—because she died—and she called
his name Ben-oni. And his father called him Benjamin.\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		And Rachel died. And she was buried on the road to Ephrat. It is
Bethlehem.\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		And Jacob set up a pillar on her grave. It is the pillar of Rachel’s
grave to this day.\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		And Israel traveled and pitched his tent past Migdal-Eder.\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		And it was when Israel was tenting in that land: and Reuben went and
lay with Bilhah, his father’s concubine. And Israel heard.

And Jacob’s sons were twelve.\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		The sons of Leah were Jacob’s firstborn, Reuben, and Simeon and Levi
and Judah and Issachar and Zebulun.\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		The sons of Rachel were Joseph and Benjamin.\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And the sons of Bilhah, Rachel’s maid, were Dan and Naphtali.\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		And the sons of Zilpah, Leah’s maid, were Gad and Asher. These were
Jacob’s sons, who were born to him in Paddan Aram.\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		And Jacob came to Isaac, his father, at Mamre, at Kiriath Arba—it is
Hebron—where Abraham and Isaac had resided.\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		And Isaac’s days were a hundred years and eighty years,\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		and Isaac expired. And he died and was gathered to his people, old and
full of days. And Esau and Jacob, his sons, buried him.\\
	}
}
{
}

