\Chapter{36}

\Verse{1}
{
	\hR{}
}
{
	\eR{
		36

¹ And these are the records of Esau: He is Edom.\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		Esau had taken his wives from the daughters of Canaan: Adah, daughter
of Elon, the Hittite, and Aholibamah, daughter of Anah, daughter of
Zibeon, the Hivite,

36:2–3. Adah, daughter of Elon … Aholibamah, daughter of Anah …
Basemath, daughter of Ishmael. These names are in conflict with the
names of Esau’s wives given earlier (26:34; 28:9). Rashi gives midrashic
explanations for this confusion, Ibn Ezra suggests that they each had
two names, and Ramban says that it is possible that Esau’s first two
wives died, he married two others, and he renamed his third wife. The
character and variety of their solutions indicate that they did not know
what the reason was for this confusion in the text. Critical scholars
have not solved it in terms of standard source divisions either. It may
be a combination of scribal and source reasons. It remains a classic
puzzle to be solved.\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		and Basemath, daughter of Ishmael, sister of Nebaioth.\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And Adah gave birth for Esau to Eliphaz, and Basemath gave birth to
Reuel,\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		and Aholibamah gave birth to Jeush and Jalam and Korah. These are
Esau’s sons, who were born to him in the land of Canaan.\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And Esau took his wives and his sons and his daughters and all the
persons of his household and his cattle and all of his animals and all
of his possessions that he had acquired in the land of Canaan, and he
went to a land, from the presence of Jacob, his brother,\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		because their property was too great for them to live together, and the
land of their residences was not able to suffice them because of their
cattle.\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And Esau lived in Mount Seir. Esau: he is Edom.\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And these are the records of Esau, father of Edom, in Mount Seir.\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		These are the names of Esau’s sons: Eliphaz, son of Adah, Esau’s wife;
Reuel, son of Basemath, Esau’s wife.\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And Eliphaz’s sons were Teman, Omar, Zepho, and Gatam and Kenaz.\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And Timna had been a concubine of Eliphaz, son of Esau, and she gave
birth to Amalek for Eliphaz. These are the sons of Adah, Esau’s wife.\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And these are the sons of Reuel: Nahath and Zerah, Shammah and Mizzeh.
These were the sons of Basemath, Esau’s wife.\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And these were the sons of Aholibamah, daughter of Anah, daughter of
Zibeon, Esau’s wife: and she gave birth for Esau to Jeush and Jalam and
Korah.\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		These are the chiefs of the children of Esau: the sons of Eliphaz,
Esau’s firstborn: chief Teman, chief Omar, chief Zepho, chief Kenaz,\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		chief Korah, chief Gatam, chief Amalek. These are the chiefs of
Eliphaz in the land of Edom. These are the sons of Adah.\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And these are the sons of Reuel, son of Esau: chief Nahath, chief
Zerah, chief Shammah, chief Mizzah. These are the chiefs of Reuel in the
land of Edom. These are the sons of Basemath, Esau’s wife.\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And these are the sons of Aholibamah, Esau’s wife: chief Jeush, chief
Jalam, chief Korah. These were the chiefs of Aholibamah, daughter of
Anah, Esau’s wife.\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		These are the sons of Esau, and these are their chiefs. That is Edom.\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		These are the sons of Seir the Horite, who live in the land: Lotan and
Shobal and Zibeon and Anah\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		and Dishon and Ezer and Dishan. These are the chiefs of the Horites,
the children of Seir, in the land of Edom.\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And the children of Lotan are Hori and Hemam, and Lotan’s sister is
Timna.\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		And these are the children of Shobal: Alvan and Manahath and Ebal,
Shepho and Onam.\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		And these are the children of Zibeon: Ajah and Anah—that is Anah who
found the water in the wilderness when he tended the asses of Zibeon,
his father.\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And these are the children of Anah: Dishon and Aholibamah, daughter of
Anah.\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		And these are the children of Dishon: Hemdan and Eshban and Ithran and
Cheran.\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		These are the children of Ezer: Bilhan and Zaavan and Akan.\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		These are the children of Dishan: Uz and Aran.\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		These are the chiefs of the Horites: chief Lotan, chief Shobal, chief
Zibeon, chief Anah,\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		chief Dishon, chief Ezer, chief Dishan. These are the chiefs of the
Horites by their chiefdoms in the land of Seir.\\
	}
}
{
}

\Verse{31}
{
	\hJ{}
}
{
	\eJ{
		And these are the kings who ruled in the land of Edom before a king
ruled the children of Israel.\\
	}
}
{
}

\Verse{32}
{
	\hJ{}
}
{
	\eJ{
		And Bela son of Beor ruled in Edom, and the name of his city was
Dinhabah.\\
	}
}
{
}

\Verse{33}
{
	\hJ{}
}
{
	\eJ{
		And Bela died, and Jobab son of Zerah from Bozrah ruled in his place.\\
	}
}
{
}

\Verse{34}
{
	\hJ{}
}
{
	\eJ{
		And Jobab died, and Husham of the land of Temani ruled in his place.\\
	}
}
{
}

\Verse{35}
{
	\hJ{}
}
{
	\eJ{
		And Husham died, and Hadad son of Bedad, who struck Midian in the
field of Moab, ruled in his place, and the name of his city was Avith.\\
	}
}
{
}

\Verse{36}
{
	\hJ{}
}
{
	\eJ{
		And Hadad died, and Samlah of Masrekah ruled in his place.\\
	}
}
{
}

\Verse{37}
{
	\hJ{}
}
{
	\eJ{
		And Samlah died, and Saul of Rehoboth on the river ruled in his place.\\
	}
}
{
}

\Verse{38}
{
	\hJ{}
}
{
	\eJ{
		And Saul died, and Baal-hanan son of Achbor ruled in his place.\\
	}
}
{
}

\Verse{39}
{
	\hJ{}
}
{
	\eJ{
		And Baal-hanan son of Achbor died, and Hadar ruled in his place, and
the name of his city was Pau; and his wife’s name was Mehetabel daughter
of Matred daughter of Mezahab.\\
	}
}
{
}

\Verse{40}
{
	\hJ{}
}
{
	\eJ{
		And these are the names of the chiefs of Esau by their families, by
their places, by their names: chief Timnah, chief Alvah, chief Jetheth,\\
	}
}
{
}

\Verse{41}
{
	\hJ{}
}
{
	\eJ{
		chief Aholibamah, chief Elah, chief Pinon,\\
	}
}
{
}

\Verse{42}
{
	\hJ{}
}
{
	\eJ{
		chief Kenaz, chief Teman, chief Mibzar,\\
	}
}
{
}

\Verse{43}
{
	\hJ{}
}
{
	\eJ{
		chief Magdiel, chief Iram.

These are the chiefs of Edom by their homes in the land of their
possession. That is Esau, father of Edom.\\
	}
}
{
}

