\Chapter{37}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		And Jacob lived in the land of his father’s residences, in the land of
Canaan.\\
	}
}
{
}

\Verse{2}
{
	\hR{}
}
{
	\eR{
		These are the records of Jacob: Joseph, at seventeen years old, had
been tending the sheep with his brothers, and he was a boy with the sons
of Bilhah and the sons of Zilpah, his father’s wives; and Joseph brought
a bad report of them to their father.\\
	}
}
{
}

\Verse{3}
{
	\hE{}
}
{
	\eE{
		And Israel had loved Joseph the most of all his children because he was
a son of old age to him. And he made him a coat of many colors.\\
	}
}
{
}

\Verse{4}
{
	\hE{}
}
{
	\eE{
		And his brothers saw that their father loved him the most of all his
brothers. And they hated him. And they were not able to speak a greeting
to him.\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		And Joseph had a dream and told it to his brothers, and they went on to
hate him more.\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And he said to them, “Listen to this dream that I had:\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		and here we were binding sheaves in the field; and here was my sheaf
rising and standing up, too; and, here, your sheaves surrounded and
bowed to my sheaf.”\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		And his brothers said to him, “Will you rule over us?! Will you
dominate us?!” And they went on to hate him more because of his dreams
and because of his words.\\
	}
}
{
}

\Verse{9}
{
	\hJ{}
}
{
	\eJ{
		And he had yet another dream and told it to his brothers. And he said,
“Here, I’ve had another dream, and here were the sun and the moon and
eleven stars bowing to me.”\\
	}
}
{
}

\Verse{10}
{
	\hJ{}
}
{
	\eJ{
		And he told it to his father and to his brothers.

And his father was annoyed at him and said to him, “What is this dream
that you’ve had? Shall we come, I and your mother and your brothers, to
bow to you to the ground?!”\\
	}
}
{
}

\Verse{11}
{
	\hJ{}
}
{
	\eJ{
		And his brothers were jealous of him, and his father took note of the
thing.\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		And his brothers went to feed their father’s sheep in Shechem.\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		And Israel said to Joseph, “Aren’t your brothers feeding in Shechem?
Come on and I’ll send you to them.”

And he said to him, “I’m here.”\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		And he said to him, “Go, see how your brothers are and how the sheep
are and bring me back word.” And he sent him from the valley of Hebron.

And he came to Shechem.\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		And a man found him, and here he was straying in a field. And the man
asked him, saying, “What are you looking for?”\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		And he said, “I’m looking for my brothers. Tell me, where are they
feeding?”\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		And the man said, “They traveled on from here. Because I heard them
saying, ‘Let’s go to Dothan.’”

And Joseph went after his brothers and found them in Dothan.\\
	}
}
{
}

\Verse{18}
{
	\hE{}
}
{
	\eE{
		And they saw him from a distance, and before he came close to them
they conspired against him: to kill him.\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		And the brothers said to one another, “Here comes the dream-master,
that one there!\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		And now, come on and let’s kill him and throw him in one of the pits,
and we’ll say a wild animal ate him, and we’ll see what his dreams will
be!”

37:20 wild animal. Literally, a bad animal—not just any wild animal.
This expression will occur one more time in the Torah: the blessings of
the covenant at Sinai will include a divine promise to eliminate wild
(bad) animals from the land. The value of that blessing is rendered more
visible by the recollection of Jacob’s pain when he believes that such a
creature has taken the life of his child.\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		And Reuben heard, and he saved him from their hand. And he said,
“Let’s not take his life.”\\
	}
}
{
}

\Verse{22}
{
	\hE{}
}
{
	\eE{
		And Reuben said to them, “Don’t spill blood. Throw him into this pit
that’s in the wilderness, and don’t put out a hand against him”—in order
to save him from their hand, to bring him back to his father.\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		And it was when Joseph came to his brothers: and they took off
Joseph’s coat, the coat of many colors, which he had on.\\
	}
}
{
}

\Verse{24}
{
	\hE{}
}
{
	\eE{
		And they took him and threw him into the pit. And the pit was empty;
there was no water in it.\\
	}
}
{
}

\Verse{25}
{
	\hE{}
}
{
	\eE{
		And they sat down to eat bread.

And they raised their eyes and saw, and here was a caravan of
Ishmaelites coming from Gilead, and their camels were carrying spices
and balsam and myrrh, going to bring them down to Egypt.\\
	}
}
{
}

\Verse{26}
{
	\hJ{}
}
{
	\eJ{
		And Judah said to his brothers, “What profit is there if we kill our
brother and cover his blood?\\
	}
}
{
}

\Verse{27}
{
	\hJ{}
}
{
	\eJ{
		Come on and let’s sell him to the Ishmaelites, and let our hand not be
on him, because he’s our brother, our flesh.” And his brothers listened.\\
	}
}
{
}

\Verse{28}
{
	\hE{}
}
{
	\eE{
		And Midianite people, merchants, passed, and they pulled and lifted
Joseph from the pit. And they sold Joseph to the Ishmaelites for twenty
weights of silver. And they brought Joseph to Egypt.\\
	}
}
{
}

\Verse{29}
{
	\hE{}
}
{
	\eE{
		And Reuben came back to the pit, and here: Joseph was not in the pit.
And he tore his clothes.\\
	}
}
{
}

\Verse{30}
{
	\hE{}
}
{
	\eE{
		And he went back to his brothers and said, “The boy’s gone! And I,
where can I go?”\\
	}
}
{
}

\Verse{31}
{
	\hJ{}
}
{
	\eJ{
		And they took Joseph’s coat and slaughtered a he-goat and dipped the
coat in the blood.\\
	}
}
{
}

\Verse{32}
{
	\hJ{}
}
{
	\eJ{
		And they sent the coat of many colors and brought it to their father
and said, “We found this. Recognize: is it your son’s coat or not?”\\
	}
}
{
}

\Verse{33}
{
	\hJ{}
}
{
	\eJ{
		And he recognized it and said, “My son’s coat. A wild animal ate him.
Joseph is torn up!”\\
	}
}
{
}

\Verse{34}
{
	\hJ{}
}
{
	\eJ{
		And Jacob ripped his clothes and wore sackcloth on his hips and
mourned over his son many days.\\
	}
}
{
}

\Verse{35}
{
	\hJ{}
}
{
	\eJ{
		And all his sons and all his daughters got up to console him, and he
refused to be consoled, and he said, “Because I’ll go down mourning to
my son at Sheol,” and his father wept for him.\\
	}
}
{
}

\Verse{36}
{
	\hE{}
}
{
	\eE{
		And the Medanites sold him to Egypt, to Potiphar, an official of
Pharaoh, chief of the guards.\\
	}
}
{
}

