\Chapter{38}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		38

¹ And it was at that time, and Judah went 3 O down from his brothers and
turned to an Adullamite man, and his name was Hirah.\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		And Judah saw a daughter of a Canaanite man there, and his name was
Shua. And he took her and came to her.\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		And she became pregnant and gave birth to a son, and he called his name
Er.\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		And she became pregnant again and gave birth to a son, and she called
his name Onan.\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		And she proceeded again to give birth to a son, and she called his name
Shelah. (And he was at Chezib when she gave birth to him.)\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And Judah took a wife for Er, his firstborn, and her name was Tamar.\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		And Er, Judah’s firstborn, was bad in YHWH’s eyes, and YHWH killed him.\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		And Judah said to Onan, “Come to your brother’s wife and couple as a
brother-in-law with her and raise seed for your brother.”\\
	}
}
{
}

\Verse{9}
{
	\hJ{}
}
{
	\eJ{
		And Onan knew that the seed would not be his. And it was when he came
to his brother’s wife: and he spent on the ground so as not to give seed
for his brother.\\
	}
}
{
}

\Verse{10}
{
	\hJ{}
}
{
	\eJ{
		And what he did was bad in YHWH’s eyes, and He killed him, too.\\
	}
}
{
}

\Verse{11}
{
	\hJ{}
}
{
	\eJ{
		And Judah said to Tamar, his daughter-in-law, “Live as a widow at your
father’s house until my son Shelah grows up” (because he said, “Or else
he, too, will die like his brothers”). And Tamar went and lived at her
father’s house.\\
	}
}
{
}

\Verse{12}
{
	\hJ{}
}
{
	\eJ{
		And the days were many, and Judah’s wife, the daughter of Shua, died.
And Judah was consoled. And he went up to his sheepshearers, he and his
friend Hirah, the Adullamite, to Timnah.\\
	}
}
{
}

\Verse{13}
{
	\hJ{}
}
{
	\eJ{
		And it was told to Tamar, saying, “Here, your father-in-law is going
up to Timnah to shear his sheep.”\\
	}
}
{
}

\Verse{14}
{
	\hJ{}
}
{
	\eJ{
		And she took off her widowhood clothes from on her and covered herself
with a veil and wrapped herself and sat in a visible place that was on
the road to Timnah, because she saw that Shelah had grown up and she had
not been given to him as a wife.\\
	}
}
{
}

\Verse{15}
{
	\hJ{}
}
{
	\eJ{
		And Judah saw her and thought her to be a prostitute because she had
covered her face.\\
	}
}
{
}

\Verse{16}
{
	\hJ{}
}
{
	\eJ{
		And he turned to her by the road.

And he said, “Come on. Let me come to you,” because he did not know that
she was his daughter-in-law.

And she said, “What will you give me when you come to me?”\\
	}
}
{
}

\Verse{17}
{
	\hJ{}
}
{
	\eJ{
		And he said, “I’ll have a goat kid sent from the flock.”

And she said, “If you’ll give a pledge until you send it.”\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		And he said, “What is the pledge that I’ll give you?”

And she said, “Your seal and your cord and your staff that’s in your
hand.” And he gave them to her, and he came to her, and she became
pregnant by him.\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		And she got up and went and took off her veil from on her and put on
her widowhood clothes.\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		And Judah sent the goat kid by the hand of his friend the Adullamite
to take back the pledge from the woman’s hand, and he did not find her.\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		And he asked the people of her place, saying, “Where is the sacred
prostitute? She was visibly by the road.”

And they said, “There was no sacred prostitute here.”\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		And he came back to Judah and said, “I didn’t find her, and also the
people of the place said There was no sacred prostitute here.’”\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		And Judah said, “Let her take them or else we’ll be a disgrace. Here,
I’ve sent this goat kid, and you didn’t find her.”\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		And it was about three months, and it was told to Judah, saying, “Your
daughter-in-law Tamar has whored, and, here, she’s pregnant by whoring
as well.”

And Judah said, “Bring her out and let her be burned.”\\
	}
}
{
}

\Verse{25}
{
	\hJ{}
}
{
	\eJ{
		She was brought out. And she sent to her father-in-law, saying, “I’m
pregnant by the man to whom these belong,” and she said, “Recognize: to
whom do these seal and cords and staff belong?”\\
	}
}
{
}

\Verse{26}
{
	\hJ{}
}
{
	\eJ{
		And Judah recognized and said, “She’s more right than I am, because of
the fact that I didn’t give her to my son Shelah.” And he did not go on
to know her again.\\
	}
}
{
}

\Verse{27}
{
	\hJ{}
}
{
	\eJ{
		And it was at the time that she was giving birth, and here were twins
in her womb.\\
	}
}
{
}

\Verse{28}
{
	\hJ{}
}
{
	\eJ{
		And it was as she was giving birth, and one put out his hand, and the
midwife took a scarlet thread and tied it on his hand, saying, “This one
came out first.”\\
	}
}
{
}

\Verse{29}
{
	\hJ{}
}
{
	\eJ{
		And it was as he pulled his hand back, and here his brother came out.
And she said, “What a breach you’ve made for yourself!” And he called
his name Perez.\\
	}
}
{
}

\Verse{30}
{
	\hJ{}
}
{
	\eJ{
		And his brother who had the scarlet thread on his hand came out after.
And he called his name Zerah.\\
	}
}
{
}

