\Chapter{42}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		42

¹ And Jacob saw that there was grain in Egypt, and Jacob said to his
sons, “Why do you look at each other?”\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		And he said, “Here I’ve heard that there’s grain in Egypt. Go down
there and buy grain for us from there, and we’ll live and not die.”\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		And ten of Joseph’s brothers went down to buy grain from Egypt,\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		and Jacob did not send Joseph’s brother Benjamin with his brothers
because, he said, “In case some harm will happen to him.”\\
	}
}
{
}

\Verse{5}
{
	\hE{}
}
{
	\eE{
		And the sons of Israel came to buy among those who were coming, because
the famine was in the land of Canaan.\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And Joseph was the one in charge over the land; he was the one who sold
grain to all the people of the land. And Joseph’s brothers came and
bowed to him, noses to the ground.\\
	}
}
{
}

\Verse{7}
{
	\hE{}
}
{
	\eE{
		And Joseph saw his brothers and recognized them, but he made himself
unrecognizable to them, and he spoke with them in hard tones. And he
said to them, “From where have you come?”

And they said, “From the land of Canaan, to buy food.”\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		And Joseph recognized his brothers, but they did not recognize him,\\
	}
}
{
}

\Verse{9}
{
	\hJ{}
}
{
	\eJ{
		and Joseph remembered the dreams that he had had about them. And he
said to them, “You’re spies. You came to see the land exposed.”\\
	}
}
{
}

\Verse{10}
{
	\hJ{}
}
{
	\eJ{
		And they said to him, “No, my lord, your servants came to buy food.\\
	}
}
{
}

\Verse{11}
{
	\hJ{}
}
{
	\eJ{
		We’re all sons of one man. We’re honest men. Your servants weren’t
spying.”\\
	}
}
{
}

\Verse{12}
{
	\hJ{}
}
{
	\eJ{
		And he said to them, “No, but you’ve come to see the land exposed.”\\
	}
}
{
}

\Verse{13}
{
	\hJ{}
}
{
	\eJ{
		And they said, “Your servants are twelve brothers. We’re sons of one
man in the land of Canaan, and, here, the youngest is with our father
today, and one is no more.”\\
	}
}
{
}

\Verse{14}
{
	\hJ{}
}
{
	\eJ{
		And Joseph said to them, “It’s as I spoke to you, saying: you’re
spies.\\
	}
}
{
}

\Verse{15}
{
	\hJ{}
}
{
	\eJ{
		By this you’ll be tested: by Pharaoh’s life, you won’t go out of here
except by your youngest brother’s coming here.\\
	}
}
{
}

\Verse{16}
{
	\hJ{}
}
{
	\eJ{
		Send one from among you, and let him get your brother, and you remain
in prison, and your words will be tested: is the truth with you? And if
not, then by Pharaoh’s life you’re spies.”\\
	}
}
{
}

\Verse{17}
{
	\hJ{}
}
{
	\eJ{
		And he gathered them under watch for three days.\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		And Joseph said to them on the third day, “Do this and live, as I fear
God:\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		If you’re honest, one brother from among you will be held at the place
where you’re under watch; and you, go, bring grain for the famine in
your houses.\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		And you will bring your youngest brother to me, and your words will be
confirmed, and you won’t die.” And they did so.\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		And they said, each to his brother, “But we’re guilty over our
brother, because we saw his soul’s distress when he implored us and we
didn’t listen. On account of that this distress has come to us!”\\
	}
}
{
}

\Verse{22}
{
	\hE{}
}
{
	\eE{
		And Reuben answered them, saying, “Didn’t I say to you, saying, ‘Don’t
sin against the boy’? And you didn’t listen. And his blood, too, is
required here!”\\
	}
}
{
}

\Verse{23}
{
	\hE{}
}
{
	\eE{
		And they did not know that Joseph was listening, because an
interpreter was between them.\\
	}
}
{
}

\Verse{24}
{
	\hE{}
}
{
	\eE{
		And he turned from them and wept. And he came back to them and spoke
to them and took Simeon from them and shackled him before their eyes.\\
	}
}
{
}

\Verse{25}
{
	\hE{}
}
{
	\eE{
		And Joseph commanded that they fill their containers with grain and to
put their silver back in each man’s sack and to give them provisions for
the road. And he did that for them.\\
	}
}
{
}

\Verse{26}
{
	\hJ{}
}
{
	\eJ{
		And they loaded their grain on their asses and went from there.\\
	}
}
{
}

\Verse{27}
{
	\hJ{}
}
{
	\eJ{
		And one opened his sack to give fodder to his ass at a lodging place,
and he saw his silver, and here it was in the mouth of his bag.\\
	}
}
{
}

\Verse{28}
{
	\hJ{}
}
{
	\eJ{
		And he said to his brothers, “My silver’s been put back, and here it
is in my bag, too.”

And their heart went out, and the brothers trembled to one another,
saying, “What is this that God has done to us?”\\
	}
}
{
}

\Verse{29}
{
	\hJ{}
}
{
	\eJ{
		And they came to Jacob, their father, to the land of Canaan, and told
him all the things that happened to them, saying,\\
	}
}
{
}

\Verse{30}
{
	\hJ{}
}
{
	\eJ{
		“The man, the lord of the land, spoke with us hard and accused us of
spying on the land.\\
	}
}
{
}

\Verse{31}
{
	\hJ{}
}
{
	\eJ{
		And we said to him, ‘We’re honest. We weren’t spying.\\
	}
}
{
}

\Verse{32}
{
	\hJ{}
}
{
	\eJ{
		We’re twelve brothers, our father’s sons; one is no more, and the
youngest is with our father in the land of Canaan today’.\\
	}
}
{
}

\Verse{33}
{
	\hJ{}
}
{
	\eJ{
		And the man, the lord of the land, said to us, ‘By this I’ll know that
you’re honest: leave one brother from among you with me, and take for
the famine in your houses and go,\\
	}
}
{
}

\Verse{34}
{
	\hJ{}
}
{
	\eJ{
		and bring your youngest brother to me, so I may know that you aren’t
spies, that you’re honest. I’ll give you your brother, and you’ll go
around in the land.’”\\
	}
}
{
}

\Verse{35}
{
	\hE{}
}
{
	\eE{
		And it was: they were emptying their sacks, and here was each man’s
bundle of silver in his sack, and they saw the bundles of their silver,
they and their father, and they were afraid.\\
	}
}
{
}

\Verse{36}
{
	\hE{}
}
{
	\eE{
		And their father, Jacob, said to them, “You’ve bereaved me! Joseph is
gone, and Simeon’s gone, and you’ll take Benjamin. All these have
happened to me!”\\
	}
}
{
}

\Verse{37}
{
	\hE{}
}
{
	\eE{
		And Reuben said to his father, saying, “Kill my two sons if I don’t
bring him back to you. Put him in my hand, and I’ll bring him back to
you.”\\
	}
}
{
}

\Verse{38}
{
	\hJ{}
}
{
	\eJ{
		And he said, “My son will not go down with you. Because his brother’s
dead, and he’s left by himself, and if some harm would happen to him on
the way in which you’re going then you’ll bring down my gray hair in
anguish to Sheol.”\\
	}
}
{
}

