\Chapter{43}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		43

¹ And the famine was heavy in the land.\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		And it was when they had finished eating the grain that they had
brought from Egypt: and their father said to them, “Go back. Buy us a
little food.”\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		And Judah said to him, saying, “The man certified to us, saying, ‘You
won’t see my face unless your brother is with you.’\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		If you’re sending our brother with us, we’ll go down and buy food for
you,\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		and if you’re not sending, we won’t go down, because the man said to
us, ‘You won’t see my face unless your brother is with you.’”\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And Israel said, “Why have you done me wrong, to tell the man that you
have another brother?”\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		And they said, “The man asked about us and about our birthplace,
saying, ‘Is your father still alive? Do you have a brother?’ And we told
him about these things. Could we have known that he would say, ‘Bring
your brother down’?”\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		And Judah said to Israel, his father, “Send the boy with me, so we may
get up and go, and we’ll live and not die, we and you and our infants as
well.\\
	}
}
{
}

\Verse{9}
{
	\hJ{}
}
{
	\eJ{
		I’ll be security for him. You’ll seek him from my hand. If I don’t
bring him to you and set him before you, then I’ll have sinned against
you for all time.\\
	}
}
{
}

\Verse{10}
{
	\hJ{}
}
{
	\eJ{
		For, if we hadn’t delayed, by now we would have come back twice.”\\
	}
}
{
}

\Verse{11}
{
	\hJ{}
}
{
	\eJ{
		And Israel, their father, said to them, “If that’s how it is, then do
this: Take some of the best fruit of the land in your containers and
take a gift down to the man, a little balm and a little honey, gum and
myrrh, pistachios and almonds.\\
	}
}
{
}

\Verse{12}
{
	\hJ{}
}
{
	\eJ{
		And take double the silver in your hand, and take back in your hand
the silver that was put back in the mouth of your bags. Maybe it was a
mistake.\\
	}
}
{
}

\Verse{13}
{
	\hJ{}
}
{
	\eJ{
		And take your brother. And get up, go back to the man.\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		And may El Shadday give you mercy before the man, so he’ll send your
other brother and Benjamin to you. And I: if I’m bereaved I’m bereaved!”\\
	}
}
{
}

\Verse{15}
{
	\hJ{}
}
{
	\eJ{
		And the men took this gift and took double the silver in their hand
and Benjamin and got up and went down to Egypt and stood before Joseph.\\
	}
}
{
}

\Verse{16}
{
	\hJ{}
}
{
	\eJ{
		And Joseph saw Benjamin with them and said to the one who was over his
house, “Bring the men to the house, and slaughter and prepare an animal,
because the men will eat with me at noon.”\\
	}
}
{
}

\Verse{17}
{
	\hJ{}
}
{
	\eJ{
		And the man did as Joseph said, and the man brought the men to
Joseph’s house.\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		And the men were afraid because they were brought to Joseph’s house,
and they said, “We’re being brought on account of the silver that came
back in our bags the first time, in order to roll over us and to fall
upon us and to take us as slaves—and our asses.”\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		And they went over to the man who was over Joseph’s house and spoke to
him at the entrance of the house\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		and said, “Please, my lord, we came down the first time to buy food,\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		and it was when we came to the lodging place, and we opened our bags,
and here was each man’s silver in the mouth of his bag, our money in its
full weight. And we’ve brought it in our hand,\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		and we’ve brought down additional silver in our hand to buy food. We
don’t know who put our silver in our bags.”\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		And he said, “Peace to you. Don’t be afraid. Your God and your
father’s God put treasure in your bags for you. Your silver came to me.”
And he brought Simeon out to them.\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		And the man brought the men to Joseph’s house, and he gave water, and
they washed their feet, and he gave fodder for their asses.\\
	}
}
{
}

\Verse{25}
{
	\hJ{}
}
{
	\eJ{
		And they prepared the gift until Joseph’s arrival at noon because they
heard that they would eat bread there.\\
	}
}
{
}

\Verse{26}
{
	\hJ{}
}
{
	\eJ{
		And Joseph came to the house, and they brought the gift for him that
was in their hand to the house, and they bowed to him to the ground.\\
	}
}
{
}

\Verse{27}
{
	\hJ{}
}
{
	\eJ{
		And he asked if they were well, and he said, “Is your old father whom
you mentioned well? Is he still alive?”\\
	}
}
{
}

\Verse{28}
{
	\hJ{}
}
{
	\eJ{
		And they said, “Your servant, our father, is well. He’s still alive.”
And they knelt and bowed.\\
	}
}
{
}

\Verse{29}
{
	\hJ{}
}
{
	\eJ{
		And he raised his eyes and saw Benjamin, his brother, his mother’s
son, and said, “Is this your youngest brother whom you mentioned to me?”
And he said, “May God be gracious to you, my son.”\\
	}
}
{
}

\Verse{30}
{
	\hJ{}
}
{
	\eJ{
		And Joseph hurried because his feelings for his brother were boiling,
and he looked for a place to weep and came to his room and wept there.\\
	}
}
{
}

\Verse{31}
{
	\hJ{}
}
{
	\eJ{
		And he washed his face and went out and restrained himself and said,
“Put out bread.”\\
	}
}
{
}

\Verse{32}
{
	\hJ{}
}
{
	\eJ{
		And they put it out for him by himself and for them by themselves and
for the Egyptians who were eating with him by themselves, because the
Egyptians could not eat bread with the Hebrews because that is an
offensive thing to Egypt.\\
	}
}
{
}

\Verse{33}
{
	\hJ{}
}
{
	\eJ{
		And they sat before him, the firstborn according to his birthright and
the youngest according to his youth. And the men looked amazed at one
another.\\
	}
}
{
}

\Verse{34}
{
	\hJ{}
}
{
	\eJ{
		And he conveyed portions from before him to them, and he made
Benjamin’s portion five times more than the portions of all of them, and
they drank and were drunk with him.\\
	}
}
{
}

