\Chapter{44}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		44

¹ And he commanded the one who was over his house, saying, “Fill the
men’s bags with as much food as they can carry and put each man’s silver
in the mouth of his bag,\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		and put my cup, the silver cup, in the mouth of the youngest one’s bag,
and the silver for his grain.” And he did according to Joseph’s word
that he spoke.\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		The morning was light: and the men had been sent away, they and their
asses.\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		They had gone out of the city. They had not gone far, and Joseph had
said to the one who was over his house, “Get up. Pursue the men, and
you’ll catch up with them and say to them, ‘Why did you pay back bad for
good?\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		Isn’t this the thing from which my lord drinks? And he divines by it!
You’ve done bad, this thing that you’ve done.’”\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And he caught up with them and spoke these things to them.\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		And they said to him, “Why would my lord speak things like these? Far
be it from your servants to do a thing like this.\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		Here, we brought the silver that we found in the mouth of our bags back
to you from the land of Canaan, so how would we steal silver or gold
from your lord’s house?!\\
	}
}
{
}

\Verse{9}
{
	\hJ{}
}
{
	\eJ{
		The one among your servants with whom it’s found, let him die, and also
we’ll become my lord’s servants.”\\
	}
}
{
}

\Verse{10}
{
	\hJ{}
}
{
	\eJ{
		And he said, “Now, also, it will be so according to your words: the
one with whom it’s found will become my servant. And you will be free.”\\
	}
}
{
}

\Verse{11}
{
	\hJ{}
}
{
	\eJ{
		And they hurried, and each man lowered his bag to the ground, and each
man opened his bag.\\
	}
}
{
}

\Verse{12}
{
	\hJ{}
}
{
	\eJ{
		And he searched. With the oldest he began, and with the youngest he
finished. And the cup was found in Benjamin’s bag.\\
	}
}
{
}

\Verse{13}
{
	\hJ{}
}
{
	\eJ{
		And they ripped their clothes, and each man loaded his ass, and they
went back to the city.\\
	}
}
{
}

\Verse{14}
{
	\hJ{}
}
{
	\eJ{
		And Judah and his brothers came to Joseph’s house, and he was still
there, and they fell to the ground before him.\\
	}
}
{
}

\Verse{15}
{
	\hJ{}
}
{
	\eJ{
		And Joseph said to them, “What is this thing that you’ve done? Didn’t
you know that a man like me would divine?”\\
	}
}
{
}

\Verse{16}
{
	\hJ{}
}
{
	\eJ{
		And Judah said, “What shall we say to my lord? What shall we speak? By
what shall we justify ourselves? God has found your servants’ crime.
Here we’re my lord’s servants, both we and the one in whose hand the cup
was found.”\\
	}
}
{
}

\Verse{17}
{
	\hJ{}
}
{
	\eJ{
		And he said, “Far be it from me to do this. The man in whose hand the
cup was found: he will be my servant; and you, go up in peace to your
father.”\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		AND HE WENT OVER

¹⁸ And Judah went over to him and said, “Please, my lord, let your
servant speak something in my lord’s ears, and let your anger not flare
at your servant, because you’re like Pharaoh himself.\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		My lord asked his servants, saying, ‘Do you have a father or brother?’\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		and we said to my lord, ‘We have an old father and a young son of his
old age, and his brother’s dead, and he’s left alone of his mother, and
his father loves him.’\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		And you said to your servants, ‘Bring him down to me, so I may set my
eye on him.’\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		And we said to my lord, The boy can’t leave his father; if he left his
father he’d die.’\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		And you said to your servants, ‘If your youngest brother doesn’t come
down with you, you won’t see my face again.’\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		And it was, when we went up to your servant, my father, and told him
my lord’s words,\\
	}
}
{
}

\Verse{25}
{
	\hJ{}
}
{
	\eJ{
		that our father said, ‘Go back. Buy us a little food.’\\
	}
}
{
}

\Verse{26}
{
	\hJ{}
}
{
	\eJ{
		And we said, ‘We can’t go down. If our youngest brother is with us
then we’ll go down, because we can’t see the man’s face if our youngest
brother isn’t with us.’\\
	}
}
{
}

\Verse{27}
{
	\hJ{}
}
{
	\eJ{
		And your servant, my father, said to us, ‘You know that my wife gave
birth to two for me,\\
	}
}
{
}

\Verse{28}
{
	\hJ{}
}
{
	\eJ{
		and one went away from me, and I said he’s surely torn up, and I
haven’t seen him since.

44:28; since. It is hard to convey the irony in the wording in English
translation. Jacob says, “I haven’t seen him since” (literally, “up to
here,”  and later Joseph says, “You didn’t send me here”\\
	}
}
{
}

\Verse{29}
{
	\hJ{}
}
{
	\eJ{
		And if you take this one from me as well and some harm happens to him,
then you’ll bring down my gray hair in wretchedness to Sheol.’\\
	}
}
{
}

\Verse{30}
{
	\hJ{}
}
{
	\eJ{
		And now, when I come to your servant, my father, and the boy isn’t
with us, and he’s bound to him soul to soul,\\
	}
}
{
}

\Verse{31}
{
	\hJ{}
}
{
	\eJ{
		it will be, when he sees that the boy isn’t there, that he’ll die. And
your servants will have brought down your servant our father’s gray hair
in anguish to Sheol,\\
	}
}
{
}

\Verse{32}
{
	\hJ{}
}
{
	\eJ{
		because your servant offered security for the boy to my father,
saying, ‘If I don’t bring him to you, then I’ll have sinned against my
father for all time.’\\
	}
}
{
}

\Verse{33}
{
	\hJ{}
}
{
	\eJ{
		And now, let your servant stay as my lord’s servant in place of the
boy, and let the boy go up with his brothers—\\
	}
}
{
}

\Verse{34}
{
	\hJ{}
}
{
	\eJ{
		for how could I go up to my father and the boy isn’t with me—or else
I’ll see the wretchedness that will find my father.”\\
	}
}
{
}

