\Chapter{47}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		47

¹ And Joseph came and told Pharaoh and said, “My father and my brothers
and their flock and their oxen and all that they own have come from the
land of Canaan, and here they are in the land of Goshen.”\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		And he took several of his brothers, five men, and set them before
Pharaoh.\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		And Pharaoh said to his brothers, “What is your work?”

And they said to Pharaoh, “Your servants are shepherds, both we and our
fathers,”\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		and they said to Pharaoh, “We came to reside in the land because
there’s no pasture for your servants’ flock because the famine is heavy
in the land of Canaan. And now may your servants live in the land of
Goshen.”\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And Pharaoh said to Joseph, saying, “Your father and your brothers have
come to you.\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		The land of Egypt is before you. Settle your father and your brothers
in the best of the land. Let them live in the land of Goshen. And if you
know—and if there are among them—worthy men, then you shall make them
livestock officers over those that I have.”\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And Joseph brought Jacob, his father, and stood him in front of
Pharaoh. And Jacob blessed Pharaoh.\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And Pharaoh said to Jacob, “How many are the days of the years of your
life?”\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And Jacob said to Pharaoh, “The days of the years of my residences are
a hundred thirty years. The days of the years of my life have been few
and bad, and they haven’t attained the days of the years of my fathers’
lives, in the days of their residences.”\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And Jacob blessed Pharaoh and went out from in front of Pharaoh.\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And Joseph settled his father and his brothers and gave them a
possession in the land of Egypt, in the best of the land, in the land of
Rameses, as Pharaoh had commanded.\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And Joseph supported his father and his brothers and all of his
father’s household, bread by the number of infants.\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		And there was no bread in all the land of Egypt, because the famine
was very heavy, and the land of Egypt and the land of Canaan languished
because of the famine.\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		And Joseph collected all the silver that was found in the land of
Egypt and in the land of Canaan for the grain that they were buying, and
Joseph brought the silver to Pharaoh’s house.\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		And the silver came to an end from the land of Egypt and from the land
of Canaan. And all of Egypt came to Joseph, saying, “Give us bread! And
why should we die in front of you? Because there’s no more silver!”\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		And Joseph said, “Give your livestock, and I’ll give it to you for
your livestock if there’s no more silver.”\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		And they brought their livestock to Joseph, and Joseph gave them bread
for the horses and for the livestock of the flocks and for the livestock
of the oxen and for the asses, and he sustained them with bread for all
their livestock in that year.\\
	}
}
{
}

\Verse{18}
{
	\hE{}
}
{
	\eE{
		And that year came to an end, and they came to him in the second year
and said to him, “We won’t conceal from my lord that the silver has come
to an end and the cattle livestock have gone to my lord. Nothing is left
in front of my lord except our body and our land.\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		Why should we die before your eyes, both we and our land? Buy us and
our land for bread, and we and our land will be servants to Pharaoh; and
give seed so we’ll live and not die, and the land won’t be devastated.”\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		And Joseph bought all the land of Egypt for Pharaoh, because Egypt,
each man, sold his field, because the famine was strong on them. And the
land became Pharaoh’s.\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		And the people: he moved them to cities, from one edge of Egypt’s
border to its other edge.\\
	}
}
{
}

\Verse{22}
{
	\hE{}
}
{
	\eE{
		Only the priests’ land he did not buy, because it was a law for the
priests from Pharaoh, and they ate their statutory share that Pharaoh
had given them. On account of this they did not sell their land.\\
	}
}
{
}

\Verse{23}
{
	\hE{}
}
{
	\eE{
		And Joseph said to the people, “Here, I’ve bought you and your land
for Pharaoh today. Look: seed for you. And you’ll sow the land;\\
	}
}
{
}

\Verse{24}
{
	\hE{}
}
{
	\eE{
		and it will be, at the harvests, that you’ll give a fifth to Pharaoh,
and the four parts will be yours for field seed and for you to eat and
for whoever is in your households and for your infants to eat.”\\
	}
}
{
}

\Verse{25}
{
	\hE{}
}
{
	\eE{
		And they said, “You’ve kept us alive! Let us find favor in my lord’s
eyes, and we’ll be servants to Pharaoh.”\\
	}
}
{
}

\Verse{26}
{
	\hE{}
}
{
	\eE{
		And Joseph set it as a law to this day on Egypt’s land: to Pharaoh the
fifth. Only the land of the priests alone was not Pharaoh’s.\\
	}
}
{
}

\Verse{27}
{
	\hJ{}
}
{
	\eJ{
		And Israel lived in Egypt in the land of Goshen, and they held
property in it. And they were fruitful and multiplied very much.\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		AND HE LIVED

²⁸ And Jacob lived in the land of Egypt seventeen years. And Jacob’s
days, the years of his life, were seven years and a hundred forty years.\\
	}
}
{
}

\Verse{29}
{
	\hJ{}
}
{
	\eJ{
		And Israel’s days to die drew close. And he called his son, Joseph,
and said to him, “If I’ve found favor in your eyes, place your hand
under my thigh and practice kindness and faithfulness with me: don’t
bury me in Egypt.\\
	}
}
{
}

\Verse{30}
{
	\hJ{}
}
{
	\eJ{
		And I’ll lie with my fathers, and you’ll carry me out of Egypt and
bury me in their burial place.”

And he said, “I’ll do according to your word.”

And he said, “Swear to me.”

And he swore to him. And Israel bowed at the head of the bed.\\
	}
}
{
}

\Verse{31}
{
	\hJ{}
}
{
	\eJ{
	}
}
{
}

