\Chapter{48}

\Verse{1}
{
	\hE{}
}
{
	\eE{
		48

¹ And it was after these things, and one said to Joseph, “Here, your
father is sick.” And he took his two sons with him, Man-asseh and
Ephraim.\\
	}
}
{
}

\Verse{2}
{
	\hE{}
}
{
	\eE{
		And one told Jacob and said, “Here, your son Joseph is coming to you.”
And Israel fortified himself and sat up on the bed.\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And Jacob said to Joseph, “El Shadday appeared to me in Luz in the land
of Canaan, and He blessed me\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		and said to me, ‘Here, I’m making you fruitful and multiplying you, and
I’ll make you into a community of peoples, and I’ll give this land to
your seed after you, an eternal possession.’\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And now, your two sons who were born to you in the land of Egypt by my
arrival to you at Egypt: they’re mine. Ephraim and Man-asseh will be
like Reuben and Simeon to me.\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And your offspring that you’ll have after them will be yours. They
shall be called by their brothers’ names with regard to their
inheritance.\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And I: when I was coming from Paddan Aram, Rachel died by me in the
land of Canaan on the way when there was still a span of land to come to
Ephrat, and I buried her there on the Ephrat road. That’s Bethlehem.”\\
	}
}
{
}

\Verse{8}
{
	\hE{}
}
{
	\eE{
		And Israel saw Joseph’s sons and said, “Who are these?”\\
	}
}
{
}

\Verse{9}
{
	\hE{}
}
{
	\eE{
		And Joseph said to his father, “They’re my sons, whom God has given me
here.”

And he said, “Bring them to me, and I’ll bless them.”\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		And Israel’s eyes were heavy from old age. He was not able to see. And
he brought them close to him, and he kissed them and embraced them.\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		And Israel said to Joseph, “I didn’t expect to see your face; and,
here, God has shown me your seed as well.”\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		And Joseph brought them out from between his knees, and he bowed, his
nose to the ground.\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		And Joseph took the two of them, Ephraim in his right hand, at
Israel’s left; and Manasseh in his left hand, at Israel’s right; and he
brought them over to him.\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		And Israel put out his right hand and placed it on Ephraim’s head—and
he was the younger—and his left hand on Manasseh’s head. He crossed his
hands—because Manasseh was the firstborn.\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		And he blessed Joseph and said, “The God before whom my fathers,
Abraham and Isaac, walked, who shepherded me from my start to this day,\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		the angel who redeemed me from all bad, may He bless the boys. And may
my name be called on them, and the name of my fathers, Abraham and
Isaac. And may they spawn into a great number within the earth.”\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		And Joseph saw that his father had placed his right hand on Ephraim’s
head, and it was bad in his eyes, and he held up his father’s hand to
turn it from on Ephraim’s head onto Manasseh’s head,\\
	}
}
{
}

\Verse{18}
{
	\hE{}
}
{
	\eE{
		and Joseph said to his father, “Not like that, my father, because this
is the firstborn. Set your right hand on his head.”\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		And his father refused and said, “I know, my son, I know. He, too,
will become a people; and he, too, will be great. But in fact his little
brother will be greater than he, and his seed will be full-fledged of
nations.”\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		And he blessed them in that day, saying, “Israel will bless with you,
saying: ‘May God make you like Ephraim and like Manasseh.’” And he set
Ephraim before Manasseh.\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		And Israel said to Joseph, “Here, I’m dying. And God will be with you
and will bring you back to your fathers’ land. And I’ve given you one
shoulder over your brothers, which I took from the Amorite’s hand with
my sword and my bow.”\\
	}
}
{
}

