\Chapter{50}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		50

¹ And Joseph fell upon his father’s face and wept over him and kissed
him.\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		And Joseph commanded his servants, the physicians, to embalm his
father. And the physicians embalmed Israel,\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		and they spent forty days on him, because that is the number of days
they spent on the embalming, and Egypt mourned him seventy days.\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		And his mourning days passed, and Joseph spoke to Pharaoh’s house,
saying, “If I’ve found favor in your eyes, speak in Pharaoh’s ears,
saying,\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		‘My father had me swear, saying, “Here I’m dying. In my tomb, which I
dug for me in the land of Canaan: you shall bury me there.” And now, let
me go up so I may bury my father and come back.’”\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And Pharaoh said, “Go up and bury your father as he had you swear.”\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		And Joseph went up to bury his father, and all of Pharaoh’s servants,
the elders of his house, and all the elders of the land of Egypt,\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		and all of Joseph’s house and his brothers and his father’s house. Only
their infants and their flock and their oxen they left in the land of
Goshen.\\
	}
}
{
}

\Verse{9}
{
	\hJ{}
}
{
	\eJ{
		And both chariots and horsemen went up with him. It was a very heavy
camp.\\
	}
}
{
}

\Verse{10}
{
	\hJ{}
}
{
	\eJ{
		And they came to the threshing floor of Atad, which is across the
Jordan, and they had a very big and heavy funeral, and he made a
mourning for his father or seven days.\\
	}
}
{
}

\Verse{11}
{
	\hJ{}
}
{
	\eJ{
		And the Canaanite residents of the land saw the mourning at the
threshing floor of Atad and said, “This is a heavy mourning to Egypt.”
On account of this its name was called Abel of Egypt, which is beyond
the Jordan.\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And his sons did so for him, as he had commanded them.\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And his sons carried him to the land of Canaan and buried him in the
cave of the field of Machpelah, as Abraham had bought the field as a
possession for a tomb from Ephron, the Hittite, facing Mamre.\\
	}
}
{
}

\Verse{14}
{
	\hJ{}
}
{
	\eJ{
		And, after his burial of his father, Joseph came back to Egypt, he and
his brothers and all those who went up with him to bury his father.\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		And Joseph’s brothers saw that their father was dead, and they said,
“If Joseph will despise us he’ll pay us back all the bad that we dealt
to him.”\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		And they commanded to Joseph, saying, “Your father had commanded
before his death, saying,\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		‘You shall say this to Joseph: Please, bear your brothers’ offense and
their sin, because they dealt you bad.’ And now bear the offense of the
servants of your father’s God.”

And Joseph wept when they spoke to him.\\
	}
}
{
}

\Verse{18}
{
	\hE{}
}
{
	\eE{
		And his brothers also went and fell in front of him and said, “Here,
we’re yours as slaves.”\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		And Joseph said to them, “Don’t be afraid, because am I in God’s
place?\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		And you thought bad against me. God thought for good: in order to do
as it is today, to keep alive a numerous people.\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		And now, don’t be afraid. I’ll provide for you and your infants.” And
he consoled them. And he spoke on their heart.\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		And Joseph lived in Egypt, he and his father’s house. And Joseph lived
a hundred ten years,\\
	}
}
{
}

\Verse{23}
{
	\hE{}
}
{
	\eE{
		and Joseph saw children of Ephraim’s of the third generation. Also
children of Machir, son of Manasseh, were born on Joseph’s knees.\\
	}
}
{
}

\Verse{24}
{
	\hE{}
}
{
	\eE{
		And Joseph said to his brothers, “I’m dying. And God will take account
of you and will bring you up from this land to the land that He swore to
Abraham, to Isaac, and to Jacob.”\\
	}
}
{
}

\Verse{25}
{
	\hE{}
}
{
	\eE{
		And Joseph had the children of Israel swear, saying, “God will take
account of you, and you’ll bring up my bones from here.”\\
	}
}
{
}

\Verse{26}
{
	\hE{}
}
{
	\eE{
		And Joseph died, a hundred ten years old, and they embalmed him and
set him in a coffin in Egypt.

------------------------------------------------------------------------

COMMENTARY ON THE TORAH

------------------------------------------------------------------------

The book of Exodus tells the story of the birth of a nation in slavery
and ends with the nation’s establishment of its own center, leaders, and
symbols in freedom. Genesis involves a continuous narrowing of attention
from the universe to the earth to humanity to a particular family;
Exodus begins to broaden the circumference of attention again as the
family grows into a nation—and comes into conflict with another nation.
Whereas Genesis sets the rest of the books of the Bible in context,
Exodus does not set them in context so much as introduce fundamental
components that will function centrally in almost all the coming books
of the Bible. Exodus introduces the nation of Israel. It introduces
prophecy. It introduces law. Arguably most important of all, it
introduces the theme of YHWH’s becoming known to the world.\\
	}
}
{
}

