\Chapter{5}

\Verse{1}
{
	\hBookOfRecords{זה ספר תולדת אדם ביום ברא אלהים אדם בדמות אלהים עשה אתו}
}
{
	\eBookOfRecords{
		This is the Book of Records of the Human.\\
		In the day of God’s creating a human,\\
		He made it in the likeness of God.\\
	}
}
{
}

\Verse{2}
{
	\hBookOfRecords{זכר ונקבה בראם ויברך אתם ויקרא את שמם אדם ביום הבראם}
}
{
	\eBookOfRecords{
		He created them male and female,\\
		and he blessed them\\
		and called their name “Human”\\
		in the day of their being created.\\
	}
}
{
}

\Verse{3}
{
	\hBookOfRecords{ויחי אדם שלשים ומאת שנה ויולד בדמותו כצלמו ויקרא את שמו שת}
}
{
	\eBookOfRecords{
		And the human lived a hundred thirty years.
		And he fathered in his likeness—like his image.
		And called his name Seth.\\
	}
}
{
}

\Verse{4}
{
	\hBookOfRecords{ויהיו ימי אדם אחרי הולידו את שת שמנה מאות שנה ויולד בנים ובנות}
}
{
	\eBookOfRecords{
		And the human’s days after his fathering Seth were eight hundred years.\\
		And he fathered sons and daughters.\\
	}
}
{
}

\Verse{5}
{
	\hBookOfRecords{ויהיו כל ימי אדם אשר חי תשע מאות שנה ושלשים שנה וימת}
}
{
	\eBookOfRecords{
		And all of the human’s days that he lived were nine hundred years and thirty years.\\
		And he died.\\
	}
}
{
}

\Verse{6}
{
	\hBookOfRecords{ויחי שת חמש שנים ומאת שנה ויולד את אנוש}
}
{
	\eBookOfRecords{
		And Seth lived five years and a hundred years.\\
		And he fathered Enosh.\\
	}
}
{
}

\Verse{7}
{
	\hBookOfRecords{ויחי שת אחרי הולידו את אנוש שבע שנים ושמנה מאות שנה ויולד בנים ובנות}
}
{
	\eBookOfRecords{
		And Seth lived after his fathering Enosh seven years and eight hundred years.\\
		And he fathered sons and daughters.\\
	}
}
{
}

\Verse{8}
{
	\hBookOfRecords{ויהיו כל ימי שת שתים עשרה שנה ותשע מאות שנה וימת}
}
{
	\eBookOfRecords{
		And all of Seth’s days were twelve years and nine hundred years.\\
		And he died.\\
	}
}
{
}

\Verse{9}
{
	\hBookOfRecords{ויחי אנוש תשעים שנה ויולד את קינן}
}
{
	\eBookOfRecords{
		And Enosh lived ninety years,\\
		And he fathered Cainan.\\
	}
}
{
}

\Verse{10}
{
	\hBookOfRecords{ויחי אנוש אחרי הולידו את קינן חמש עשרה שנה ושמנה מאות שנה ויולד בנים ובנות}
}
{
	\eBookOfRecords{
		And Enosh lived after his fathering Cainan fifteen years and eight hundred years,\\
		And he fathered sons and daughters.\\
	}
}
{
}

\Verse{11}
{
	\hBookOfRecords{ויהיו כל ימי אנוש חמש שנים ותשע מאות שנה וימת}
}
{
	\eBookOfRecords{
		And all of Enosh’s days were five years and nine hundred years.\\
		And he died.\\
	}
}
{
}

\Verse{12}
{
	\hBookOfRecords{ויחי קינן שבעים שנה ויולד את מהללאל}
}
{
	\eBookOfRecords{
		And Cainan lived seventy years.\\
		And he fathered Mahalalel.\\
	}
}
{
}

\Verse{13}
{
	\hBookOfRecords{ויחי קינן אחרי הולידו את מהללאל ארבעים שנה ושמנה מאות שנה ויולד בנים ובנות}
}
{
	\eBookOfRecords{
		And Cainan lived after his fathering Mahalalel forty years and eight hundred years,\\
		And he fathered sons and daughters.\\
	}
}
{
}

\Verse{14}
{
	\hBookOfRecords{ויהיו כל ימי קינן עשר שנים ותשע מאות שנה וימת}
}
{
	\eBookOfRecords{
		And all of Cainan’s days were ten years and nine hundred years.\\
		And he died.\\
	}
}
{
}

\Verse{15}
{
	\hBookOfRecords{ויחי מהללאל חמש וששים שנה ויולד את ירד}
}
{
	\eBookOfRecords{
		And Mahalalel lived five and sixty years.\\
		And he fathered Jared.\\
	}
}
{
}

\Verse{16}
{
	\hBookOfRecords{ויחי מהללאל אחרי הולידו את ירד שלשים שנה ושמנה מאות שנה ויולד בנים ובנות}
}
{
	\eBookOfRecords{
		And Mahalalel lived after his fathering Jared thirty years and eight hundred years.\\
		And he fathered sons and daughters.\\
	}
}
{
}

\Verse{17}
{
	\hBookOfRecords{ויהיו כל ימי מהללאל חמש ותשעים שנה ושמנה מאות שנה וימת}
}
{
	\eBookOfRecords{
		And all of Mahalalel’s days were ninety-five years and eight hundred years.\\
		And he died.\\
	}
}
{
}

\Verse{18}
{
	\hBookOfRecords{ויחי ירד שתים וששים שנה ומאת שנה ויולד את חנוך}
}
{
	\eBookOfRecords{
		And Jared lived sixty-two years and a hundred years.\\
		And he fathered Enoch.\\
	}
}
{
}

\Verse{19}
{
	\hBookOfRecords{ויחי ירד אחרי הולידו את חנוך שמנה מאות שנה ויולד בנים ובנות}
}
{
	\eBookOfRecords{
		And Jared lived after his fathering Enoch eight hundred years.\\
		And he fathered sons and daughters.\\
	}
}
{
}

\Verse{20}
{
	\hBookOfRecords{ויהיו כל ימי ירד שתים וששים שנה ותשע מאות שנה וימת}
}
{
	\eBookOfRecords{
		And all of Jared’s days were sixty-two years and nine hundred years.\\
		And he died.\\
	}
}
{
}

\Verse{21}
{
	\hBookOfRecords{ויחי חנוך חמש וששים שנה ויולד את מתושלח}
}
{
	\eBookOfRecords{
		And Enoch lived sixty-five years.\\
		And he fathered Methuselah.\\
	}
}
{
}

\Verse{22}
{
	\hBookOfRecords{ויתהלך חנוך את האלהים אחרי הולידו את מתושלח שלש מאות שנה ויולד בנים ובנות}
}
{
	\eBookOfRecords{
		And Enoch walked with God after his fathering Methuselah three hundred years.\\
		And he fathered sons and daughters.\\
	}
}
{

\aB{What's going on here?} \aA{Not there yet, come with me.}

}

\Verse{23}
{
	\hBookOfRecords{ויהיו כל ימי חנוך חמש וששים שנה ושלש מאות שנה}
}
{
	\eBookOfRecords{
		And all of Enoch’s days were sixty-five years and three hundred years.
	}
}
{

\aB{What's going on here?} \aA{LKhHh HhLKh.}

\aB{Are you ok?} \aA{Always here, walk with me.}

}

\Verse{24}
{
	\hBookOfRecords{ויתהלך חנוך את האלהים ואיננו כי לקח אתו אלהים}
}
{
	\eBookOfRecords{
		And Enoch walked with God.\\
		And he was not, because God took him.\\
	}
}
{

\aB{What's going on here?} \aA{LQX XLQ.}

\aB{Roman numerals?} \aA{No man, follow me.}

\aB{Come on, what's come over you?} \aA{Stick with me, I'll explain.}

\aB{Is there a lesson in all this?} \aA{Trust me, just participate \& follow me.}

\aB{Follow you how, and to where?}

\aA{Just like that,} \aC{I promise it's all clear.}

\aC{We just missed a bit,} \aA{look we're here.}

\newpage
\vspace*{\fill}

\begin{quote}
\textbf{\hAJ{\cR{ח}\cK{נ}\cB{ך}}} (\textit{ḥ-n-k / ḥănōḵ}) \emph{n.}\\
Meaning \emph{to educate}, \emph{to \cB{train}}, \emph{to teach}, to \emph{educate}.\\
Form of the name \emph{\cR{Enoch}}.

\medskip

\textbf{\hAJ{\cR{ה}\cK{ל}\cB{ך}}} (\textit{h-l-k / hālak}) \emph{v.}\\
Meaning \emph{to go}, \emph{to \cR{walk}}, or \emph{to proceed}; move away along a path.

\medskip

% This spells NAHAS
\textbf{\hAJ{\cR{ח}\cK{ל}\cB{ק}}} (\textit{ḥ-l-q / ḥéleq}) \emph{n. v.}\\
Noun meaning \emph{part}, \emph{allotment}, \emph{share}.\\
Also, in addition, can mean a small amount of time.\\
Has verbal forms meaning \emph{to divide}, \emph{to split}, \emph{to share}\\
Adjectival meanings include \emph{smooth}, \emph{slippery}.\\
Sequential duplication \hAJ{\cR{ח}\cK{ל}\cB{ק}\cK{ל}\cB{ק}} refers to something slick.\footnote{Cf. \hAJ{ערום} v. \hAJ{ערומים}}

\medskip

% Spells "MR"
\textbf{\hAJ{\cK{ל}\cB{ק}\cR{ח}}} (\textit{l-q-ḥ / lāqaḥ}) \emph{v., n.}\\
Meaning \emph{to \cR{take}}; also \emph{\cB{lesson}}, \emph{message} in education (\textit{léqaḥ}),
the \emph{\cR{take}-\cR{away}} \emph{\cB{lesson}}.\footnote{Related to arabic laḥiqa (“to stick together”) through metathesis.}

\medskip

% Spells "MRS"
\textbf{\hAJ{\cK{ל}\cB{ק}\cR{ח} \cR{ח}\cK{ל}\cB{ק}}} (\textit{l-q-ḥ ḥ-l-q / lāqaḥ ḥéleq}) \emph{v.}\\
Meaning literally \emph{“to take part.”}, \emph{to participate}, \emph{to be a part of}.\\
From \hAJ{\cK{ל}\cB{ק}\cR{ח}} (“to \cR{take}”) + \hAJ{\cR{ח}\cK{ל}\cB{ק}} (“part,” “portion”).
\end{quote}

\vspace*{\fill}
\newpage
\vspace*{\fill}

\Verse{24a}
{
	\hBookOfRecords{%
		\cK{וית}
		\cB{הלך}
		\cR{חנך}
		\cK{אתו אלהים}
	}
}
{
	\eBookOfRecords{
		\cK{And} \cB{walked} \cR{Enoch} \cK{with god.}\\
	}
}
{
}

\Verse{24b}
{
	\hBookOfRecords{%
		\cK{ו}
		\cR{איננוכי}
		\cB{לקח}
		\cK{את ה אלהים}
	}
}
{
	\eBookOfRecords{
		\cK{And} \cR{he was not, because} \cK{god} \cB{took} \cK{him}.\\
	}
}
{
}

\vspace*{\fill}
\newpage

}

\Verse{25}
{
	\hBookOfRecords{ויחי מתושלח שבע ושמנים שנה ומאת שנה ויולד את למך}
}
{
	\eBookOfRecords{
		And Methuselah lived eighty-seven years and a hundred years,\\
		and he fathered Lamech.\\
	}
}
{
}

\Verse{26}
{
	\hBookOfRecords{ויחי מתושלח אחרי הולידו את למך שתים ושמנים שנה ושבע מאות שנה ויולד בנים ובנות}
}
{
	\eBookOfRecords{
		And Methuselah lived after his fathering Lamech\\
		eighty-two years and seven hundred years,\\
		and he fathered sons and daughters.\\
	}
}
{
}

\Verse{27}
{
	\hBookOfRecords{ויהיו כל ימי מתושלח תשע וששים שנה ותשע מאות שנה וימת}
}
{
	\eBookOfRecords{
		And all of Methuselah’s days\\
		were sixty-nine years and nine hundred years.\\
		And he died.\\
	}
}
{
}

\Verse{28}
{
	\hBookOfRecords{ויחי למך שתים ושמנים שנה ומאת שנה ויולד בן}
}
{
	\eBookOfRecords{
		And Lamech lived eighty-two years and a hundred years,\\
		and he fathered a son.\\
	}
}
{
}

\Verse{29}
{
	\hR{ויקרא את שמו נח לאמר זה ינחמנו ממעשנו ומעצבון ידינו מן האדמה אשר אררה יהוה}
}
{
	\eR{
		and called his name Noah, saying,\\
		“This one will console us from our labor\\
		and from our hands’ suffering from the ground,\\
		which YHWH has cursed.”\\
	}
}
{
}

\Verse{30}
{
	\hBookOfRecords{ויחי למך אחרי הולידו את נח חמש ותשעים שנה וחמש מאות שנה ויולד בנים ובנות}
}
{
	\eBookOfRecords{
		And Lamech lived after his fathering Noah\\
		ninety-five years and five hundred years,\\
		and he fathered sons and daughters.\\
	}
}
{
}

\Verse{31}
{
	\hBookOfRecords{ויהיו כל ימי למך שבע ושבעים שנה ושבע מאות שנה וימת}
}
{
	\eBookOfRecords{
		And all of Lamech’s days\\
		were seventy-seven years and seven hundred years.\\
		And he died.\\
	}
}
{
}

\Verse{32}
{
	\hBookOfRecords{ויהי נח בן חמש מאות שנה ויולד נח את שם את חם ואת יפת}
}
{
	\eBookOfRecords{
		And Noah was five hundred years old,\\
		and Noah fathered Shem, Ham, and Yaphet.\\
	}
}
{
}
