\Chapter{22}

\Verse{1}
{
	\hE{ויהי אחר הדברים האלה והאלהים נסה את אברהם ויאמר אליו אברהם ויאמר הנני}
}
{
	\eE{
		And it was after these things,\\
		and God tested Abraham.\\
		And He said to him, “Abraham.”\\
		And he said, “I’m here.”\\
	}
}
{
}

\Verse{2}
{
	\hE{ויאמר קח נא את בנך את יחידך אשר אהבת את יצחק ולך לך אל ארץ המריה והעלהו שם לעלה על אחד ההרים אשר אמר אליך}
}
{
	\eE{
		And He said, “Take your son,\\
		your only one, whom you love,\\
		Isaac,\\
		and go to the land of Mo-riah\\
		and make him a burnt offering there\\
		on one of the mountains that I’ll say to you.”\\
	}
}
{
}

\Verse{3}
{
	\hE{וישכם אברהם בבקר ויחבש את חמרו ויקח את שני נעריו אתו ואת יצחק בנו ויבקע עצי עלה ויקם וילך אל המקום אשר אמר לו האלהים}
}
{
	\eE{
		And Abraham got up early in the morning\\
		and harnessed his ass\\
		and took his two boys with him\\
		and Isaac, his son.\\
		And he cut the wood for the burnt offering,\\
		and he got up and went to the place\\
		that God had said to him.\\
	}
}
{
	\aB{Who are you by the way?}

	\aA{In what sense?}
}

\Verse{4}
{
	\hE{ביום השלישי וישא אברהם את עיניו וירא את המקום מרחק}
}
{
	\eE{
		On the third day:\\
		and Abraham raised his eyes\\
		and saw the place from a distance.\\
	}
}
{
	\aB{A name would be nice.}

	\aA{We can't here.}
}

\Verse{5}
{
	\hE{ויאמר אברהם אל נעריו שבו לכם פה עם החמור ואני והנער נלכה עד כה ונשתחוה ונשובה אליכם}
}
{
	\eE{
		And Abraham said to his boys,\\
		“Sit here with the ass;\\
		and I and the boy:\\
		we’ll go over there,\\
		and we’ll bow,\\
		and we’ll come back to you.”\\
	}
}
{
	\aB{An initial at least?}

	\aA{Most I can do.}
}

\Verse{6}
{
	\hE{ויקח אברהם את עצי העלה וישם על יצחק בנו ויקח בידו את האש ואת המאכלת וילכו שניהם יחדו}
}
{
	\eE{
		And Abraham took the wood for the burnt offering\\
		and put it on Isaac, his son,\\
		and took the fire and the knife in his hand.\\
		And the two of them went together.\\
	}
}
{
	\aB{So can you?}

	\aA{Of course}
}

\Verse{7}
{
	\hE{ויאמר יצחק אל אברהם אביו ויאמר אבי ויאמר הנני בני ויאמר הנה האש והעצים ואיה השה לעלה}
}
{
	\eE{
		And Isaac said to Abraham, his father;\\
		and he said, “My father.”\\
		And he said, “I’m here, my son.”\\
		And he said, “Here are the fire and the wood,\\
		but where is the sheep for the burnt offering?”\\
	}
}
{
	\aB{Who are you?}

	\aA{What's in a name}
}

\Verse{8}
{
	\hE{ויאמר אברהם אלהים יראה לו השה לעלה בני וילכו שניהם יחדו}
}
{
	\eE{
		And Abraham said,\\
		“God will see to the sheep for the burnt offering,\\
		my son.”\\
		And the two of them went together.\\
	}
}
{
	\aB{An initial I said.}

	\aA{As in the beginning}
}

\Verse{9}
{
	\hE{ויבאו אל המקום אשר אמר לו האלהים ויבן שם אברהם את המזבח ויערך את העצים ויעקד את יצחק בנו וישם אתו על המזבח ממעל לעצים}
}
{
	\eE{
		And they came to the place\\
		that God had said to him.\\
		And Abraham built the altar there\\
		and arranged the wood,\\
		and he bound Isaac, his son,\\
		and put him on the altar\\
		on top of the wood.\\
	}
}
{
	\aB{Spit it out.}

	\aA{Not that way}
}

\Verse{10}
{
	\hE{וישלח אברהם את ידו ויקח את המאכלת לשחט את בנו}
}
{
	\eE{
		And Abraham put out his hand\\
		and took the knife\\
		to slaughter his son.\\
	}
}
{
	\aB{What do they call you?}

	\aA{Who are you calling they}
}

\Verse{11}
{
	\hRJE{ויקרא אליו מלאך יהוה מן השמים ויאמר אברהם אברהם ויאמר הנני}
}
{
	\eRJE{
		And an angel of YHWH called to him from the skies\\
		and said, “Abraham! Abraham!”\\
		And he said, “I’m here.”\\
	}
}
{
	\aB{The ones who know you.}

	\vspace{\baselineskip}
	\hrule
	\vspace{\baselineskip}

	\aAc{(\emph{Narrator: A curious silence elapses.})}
}

\Verse{12}
{
	\hRJE{ויאמר אל תשלח ידך אל הנער ואל תעש לו מאומה כי עתה ידעתי כי ירא אלהים אתה ולא חשכת את בנך את יחידך ממני}
}
{
	\eRJE{
		And he said,\\
		“Don’t put your hand out toward the boy,\\
		and don’t do anything to him,\\
		because now I know that you fear L\hspace{-0.22em}Ꞁ,\\
		and you didn’t withhold your son,\\
		your only one, from me.”\\
	}
}
{
	\aA{They usually call me J}
}

\Verse{13}
{
	\hRJE{וישא אברהם את עיניו וירא והנה איל אחר נאחז בסבך בקרניו וילך אברהם ויקח את האיל ויעלהו לעלה תחת בנו}
}
{
	\eRJE{
		And Abraham raised his eyes and saw,\\
		and here was a ram behind,\\
		caught in the thicket by its horns.\\
		And Abraham went and took the ram\\
		and made it a burnt offering\\
		instead of his son.\\
	}
}
{

	\aB{You?}
	\aA{And that would make you}

}

\Verse{14}
{
	\hRJE{ויקרא אברהם שם המקום ההוא יהוה יראה אשר יאמר היום בהר יהוה יראה}
}
{
	\eRJE{
		And Abraham called the name of that place\\
		“YHWH Yir’eh,”\\
		as is said today:\\
		“In YHWH’s mountain it will be seen.”\\
	}
}
{
	\aB{No way}

	\aA{Now wait.}

}

\Verse{15}
{
	\hRJE{ויקרא מלאך יהוה אל אברהם שנית מן השמים}
}
{
	\eRJE{
		And an angel of YHWH called to Abraham\\
		a second time from the skies\\
	}
}
{
	\aA{Don't say---}

	\aB{I can't, You th---}
}

\Verse{16}
{
	\hE{ויאמר בי נשבעתי}
	\hRJE{נאם יהוה}
	\hE{כי יען אשר עשית את הדבר הזה ולא חשכת את בנך את יחידך}
}
{
	\eE{
		and said, “I swear by me—\\
	}
	\eRJE{
		word of YHWH—\\
	}
	\eE{
		that because you did this thing\\
		and didn’t withhold your son,\\
		your only one,\\
	}
}
{
	\aA{Yeah no one wou---}

	\aB{ink any one wou---}
}

\Verse{17}
{
	\hE{כי ברך אברכך והרבה ארבה את זרעך ככוכבי השמים וכחול אשר על שפת הים וירש זרעך את שער איביו}
}
{
	\eE{
		that I’ll bless you\\
		and multiply your seed\\
		like the stars of the skies\\
		and like the sand that’s on the seashore,\\
		and your seed will possess its enemies’ gate.\\
	}
}
{
	\aA{---ld \textsc{be}lie\textsc{ve y}ou}

	\aB{---\textsc{ld} be\textsc{lie}ve \textsc{me} \textsc{an}yway.}
}

\Verse{18}
{
	\hE{והתברכו בזרעך כל גויי הארץ עקב אשר שמעת בקלי}
}
{
	\eE{
		And all the nations of the earth\\
		will be blessed through your seed\\
		because you listened to my voice\\
	}
}
{
	\begin{quote}
	\aAc{\textsc{\cK{A}\cR{n}\cB{y}\cK{w}\cR{a}\cB{y}}}
	\end{quote}

	\vspace{\baselineskip}
	\hrule
	\vspace{\baselineskip}

	\aAc{(\emph{Narrator: A knowing silence elapses.})}

}

\Verse{19}
{
	\hE{וישב אברהם אל נעריו ויקמו וילכו יחדו אל באר שבע וישב אברהם בבאר שבע}
}
{
	\eE{
		And Abraham went back to his boys\\
		And they got up\\
		And went together to Beer-sheba\\
		And Abraham lived in Beer-sheba\\
	}
}
{

}

\Verse{20}
{
	\hJ{ויהי אחרי הדברים האלה ויגד לאברהם לאמר הנה ילדה מלכה גם הוא בנים לנחור אחיך}
}
{
	\eJ{
		And it was after these things,\\
		and it was told to Abraham, saying,\\
		“Here Milcah has given birth, she also,\\
		to sons for your brother Nahor:\\
	}
}
{
}

\Verse{21}
{
	\hJ{את עוץ בכרו ואת בוז אחיו ואת קמואל אבי ארם}
}
{
	\eJ{
		Uz, his firstborn,\\
		and Buz his brother,\\
		and Kemuel, the father of Aram,\\
	}
}
{
}

\Verse{22}
{
	\hJ{ואת כשד ואת חזו ואת פלדש ואת ידלף ואת בתואל}
}
{
	\eJ{
		and Chesed and Hazo\\
		and Pildash and Jidlaph\\
		and Bethuel.\\
	}
}
{
}

\Verse{23}
{
	\hJ{ובתואל ילד את רבקה שמנה אלה ילדה מלכה לנחור אחי אברהם}
}
{
	\eJ{
		And Bethuel fathered Rebekah.”\\
		Milcah gave birth to these eight\\
		for Nahor, Abraham’s brother.\\
	}
}
{
}

\Verse{24}
{
	\hJ{ופילגשו ושמה ראומה ותלד גם הוא את טבח ואת גחם ואת תחש ואת מעכה}
}
{
	\eJ{
		And his concubine,\\
		whose name was Reumah,\\
		she too gave birth,\\
		to Tebah and Gaham\\
		and Tahash and Maacah.\\
	}
}
{
}