\Chapter{1}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses in the wilderness of Sinai in the Tent of
Meeting on the first day of the second month in the second year of their
exodus from the land of Egypt, saying,

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Add up the heads of all of the congregation of Israel by their
families, by their fathers’ houses, with the number of names of every
male by their heads.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		From twenty years old and up, everyone going out to the army in Israel:
you shall count them by their army units, you and Aaron.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		“And a man for each tribe shall be with you; each is the head of his
fathers’ house.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And these are the names of the men who will stand with you: For Reuben,
Elizur son of Shedeur.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		For Simeon, Shelumiel son of Zurishadday.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		For Judah, Nahshon son of Amminadab.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		For Issachar, Nethanel son of Zuar.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		For Zebulun, Eliab son of Helon.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		For the children of Joseph: for Ephraim, Elishama son of Ammihud; for
Manasseh, Gamaliel son of Pedahzur.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		For Benjamin, Abidan son of Gideoni.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		For Dan, Ahiezer son of Ammishadday.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		For Asher, Pagiel son of Ochran.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		For Gad, Eliasaph son of Deuel.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		For Naphtali, Ahira son of Enan.”

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		These were the prominent ones of the congregation, chieftains of their
fathers’ tribes. They were heads of Israel’s thousands.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And Moses and Aaron took these men who were designated by name,

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		and they assembled all of the congregation on the first day of the
second month, and they were recorded by their families, by their
fathers’ houses, with the number of names, from twenty years old and up,
by their heads,

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		as YHWH commanded Moses. And he counted them in the wilderness of
Sinai.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And the children of Reuben, Israel’s first-born, were: by their
records, by their families, by their fathers’ house, with the number of
names, by their heads, every male from twenty years old and up, everyone
going out to the army,

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		the tribe of Reuben’s counts were forty-six thousand five hundred.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		For the children of Simeon: by their records, by their families, by
their fathers’ house, their counts with the number of names, by their
heads, every male from twenty years old and up, everyone going out to
the army,

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		the tribe of Simeon’s counts were fifty-nine thousand three hundred.

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		For the children of Gad: by their records, by their families, by their
fathers’ house, with the number of names, from twenty years old and up,
everyone going out to the army,

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		the tribe of Gad’s counts were forty-five thousand six hundred fifty.

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		For the children of Judah: by their records, by their families, by
their fathers’ house, with the number of names, from twenty years old
and up, everyone going out to the army,

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		the tribe of Judah’s counts were seventy-four thousand six hundred.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		For the children of Issachar: by their records, by their families, by
their fathers’ house, with the number of names, from twenty years old
and up, everyone going out to the army,

[image]\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		the tribe of Issachar’s counts were fifty-four thousand four hundred.

[image]\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		For the children of Zebulun: by their records, by their families, by
their fathers’ house, with the number of names, from twenty years old
and up, everyone going out to the army,

[image]\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		the tribe of Zebulun’s counts were fifty-seven thousand four hundred.

[image]\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		For the children of Joseph:

For the children of Ephraim: by their records, by their families, by
their fathers’ house, with the number of names, from twenty years old
and up, everyone going out to the army,

[image]\\
	}
}
{
}

\Verse{33}
{
	\hP{}
}
{
	\eP{
		the tribe of Ephraim’s counts were forty thousand five hundred.

[image]\\
	}
}
{
}

\Verse{34}
{
	\hP{}
}
{
	\eP{
		For the children of Manasseh: by their records, by their families, by
their fathers’ house, with the number of names, from twenty years old
and up, everyone going out to the army,

[image]\\
	}
}
{
}

\Verse{35}
{
	\hP{}
}
{
	\eP{
		the tribe of Manasseh’s counts were thirty-two thousand two hundred.

[image]\\
	}
}
{
}

\Verse{36}
{
	\hP{}
}
{
	\eP{
		For the children of Benjamin: by their records, by their families, by
their fathers’ house, with the number of names, from twenty years old
and up, everyone going out to the army,

[image]\\
	}
}
{
}

\Verse{37}
{
	\hP{}
}
{
	\eP{
		the tribe of Benjamin’s counts were thirty-five thousand four hundred.

[image]\\
	}
}
{
}

\Verse{38}
{
	\hP{}
}
{
	\eP{
		For the children of Dan: by their records, by their families, by their
fathers’ house, with the number of names, from twenty years old and up,
everyone going out to the army,

[image]\\
	}
}
{
}

\Verse{39}
{
	\hP{}
}
{
	\eP{
		the tribe of Dan’s counts were sixty-two thousand seven hundred.

[image]\\
	}
}
{
}

\Verse{40}
{
	\hP{}
}
{
	\eP{
		For the children of Asher: by their records, by their families, by
their fathers’ house, with the number of names, from twenty years old
and up, everyone going out to the army,

[image]\\
	}
}
{
}

\Verse{41}
{
	\hP{}
}
{
	\eP{
		the tribe of Asher’s counts were forty-one thousand five hundred.

[image]\\
	}
}
{
}

\Verse{42}
{
	\hP{}
}
{
	\eP{
		The children of Naphtali: by their records, by their families, by
their fathers’ house, with the number of names, from twenty years old
and up, everyone going out to the army,

[image]\\
	}
}
{
}

\Verse{43}
{
	\hP{}
}
{
	\eP{
		the tribe of Naphtali’s counts were fifty-three thousand four hundred.

[image]\\
	}
}
{
}

\Verse{44}
{
	\hP{}
}
{
	\eP{
		These are the counts that Moses and Aaron and Israel’s chieftains
made. (They were twelve men, one each for his fathers’ house.)

[image]\\
	}
}
{
}

\Verse{45}
{
	\hP{}
}
{
	\eP{
		And they were all of the counts of the children of Israel, by their
fathers’ house, from twenty years old and up, everyone going out to the
army in Israel.

[image]\\
	}
}
{
}

\Verse{46}
{
	\hP{}
}
{
	\eP{
		And all of the counts were six hundred three thousand five hundred
fifty.

[image]\\
	}
}
{
}

\Verse{47}
{
	\hP{}
}
{
	\eP{
		And the Levites, by their fathers’ tribe, were not counted among them,

[image]\\
	}
}
{
}

\Verse{48}
{
	\hP{}
}
{
	\eP{
		for YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{49}
{
	\hP{}
}
{
	\eP{
		“Except: you shall not count the tribe of Levi, and you shall not add
up their heads among the children of Israel.

[image]\\
	}
}
{
}

\Verse{50}
{
	\hP{}
}
{
	\eP{
		And you: appoint the Levites over the Tabernacle of the Testimony and
over all its equipment and over everything it has. They shall carry the
Tabernacle and all its equipment, and they shall attend to it, and they
shall camp around the Tabernacle.

[image]\\
	}
}
{
}

\Verse{51}
{
	\hP{}
}
{
	\eP{
		And when the Tabernacle travels, the Levites shall take it down; and
when the Tabernacle camps, the Levites shall set it up. And an outsider
who comes close shall be put to death.

[image]\\
	}
}
{
}

\Verse{52}
{
	\hP{}
}
{
	\eP{
		And the children of Israel shall camp, each at his camp, each at his
flag, by their army units,

[image]\\
	}
}
{
}

\Verse{53}
{
	\hP{}
}
{
	\eP{
		and the Levites shall camp all around the Tabernacle of the Testimony,
so there will not be a rage on the congregation of the children of
Israel, and the Levites shall keep the charge of the Tabernacle of the
Testimony.”

[image]\\
	}
}
{
}

\Verse{54}
{
	\hP{}
}
{
	\eP{
		And the children of Israel did according to everything that YHWH had
commanded Moses. They did so.

[image]\\
	}
}
{
}

