\Chapter{2}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		2

¹ And YHWH spoke to Moses and to Aaron, saying,

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“The children of Israel shall camp, each by his flag with the signs of
their fathers’ house; they shall camp opposite, all around the Tent of
Meeting.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And the ones camping on the east: to the east is the flag of Judah’s
camp by their armies. And the chieftain of the children of Judah is
Nahshon son of Amminadab,

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		and his army and its counts are seventy-four thousand six hundred.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And the ones camping next to it are: the tribe of Issachar. And the
chieftain of the children of Issachar is Nethanel son of Zuar,

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		and his army and its counts are fifty-four thousand four hundred.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		The tribe of Zebulun. And the chieftain of the children of Zebulun is
Eliab son of Helon,

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		and his army and its counts are fifty-seven thousand four hundred.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		All the counts of Judah’s camp are one hundred eighty-six thousand four
hundred by their army units. They shall travel first.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		“The flag of Reuben’s camp on the south by their armies. And the
chieftain of the children of Reuben is Elizur son of Shedeur,

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		and his army and its counts are forty-six thousand five hundred.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And the ones camping next to it are: the tribe of Simeon. And the
chieftain of the children of Simeon is Shelumiel son of Zurishadday,

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		and his army and their counts are fifty-nine thousand three hundred.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And the tribe of Gad. And the chieftain of the children of Gad is
Eliasaph son of Reuel,

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		and his army and their counts are forty-five thousand six hundred
fifty.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		All the counts of Reuben’s camp are one hundred fifty-one thousand
four hundred fifty by their army units. And they shall travel second.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		“And the Tent of Meeting, the Levites’ camp, shall travel inside the
camps. As they camp, so they shall travel: each at his position by their
flags.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		“The flag of Ephraim’s camp by their armies on the west. And the
chieftain of the children of Ephraim is Elishama son of Ammihud,

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		and his army and their counts are forty thousand five hundred.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And next to it: the camp of Manasseh. And the chieftain of the
children of Manasseh is Gamaliel son of Pedahzur,

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		and his army and their counts are thirty-two thousand two hundred.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And the tribe of Benjamin. And the chieftain of the children of
Benjamin is Abidan son of Gideoni,

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		and his army and their counts are thirty-five thousand four hundred.

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		All the counts of Ephraim’s camp are one hundred eight thousand one
hundred by their army units. And they shall travel third.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		“The flag of Dan’s camp on the north by their armies. And the
chieftain of the children of Dan is Ahiezer son of Ammishadday,

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		and his army and their counts are sixty-two thousand seven hundred.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		And the ones camping next to it are: the tribe of Asher. And the
chieftain of the children of Asher is Pagiel son of Ochran,

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		and his army and their counts are forty-one thousand five hundred.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		And the tribe of Naphtali. And the chieftain of the children of
Naphtali is Ahira son of Enan,

[image]\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		and his army and their counts are fifty-three thousand four hundred.

[image]\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		All the counts of Dan’s camp are one hundred fifty-seven thousand six
hundred. They shall travel last, by their flags.”

[image]\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		These are the counts of the children of Israel by their fathers’
house, all the counts of the camps by their armies: six hundred three
thousand five hundred fifty.

[image]\\
	}
}
{
}

\Verse{33}
{
	\hP{}
}
{
	\eP{
		And the Levites were not counted among the children of Israel, as YHWH
had commanded Moses.

[image]\\
	}
}
{
}

\Verse{34}
{
	\hP{}
}
{
	\eP{
		And the children of Israel did according to all that YHWH commanded
Moses. So they camped by their flags, and so they traveled, each by his
families, by his fathers’ house.

[image]\\
	}
}
{
}

