\Chapter{3}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		3

¹ These are the records of Aaron and Moses in the day YHWH spoke to Moses
in Mount Sinai.

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		And these are the names of Aaron’s sons: the firstborn Nadab, and Abihu
and Eleazar and Ithamar.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		These are the names of Aaron’s sons, the anointed priests, who filled
their hand to function as priests.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And Nadab and Abihu died in front of YHWH when they brought forward
unfitting fire in front of YHWH in the wilderness of Sinai, and they had
no sons; and Eleazar and Ithamar functioned as priests in front of
Aaron, their father.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		“Bring forward the tribe of Levi and stand it in front of Aaron, the
priest, so they will attend to him.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And they shall keep his charge and the charge of all the congregation
in front of the Tent of Meeting, to do the work of the Tabernacle.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And they shall keep all the equipment of the Tent of Meeting and the
charge of the children of Israel, to do the work of the Tabernacle.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And you shall give the Levites to Aaron and to his sons. They are
given—given—to him from the children of Israel.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And you shall appoint Aaron and his sons, that they shall keep their
priesthood, and an outsider who comes close shall be put to death.”

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		“And I, here, I have taken the Levites from among the children of
Israel in place of every firstborn, the first birth of the womb, from
the children of Israel. And the Levites shall be mine.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		Because every firstborn is mine. In the day that I struck every
firstborn in the land of Egypt, I consecrated every firstborn in Israel
to me, from human to animal. They shall be mine. I am YHWH.”

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses in the wilderness of Sinai, saying,

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		“Count the children of Levi by their fathers’ house, by their
families. You shall count them: every male from a month old and up.”

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And Moses counted them by YHWH’s word as he was commanded.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And these were Levi’s sons by their names: Gershon and Kohath and
Merari.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And these are the names of Gershon’s sons by their families: Libni and
Shimei.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And Kohath’s sons by their families: Amram and Izhar, Hebron and
Uzziel.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And Merari’s sons by their families: Mahli and Mushi. These are the
Levite families by their fathers’ house.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		Gershon had the Libnite family and the Shimeite family. These are the
Gershonite families.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		Their counts by the number of every male from a month old and up:
their counts were seven thousand five hundred.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		The Gershonite families were to camp behind the Tabernacle, to the
west.

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		And the chieftain of the Gershonite father’s house was Eliasaph son of
Lael.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And the charge of the sons of Gershon in the Tent of Meeting was the
Tabernacle and the tent, its covering and the cover of the entrance of
the Tent of Meeting

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		and the courtyard’s hangings and the cover for the entrance of the
courtyard that is all around the Tabernacle and the altar, and its
cords, for all of its service.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		And Kohath had the Amramite family and the Izharite family and the
Hebronite family and the Uzzielite family. These are the Kohathite
families.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		By the number of every male from a month old and up: eight thousand
six hundred keeping the charge of the Holy.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		The families of the children of Kohath were to camp to the south.

[image]\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		And the chieftain of the father’s house for the Kohathite families was
Elizaphan son of Uzziel.

[image]\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		And their charge was the ark and the table and the menorah and the
altars and the equipment of the Holy with which they minister and the
cover and all of its service.

[image]

3:31; menorah. The lampstand has been compared in appearance—and as a
symbol—to a tree, and especially to the tree of life. It is therefore
notable that it is mentioned here as being the responsibility of the
Kohathites. And then just a few verses later the Kohathites are
identified as the Levite group who must be careful that their closeness
to the holy not cause them to die (see the comment on 4:15). The
menorah, the sacred object, which became a symbol of Israel (more
properly so than the six-pointed star that became a symbol some two
thousand years after this text), is also a reminder of the essential
human relationship to life and death that begins the Torah.\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		And the chieftain of chieftains of the Levites was Eleazar son of
Aaron, the priest, with responsibility for those who keep the charge of
the Holy.

[image]\\
	}
}
{
}

\Verse{33}
{
	\hP{}
}
{
	\eP{
		And Merari had the Mahlite family and the Mushite family. These are
the Merarite families.

[image]\\
	}
}
{
}

\Verse{34}
{
	\hP{}
}
{
	\eP{
		And their counts by the number of every male from a month old and up:
six thousand two hundred.

[image]\\
	}
}
{
}

\Verse{35}
{
	\hP{}
}
{
	\eP{
		And the chieftain of the father’s house for the Merarite families was
Zuriel son of Abihail. They were to camp on the side of the Tabernacle
to the north.

[image]\\
	}
}
{
}

\Verse{36}
{
	\hP{}
}
{
	\eP{
		And the responsibility of the charge of the children of Merari was the
Tabernacle’s frames and its bars and its columns and its bases and all
of its equipment and all of its service

[image]\\
	}
}
{
}

\Verse{37}
{
	\hP{}
}
{
	\eP{
		and the courtyard’s columns all around and their bases and their pegs
and their cords.

[image]\\
	}
}
{
}

\Verse{38}
{
	\hP{}
}
{
	\eP{
		And those who camped in front of the Tabernacle, on the east, in front
of the Tent of Meeting, to the east, were Moses and Aaron and his sons,
keeping the charge of the holy place, for the charge of the children of
Israel. And the outsider who will come close shall be put to death.

[image]\\
	}
}
{
}

\Verse{39}
{
	\hP{}
}
{
	\eP{
		All the counts of the Levites that Moses and Aaron made by YHWH’s
word, by their families, every male from a month old and up were
twenty-two thousand.

[image]\\
	}
}
{
}

\Verse{40}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Moses, “Count every male firstborn of the children of
Israel from a month old and up, and add up the number of their names.

[image]\\
	}
}
{
}

\Verse{41}
{
	\hP{}
}
{
	\eP{
		And you shall take the Levites for me—I am YHWH—in place of every
firstborn in the children of Israel, and the Levites’ animals in place
of every firstborn in the animals of the children of Israel.”

[image]\\
	}
}
{
}

\Verse{42}
{
	\hP{}
}
{
	\eP{
		And Moses counted, as YHWH commanded him, every firstborn in the
children of Israel.

[image]\\
	}
}
{
}

\Verse{43}
{
	\hP{}
}
{
	\eP{
		And every male firstborn, by the number of names, from a month old and
up, by their counts were twenty-two thousand two hundred seventy-three.

[image]\\
	}
}
{
}

\Verse{44}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{45}
{
	\hP{}
}
{
	\eP{
		“Take the Levites in place of every firstborn in the children of
Israel, and the Levites’ animals in place of their animals, and the
Levites shall be mine. I am YHWH.

[image]\\
	}
}
{
}

\Verse{46}
{
	\hP{}
}
{
	\eP{
		And for the redemption of the two hundred seventy-three who are left
over above the Levites from the firstborn of the children of Israel,

[image]\\
	}
}
{
}

\Verse{47}
{
	\hP{}
}
{
	\eP{
		you shall take five shekels each per head; you shall take it by the
shekel of the Holy. (The shekel is twenty gerah.)

[image]\\
	}
}
{
}

\Verse{48}
{
	\hP{}
}
{
	\eP{
		And you shall give the money to Aaron and to his sons for the
redemption of those left over among them.”

[image]\\
	}
}
{
}

\Verse{49}
{
	\hP{}
}
{
	\eP{
		And Moses took the money of the redemption from those left over above
those who were redeemed by the Levites.

[image]\\
	}
}
{
}

\Verse{50}
{
	\hP{}
}
{
	\eP{
		He took the money from the firstborn of the children of Israel: one
thousand three hundred sixty-five by the shekel of the Holy.

[image]\\
	}
}
{
}

\Verse{51}
{
	\hP{}
}
{
	\eP{
		And Moses gave the money for those who were redeemed to Aaron and to
his sons by YHWH’s word, as YHWH commanded Moses.

[image]\\
	}
}
{
}

