\Chapter{4}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		4

¹ And YHWH spoke to Moses and to Aaron, saying,

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Add up the heads of the children of Kohath from among the children of
Levi by their families, by their fathers’ house,

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		from thirty years old and up to fifty years old, everyone who would
come to the army to do work in the Tent of Meeting.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		This is the work of the sons of Kohath in the Tent of Meeting: the Holy
of Holies.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		“And Aaron and his sons shall come when the camp is to travel, and they
shall take down the covering pavilion and cover the ark of the testimony
with it.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And they shall put a cover of leather and shall spread a fabric all of
blue above it and put in its poles.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And on the table of show bread they shall spread a blue fabric, and
they shall put on it the dishes and the pans and the bowls and the
libation jars; and the continual bread shall be on it.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And they shall spread a scarlet fabric over them and cover it with a
leather covering and set its poles.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And they shall take a blue fabric and cover the menorah for lighting
and its lamps and its tongs and its fire-holders and all its equipment
for oil with which they will minister for it.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And they shall put it and all its equipment into a leather covering
and put it on a beam.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And on the gold altar they shall spread a blue fabric, and they shall
cover it with a leather covering and set its poles.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And they shall take all the equipment for ministering with which they
minister in the Holy and put them into a blue fabric and cover them with
a leather covering and put them on a beam.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And they shall clear the ashes from the altar and spread a purple
fabric over it.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And they shall put on it all its equipment with which they minister at
it—the fire-holders, the forks and the shovels and the basins—all the
altar’s equipment, and they shall spread a leather covering on it and
set its poles.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And Aaron and his sons will finish covering the Holy and all the
equipment of the Holy when the camp is to travel, and after that the
children of Kohath shall come to carry, so they shall not touch the holy
and die. These are what the children of Kohath are to carry in the Tent
of Meeting.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		“And the responsibility of Eleazar son of Aaron, the priest, is the
oil for lighting and the incense of fragrances and the continual grain
offering and the anointing oil—the responsibility for all of the
Tabernacle and everything that is in it, in the Holy and in its
equipment.”

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses and to Aaron, saying,

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		“You shall not cut off the tribe of the Kohathite families from among
the Levites,

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		but do this to them so they will live and not die when they come close
to the Holy of Holies: Aaron and his sons shall come, and they shall set
them each at his work and to what he is to carry,

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		and they shall not come to see as the Holy is covered up and die.”

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		ADD UP

²¹ And YHWH spoke to Moses, saying,

[image]

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		“Add up the heads of the children of Gershon, them as well, by their
fathers’ house, by their families.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		You shall count them from thirty years old and up to fifty years old,
everyone who would come to do army service, to do work in the Tent of
Meeting.

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		This is the work of the Gershonite families, for work and for
carrying:

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And they shall carry the curtains of the Tabernacle, and the Tent of
Meeting, its covering, and the leather covering that is on it above, and
the cover of the entrance of the Tent of Meeting

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		and the courtyard’s hangings and the cover for the entrance of the
gate of the courtyard that is all around the Tabernacle and the altar,
and their cords and all the equipment for their service. And everything
that will be done for them: they shall do the work.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		All the work of the children of the Gershonites shall be by the word
of Aaron and his sons, for all their carrying and all their work. And
you shall supervise them in the task: all their carrying.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		This is the work of the families of the children of the Gershonites in
the Tent of Meeting. And their charge is in the hand of Ithamar son of
Aaron, the priest.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		“The children of Merari by their families, by their fathers’ house:
you shall count them.

[image]\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		You shall count them from thirty years old and up to fifty years old,
everyone who would come to the army, to do the work of the Tent of
Meeting.

[image]\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		And this is their carrying task, for all their work in the Tent of
Meeting: the Tabernacle’s frames and its bars and its columns and its
bases

[image]\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		and the courtyard’s columns all around and their bases and their pegs
and their cords, for all their equipment and all their service. And you
shall take account of the equipment for their carrying task by name.

[image]\\
	}
}
{
}

\Verse{33}
{
	\hP{}
}
{
	\eP{
		This is the work of the families of the children of Merari, for all
their work in the Tent of Meeting in the hand of Ithamar son of Aaron,
the priest.”

[image]\\
	}
}
{
}

\Verse{34}
{
	\hP{}
}
{
	\eP{
		And Moses and Aaron and the congregation’s chieftains counted the
Kohathite children by their families and by their fathers’ house

[image]\\
	}
}
{
}

\Verse{35}
{
	\hP{}
}
{
	\eP{
		from thirty years old and up to fifty years old, everyone who would
come to the army for the work of the Tent of Meeting.

[image]\\
	}
}
{
}

\Verse{36}
{
	\hP{}
}
{
	\eP{
		And their counts by their families were two thousand seven hundred
fifty.

[image]\\
	}
}
{
}

\Verse{37}
{
	\hP{}
}
{
	\eP{
		These are the counts of the Kohathite families, everyone who worked in
the Tent of Meeting, whom Moses and Aaron counted by YHWH’s word through
Moses’ hand.

[image]\\
	}
}
{
}

\Verse{38}
{
	\hP{}
}
{
	\eP{
		And the counts of the children of Gershon by their families and by
their fathers’ house

[image]\\
	}
}
{
}

\Verse{39}
{
	\hP{}
}
{
	\eP{
		from thirty years old and up to fifty years old, everyone who would
come to the army for work in the Tent of Meeting:

[image]\\
	}
}
{
}

\Verse{40}
{
	\hP{}
}
{
	\eP{
		And their counts by their families, by their fathers’ house, were two
thousand six hundred thirty.

[image]\\
	}
}
{
}

\Verse{41}
{
	\hP{}
}
{
	\eP{
		These are the counts of the families of the children of Gershon,
everyone who worked in the Tent of Meeting, whom Moses and Aaron counted
by YHWH’s word.

[image]\\
	}
}
{
}

\Verse{42}
{
	\hP{}
}
{
	\eP{
		And the counts of the families of the children of Merari by their
families, by their fathers’ house

[image]\\
	}
}
{
}

\Verse{43}
{
	\hP{}
}
{
	\eP{
		from thirty years old and up to fifty years old, everyone who would
come to the army for work in the Tent of Meeting:

[image]\\
	}
}
{
}

\Verse{44}
{
	\hP{}
}
{
	\eP{
		And their counts by their families were three thousand two hundred.

[image]\\
	}
}
{
}

\Verse{45}
{
	\hP{}
}
{
	\eP{
		These are the counts of the families of the children of Merari whom
Moses and Aaron counted by YHWH’s word through Moses’ hand.

[image]\\
	}
}
{
}

\Verse{46}
{
	\hP{}
}
{
	\eP{
		All the counts that Moses and Aaron and Israel’s chieftains made of
the Levites by their families and by their fathers’ house

[image]\\
	}
}
{
}

\Verse{47}
{
	\hP{}
}
{
	\eP{
		from thirty years old and up to fifty years old, everyone who was
coming to do the service of work and the service of carrying in the Tent
of Meeting:

[image]\\
	}
}
{
}

\Verse{48}
{
	\hP{}
}
{
	\eP{
		And their counts were eight thousand five hundred eighty.

[image]\\
	}
}
{
}

\Verse{49}
{
	\hP{}
}
{
	\eP{
		By YHWH’s word he counted them by Moses’ hand, each man by his work or
by his carrying, and his counts were as YHWH commanded Moses.

[image]\\
	}
}
{
}

