\Chapter{5}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		5

¹ And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Command the children of Israel that they shall have every leper and
everyone who has an emission and everyone who is impure by a person go
from the camp.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		Male or female, you shall have them go; you shall have them go outside
the camp so they will not make their camps, among which I tent, impure.”

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And the children of Israel did so, and they had them go outside the
camp. As YHWH spoke to Moses, so the children of Israel did.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel: A man or a woman—when they will do
any of the sins of humans, to make a breach against YHWH—so that person
has guilt,

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		then they shall confess their sin that they have done. And he shall pay
back for his guilt with its principal, and he shall add to it a fifth of
it, and he shall give it to the one whom he wronged.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And if the man does not have a redeemer, to pay him back for the guilt,
the guilt that is paid back is YHWH’s, for the priest, apart from the
ram of atonement by which he will make atonement for him.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And every donation of all the holy things of the children of Israel
that they will bring forward to the priest shall be his.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And each man’s holy things shall be his; what each man gives to the
priest shall be his.”

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel, and you shall say to them: Any man
whose wife will go astray and will make a breach of faith with him,

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		and a man has lain with her—an intercourse of seed—and it has been
hidden from her husband’s eyes, and she has kept concealed, and she has
been made impure, and there is no witness against her, and she has not
been caught,

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		and a spirit of jealousy has come over him, and he is jealous about
his wife, and she has been made impure, or a spirit of jealousy has come
over him, and he is jealous about his wife, and she has not been made
impure:

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		then the man shall bring his wife to the priest and shall bring her
offering along with her: a tenth of an ephah of barley flour. He shall
not pour oil on it and shall not put frankincense on it, because it is
an offering about jealousies, an offering of bringing to mind: causing a
crime to be brought to mind.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		“And the priest shall bring her forward and stand her in front of
YHWH.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And the priest shall take holy water in a clay container, and the
priest shall take some of the dust that will be on the Tabernacle’s
floor and put it into the water.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And the priest shall stand the woman in front of YHWH and loosen the
hair of the woman’s head and put the offering of bringing to mind on her
hands; it is an offering of jealousies. And in the priest’s hand shall
be the bitter cursing water.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And the priest shall have her swear, and he shall say to the woman:
‘If a man has not lain with you, and if you have not gone astray in
impurity with someone in place of your husband, be cleared by this
bitter cursing water.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		But you, if you have gone astray with someone in place of your husband
and if you have been made impure, and if a man other than your husband
has had his intercourse with you,’

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		then the priest shall have the woman swear a curse oath, and the
priest shall say to the woman, ‘let YHWH make you a curse and an oath
among your people when YHWH sets your thigh sagging and your womb
swelling,

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		and this cursing water will come in your insides, to swell the womb
and make the thigh sag.’

“And the woman shall say, ‘Amen, amen.’

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		“And the priest shall write these curses in a scroll and rub them into
the bitter water.

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		And he shall have the woman drink the bitter cursing water, and the
bitter cursing water will come into her.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And the priest shall take the offering of jealousies from the woman’s
hand and elevate the offering in front of YHWH, and he shall bring her
forward to the altar.

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		And the priest shall take a fistful from the grain offering, a
representative portion of it, and burn it to smoke at the altar, and
after that he shall have the woman drink the water.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		When he has had her drink the water, then it will be, if she has been
made impure and has made a breach of faith with her husband, when the
bitter cursing water will come into her, and her womb will swell and her
thigh will sag, then the woman will become a curse among her people.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		And if the woman has not been made impure, and she is pure, then she
shall be cleared and shall conceive seed.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		“This is the instruction for jealousies, when a woman will go astray
with someone in place of her husband and be made impure,

[image]\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		or when a spirit of jealousy will come over a man and he will be
jealous about his wife. And the priest shall stand the woman in front of
YHWH and do all of this instruction to her.

[image]\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		And the man shall be clear of a crime, and that woman shall bear her
crime.”

[image]\\
	}
}
{
}

