\Chapter{6}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		6

¹ And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel, and you shall say to them: When a man
or a woman will expressly make a Nazirite vow to make a separation for
YHWH,

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		he shall separate from wine and beer; he shall not drink any vinegar of
wine or vinegar of beer, and he shall not drink any juice of grapes, and
he shall not eat fresh or dried grapes.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		All the days of his being a Nazirite, he shall not eat anything that is
made from the grapevine, from seeds to skin.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		All the days of his Nazirite vow, a razor shall not pass on his head;
until the fulfillment of the days that he will make a separation for
YHWH, he shall be holy, growing the hair of his head loose.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		All the days of his making a separation for YHWH he shall not come to a
dead person.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		For his father and for his mother, for his brother and for his sister:
he shall not become impure for them when they die, because the crown of
his God is on his head.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		All the days of his being a Nazirite he is holy to YHWH.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And if someone will die by chance suddenly by him and will make his
head’s crown impure, then he shall shave his head on the day of his
purification: he shall shave it on the seventh day.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And on the eighth day he shall bring two turtledoves or two pigeons to
the priest, to the entrance of the Tent of Meeting.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And the priest shall do one as a sin offering and one as a burnt
offering and shall make atonement over him in that he has sinned over a
person. And he shall make his head holy on that day.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And he shall make a separation for YHWH for the days of his being a
Nazirite, and he shall bring a lamb in its first year for a guilt
offering, and the first days shall fall because his Nazirite state
became impure.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		“And this is the instruction for the Nazirite: On the day of the
fulfillment of the days of his being a Nazirite one shall bring him to
the entrance of the Tent of Meeting.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And he shall make his offering to YHWH: one unblemished lamb in its
first year for a burnt offering and one unblemished ewe-lamb in its
first year for a sin offering and one unblemished ram for a peace
offering

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		and a basket of unleavened bread of fine flour, cakes mixed with oil
and unleavened wafers with oil poured on them with their grain offering
and their libations.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And the priest shall bring it forward in front of YHWH and shall do
his sin offering and his burnt offering.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And he shall make the ram a peace-offering sacrifice to YHWH with the
basket of unleavened bread, and the priest shall do his grain offering
and his libation.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And the Nazirite shall shave his head’s crown at the entrance of the
Tent of Meeting and shall take the hair of his head’s crown and put it
on the fire that is under the peace-offering sacrifice.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And the priest shall take the cooked shoulder from the ram and one
unleavened cake from the basket and one unleavened wafer and put them on
the Nazirite’s hands after his crown is shaved.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And the priest shall elevate them, an elevation offering in front of
YHWH. It is holy for the priest along with the breast of the elevation
offering and the thigh of the donation. And after that the Nazirite may
drink wine.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		This is the instruction for the Nazirite who will vow his offering to
YHWH for his being a Nazirite outside of what his hand may attain.
According to his vow that he will make, so he shall do along with the
instruction of his being a Nazirite.”

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		“Speak to Aaron and to his sons, saying, This is how you shall bless
the children of Israel; say to them:

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		May YHWH bless you and watch over you.

[image]

------------------------------------------------------------------------\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		May YHWH make His face shine to you and be gracious to you.

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		May YHWH raise His face to you and give you peace.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		And they shall set my name on the children of Israel, and I shall
bless them.”

[image]\\
	}
}
{
}

