\Chapter{8}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Speak to Aaron, and you shall say to him: ‘When you put up the lamps,
the seven lamps shall shed light opposite the front of the menorah.’”

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And Aaron did so. He put up its lamps opposite the front of the menorah
as YHWH had commanded Moses.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And this was the menorah’s construction: hammered work of gold;
including its shaft, including its flower, it was hammered work.
According to the appearance that YHWH had shown Moses, so he made the
menorah.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		“Take the Levites from among the children of Israel, and make them
pure.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And this is what you shall do to them to make them pure: you shall
sprinkle water of sin expiation on them, and they shall pass a razor
over all of their flesh, and they shall wash their clothes, and so they
will be made pure.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And they shall take a bull of the cattle and its grain offering, fine
flour mixed with oil; and you shall take a second bull of the cattle for
a sin offering.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And you shall bring the Levites forward in front of the Tent of
Meeting, and you shall assemble all of the congregation of the children
of Israel.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And you shall bring the Levites forward in front of YHWH, and the
children of Israel shall lay their hands on the Levites.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And Aaron shall make the Levites an elevation offering in front of
YHWH from the children of Israel, and they shall be to do YHWH’s
service.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And the Levites shall lay their hands on the bulls’ heads. And make
one a sin offering and one a burnt offering for YHWH to make atonement
for the Levites.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And you shall stand the Levites in front of Aaron and in front of his
sons and make them an elevation offering for YHWH.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And you shall distinguish the Levites from among the children of
Israel, and the Levites shall be mine.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And after that the Levites shall come to work at the Tent of Meeting,
when you have made them pure and made them an elevation offering.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		Because they are given, given, to me from among the children of
Israel. I have taken them to me in place of the first birth of every
womb, the firstborn of everyone from the children of Israel.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		Because every firstborn of the children Israel is mine, of human and
of animal; on the day that I struck every firstborn in the land of Egypt
I consecrated them to me.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And I took the Levites in place of every firstborn of the children of
Israel

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		and gave the Levites—they are given—to Aaron and to his sons from
among the children of Israel to do the work of the children of Israel in
the Tent of Meeting and to make atonement for the children of Israel, so
there will not be a plague in the children of Israel when the children
of Israel would come near to the Holy.”

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And Moses and Aaron and all the congregation of the children of Israel
did to the Levites according to all that YHWH commanded Moses about the
Levites; the children of Israel did so to them.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And the Levites did sin expiation and washed their clothes, and Aaron
made them an elevation offering in front of YHWH, and Aaron made
atonement for them to make them pure.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And after that the Levites came to do their work in the Tent of
Meeting in front of Aaron and in front of his sons. As YHWH commanded
Moses about the Levites, so they did to them.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		“This is what the Levites have: from twenty-five years old and up each
shall come to do army service by the work of the Tent of Meeting;

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		and from fifty years old he shall go back from the army service and
shall not work anymore;

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		and he shall minister with his brothers in the Tent of Meeting to keep
the charge, but he shall not do work. You shall do thus to the Levites
regarding their charge.”

[image]\\
	}
}
{
}

