\Chapter{9}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		9

¹ And YHWH had spoken to Moses in the wilderness of Sinai in the second
year of their exodus from the land of Egypt, in the first month, saying,

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“And the children of Israel shall do the Passover at its appointed
time.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		On the fourteenth day in this month ‘between the two evenings’ you
shall do it at its appointed time. You shall do it according to all of
its law and according to all of its judgments.”

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And Moses had spoken to the children of Israel to do the Passover,

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		and they had done the Passover in the first month on the fourteenth day
of the month “between the two evenings” in the wilderness of Sinai.
According to all that YHWH had commanded Moses, so the children of
Israel had done.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And there had been people who were impure by a human being and so had
not been able to do the Passover on that day, and they had come forward
in front of Moses and in front of Aaron on that day,

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		and those people had said to him, “We’re impure by a human being. Why
should we be excluded so as not to make YHWH’s offering at its appointed
time among the children of Israel?”

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And Moses had said, “Stay, and let me hear what YHWH will command about
you.”

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And YHWH had spoken to Moses, saying,

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel, saying: Any man who will be impure
by a person or on a faraway journey—among you or through your
generations—and will do the Passover for YHWH,

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		they shall do it in the second month on the fourteenth day ‘between
the two evenings.’ They shall eat it with unleavened bread and bitter
herbs.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		They shall not leave any of it until morning, and they shall not break
a bone of it. They shall do it according to all of the law of the
Passover.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		But a man who is pure and has not been on a journey and has failed to
do the Passover: that person will be cut off from his people, because he
did not make YHWH’s offering at its appointed time. That man shall bear
his sin.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And if an alien will reside with you and will do the Passover for
YHWH: according to the law of the Passover and according to its required
manner, so he shall do it. You shall have one law, for the alien and for
the citizen of the land.”

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And on the day that the Tabernacle was set up, the cloud covered the
Tabernacle of the tent of the Testimony, and in the evening it would be
over the Tabernacle like the appearance of fire until morning.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		So it would be always: the cloud would cover it and the appearance of
fire at night.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And according to when the cloud was lifted from over the tent, after
that the children of Israel would travel. And in a place where the cloud
would tent, the children of Israel would camp there.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		By YHWH’s word the children of Israel would travel, and by YHWH’s word
they would camp. All the days that the cloud would tent over the
Tabernacle they would camp.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And when the cloud would extend many days over the Tabernacle, then
the children of Israel kept YHWH’s charge and would not travel.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And there were times that the cloud would be over the Tabernacle for a
number of days: by YHWH’s word they would camp, and by YHWH’s word they
would travel.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And there were times that the cloud would be there from evening until
morning, and the cloud was lifted in the morning, and then they would
travel; or for a day and a night, and the cloud was lifted, and then
they traveled.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		Whether two days or a month or a year, when the cloud would extend
long over the Tabernacle, to tent over it, the children of Israel would
camp and would not travel, and when it was lifted they would travel.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		By YHWH’s word they would camp, and by YHWH’s word they would travel.
They kept YHWH’s charge, by YHWH’s word through Moses’ hand.

[image]\\
	}
}
{
}

