\Chapter{10}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		10

¹ And YHWH spoke to Moses, saying,

[image]

------------------------------------------------------------------------

Numbers 10:2

²“Make two trumpets of silver. You shall make them hammered work. And
you shall have them for calling the congregation and for having the
camps travel.

------------------------------------------------------------------------

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And when they will blow them, then all the congregation shall be
gathered to you, to the entrance of the Tent of Meeting.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And if they will blow with one, then the chieftains, the heads of
thousands of Israel shall be gathered to you.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And when you will blow a blasting sound, then the camps that are
camping on the east shall travel.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And when you will blow a second blasting sound, then the camps that are
camping on the west shall travel. They shall blow a blasting sound for
their travels.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And for assembling the community you shall blow, but you shall not make
a blast.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And the sons of Aaron, the priests, shall blow the trumpets; and they
shall be an eternal law for you through your generations.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And when you will go to war in your land against a foe who afflicts
you, then you shall blast the trumpets, and you will be brought to mind
in front of YHWH, your God, and you will be saved from your enemies.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And on your happy occasion and at your appointed times and on your new
moons, you shall blow the trumpets over your burnt offerings and over
your peace-offering sacrifices, and they shall be for a commemoration
for you in front of your God. I am YHWH, your God.”

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And it was in the second year, in the second month, on the twentieth
of the month that the cloud was lifted from over the Tabernacle of the
Testimony.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And the children of Israel set out on their travels from the
wilderness of Sinai. And the cloud tented in the wilderness of Paran.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And they traveled from the first by YHWH’s word through Moses’ hand.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And the flag of the camp of the children of Judah traveled first by
their armies, and over its army was Nahshon son of Amminadab.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And over the army of the tribe of the children of Issachar was
Nethanel son of Zuar.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And over the army of the tribe of the children of Zebulun was Eliab
son of Helon.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And the Tabernacle was taken down; and the children of Gershon and the
children of Merari, who carried the Tabernacle, traveled.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And the flag of Reuben’s camp by their armies traveled, and over its
army was Elizur son of Shedeur.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And over the army of the tribe of the children of Simeon was Shelumiel
son of Zurishadday.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And over the army of the tribe of the children of Gad was Eliasaph son
of Deuel.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And the Kohathites, who carried the holy place, traveled; and they set
up the Tabernacle by the time they came.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And the flag of the camp of the children of Ephraim by their armies
traveled, and over its army was Elishama son of Ammihud.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		And over the army of the tribe of the children of Manasseh was
Gamaliel son of Pedahzur.

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		And over the army of the tribe of the children of Benjamin was Abidan
son of Gideoni.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And the flag of the camp of the children of Dan, the final one of all
the camps, by their armies, traveled, and over its army was Ahiezer son
of Ammishadday.

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		And over the army of the tribe of the children of Asher was Pagiel son
of Ochran.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		And over the army of the tribe of the children of Naphtali was Ahira
son of Enan.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		These were the orders of travel of the children of Israel by their
armies when they traveled.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hJ{}
}
{
	\eJ{
		And Moses said to Hobab, the son of Reuel the Midianite, Moses’
father-in-law, “We’re traveling to the place that YHWH said, ‘I’ll give
it to you.’ Come with us, and we’ll be good to you, because YHWH has
spoken of good regarding Israel.”

[image]\\
	}
}
{
}

\Verse{30}
{
	\hJ{}
}
{
	\eJ{
		And he said to him, “I won’t go, but rather I’ll go to my land and to
my birthplace.”

[image]\\
	}
}
{
}

\Verse{31}
{
	\hJ{}
}
{
	\eJ{
		And he said, “Don’t leave us, because you know the way we should camp
in the wilderness, and you’ll be eyes for us.

[image]\\
	}
}
{
}

\Verse{32}
{
	\hJ{}
}
{
	\eJ{
		And it will be, when you go with us, that we’ll do good for you in
proportion to the good that YHWH will do for us.”

[image]\\
	}
}
{
}

\Verse{33}
{
	\hJ{}
}
{
	\eJ{
		And they traveled from the mountain of YHWH three days’ journey. And
the ark of the covenant of YHWH traveled in front of them three days’
journey to scout a resting place for them.

[image]\\
	}
}
{
}

\Verse{34}
{
	\hJ{}
}
{
	\eJ{
		And YHWH’s cloud was over them by day as they traveled from the camp.

[image]\\
	}
}
{
}

\Verse{35}
{
	\hJ{}
}
{
	\eJ{
		And it was, when the ark traveled, that Moses said, “Arise, YHWH, and
let your enemies be scattered, and let those who hate you flee from your
presence,”

[image]\\
	}
}
{
}

\Verse{36}
{
	\hJ{}
}
{
	\eJ{
		and when it rested, he said, “Come back, YHWH, the ten thousands of
thousands of Israel.”

[image]\\
	}
}
{
}

