\Chapter{11}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		11

¹ And the people were like grumblers, bad in YHWH’s ears, and YHWH heard,
and His anger flared, and a fire of YHWH burned among them and consumed
at the edge of the camp.

[image]\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		And the people cried out to Moses, and Moses prayed to YHWH, and the
fire subsided.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		And he called that place’s name Taberah because a fire of YHWH burned
among them.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hRJE{}
}
{
	\eRJE{
		And the gathered mass who were among them had a longing, and the
children of Israel, as well, went back and cried, and they said, “Who
will feed us meat?

[image]\\
	}
}
{
}

\Verse{5}
{
	\hRJE{}
}
{
	\eRJE{
		We remember the fish that we would eat in Egypt for free: the cucumbers
and the melons and the leek and the onions and the garlics.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hRJE{}
}
{
	\eRJE{
		And now, our soul is dried up. There isn’t anything—except the manna
before our eyes.”

[image]\\
	}
}
{
}

\Verse{7}
{
	\hRJE{}
}
{
	\eRJE{
		And the manna: it was like a seed of coriander, and its appearance was
like the appearance of bdellium.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hRJE{}
}
{
	\eRJE{
		The people went around and collected and ground it in mills or pounded
it in a mortar and cooked it in a pot and made it into cakes. And its
taste was like the taste of something creamy made with oil.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hRJE{}
}
{
	\eRJE{
		And when the dew descended on the camp at night, the manna would
descend on it.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses heard the people crying by their families, each at his tent
entrance, and YHWH’s anger flared very much, and it was bad in Moses’
eyes.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses said to YHWH, “Why have you done bad to your servant, and
why have I not found favor in your eyes, to set the burden of this
entire people on me?

[image]\\
	}
}
{
}

\Verse{12}
{
	\hRJE{}
}
{
	\eRJE{
		Did I conceive this entire people? Did I give birth to it, that you
should say to me, ‘Carry it in your bosom,’ the way a nurse carries a
suckling, to the land that you swore to its fathers?

[image]\\
	}
}
{
}

\Verse{13}
{
	\hRJE{}
}
{
	\eRJE{
		From where do I have meat to give to this entire people, that they cry
at me, saying, ‘Give us meat, and let’s eat’?

[image]\\
	}
}
{
}

\Verse{14}
{
	\hRJE{}
}
{
	\eRJE{
		I’m not able, I, by myself, to carry this entire people, because it’s
too heavy for me.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hRJE{}
}
{
	\eRJE{
		And if this is how you treat me, kill me, if I’ve found favor in your
eyes, and let me not see my suffering.”

[image]\\
	}
}
{
}

\Verse{16}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH said to Moses, “Gather to me seventy men from Israel’s elders
whom you’ve known because they’re the people’s elders and its officers,
and you’ll take them to the Tent of Meeting, and they’ll stand up there
with you.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hRJE{}
}
{
	\eRJE{
		And I’ll come down and speak with you there, and I’ll take some of the
spirit that is on you, and I’ll set it on them, and they’ll carry the
burden of the people with you, and you won’t bear it, you, by yourself.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hRJE{}
}
{
	\eRJE{
		And you shall say to the people, ‘Consecrate yourselves for tomorrow,
and you’ll eat meat, because you cried in YHWH’s ears saying: Who will
feed us meat, because we had it good in Egypt. And YHWH will give you
meat, and you’ll eat.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hRJE{}
}
{
	\eRJE{
		You’ll eat not for one day and not two days and not five days and not
ten days and not ten days and not twenty days.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hRJE{}
}
{
	\eRJE{
		Until a month of days! Until it will come out of your nose, and it
will be a revulsion to you! Because you rejected YHWH, who was among
you, and you cried in front of him, saying: Why is this that we went out
from Egypt?’”

[image]\\
	}
}
{
}

\Verse{21}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses said, “The people among whom I am are six hundred thousand
on foot, and you’ve said, ‘I’ll give them meat, and they’ll eat for a
month of days!’

[image]\\
	}
}
{
}

\Verse{22}
{
	\hRJE{}
}
{
	\eRJE{
		Will flock and herd be slaughtered for them, and would it provide for
them? Or will all the sea’s fish be gathered for them, and would it
provide for them?”

[image]\\
	}
}
{
}

\Verse{23}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH said to Moses, “Is YHWH’s hand getting short?! Now you’ll see
if my word happens to you or not.”

[image]\\
	}
}
{
}

\Verse{24}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses went out and spoke YHWH’s words to the people. And he
gathered seventy men from the people’s elders, and he stood them around
the tent.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH came down in a cloud and spoke to him and took some of the
spirit that was on him and put it on the seventy men of the elders. And
it was when the spirit rested on them: and they prophesied. Then they
did not do it anymore.

[image]\\
	}
}
{
}

\Verse{26}
{
	\hRJE{}
}
{
	\eRJE{
		And two men had been left in the camp. One’s name was Eldad, and the
second’s name was Medad. And the spirit rested on them. And they were
among the ones who were written, but they did not go out to the tent,
and they prophesied in the camp.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hRJE{}
}
{
	\eRJE{
		And a boy ran and told Moses, and he said, “Eldad and Medad are
prophesying in the camp!”

[image]\\
	}
}
{
}

\Verse{28}
{
	\hRJE{}
}
{
	\eRJE{
		And Joshua, son of Nun, Moses’ attendant from his chosen ones,
answered, and he said, “My lord Moses, restrain them!”

[image]\\
	}
}
{
}

\Verse{29}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses said to him, “Are you jealous for me? And who would make it
so that all of YHWH’s people were prophets, that YHWH would put His
spirit on them!”

[image]\\
	}
}
{
}

\Verse{30}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses was gathered back to the camp, he and Israel’s elders.

[image]\\
	}
}
{
}

\Verse{31}
{
	\hRJE{}
}
{
	\eRJE{
		And a wind traveled from YHWH and transported quails from the sea and
left them on the camp, about a day’s journey in one direction and about
a day’s journey in the other around the camp, and about two cubits on
the face of the earth.

[image]\\
	}
}
{
}

\Verse{32}
{
	\hRJE{}
}
{
	\eRJE{
		And the people got up all that day and all night and all the next day
and gathered the quail. The one who had the least gathered ten homers.
And they spread them out, spreading around the camp.

[image]\\
	}
}
{
}

\Verse{33}
{
	\hRJE{}
}
{
	\eRJE{
		And the meat was still between their teeth, not yet chewed, and YHWH’s
anger flared at the people, and YHWH struck at the people, a very great
strike.

[image]\\
	}
}
{
}

\Verse{34}
{
	\hRJE{}
}
{
	\eRJE{
		And he called that place’s name Kibroth Hattaavah, because they buried
the people who were longing there.

[image]\\
	}
}
{
}

\Verse{35}
{
	\hRJE{}
}
{
	\eRJE{
		From Kibroth Hattaavah the people traveled to Hazeroth, and they were
in Hazeroth.

[image]\\
	}
}
{
}

