\Chapter{12}

\Verse{1}
{
	\hE{}
}
{
	\eE{
		12

¹ And Miriam and Aaron spoke against Moses about the Cushite wife whom he
had taken—because he had taken a Cushite wife.

[image]\\
	}
}
{
}

\Verse{2}
{
	\hE{}
}
{
	\eE{
		And they said, “Has YHWH only just spoken through Moses? Hasn’t He also
spoken through us?”

And YHWH heard.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hE{}
}
{
	\eE{
		And the man Moses was very humble, more than every human who was on the
face of the earth.

[image]

[image]\\
	}
}
{
}

\Verse{4}
{
	\hE{}
}
{
	\eE{
		And YHWH said suddenly to Moses and to Aaron and to Miriam, “Go out,
the three of you, to the Tent of Meeting.” And the three of them went
out.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hE{}
}
{
	\eE{
		And YHWH came down in a column of cloud and stood at the entrance of
the tent. And He called, “Aaron and Miriam.” And the two of them went
out.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hE{}
}
{
	\eE{
		And He said, “Hear my words:

If there will be a prophet among you,

I, YHWH, shall be known to him in a vision;

in a dream I shall speak through him.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hE{}
}
{
	\eE{
		Not so is my servant Moses;

in all my house he is faithful.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hE{}
}
{
	\eE{
		Mouth to mouth I shall speak through him

and vision and not in enigmas,

and he will see the form of YHWH.

And why did you not fear to speak against my servant,

against Moses?”

[image]\\
	}
}
{
}

\Verse{9}
{
	\hE{}
}
{
	\eE{
		And YHWH’s anger flared against them, and He went.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		And the cloud turned from over the tent; and, here, Miriam was
leprous, like snow. And Aaron turned to Miriam, and, here, she was
leprous.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		And Aaron said to Moses, “In me, my lord. Don’t set a sin on us, which
we did foolishly and which we sinned.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		Let her not be like the dead who, when he comes out of his mother’s
womb, half of his flesh is eaten up!”

[image]\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		And Moses cried out to YHWH, saying, “Oh, God, heal her!”

[image]\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		And YHWH said to Moses, “And if her father had spit in her face,
wouldn’t she be humiliated seven days? Let her be closed up seven days
outside the camp, and after that let her be gathered back.”

[image]\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		And Miriam was closed up outside the camp seven days. And the people
did not travel until Miriam was gathered back, and after that the people
traveled from Hazeroth. And they camped in the Paran wilderness.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		[image]\\
	}
}
{
}

