\Chapter{13}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Send men and let them scout the land of Canaan that I’m giving to the
children of Israel. You shall send one man for each tribe of his
fathers, every one of them a chieftain.”

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And Moses sent them from the wilderness of Paran by YHWH’s word. They
were all men who were heads of the children of Israel.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And these are their names: For the tribe of Reuben, Shammua son of
Zaccur.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		For the tribe of Simeon, Shaphat son of Hori.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		For the tribe of Judah, Caleb son of Jephunneh.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		For the tribe of Issachar, Igal son of Joseph.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		For the tribe of Ephraim, Hoshea son of Nun.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		For the tribe of Benjamin, Palti son of Raphu.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		For the tribe of Zebulun, Gaddiel son of Sodi.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		For the tribe of Joseph: of the tribe of Manasseh, Gaddi son of Susi.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		For the tribe of Dan, Ammiel son of Gemalli.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		For the tribe of Asher, Sethur son of Michael.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		For the tribe of Naphtali, Nahbi son of Vophsi.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		For the tribe of Gad, Geuel son of Machi.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		These are the names of the men whom Moses sent to scout the land. And
Moses called Hoshea son of Nun Joshua.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hJ{}
}
{
	\eJ{
		And Moses sent them to scout the land of Canaan. And he said to them,
“Go up there in the Negeb, and you shall go up the mountain

[image]\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		and see the land, how it is; and the people who live on it, are they
strong or weak, are they few or many;

[image]\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		and how is the land in which they live, is it good or bad; and how are
the cities in which they live, are they in camps or in fortified places;

[image]\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		and how is the land, is it fat or meager; does it have trees or not;
and exert strength and take some fruit of the land.”

And it was the days of the first grapes.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		And they went up and scouted the land from the wilderness of Zin to
Rehob at the entrance of Hamath.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		And they went up in the Negeb and came to Hebron. And Ahiman, Sheshai,
and Talmai, the offspring of the giants, were there. (And Hebron was
built seven years before Zoan of Egypt.)

[image]\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		And they came to the Wadi Eshcol, and they cut a branch and one
cluster of grapes from there—and carried it on a pole by two people—and
some pomegranates and some figs.

[image]\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		That place was called Wadi Eshcol on account of the cluster that the
children of Israel cut from there.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hRJE{}
}
{
	\eRJE{
		And they came back from scouting the land at the end of forty days.

[image]\\
	}
}
{
}

\Verse{26}
{
	\hRJE{}
}
{
	\eRJE{
		And they went and came to Moses and to Aaron and to all the
congregation of the children of Israel, to the wilderness of Paran, at
Kadesh; and they brought back word to them and all the congregation and
showed them the land’s fruit.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hRJE{}
}
{
	\eRJE{
		And they told him and said, “We came to the land where you sent us,
and also it’s flowing with milk and honey, and this is its fruit.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hRJE{}
}
{
	\eRJE{
		Nonetheless: the people who live in the land are strong. And the
cities are fortified, very big. And also we saw the offspring of the
giants there.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hRJE{}
}
{
	\eRJE{
		Amalek lives in the land of the Negeb, and the Hittite and the
Jebusite and the Amorite live in the mountains, and the Canaanite lives
by the sea and along the Jordan.”

[image]\\
	}
}
{
}

\Verse{30}
{
	\hRJE{}
}
{
	\eRJE{
		And Caleb quieted the people toward Moses and said, “Let’s go up, and
we’ll take possession of it, because we’ll be able to handle it.”

[image]\\
	}
}
{
}

\Verse{31}
{
	\hRJE{}
}
{
	\eRJE{
		And the men who went up with him said, “We won’t be able to go up
against the people, because they’re stronger than we are.”

[image]\\
	}
}
{
}

\Verse{32}
{
	\hRJE{}
}
{
	\eRJE{
		And they brought out a report of the land that they had scouted to the
children of Israel, saying, “The land through which we passed to scout
it: it’s a land that eats those who live in it, and all the people whom
we saw in it were people of size!

[image]\\
	}
}
{
}

\Verse{33}
{
	\hRJE{}
}
{
	\eRJE{
		And we saw the Nephilim there, sons of giants from the Nephilim, and
we were like grasshoppers in our eyes, and so were we in their eyes.”

[image]\\
	}
}
{
}

