\Chapter{14}

\Verse{1}
{
	\hRJE{}
}
{
	\eRJE{
		14

¹ And all the congregation raised and let out their voices! And the
people wept that night.

[image]\\
	}
}
{
}

\Verse{2}
{
	\hRJE{}
}
{
	\eRJE{
		And all the children of Israel complained at Moses and at Aaron, and
all the congregation said to them, “If only we had died in the land of
Egypt! Or in this wilderness, if only we had died!

[image]\\
	}
}
{
}

\Verse{3}
{
	\hRJE{}
}
{
	\eRJE{
		And why is YHWH bringing us to this land to fall by the sword? Our
wives and our infants will become a spoil! Isn’t it better for us to go
back to Egypt?”

[image]\\
	}
}
{
}

\Verse{4}
{
	\hRJE{}
}
{
	\eRJE{
		And they said, each man to his brother, “Let’s appoint a chief and go
back to Egypt.”

[image]\\
	}
}
{
}

\Verse{5}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses and Aaron fell on their faces in front of all the community
of the congregation of the children of Israel.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hRJE{}
}
{
	\eRJE{
		And Joshua son of Nun and Caleb son of Jephunneh, from those who had
scouted the land, had torn their clothes.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hRJE{}
}
{
	\eRJE{
		And they said to all the congregation of the children of Israel,
saying, “The land through which we passed to scout it: the land is very,
very good!

[image]\\
	}
}
{
}

\Verse{8}
{
	\hRJE{}
}
{
	\eRJE{
		If YHWH desires us, then He’ll bring us to this land and give it to us,
a land that flows with milk and honey!

[image]\\
	}
}
{
}

\Verse{9}
{
	\hRJE{}
}
{
	\eRJE{
		Just don’t revolt against YHWH. And you, don’t fear the people of the
land, because they’re our bread! Their protection has turned from them,
while YHWH is with us. Don’t fear them.”

[image]\\
	}
}
{
}

\Verse{10}
{
	\hRJE{}
}
{
	\eRJE{
		And all the congregation said to batter them with stones.

And YHWH’s glory appeared at the Tent of Meeting to all the children of
Israel!

[image]\\
	}
}
{
}

\Verse{11}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said to Moses, “How long will this people reject me, and how
long will they not trust in me, with all the signs that I’ve done among
them?

[image]\\
	}
}
{
}

\Verse{12}
{
	\hJ{}
}
{
	\eJ{
		I’ll strike them with an epidemic and dispossess them, and I’ll make
you into a bigger and more powerful nation than they are.”

[image]\\
	}
}
{
}

\Verse{13}
{
	\hJ{}
}
{
	\eJ{
		And Moses said to YHWH, “And Egypt will hear it, for you brought this
people up from among them with your power,

[image]\\
	}
}
{
}

\Verse{14}
{
	\hJ{}
}
{
	\eJ{
		and they’ll say it to those who live in this land. They’ve heard that
you, YHWH, are among this people; that you, YHWH, have appeared
eye-to-eye; and your cloud stands over them; and you go in front of them
in a column of cloud by day and in a column of fire by night.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hJ{}
}
{
	\eJ{
		And if you kill this people as one man, then the nations that have
heard about you will say it, saying,

[image]\\
	}
}
{
}

\Verse{16}
{
	\hJ{}
}
{
	\eJ{
		‘Because YHWH wasn’t able to bring this people to the land that He
swore to them, He slaughtered them in the wilderness.’

[image]\\
	}
}
{
}

\Verse{17}
{
	\hJ{}
}
{
	\eJ{
		And now, let my Lord’s power be big, as you spoke, saying,

[image]\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		‘YHWH is slow to anger and abounding in kindness, bearing crime and
offense; though not making one innocent: reckoning fathers’ crime on
children, on third generations and on fourth generations.’

[image]\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		Forgive this people’s crime in proportion to the magnitude of your
kindness and as you’ve borne this people from Egypt to here.”

[image]\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said, “I’ve forgiven according to your word.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		But indeed, as I live, and as YHWH’s glory has filled all the earth,

[image]\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		I swear that all of these people, who have seen my glory and my signs
that I did in Egypt and in the wilderness and who have tested me ten
times now and haven’t listened to my voice,

[image]\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		won’t see the land that I swore to their fathers, and all those who
rejected me won’t see it.

[image]\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		And my servant Caleb, because a different spirit was with him, and he
went after me completely, I’ll bring him to the land where he went, and
his seed will possess it.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hJ{}
}
{
	\eJ{
		And the Amalekite and the Canaanite live in the valley. Turn and
travel tomorrow to the wilderness by the way of the Red Sea.”

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses and to Aaron, saying,

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		“How much further for this bad congregation, that they’re complaining
against me? I’ve heard the complaints of the children of Israel that
they’re making against me.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		Say to them: As I live—word of YHWH—what you have spoken in my ears,
that is what I’ll do to you!

[image]\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		In this wilderness your carcasses will fall; and all of you who were
counted, for all your number, from twenty years old and up, who
complained against me,

[image]\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		I swear that you won’t come to the land that I raised my hand to have
you reside there—except Caleb son of Jephunneh and Joshua son of Nun.

[image]\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		And your infants, whom you said would become a spoil: I’ll bring them,
and they will know the land that you rejected!

[image]\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		And you: your carcasses will fall in this wilderness.

[image]\\
	}
}
{
}

\Verse{33}
{
	\hP{}
}
{
	\eP{
		And your children will be roving in the wilderness forty years, and
they’ll bear your whoring until the end of your carcasses in the
wilderness.

[image]\\
	}
}
{
}

\Verse{34}
{
	\hP{}
}
{
	\eP{
		For the number of days that you scouted the land, forty days, you
shall bear your crimes a day for each year, forty years, and you shall
know my frustration!

[image]\\
	}
}
{
}

\Verse{35}
{
	\hP{}
}
{
	\eP{
		I, YHWH, have spoken: If I shall not do this to all this bad
congregation who are gathered against me: in this wilderness they shall
end, and they shall die there!”

[image]\\
	}
}
{
}

\Verse{36}
{
	\hP{}
}
{
	\eP{
		And the men whom Moses sent to scout the land and came back and caused
all the congregation to complain against him, bringing out a report
about the land:

[image]

[image]\\
	}
}
{
}

\Verse{37}
{
	\hP{}
}
{
	\eP{
		the men who brought out the bad report of the land died in a plague in
front of YHWH.

[image]\\
	}
}
{
}

\Verse{38}
{
	\hP{}
}
{
	\eP{
		But, out of those men who went to scout the land, Joshua son of Nun
and Caleb son of Jephunneh lived.

[image]

------------------------------------------------------------------------

³⁹ And Moses spoke these things to all the children of Israel, and the
people mourned very much.

[image]\\
	}
}
{
}

\Verse{40}
{
	\hJ{}
}
{
	\eJ{
		And they got up in the morning and went up to the top of the mountain,
saying, “Here we are, and we’ll go up to the place that YHWH said,
because we’ve sinned.”

[image]\\
	}
}
{
}

\Verse{41}
{
	\hJ{}
}
{
	\eJ{
		And Moses said, “Why are you violating YHWH’s word? And it won’t
succeed.

[image]\\
	}
}
{
}

\Verse{42}
{
	\hJ{}
}
{
	\eJ{
		Don’t go up, so you won’t be stricken in front of your enemies,
because YHWH isn’t among you.

[image]\\
	}
}
{
}

\Verse{43}
{
	\hJ{}
}
{
	\eJ{
		Because the Amalekite and the Canaanite are there in front of you, and
you’ll fall by the sword because of the fact that you’ve gone back from
following YHWH, and YHWH won’t be with you.”

[image]\\
	}
}
{
}

\Verse{44}
{
	\hJ{}
}
{
	\eJ{
		And they acted heedlessly, going up to the top of the mountain. And
the ark of the covenant of YHWH and Moses did not draw away from the
camp.

[image]\\
	}
}
{
}

\Verse{45}
{
	\hJ{}
}
{
	\eJ{
		And the Amalekite and the Canaanite who lived in that mountain came
down, and they struck them and crushed them as far as Hormah.

[image]\\
	}
}
{
}

