\Chapter{15}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		15

¹ And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel, and you shall say to them: When you
will come to the land of your homes that I am giving to you,

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		and you will make a fire offering to YHWH, a burnt offering or a
sacrifice, to express a vow or as a contribution or at your appointed
times, to make a pleasant smell to YHWH from the cattle or from the
flock,

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		then the one bringing his offering to YHWH shall bring forward a grain
offering, fine flour, one-tenth of a measure, mixed with a fourth of a
hin of oil.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And you shall make wine for a libation with the burnt offering or the
sacrifice, a fourth of a hin for one lamb.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		Or for a ram, you shall make a grain offering, fine flour, two tenths,
mixed with oil, a third of a hin,

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		and you shall bring forward wine for a libation, a third of a hin, a
pleasant smell to YHWH.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And if you will make a bull a burnt offering or a sacrifice, to express
a vow, or a peace offering to YHWH,

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		then he shall bring forward with the bull a grain offering, fine flour,
three tenths, mixed with oil, half of a hin,

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		and you shall bring forward wine for a libation, half of a hin, an
offering by fire of a pleasant smell to YHWH.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		It shall be done this way for one ox or for one ram or for a lamb of
the sheep or of the goats.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		By the number that you will do, you shall do each one of their number
this way.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		Every citizen shall do these this way when bringing forward an
offering by fire of a pleasant smell to YHWH.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And when an alien will reside with you—or someone who is among
you—through your generations and will make an offering by fire of a
pleasant smell to YHWH, as you will do so he shall do.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		You, congregation, and the resident alien have one law, an eternal law
through your generations: it will be the same for you and for the alien
in front of YHWH.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		You and the alien who resides with you shall have one instruction and
one judgment.”

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel, and you shall say to them: When you
come to the land where I’m bringing you,

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		then it will be that when you eat some of the land’s bread you shall
make a donation to YHWH.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		The first of your dough: you shall make a loaf as a donation. Like a
donation from the threshing floor, so you shall donate it.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		From the first of your dough you shall give a donation to YHWH through
your generations.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		“And when you will make a mistake and not do all of these commandments
that YHWH has spoken to Moses,

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		everything that YHWH has commanded you by Moses’ hand, from the day
that YHWH commanded and on through your generations,

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		then it will be that, if it was done by mistake, out of the
congregation’s sight, then all the congregation shall do one bull of the
cattle as a burnt offering for a pleasant smell to YHWH and its grain
offering and its libation according to the required manner and one goat
for a sin offering.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And the priest shall make atonement for all the congregation of the
children of Israel, and it will be forgiven for them, because it was a
mistake, and they brought their offering, an offering by fire to YHWH,
and their sin offering in front of YHWH for their mistake.

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		And it will be forgiven for all the congregation of the children of
Israel and the alien who resides among them, because it was by mistake
for all the people.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		“And if one person will sin by mistake, then he shall bring a she-goat
in its first year for a sin offering.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		And the priest shall make atonement for the person who made the
mistake, sinning by mistake, in front of YHWH to make atonement for him,
and it will be forgiven for him.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		The citizen among the children of Israel and for the alien who resides
among them: you shall have one instruction for one who acts by mistake.

[image]\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		“But the person who will act with a high hand, a citizen or an alien,
he is blaspheming YHWH, and that person will be cut off from among his
people,

[image]\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		because he disdained YHWH’s word and broke His commandment. That
person will be cut off. His crime is in him.”

[image]\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		And the children of Israel were in the wilderness, and they found a
man collecting wood on the Sabbath day.

[image]\\
	}
}
{
}

\Verse{33}
{
	\hP{}
}
{
	\eP{
		And those who found him collecting wood brought him forward to Moses
and to Aaron and to all the congregation.

[image]\\
	}
}
{
}

\Verse{34}
{
	\hP{}
}
{
	\eP{
		And they left him under watch because it had not been determined what
should be done to him.

[image]\\
	}
}
{
}

\Verse{35}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Moses, “The man shall be put to death! All the
congregation is to batter him with stones outside the camp.”

[image]\\
	}
}
{
}

\Verse{36}
{
	\hP{}
}
{
	\eP{
		And all the congregation brought him outside the camp and battered him
with stones, and he died, as YHWH commanded Moses.

[image]\\
	}
}
{
}

\Verse{37}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Moses, saying,

[image]\\
	}
}
{
}

\Verse{38}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel, and you shall say to them that they
shall make fringe on the corners of their clothes through their
generations. And they shall put a blue string on the fringe of the
corner.

[image]\\
	}
}
{
}

\Verse{39}
{
	\hP{}
}
{
	\eP{
		And you shall have the fringe so you will see it and bring to mind all
of YHWH’s commandments and will do them, and you will not go around
after your heart and after your eyes, because you whore after them.

[image]\\
	}
}
{
}

\Verse{40}
{
	\hP{}
}
{
	\eP{
		So you will bring to mind and do all my commandments, and you will be
holy to your God.

[image]\\
	}
}
{
}

\Verse{41}
{
	\hP{}
}
{
	\eP{
		I am YHWH, your God, who brought you out from the land of Egypt to be
God to you. I am YHWH, your God.”

[image]\\
	}
}
{
}

