\Chapter{16}

\Verse{1}
{
	\hRJE{}
}
{
	\eRJE{
		And Korah son of Izhar son of Kohath son of Levi, and Dathan and
Abiram, sons of Eliab, and On, son of Peleth, sons of Reuben, took

[image]

[image]\\
	}
}
{
}

\Verse{2}
{
	\hRJE{}
}
{
	\eRJE{
		and got up in front of Moses—and two hundred fifty people from the
children of Israel, chieftains of the congregation, prominent ones of
the assembly, people of repute.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hRJE{}
}
{
	\eRJE{
		And they assembled against Moses and against Aaron and said to them,
“You have much! Because all of the congregation, all of them, are holy,
and YHWH is among them. And why do you raise yourselves up over YHWH’s
community?”

[image]\\
	}
}
{
}

\Verse{4}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses listened, and he fell on his face.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hRJE{}
}
{
	\eRJE{
		And he spoke to Korah and to all of his congregation, saying, “In the
morning YHWH will make known who is His and who is holy, and He will
bring him close to Him. And He will bring the one He chooses close to
Him.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hRJE{}
}
{
	\eRJE{
		Do this: Take incense burners, Korah and all his congregation,

[image]\\
	}
}
{
}

\Verse{7}
{
	\hRJE{}
}
{
	\eRJE{
		and put fire in them and set incense on them in front of YHWH tomorrow.
And it will be that the man whom YHWH will choose, he will be the holy
one. You have much, sons of Levi!”

[image]\\
	}
}
{
}

\Verse{8}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses said to Korah, “Listen, sons of Levi,

[image]\\
	}
}
{
}

\Verse{9}
{
	\hRJE{}
}
{
	\eRJE{
		is it too small a thing for you that Israel’s God has distinguished you
from the congregation of Israel to bring you close to him, to do the
work of YHWH’s Tabernacle and to stand in front of the congregation to
minister for them,

[image]\\
	}
}
{
}

\Verse{10}
{
	\hRJE{}
}
{
	\eRJE{
		and that He has brought you and all your brothers, the sons of Levi,
with you close to Him? And you seek priesthood as well?!

[image]\\
	}
}
{
}

\Verse{11}
{
	\hRJE{}
}
{
	\eRJE{
		Therefore you and all your congregation who are gathering are against
YHWH! And Aaron, what is he that you complain against him?”

[image]

[image]\\
	}
}
{
}

\Verse{12}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses sent to call Dathan and Abiram, sons of Eliab, and they
said, “We won’t come up.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hRJE{}
}
{
	\eRJE{
		Is it a small thing that you brought us up from a land flowing with
milk and honey to kill us in the wilderness, that you lord it over us as
well?

[image]\\
	}
}
{
}

\Verse{14}
{
	\hRJE{}
}
{
	\eRJE{
		Besides, you haven’t brought us to a land flowing with milk and honey
or given us possession of field or vineyard. Will you put out those
people’s eyes? We won’t come up.”

[image]\\
	}
}
{
}

\Verse{15}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses was very angry, and he said to YHWH, “Don’t turn to their
offering. Not one ass of theirs have I taken away, and I haven’t wronged
one of them.”

[image]\\
	}
}
{
}

\Verse{16}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses said to Korah, “You and all your congregation, be in front
of YHWH—you and they and Aaron—tomorrow.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hRJE{}
}
{
	\eRJE{
		And each man take his fire-holder, and put incense on them, and each
man bring his fire-holder forward in front of YHWH, two hundred fifty
fire-holders, and you and Aaron, each man his fire-holder.”

[image]\\
	}
}
{
}

\Verse{18}
{
	\hRJE{}
}
{
	\eRJE{
		And each man took his fire-holder, and they put fire on them and set
incense on them, and they stood at the entrance of the Tent of Meeting,
and Moses and Aaron.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hRJE{}
}
{
	\eRJE{
		And Korah assembled all the congregation against them, to the entrance
of the Tent of Meeting. And YHWH’s glory appeared to all the
congregation.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH spoke to Moses and to Aaron, saying,

[image]\\
	}
}
{
}

\Verse{21}
{
	\hRJE{}
}
{
	\eRJE{
		“Separate from among this congregation, and I’ll finish them in an
instant!”

[image]\\
	}
}
{
}

\Verse{22}
{
	\hRJE{}
}
{
	\eRJE{
		And they fell on their faces and said, “God, the God of the spirits of
all flesh, will one man sin and you be angry at all the congregation?”

[image]\\
	}
}
{
}

\Verse{23}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{24}
{
	\hRJE{}
}
{
	\eRJE{
		“Speak to the congregation, saying, ‘Get up from around the tabernacle
of Korah, Dathan and Abiram.’”

[image]\\
	}
}
{
}

\Verse{25}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses got up and went to Dathan and Abiram, and Israel’s elders
went after him.

[image]\\
	}
}
{
}

\Verse{26}
{
	\hRJE{}
}
{
	\eRJE{
		And he spoke to the congregation, saying, “Turn away from the tents of
these wicked men and don’t touch anything that is theirs, or else you’ll
be annihilated through all their sins.”

[image]\\
	}
}
{
}

\Verse{27}
{
	\hRJE{}
}
{
	\eRJE{
		And they got up from around the tabernacle of Korah, Dathan and
Abiram. And Dathan and Abiram came out, standing at the entrance of
their tents, and their wives and their children and their infants.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses said, “By this you’ll know that YHWH sent me to do all these
things, because it’s not from my own heart.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hRJE{}
}
{
	\eRJE{
		If these die like the death of every human, and the event of every
human happens to them, then YHWH hasn’t sent me.

[image]\\
	}
}
{
}

\Verse{30}
{
	\hRJE{}
}
{
	\eRJE{
		But if YHWH will create something, and the ground will open its mouth
and swallow them and all that they have, and they’ll go down alive to
Sheol, then you’ll know that these people have rejected YHWH.”

[image]\\
	}
}
{
}

\Verse{31}
{
	\hRJE{}
}
{
	\eRJE{
		And it was as he was finishing speaking all these things, and the
ground that was under them was broken up,

[image]\\
	}
}
{
}

\Verse{32}
{
	\hRJE{}
}
{
	\eRJE{
		and the earth opened its mouth and swallowed them and their households
and all the people who were with Korah and all the property,

[image]\\
	}
}
{
}

\Verse{33}
{
	\hRJE{}
}
{
	\eRJE{
		and they went down, they and all that they had, alive to Sheol. And
the earth covered them over, and they perished from among the community.

[image]\\
	}
}
{
}

\Verse{34}
{
	\hRJE{}
}
{
	\eRJE{
		And all Israel that was around them fled at the sound of them, for
they said, “Or else the earth will swallow us.”

[image]\\
	}
}
{
}

\Verse{35}
{
	\hRJE{}
}
{
	\eRJE{
		And fire had gone out from YHWH and consumed the two hundred fifty
people offering the incense.

[image]\\
	}
}
{
}

