\Chapter{17}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		17

¹ And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Say to Eleazar son of Aaron, the priest, that he should pick up the
fire-holders from the burning and disperse the fire, because they have
become holy.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And the fire-holders of these who sinned at the cost of their lives:
let them make them into hammered plates as plating for the altar,
because they brought them forward in front of YHWH, and they became
holy, and let them become a sign to the children of Israel.”

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And Eleazar, the priest, took the fire-holders of bronze that those who
were burned had brought forward, and they hammered them into a plating
for the altar,

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		a commemoration for the children of Israel so that no outsider, one who
is not from Aaron’s seed, will come forward to burn incense in front of
YHWH, so he will not be like Korah and like his congregation, as YHWH
spoke to him by Moses’ hand.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And all the congregation of the children of Israel complained the next
day against Moses and against Aaron, saying, “You killed YHWH’s people!”

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And it was when the congregation was assembled against Moses and
against Aaron, and they turned to the Tent of Meeting; and, here, the
cloud had covered it, and YHWH’s glory appeared.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And Moses and Aaron came to the front of the Tent of Meeting.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		“Move away from among this congregation, and I’ll finish them in an
instant!” And they fell on their faces.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And Moses said to Aaron, “Take a fire-holder and put fire from the
altar on it and set incense and carry it quickly to the congregation and
make atonement for them, because a rage has come out from in front of
YHWH! The plague has begun!”

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And Aaron took it as Moses had spoken, and he ran among the community.
And, here, the plague had begun among the people. And he put in incense
and made atonement for the people.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And he stood between the dead and the living. And the plague was
halted.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hOther{}
}
{
	\eOther{
		And the dead in the plague were fourteen thousand seven hundred, apart
from the dead over the matter of Korah.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hOther{}
}
{
	\eOther{
		And Aaron went back to Moses, to the entrance of the Tent of Meeting,
when the plague had been halted.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hOther{}
}
{
	\eOther{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{17}
{
	\hOther{}
}
{
	\eOther{
		“Speak to the children of Israel and take from them a staff for each
father’s house, from all their chieftains by their fathers’ house,
twelve staffs. You shall write each man’s name on his staff,

[image]\\
	}
}
{
}

\Verse{18}
{
	\hOther{}
}
{
	\eOther{
		and you shall write Aaron’s name on the staff of Levi, because there
shall be one staff for the head of their fathers’ house.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hOther{}
}
{
	\eOther{
		And you shall leave them in the Tent of Meeting in front of the
Testimony where I shall meet with you.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hOther{}
}
{
	\eOther{
		And it will be that the man I shall choose: his staff will bloom. And
I’ll decrease from me the complaints of the children of Israel that
they’re making against you.”

[image]\\
	}
}
{
}

\Verse{21}
{
	\hOther{}
}
{
	\eOther{
		And Moses spoke to the children of Israel, and all their chieftains
gave him a staff for each chieftain by their fathers’ house, twelve
staffs, and Aaron’s staff was among their staffs.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hOther{}
}
{
	\eOther{
		And Moses left the staffs in front of YHWH in the Tent of the
Testimony.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hOther{}
}
{
	\eOther{
		And it was the next day, and Moses came to the Tent of the Testimony;
and, here, Aaron’s staff, of the house of Levi, had bloomed; and it
brought out a bloom, and it made a blossom, and it produced almonds!

[image]\\
	}
}
{
}

\Verse{24}
{
	\hOther{}
}
{
	\eOther{
		And Moses brought out all the staffs from in front of YHWH to the
children of Israel. And they saw, and each took his staff.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hOther{}
}
{
	\eOther{
		And YHWH said to Moses, “Put back Aaron’s staff in front of the
Testimony for watching over, for a sign to rebels, and you’ll end their
complaints against me so they won’t die!”

[image]\\
	}
}
{
}

\Verse{26}
{
	\hOther{}
}
{
	\eOther{
		And Moses did it. As YHWH had commanded him, he did so.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hOther{}
}
{
	\eOther{
		And the children of Israel said to Moses, saying, “Here, we’re
expiring, we’re perishing, we’re all perishing!

[image]\\
	}
}
{
}

\Verse{28}
{
	\hOther{}
}
{
	\eOther{
		Everyone who comes close—who comes close to YHWH’s Tabernacle—will
die. Have we come to the end of expiring?!”

[image]\\
	}
}
{
}

