\Chapter{18}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		18

¹ And YHWH said to Aaron, “You and your sons and your father’s house with
you shall bear any crime of the holy place, and you and your sons with
you shall bear any crime of your priesthood.

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		And bring forward your brothers, the tribe of Levi, your father’s
tribe, with you as well, and they shall be connected to you and shall
minister to you, and you and your sons with you shall be in front of the
Tent of the Testimony.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And they shall keep your charge, the charge of all of the tent, but
they shall not come close to the equipment of the holy and to the altar,
so they will not die, both they and you.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And they shall be connected to you and shall keep the charge of the
Tent of Meeting, for all the work of the tent, but an outsider shall not
come close to you.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And you shall keep the charge of the holy and the charge of the altar,
so there will not be any more rage at the children of Israel.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And I, here, I have taken your brothers, the Levites from among the
children of Israel as a gift to you, given for YHWH, to do the work of
the Tent of Meeting.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And you and your sons with you shall watch over your priesthood for
everything of the altar’s and for inside the pavilion, and you shall
serve. I give your priesthood as a gift of service. And the outsider who
comes close shall be put to death.”

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Aaron, “And I, here, I have given charge of my
donations to you for all the holy things of the children of Israel. I
have given them to you as an anointing and to your sons as an eternal
law.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		This shall be yours from the holy of holies, from the fire: every
offering of theirs, every grain offering of theirs and every sin
offering of theirs and every guilt offering of theirs that they will pay
back to me. It is holy of holies for you and for your sons.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		You shall eat it in the holy of holies. Every male shall eat it. It
shall be holy to you.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		“And this is yours: their gift donation, all the elevation offerings
of the children of Israel. I have given them to you and to your sons and
to your daughters with you as an eternal law. Everyone who is pure in
your house shall eat it.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		“All the best of the oil and all the best of the wine and grain, the
first of them that they will give to YHWH: I have given them to you.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		The firstfruits of everything that is in their land that they will
bring to YHWH shall be yours. Everyone who is pure in your house shall
eat it.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		Every devoted thing in Israel shall be yours.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		Every first birth of a womb of all flesh that they will bring forward
to YHWH, human and animal, shall be yours. Just: you shall redeem the
human firstborn, and you shall redeem the firstborn of an impure animal.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And their redemption price: from one month old you shall redeem it at
your appraisal, five shekels of silver by the shekel of the Holy. It is
twenty gerah.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		Just: you shall not redeem a firstborn of an ox or firstborn of a
sheep or firstborn of a goat. They are holy. You shall fling their blood
on the altar and burn their fat to smoke, a fire offering for a pleasant
smell to YHWH.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And their meat shall be yours; like the breast of the elevation
offering and the right thigh it shall be yours.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		All the donations of the holy things that the children of Israel will
donate to YHWH I have given to you and to your sons and to your
daughters with you as an eternal law. It is an eternal covenant of salt
in front of YHWH for you and for your seed with you.”

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Aaron, “You shall not have a legacy in their land,
and you shall not have a portion among them. I am your portion and your
legacy among the children of Israel.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And to the children of Levi, here, I’ve given every tithe in Israel as
a legacy in exchange for their work that they’re doing, the service of
the Tent of Meeting.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And the children of Israel shall not come near to the Tent of Meeting
anymore so as to bear sin and die.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		But he, the Levite, shall do the service of the Tent of Meeting, and
they shall bear their crime. It is an eternal law through your
generations. And they shall not have a legacy among the children of
Israel,

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		because I’ve given to the Levites as a legacy the tithe of the
children of Israel that they will give to YHWH as a donation. On account
of this I’ve said to them: they shall not have a legacy among the
children of Israel.”

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		“And you shall speak to the Levites and say to them: ‘When you will
take the tithe from the children of Israel that I have given you from
them as your legacy, then you shall make a donation for YHWH from it, a
tithe of the tithe.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		And it will be counted for you as your donation, like grain from the
threshing floor and like the fill of the winepress.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		So you shall donate, you too, a donation for YHWH from all your tithes
that you will take from the children of Israel, and you shall give a
donation for YHWH to Aaron, the priest, from them.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		From all your gifts you shall make every donation for YHWH, from all
the best of it, its holy part from it.’

[image]\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		And you shall say to them: ‘When you donate the best of it from it,
then it shall be counted to the Levites like the produce of the
threshing floor and like the produce of the winepress.

[image]\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		And you shall eat it in every place, you and your house, because it is
compensation for you in exchange for your work in the Tent of Meeting.

[image]\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		And you will not bear sin over it, when you have donated its best from
it, so you will not desecrate the holy things of the children of Israel,
and you will not die.’”

[image]\\
	}
}
{
}

