\Chapter{19}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses and to Aaron, saying,

[image]

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“This is the law of the instruction that YHWH commanded, saying: Speak
to the children of Israel that they should take to you an unblemished
red cow that has no injury, on which a yoke has not gone.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And you shall give it to Eleazar, the priest, and one shall bring it
outside the camp and slaughter it in front of him.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And Eleazar, the priest, shall take some of its blood with his finger
and sprinkle some of its blood toward the front of the Tent of Meeting
seven times.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And one shall burn the cow before his eyes. He shall burn its skin and
its meat and its blood and its dung.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And the priest shall take cedarwood and hyssop and scarlet and throw
them into the fire of the cow.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And the priest shall wash his clothes and wash his flesh with water,
and after that he shall come to the camp, and the priest shall be impure
until evening.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And the one who burns it shall wash his clothes with water and wash his
flesh with water and be impure until evening.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And a man who is pure shall gather the cow’s ashes and leave them
outside the camp in a pure place, and it shall be for the congregation
of the children of Israel to be kept for water of impurity, for sin
expiation.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And the one who gathers the cow’s ashes shall wash his clothes and be
impure until evening. And it will be for the children of Israel and for
the alien who resides among them as an eternal law.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		“One who touches a dead body of any human being will be impure seven
days.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		He shall do sin expiation with it on the third day, and on the seventh
day he will be pure. And if he will not do sin expiation on the third
day, then on the seventh day he will not be pure.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		Anyone who touches a dead body of a human being who has died and does
not do sin expiation has made YHWH’s Tabernacle impure, and that person
will be cut off from Israel. Because the water of impurity was not flung
on him, he shall be impure. His impurity is still in him.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		“This is the instruction: When a human will die in a tent, anyone who
comes into the tent and everything that is in the tent will be impure
seven days.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And any open container, on which there is not a fastened cover: it is
impure.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And anyone who, at an open field, will touch a corpse slain by the
sword or a dead body or a human bone or a grave will be impure seven
days.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And they shall take for the one who is impure some of the ashes of the
fire of sin expiation, and one shall put living water on it in a
container.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And a man who is pure shall take hyssop and dip it in the water and
sprinkle it on the tent and on all the items and on the persons who were
there and on the one who touched the bone or the slain corpse or the
dead body or the grave.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And the one who is pure shall sprinkle it on the impure on the third
day and on the seventh day, so he shall expiate sin from him on the
seventh day, and he shall wash his clothes and wash in water and be pure
in the evening.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And if a man will be impure and will not do sin expiation, then that
person will be cut off from among the community, because he has made
YHWH’s holy place impure. The water of impurity has not been flung on
him: he is impure.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And it will become an eternal law for them. And one who sprinkles the
water of impurity shall wash his clothes, and one who touches the water
of impurity will be impure until evening.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And whatever the impure one will touch will be impure, and the person
who touches it will be impure until evening.”

[image]\\
	}
}
{
}

