\Chapter{20}

\Verse{1}
{
	\hRJE{}
}
{
	\eRJE{
		20

¹ And the children of Israel, all the congregation, came to the
wilderness of Zin in the first month, and the people stayed in Kadesh.
And Miriam died there and was buried there.

[image]\\
	}
}
{
}

\Verse{2}
{
	\hRJE{}
}
{
	\eRJE{
		And there was no water for the congregation, and they assembled against
Moses and against Aaron.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hRJE{}
}
{
	\eRJE{
		And the people quarreled with Moses, and they said, saying, “If only we
had expired when our brothers expired in front of YHWH!

[image]\\
	}
}
{
}

\Verse{4}
{
	\hRJE{}
}
{
	\eRJE{
		And why have you brought YHWH’s community to this wilderness to die
there, we and our cattle?

[image]\\
	}
}
{
}

\Verse{5}
{
	\hRJE{}
}
{
	\eRJE{
		And why did you bring us up from Egypt to bring us to this bad place?
It’s not a place of seed and fig and vine and pomegranate, and there’s
no water to drink!”

[image]\\
	}
}
{
}

\Verse{6}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses and Aaron came from in front of the community to the entrance
of the Tent of Meeting, and they fell on their faces. And YHWH’s glory
appeared to them.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{8}
{
	\hRJE{}
}
{
	\eRJE{
		“Take the staff and assemble the congregation, you and Aaron, your
brother. And you shall speak to the rock before their eyes, and it will
give its water. So you shall bring water out of the rock for them and
give a drink to the congregation and their cattle.”

[image]\\
	}
}
{
}

\Verse{9}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses took the staff from in front of YHWH as He commanded him.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses and Aaron assembled the community opposite the rock. And he
said to them, “Listen, rebels, shall we bring water out of this rock for
you?”

[image]\\
	}
}
{
}

\Verse{11}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses lifted his hand and struck the rock with his staff twice.
And much water came out! And the congregation and their cattle drank.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH said to Moses and to Aaron, “Because you did not trust in me,
to make me holy before the eyes of the children of Israel, therefore you
shall not bring this community to the land that I have given them!”

[image]\\
	}
}
{
}

\Verse{13}
{
	\hRJE{}
}
{
	\eRJE{
		They are the waters of Meribah, over which the children of Israel
quarreled with YHWH, and He was made holy among them.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hJ{}
}
{
	\eJ{
		And Moses sent messengers from Kadesh to the king of Edom. “Your
brother, Israel, says this: You know all the hardship that has found us:

[image]\\
	}
}
{
}

\Verse{15}
{
	\hJ{}
}
{
	\eJ{
		And our fathers went down to Egypt, and we lived in Egypt many days.
And Egypt was bad to us and to our fathers,

[image]\\
	}
}
{
}

\Verse{16}
{
	\hJ{}
}
{
	\eJ{
		and we cried to YHWH, and He heard our voice and sent an angel and
brought us from Egypt. And here we are in Kadesh, a city at the edge of
your border.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hJ{}
}
{
	\eJ{
		Let us pass through your land. We won’t pass through a field or
through a vineyard, and we won’t drink the water of a well. We’ll go by
the king’s road, we won’t turn right or left, until we pass your
border.”

[image]\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		And Edom said to him, “You won’t pass through me, or else I’ll go out
to you with the sword.”

[image]\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		And the children of Israel said to him, “We’ll go up by the highway,
and if we drink your water, I and my cattle, then I’ll pay its price.
Only, it’s nothing: let me pass through by foot.”

[image]\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		And he said, “You won’t pass.” And Edom went out to him with a heavy
mass of people and a strong hand,

[image]\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		and Edom refused to allow Israel to pass through his border. And
Israel turned away from him.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And they traveled from Kadesh, and the children of Israel, all the
congregation, came to Mount Hor.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Moses and to Aaron at Mount Hor, on the border of the
land of Edom, saying,

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		“Let Aaron be gathered to his people, because he shall not come to the
land that I have given to the children of Israel, because you rebelled
against my word at the waters of Meribah.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		Take Aaron and Eleazar, his son, and take them up Mount Hor,

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		and take off Aaron’s clothes, and you shall put them on Eleazar, his
son. And Aaron will be gathered and die there.”

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		And Moses did as YHWH commanded him. And they went up to Mount Hor
before the eyes of all the congregation.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		And Moses took off Aaron’s clothes and put them on Eleazar, his son.
And Aaron died there on the top of the mountain. And Moses and Eleazar
came down from the mountain.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		And all the congregation saw that Aaron had expired, and all the house
of Israel mourned Aaron thirty days.

[image]\\
	}
}
{
}

