\Chapter{21}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		21

¹ And the Canaanite, the king of Arad, who lived in the Negeb, heard that
Israel was coming by the way of Atharim, and he fought against Israel
and took some of them prisoners.

[image]\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		And Israel made a vow to YHWH and said, “If you will deliver this
people into my hand, then I shall completely destroy their cities.”

[image]\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		And YHWH listened to Israel’s voice and delivered the Canaanite, and
they completely destroyed them and their cities. And the name of the
place was called Hormah.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		And they traveled from Mount Hor by way of the Red Sea road to go
around the land of Edom. And the people’s soul was getting short on the
way.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		And the people spoke against God and against Moses: “Why did you bring
us up from Egypt to die in the wilderness? Because there’s no bread, and
there’s no water, and our soul is disgusted with the cursed bread.”

[image]\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And YHWH let fiery snakes go among the people, and they bit the people,
and a great many people from Israel died.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		And the people came to Moses, and they said, “We’ve sinned, because we
spoke against YHWH and against you. Pray to YHWH, that He will turn the
snake away from us.” And Moses prayed on behalf of the people.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said to Moses, “Make a fiery one and set it on a pole, and it
will be that everyone who is bitten and sees it will live.”

[image]\\
	}
}
{
}

\Verse{9}
{
	\hJ{}
}
{
	\eJ{
		And Moses made a bronze snake and set it on a pole, and it was, if a
snake bit a man, then he would look at the bronze snake and live.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		And the children of Israel traveled, and they camped in Oboth.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		And they traveled from Oboth, and they camped in Iye-abarim, in the
wilderness that is toward Moab, toward the sun’s rising.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		From there they traveled, and they camped in the Wadi Zered.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		From there they traveled, and they camped across the Arnon, which is
in the wilderness that extends from the border of the Amorite, because
Arnon is Moab’s border, between Moab and the Amorite.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		On account of this it is said in the Scroll of the Wars of YHWH:

Waheb in Suphah and the wadis of Arnon,

[image]\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		and the slope of the wadis that reached to the settlement of Ar, and
pressed to Moab’s border.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		And from there to Beer: that is the well of which YHWH said to Moses,
“Gather the people, so I may give them water.”

[image]\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		Then Israel sang this song:

Spring up, well. Sing to it.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hE{}
}
{
	\eE{
		The commanders hewed the well, the people’s nobles dug it,

with a scepter, with their staffs.

And from the wilderness to Mattanah,

[image]\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		and from Mattanah to Nahaliel, and from Nahaliel to Bamoth,

[image]\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		and from Bamoth in the valley, that is in the field of Moab, to the
top of Pisgah, which looks toward Jeshimon.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		And Israel sent messengers to Sihon, king of the Amorites, saying,

[image]\\
	}
}
{
}

\Verse{22}
{
	\hE{}
}
{
	\eE{
		“Let me pass through your land. We won’t turn in at a field and at a
vineyard and won’t drink well waters. We’ll go by the king’s road until
we pass your border.”

[image]\\
	}
}
{
}

\Verse{23}
{
	\hE{}
}
{
	\eE{
		And Sihon did not allow Israel to pass within his border. And Sihon
gathered all his people and went out to Israel at the wilderness and
came to Jahaz and fought against Israel.

[image]\\
	}
}
{
}

\Verse{24}
{
	\hE{}
}
{
	\eE{
		And Israel struck him by the sword and took possession of his land
from Arnon to Jabbok, to the children of Ammon, because the border of
the children of Ammon was strong.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hE{}
}
{
	\eE{
		And Israel took all of these cities, and Israel lived in all the
Amorite cities in Heshbon and all of its environs,

[image]\\
	}
}
{
}

\Verse{26}
{
	\hE{}
}
{
	\eE{
		because Heshbon was the city of Sihon, the king of the Amorite, and he
fought against the former king of Moab and took all of his land from his
hand as far as Arnon.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hE{}
}
{
	\eE{
		On account of this they say proverbially:

Come to Heshbon.

Built and founded is Sihon’s city.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hE{}
}
{
	\eE{
		For fire went out of Heshbon,

flame from Sihon’s town;

it consumed Ar of Moab,

the lords of the high places of Arnon.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hE{}
}
{
	\eE{
		Woe unto you, Moab:

you’ve perished, Chemosh’s people.

He’s made his sons refugees

and his daughters captive

to the king of the Amorite, Sihon.

[image]\\
	}
}
{
}

\Verse{30}
{
	\hE{}
}
{
	\eE{
		And their fiefdom perished,

Heshbon to Dibon,

and we devastated up to Nophah

which reaches to Medeba.

[image]\\
	}
}
{
}

\Verse{31}
{
	\hE{}
}
{
	\eE{
		And Israel lived in the Amorite’s land.

[image]\\
	}
}
{
}

\Verse{32}
{
	\hE{}
}
{
	\eE{
		And Moses sent to spy on Jazer, and they captured its environs and
dispossessed the Amorite who was there.

[image]\\
	}
}
{
}

\Verse{33}
{
	\hE{}
}
{
	\eE{
		And they turned and went up the road of Bashan, and Og, the king of
Bashan, went out to them, he and all his people, to war at Edrei.

[image]\\
	}
}
{
}

\Verse{34}
{
	\hE{}
}
{
	\eE{
		And YHWH said to Moses, “Don’t fear him, because I’ve delivered him
and all his people and his land into your hand, and you’ll do to him as
you did to Sihon, king of the Amorite, who lived in Heshbon.”

[image]\\
	}
}
{
}

\Verse{35}
{
	\hE{}
}
{
	\eE{
		And they struck him and his sons and all his people until he did not
have a remnant left, and they took possession of his land.

[image]\\
	}
}
{
}

