\Chapter{22}

\Verse{1}
{
	\hE{}
}
{
	\eE{
		And the children of Israel traveled, and they camped in the plains of
Moab, across the Jordan from Jericho.

[image]

[image]\\
	}
}
{
}

\Verse{2}
{
	\hE{}
}
{
	\eE{
		And Balak, son of Zippor, saw everything that Israel had done to the
Amorite.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hE{}
}
{
	\eE{
		And Moab was very fearful because of the people because it was
numerous, and Moab felt a disgust at the children of Israel.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hE{}
}
{
	\eE{
		And Moab said to the elders of Midian, “Now the community will lick up
all of our surroundings the way an ox licks up the plants of a field!”

And Balak, son of Zippor, was king of Moab at that time.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hE{}
}
{
	\eE{
		And he sent messengers to Balaam, son of Beor, at Pethor, which is on
the river—the land of the children of his people—to call him, saying,
“Here, a people has come out from Egypt. Here, it has covered the eye of
the land. And it’s sitting across from me!

[image]\\
	}
}
{
}

\Verse{6}
{
	\hE{}
}
{
	\eE{
		And now, go, curse this people for me, because it’s more powerful than
I—maybe I’ll be able: we’ll strike it, and I’ll drive it out from the
land—because I know that whoever you’ll bless will be blessed, and
whoever you’ll curse will be cursed.”

[image]\\
	}
}
{
}

\Verse{7}
{
	\hE{}
}
{
	\eE{
		And Moab’s elders and Midian’s elders went, and divination implements
were in their hand, and they came to Balaam and spoke Balak’s words to
him.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hE{}
}
{
	\eE{
		And he said to them, “Spend the night here tonight, and I’ll bring back
word to you as YHWH will speak to me.” And the chiefs of Moab stayed
with Balaam.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hE{}
}
{
	\eE{
		And God came to Balaam and said, “Who are these people with you?”

[image]\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		And Balaam said to God, “Balak, son of Zippor, king of Moab, sent to
me:

[image]\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		‘Here is a people who came out from Egypt and has covered the eye of
the land. Now go, execrate it for me. Maybe I’ll be able to fight
against it, and I’ll drive it out.’”

[image]\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		And God said to Balaam, “You shall not go with them. You shall not
curse the people, because it is blessed.”

[image]\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		And Balaam got up in the morning and said to Balak’s chiefs, “Go to
your land, because YHWH refused to allow me to go with you.”

[image]\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		And the chiefs of Moab got up and came to Balak and said, “Balaam
refused to go with us.”

[image]\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		And Balak went on again to send more numerous and prestigious chiefs
than these.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		And they came to Balaam and said to him, “Balak, son of Zippor, said
this: ‘Don’t be held back from coming to me,

[image]\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		because I’ll honor you very much, and I’ll do everything that you’ll
say to me. And go, execrate this people for me.’”

[image]\\
	}
}
{
}

\Verse{18}
{
	\hE{}
}
{
	\eE{
		And Balaam answered, and he said to Balak’s servants, “If Balak would
give me a houseful of silver and gold of his I wouldn’t be able to go
against the mouth of YHWH, my God, to do something small or big.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		And now, stay here, you as well, tonight, so I may know what YHWH will
add to speak with me.”

[image]\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		And God came to Balaam at night and said to him, “If these people have
come to call you, get up, go with them. And just the thing that I shall
speak to you—you shall do that.”

[image]\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		And Balaam got up in the morning and harnessed his ass and went with
the chiefs of Moab.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hE{}
}
{
	\eE{
		And God’s anger flared because he was going. And an angel of YHWH
stood up in the road as an adversary to him. And he was riding on his
ass, and his two boys were with him.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hE{}
}
{
	\eE{
		And the ass saw the angel of YHWH standing up in the road and his
sword drawn in his hand, and the ass turned from the road and went into
the field. And Balaam hit the ass to turn her back to the road.

[image]\\
	}
}
{
}

\Verse{24}
{
	\hE{}
}
{
	\eE{
		And the angel of YHWH stood in the pathway of the vineyards, a fence
on this side and a fence on that side.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hE{}
}
{
	\eE{
		And the ass saw the angel of YHWH, and she was pressed against the
wall, and she pressed Balaam’s foot against the wall, and he continued
hitting her.

[image]\\
	}
}
{
}

\Verse{26}
{
	\hE{}
}
{
	\eE{
		And the angel continued passing on and stood in a narrow place where
there was no way to turn right or left.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hE{}
}
{
	\eE{
		And the ass saw the angel of YHWH, and she lay down under Balaam. And
Balaam’s anger flared, and he struck the ass with a stick.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hE{}
}
{
	\eE{
		And YHWH opened the ass’s mouth, and she said to Balaam, “What have I
done to you that you’ve struck me these three times?!”

[image]\\
	}
}
{
}

\Verse{29}
{
	\hE{}
}
{
	\eE{
		And Balaam said to the ass, “Because you abused me! If there had been
a sword in my hand I would have killed you by now!”

[image]\\
	}
}
{
}

\Verse{30}
{
	\hE{}
}
{
	\eE{
		And the ass said to Balaam, “Aren’t I your ass, on whom you’ve ridden?
From your start until this day, have I been accustomed to do like this
to you?”

And he said, “No.”

[image]\\
	}
}
{
}

\Verse{31}
{
	\hE{}
}
{
	\eE{
		And YHWH uncovered Balaam’s eyes, and he saw the angel of YHWH
standing up in the road, and his sword drawn in his hand. And he knelt
and bowed to his nose.

[image]\\
	}
}
{
}

\Verse{32}
{
	\hE{}
}
{
	\eE{
		And the angel of YHWH said to him, “For what have you struck your ass
these three times? Here, I came out as an adversary because the way was
precipitous with regard to me.

[image]\\
	}
}
{
}

\Verse{33}
{
	\hE{}
}
{
	\eE{
		And the ass saw me and turned in front of me these three times. If she
hadn’t turned from in front of me, I would have killed you, too, by now
and kept her alive!”

[image]\\
	}
}
{
}

\Verse{34}
{
	\hE{}
}
{
	\eE{
		And Balaam said to the angel of YHWH, “I’ve sinned, because I didn’t
know that you were standing up toward me in the road. And now, if it’s
bad in your eyes, let me go back.”

[image]\\
	}
}
{
}

\Verse{35}
{
	\hE{}
}
{
	\eE{
		And the angel of YHWH said to Balaam, “Go with the people. And nothing
but the thing that I shall speak to you: that is what you shall speak.”
And Balaam went with Balak’s chiefs.

[image]\\
	}
}
{
}

\Verse{36}
{
	\hE{}
}
{
	\eE{
		And Balak heard that Balaam was coming, and he went out to him, to a
city of Moab that was on the Arnon border, that was at the edge of the
border.

[image]\\
	}
}
{
}

\Verse{37}
{
	\hE{}
}
{
	\eE{
		And Balak said to Balaam, “Didn’t I send to you, to call you? Why
didn’t you come to me? Am I indeed not able to honor you?!”

[image]\\
	}
}
{
}

\Verse{38}
{
	\hE{}
}
{
	\eE{
		And Balaam said to Balak, “Here, I’ve come to you. Now: will I be able
to speak anything? The thing that God will set in my mouth: that is what
I’ll speak.”

[image]\\
	}
}
{
}

\Verse{39}
{
	\hE{}
}
{
	\eE{
		And Balaam went with Balak, and they came to Kiriath Huzoth.

[image]\\
	}
}
{
}

\Verse{40}
{
	\hE{}
}
{
	\eE{
		And Balak sacrificed oxen and sheep, and he let them go to Balaam and
to the chiefs who were with them.

[image]\\
	}
}
{
}

\Verse{41}
{
	\hE{}
}
{
	\eE{
		And it was in the morning, and Balak took Balaam and brought him up to
the High Places of Baal, and he saw the outer edge of the people from
there.

[image]\\
	}
}
{
}

