\Chapter{23}

\Verse{1}
{
	\hE{}
}
{
	\eE{
		23

¹ And Balaam said to Balak, “Build seven altars for me here, and prepare
seven bulls and seven rams for me here.”

[image]\\
	}
}
{
}

\Verse{2}
{
	\hE{}
}
{
	\eE{
		And Balak did as Balaam spoke, and Balak and Balaam offered a bull and
a ram on each altar.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hE{}
}
{
	\eE{
		And Balaam said to Balak, “Stand up by your burnt offering, and let me
go. Maybe YHWH will communicate to me. And whatever He’ll show me, I’ll
tell you.” And he went to a viewpoint.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hE{}
}
{
	\eE{
		And God communicated to Balaam. And he said to Him, “I’ve arranged the
seven altars and offered a bull and a ram on each altar.”

[image]\\
	}
}
{
}

\Verse{5}
{
	\hE{}
}
{
	\eE{
		And YHWH put a word in Balaam’s mouth, and He said, “Go back to Balak,
and speak like this.”

[image]\\
	}
}
{
}

\Verse{6}
{
	\hE{}
}
{
	\eE{
		And he went back to him, and here he was, standing up by his burnt
offering, he and all the chiefs of Moab.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hE{}
}
{
	\eE{
		And he took up his pronouncement, and he said:

Balak led me from Aram,

Moab’s king from mountains of the East.

“Come, curse Jacob for me!

Come, denounce Israel!”

[image]\\
	}
}
{
}

\Verse{8}
{
	\hE{}
}
{
	\eE{
		How shall I execrate whom God hasn’t execrated?

And how shall I denounce whom YHWH hasn’t denounced?

[image]\\
	}
}
{
}

\Verse{9}
{
	\hE{}
}
{
	\eE{
		For from the top of rocks I see it,

and from hills I view it.

Here: a people dwelling separate

and not reckoned among the nations.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		Who has counted the dust of Jacob

and the number of a fourth of Israel?

May my soul die the death of the righteous,

and may my future be like his!

[image]\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		And Balak said to Balaam, “What have you done to me?! I took you to
execrate my enemies. And, here, you’ve blessed them!”

[image]\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		And he answered and said, “Isn’t it that what ever YHWH sets in my
mouth, that is what I’ll watch out to say?!”

[image]\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		And Balak said to him, “Come on with me to another place from which
you’ll see it. You’ll see nothing but its edge, and you won’t see all of
it. And execrate it for me from there.”

[image]\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		And he took him to the field of Zophim, to the top of Pisgah, and he
built seven altars and offered a bull and a ram on each altar.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		And he said to Balak, “Stand up here by your burnt offering, and I’ll
be communicated with here.”

[image]\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		And YHWH was communicated to Balaam, and He set a word in his mouth
and said, “Go back to Balak, and you shall speak this.”

[image]\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		And he came to him, and here he was, standing up by his burnt
offering, and the chiefs of Moab were with him. And Balak said to him,
“What did YHWH speak?”

[image]\\
	}
}
{
}

\Verse{18}
{
	\hE{}
}
{
	\eE{
		And he took up his pronouncement, and he said:

Get up, Balak, and listen.

Hear me, son of Zippor.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		God is not a man, that He would lie,

or a human being, that He would regret.

Has He said and will not do

or spoken and will not bring it about?

[image]\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		Here, I was taken to bless,

and He blessed, and I won’t take it back.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		He didn’t find harm in Jacob,

and He didn’t see trouble in Israel.

YHWH, its God, is with it,

and a shout for a king is in it.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hE{}
}
{
	\eE{
		God who brought them out from Egypt is like a wild ox’s horns for it.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hE{}
}
{
	\eE{
		For there’s no divination against Jacob

and no enchantment against Israel.

At this time it will be said to Jacob

and to Israel: “What has God done?”

[image]

------------------------------------------------------------------------

Numbers 23:24

²⁴ Here, a people will get up like a feline

and like a lion will raise itself.

It won’t lie down until it has eaten prey

and until it has drunk blood of carcasses.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hE{}
}
{
	\eE{
		And Balak said to Balaam, “Don’t do either: execrate them or bless
them!”

[image]\\
	}
}
{
}

\Verse{26}
{
	\hE{}
}
{
	\eE{
		And Balaam answered, and he said to Balak, “Didn’t I speak to you,
saying, ‘Everything that YHWH will speak, that is what I’ll do’?”

[image]\\
	}
}
{
}

\Verse{27}
{
	\hE{}
}
{
	\eE{
		And Balak said to Balaam, “Come on. I’ll take you to another place.
Maybe it will be right in God’s eyes, and you’ll execrate it for me from
there.”

[image]\\
	}
}
{
}

\Verse{28}
{
	\hE{}
}
{
	\eE{
		And Balak took Balaam to the top of Peor, which looks out over
Jeshimon.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hE{}
}
{
	\eE{
		And Balaam said to Balak, “Build seven altars for me here and prepare
seven bulls and seven rams for me here.”

[image]\\
	}
}
{
}

