\Chapter{24}

\Verse{1}
{
	\hE{}
}
{
	\eE{
		24

¹ And Balaam saw that it was good in YHWH’s eyes to bless Israel, and he
did not go as in previous times to divinations. And he turned his face
to the wilderness,

[image]\\
	}
}
{
}

\Verse{2}
{
	\hE{}
}
{
	\eE{
		and Balaam raised his eyes and saw Israel, tenting according to its
tribes, and God’s spirit came on him.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hE{}
}
{
	\eE{
		And he took up his pronouncement, and he said:

Word of Balaam, son of Beor,

and word of the man, opened of eye;

[image]\\
	}
}
{
}

\Verse{4}
{
	\hE{}
}
{
	\eE{
		word of the one who hears God’s sayings,

who sees Shadday’s vision,

falling, but with eyes uncovered.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hE{}
}
{
	\eE{
		How good your tents are, Jacob,

your tabernacles, Israel.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hE{}
}
{
	\eE{
		They spread like palms,

like gardens by a river,

like aloes YHWH planted,

like cedars by water.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hE{}
}
{
	\eE{
		It drips water from its branches

and its seed in plentiful water.

And its king will be higher than Agag,

and its kingdom will be elevated.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hE{}
}
{
	\eE{
		God who brought it out from Egypt

is like a wild ox’s horns for it.

He shall eat up nations, its foes,

and break their bones

and pierce with His arrows.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hE{}
}
{
	\eE{
		It bent, lay down, like a lion;

and, like a feline, who will rouse it?

Those who bless you: he’s blessed.

And those who curse you: he’s cursed.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		And Balak’s anger flared at Balaam, and he wrung his hands, and Balak
said to Balaam, “I called you to execrate my enemies; and, here, you’ve
blessed these three times!

[image]\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		And now, flee to your place! I said I would honor you; and, here, YHWH
has held you back from honor!”

[image]\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		And Balaam said to Balak, “Didn’t I speak to your messengers whom you
sent to me as well, saying,

[image]\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		‘If Balak would give me a houseful of silver and gold of his I
wouldn’t be able to go against the mouth of YHWH, to do good or bad from
my own heart. Whatever YHWH speaks, that is what I’ll speak.’

[image]\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		And now, here, I’m going to my people. Come. I’ll advise you of what
this people will do to your people in the future days.”

[image]\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		And he took up his pronouncement, and he said:

Word of Balaam, son of Beor,

and word of the man whose eye is whole;

[image]\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		word of the one who hears God’s sayings

and who knows the Highest’s knowledge,

who sees Shadday’s vision,

falling, but with eyes uncovered.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		I see it—and not now;

I view it—and not close:

a star has stepped from Jacob,

and a scepter has come up from Israel

and pierced the temples of Moab

and the crown of all the children of Seth.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hE{}
}
{
	\eE{
		And Edom was a possession,

and Seir was a possession of its enemies,

and Israel was making triumph.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		And one from Jacob dominated

and destroyed a remnant from a city.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		And he saw Amalek, and he took up his pronouncement, and he said:

Amalek was foremost of nations,

and its future arrives at destruction.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		And he saw the Kenites, and he took up his pronouncement and said:

Your residence is strong,

and set your nest in a cliff.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hE{}
}
{
	\eE{
		But Cain will be for burning

How long will Asshur hold you prisoner?

[image]\\
	}
}
{
}

\Verse{23}
{
	\hE{}
}
{
	\eE{
		And he took up his pronouncement, and he said:

Woe. Who will live more than what God set him?

[image]\\
	}
}
{
}

\Verse{24}
{
	\hE{}
}
{
	\eE{
		And ships from the hand of Kittim:

And they degraded Asshur, and they degraded Eber.

And it, too, arrives at destruction.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hE{}
}
{
	\eE{
		And Balaam got up and went, and he went back to his place. And Balak,
too, went his way.

[image]\\
	}
}
{
}

