\Chapter{25}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		25

¹ And Israel lived in Shittim, and the people began to prostitute
themselves to the daughters of Moab:

[image]\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		And they attracted the people to the sacrifices of their gods, and the
people ate and bowed to their gods,

[image]\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		and Israel was associated with Baal Peor. And YHWH’s anger flared at
Israel.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said to Moses, “Take all of the leaders of the people and hang
them in front of the sun, and YHWH’s flaring anger will go back from
Israel.”

[image]\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		And Moses said to Israel’s judges, “Each of you, kill those of his
people who are associated with Baal Peor.”

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And, here, a man from the children of Israel came and brought forward a
Midianite woman to his brothers before the eyes of Moses and before the
eyes of all the congregation of the children of Israel while they were
mourning at the entrance of the Tent of Meeting.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And Phinehas son of Eleazar son of Aaron, the priest, saw, and he got
up from among the congregation and took a spear in his hand.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And he came after the Israelite man to the enclosure and ran the two of
them through, the Israelite man and the woman, to her stomach, and the
plague was halted from the children of Israel.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And the dead in the plague were twenty-four thousand.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		PHINEHAS

¹⁰ And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		“Phinehas son of Eleazar son of Aaron, the priest, has turned back my
fury from the children of Israel by his carrying out my jealousy among
them, so I didn’t finish the children of Israel in my jealousy.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		Therefore, say: Here, I’m giving him my covenant of peace,

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		and it shall be his, and his seed’s after him, a covenant of eternal
priesthood, because he was jealous for his God, and he made atonement
for the children of Israel.”

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And the name of the stricken Israelite man, who was struck with the
Midianite woman, was Zimri son of Salu, chieftain of a father’s house of
the Simeonites.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And the name of the stricken Midianite woman was Cozbi daughter of
Zur. He was head of the people of a father’s house in Midian.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		“Afflict the Midianites—and you shall strike them—

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		because they have been afflicting you with their conspiracies that
they made against you over the matter of Peor and over the matter of
Cozbi, the daughter of a chieftain of Midian, their sister who was
struck on the day of the plague over the matter of Peor.”

[image]\\
	}
}
{
}

\Verse{19}
{
	\hOther{}
}
{
	\eOther{
		And it was after the plague.

[image]\\
	}
}
{
}

