\Chapter{26}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		26

¹ And YHWH said to Moses and to Eleazar son of Aaron, the priest, saying,

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Add up the heads of all of the congregation of Israel from twenty
years old and up, by their fathers’ house, everyone going out to
Israel’s army.”

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And Moses and Eleazar, the priest, spoke with them in the plains of
Moab by the Jordan toward Jericho, saying,

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		“From twenty years old and up,” as YHWH commanded Moses and the
children of Israel who had gone out from the land of Egypt.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		Reuben, Israel’s firstborn; the children of Reuben:

Hanoch: the family of the Hanochites. Of Pallu: the family of the
Palluites.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		Of Hezron: the family of the Hezronites. Of Carmi: the family of the
Carmites.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		These are the families of the Reubenites, and their counts were
forty-three thousand seven hundred thirty.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And Pallu’s sons: Eliab.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And Eliab’s sons: Nemuel and Dathan and Abiram. That is the Dathan and
Abiram, prominent ones of the congregation, who fought against Moses and
against Aaron in Korah’s congregation when they fought against YHWH,

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		and the earth opened its mouth and swallowed them and Korah when the
congregation died, when the fire consumed the two hundred fifty men, and
they became a sign.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		But Korah’s sons did not die.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		The children of Simeon by their families:

Of Nemuel: the family of the Nemuelites. Of Jamin: the family of the
Jaminites. Of Jachin: the family of the Jachinites.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		Of Zerah: the family of the Zerahites. Of Saul: the family of the
Saulites.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		These are the families of the Simeonites: twenty-two thousand two
hundred.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		The children of Gad by their families:

Of Zephon: the family of the Zephonites. Of Haggi: the family of the
Haggites. Of Shuni: the family of the Shunites.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		Of Ozni: the family of the Oznites. Of Eri: the family of the Erites.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		Of Arod: the family of the Arodites. Of Areli: the family of the
Arelites.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		These are the families of the children of Gad by their counts: forty
thousand five hundred.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		Judah’s sons were Er and Onan, but Er and Onan died in the land of
Canaan.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		Then the children of Judah by their families were:

Of Shelah: the family of the Shelanites. Of Perez: the family of the
Perezites. Of Zerah: the family of the Zerahites.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And the children of Perez were: Of Hezron: the family of the
Hezronites. Of Hamul: the family of the Hamulites.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		These are the families of Judah by their counts: seventy-six thousand
five hundred.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		The children of Issachar by their families:

Tola: the family of the Tolaites. Of Puwah, the family of the Punites.

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		Of Jashub: the family of the Jashubites. Of Shimron: the family of the
Shimronites.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		These are the families of Issachar by their counts: sixty-four
thousand three hundred.

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		The children of Zebulun by their families:

Of Sered: the family of the Seredites. Of Elon: the family of the
Elonites. Of Jahleel: the family of the Jahleelites.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		These are the families of the Zebulunites by their counts: sixty
thousand five hundred.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		The children of Joseph by their families were Manasseh and Ephraim.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		Of the children of Manasseh: Of Machir: the family of the Machirites.
And Machir fathered Gilead. Of Gilead: the family of the Gileadites.

[image]\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		These are the children of Gilead: Of Iezer: the family of the
Iezerites. Of Helek: the family of the Helekites.

[image]\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		And Asriel: the family of the Asrielites. And Shechem: the family of
the Shechemites.

[image]\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		And Shemida: the family of the Shemidaites. And Hepher: the family of
the Hepherites.

[image]\\
	}
}
{
}

\Verse{33}
{
	\hP{}
}
{
	\eP{
		And Zelophehad son of Hepher had no sons, just daughters, and the
names of Zelophehad’s daughters were Mahlah and Noah, Hoglah, Milcah,
and Tirzah.

[image]\\
	}
}
{
}

\Verse{34}
{
	\hP{}
}
{
	\eP{
		These are the families of Manasseh; and their counts: fifty-two
thousand seven hundred.

[image]\\
	}
}
{
}

\Verse{35}
{
	\hP{}
}
{
	\eP{
		These are the children of Ephraim by their families:

Of Shuthelah: the family of the Shuthelahites. Of Becher: the family of
the Becherites. Of Tahan: the family of the Tahanites.

[image]\\
	}
}
{
}

\Verse{36}
{
	\hP{}
}
{
	\eP{
		And these are the children of Shuthelah: Of Eran: the family of the
Eranites.

[image]\\
	}
}
{
}

\Verse{37}
{
	\hP{}
}
{
	\eP{
		These are the families of the children of Ephraim by their counts:
thirty-two thousand five hundred. These are the sons of Joseph after
their families.

[image]\\
	}
}
{
}

\Verse{38}
{
	\hP{}
}
{
	\eP{
		The children of Benjamin by their families:

Of Bela: the family of the Belaites. Of Ashbel: the family of the
Ashbelites. Of Ahiram: the family of the Ahiramites.

[image]\\
	}
}
{
}

\Verse{39}
{
	\hP{}
}
{
	\eP{
		Of Shephupham: the family of the Shuphamites. Of Hupham: the family of
the Huphamites.

[image]\\
	}
}
{
}

\Verse{40}
{
	\hP{}
}
{
	\eP{
		And the children of Bela were Ard and Naaman: the family of the
Ardites. Of Naaman: the family of the Naamites.

[image]\\
	}
}
{
}

\Verse{41}
{
	\hP{}
}
{
	\eP{
		These are the children of Benjamin by their families; and their
counts: forty-five thousand six hundred.

[image]\\
	}
}
{
}

\Verse{42}
{
	\hP{}
}
{
	\eP{
		These are the children of Dan by their families:

Of Shuham: the family of the Shuhamites. These are the families of Dan
after their families.

[image]\\
	}
}
{
}

\Verse{43}
{
	\hP{}
}
{
	\eP{
		All the families of the Shuhamites by their counts: sixty-four
thousand four hundred.

[image]\\
	}
}
{
}

\Verse{44}
{
	\hP{}
}
{
	\eP{
		The children of Asher by their families:

Of Imnah: the family of Imnah. Of Ishvi: the family of the Ishvites. Of
Beriah: the family of the Beriites.

[image]\\
	}
}
{
}

\Verse{45}
{
	\hP{}
}
{
	\eP{
		Of the children of Beriah: Of Heber: the family of the Heberites. Of
Malchiel: the family of the Malchielites.

[image]\\
	}
}
{
}

\Verse{46}
{
	\hP{}
}
{
	\eP{
		And Asher’s daughter’s name was Serah.

[image]\\
	}
}
{
}

\Verse{47}
{
	\hP{}
}
{
	\eP{
		These are the families of the children of Asher by their counts:
fifty-three thousand four hundred.

[image]\\
	}
}
{
}

\Verse{48}
{
	\hP{}
}
{
	\eP{
		The children of Naphtali by their families:

Of Jahzeel: the family of the Jahzeelites. Of Guni: the family of the
Gunites.

[image]\\
	}
}
{
}

\Verse{49}
{
	\hP{}
}
{
	\eP{
		Of Jezer: the family of the Jezerites. Of Shillem: the family of the
Shillemites.

[image]\\
	}
}
{
}

\Verse{50}
{
	\hP{}
}
{
	\eP{
		These are the families of Naphtali by their families, and their
counts: forty-five thousand four hundred.

[image]\\
	}
}
{
}

\Verse{51}
{
	\hP{}
}
{
	\eP{
		These are the counts of the children of Israel: six hundred one
thousand seven hundred thirty.

[image]\\
	}
}
{
}

\Verse{52}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{53}
{
	\hP{}
}
{
	\eP{
		“The land shall be distributed to these as a legacy with the number of
names.

[image]\\
	}
}
{
}

\Verse{54}
{
	\hP{}
}
{
	\eP{
		For the large you shall make its legacy larger, and for the small you
shall make its legacy smaller. Each man will be given his legacy
according to his counts.

[image]\\
	}
}
{
}

\Verse{55}
{
	\hP{}
}
{
	\eP{
		Just: the land shall be distributed by lot. They shall have a legacy
by the names of their fathers’ tribes.

[image]\\
	}
}
{
}

\Verse{56}
{
	\hP{}
}
{
	\eP{
		Its legacy shall be distributed according to the lot, whether large or
small.”

[image]\\
	}
}
{
}

\Verse{57}
{
	\hP{}
}
{
	\eP{
		And these are the counts of the Levites by their families:

Of Gershon: the family of the Gershonites. Of Kohath: the family of the
Kohathites. Of Merari: the family of the Merarites.

[image]\\
	}
}
{
}

\Verse{58}
{
	\hP{}
}
{
	\eP{
		These are the families of the Levites: the family of the Libnites, the
family of the Hebronites, the family of the Mahlites, the family of the
Mushites, the family of the Korahites.

And Kohath fathered Amram.

[image]\\
	}
}
{
}

\Verse{59}
{
	\hP{}
}
{
	\eP{
		And the name of Amram’s wife was Jochebed, a daughter of Levi, who was
born to Levi in Egypt. And she gave birth for Amram to Aaron and Moses
and Miriam, their sister.

[image]\\
	}
}
{
}

\Verse{60}
{
	\hP{}
}
{
	\eP{
		And Nadab and Abihu, Eleazar and Ithamar were born to Aaron.

[image]\\
	}
}
{
}

\Verse{61}
{
	\hP{}
}
{
	\eP{
		And Nadab and Abihu died when they brought forward unfitting fire in
front of YHWH.

[image]\\
	}
}
{
}

\Verse{62}
{
	\hP{}
}
{
	\eP{
		And their counts were twenty-three thousand, every male from a month
old and up, because they were not counted among the children of Israel
because a legacy was not given to them among the children of Israel.

[image]\\
	}
}
{
}

\Verse{63}
{
	\hP{}
}
{
	\eP{
		These are the counts of Moses and Eleazar, the priest, who counted the
children of Israel in the plains of Moab by the Jordan toward Jericho;

[image]\\
	}
}
{
}

\Verse{64}
{
	\hP{}
}
{
	\eP{
		and there was not a man among these from the counts of Moses and
Aaron, the priest, who counted the children of Israel in the wilderness
of Sinai,

[image]\\
	}
}
{
}

\Verse{65}
{
	\hP{}
}
{
	\eP{
		because YHWH said of them, “They shall die in the wilderness,” and not
a man was left of them except Caleb son of Jephunneh and Joshua son of
Nun.

[image]\\
	}
}
{
}

