\Chapter{27}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		27

¹ And the daughters of Zelophehad son of Hepher son of Gilead son of
Machir son of Manasseh, of the families of Manasseh son of Joseph, came
forward. And these are his daughters’ names: Mahlah, Noah, and Hoglah
and Milcah and Tirzah.

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		And they stood in front of Moses and in front of Eleazar, the priest,
and in front of the chieftains and all the congregation at the entrance
of the Tent of Meeting, saying,

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		“Our father died in the wilderness. And he wasn’t among the
congregation who were gathered against YHWH: in Korah’s congregation.
Rather, he died through his own sin. And he had no sons.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		Why should our father’s name be subtracted from among his family
because he didn’t have a son? Give us a possession among our father’s
brothers.”

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And Moses brought their case forward in front of YHWH.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Moses, saying,

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		“Zelophehad’s daughters speak right. You shall give them a possession
for a legacy among their father’s brothers, and you shall pass their
father’s legacy to them.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And you shall speak to the children of Israel, saying, ‘A man who will
die and not have a son: you shall pass his legacy to his daughter.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And if he does not have a daughter, then you shall give his legacy to
his brothers.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And if he does not have brothers, then you shall give his legacy to
his father’s brothers.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And if there are no brothers of his father, then you shall give his
legacy to his relative who is closest to him of his family, and he shall
possess it.’ And it shall become a law of judgment for the children of
Israel, as YHWH commanded Moses.”

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Moses, “Go up to this mountain of Abarim and see the
land that I’ve given to the children of Israel.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And you’ll see it, and then you’ll be gathered to your people, you as
well, as Aaron, your brother, was gathered,

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		because you rebelled against my word in the wilderness of Zin in the
congregation’s quarrel to make me holy with water before their eyes.
That is the water of Meribah of Kadesh at the wilderness of Zin.”

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And Moses spoke to YHWH, saying,

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		“Let YHWH, God of the spirits of all flesh, appoint a man over the
congregation

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		who will go out in front of them and who will come in in front of them
and who will bring them out and who will bring them in, so YHWH’s
congregation won’t be like sheep that don’t have a shepherd.”

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Moses, “Take Joshua son of Nun, a man with spirit in
him, and lay your hand on him.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And you shall stand him in front of Eleazar, the priest, and in front
of all the congregation, and you shall command him before their eyes.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And you shall put some of your eminence on him so that all the
congregation of the children of Israel will hear.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And he shall stand in front of Eleazar, the priest; and he shall ask
him in judgment of the Urim in front of YHWH. By his word they shall go
out, and by his word they shall come in, he and all the children of
Israel with him and all the congregation.”

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And Moses did as YHWH commanded him, and he took Joshua and stood him
in front of Eleazar, the priest, and in front of all the congregation.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		And he laid his hands on him and commanded him, as YHWH had spoken by
Moses’ hand.

[image]\\
	}
}
{
}

