\Chapter{28}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		28

¹ And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Command the children of Israel, and you shall say to them: You shall
observe to bring forward my sacrifice to me, my bread, for my offering
by fire, my pleasant smell, at its appointed time.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		“And you shall say to them: This is the offering by fire that you shall
bring forward to YHWH: two unblemished one-year-old lambs per day as a
continual burnt offering.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		You shall do one lamb in the morning, and you shall do the second lamb
‘between the two evenings.’

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And a tenth of an ephah of fine flour for a grain offering, mixed with
a fourth of a hin of pressed oil,

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		the continual burnt offering that was done at Mount Sinai for a
pleasant smell, an offering by fire to YHWH.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And its libation shall be a fourth of a hin for one lamb. Pour a
libation of beer in the holy place for YHWH.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And you shall do the second lamb ‘between the two evenings,’ and you
shall do it like the morning grain offering and like its libation, an
offering by fire of a pleasant smell to YHWH.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		“And on the Sabbath day two unblemished one-year-old lambs and two
tenths of fine flour, a grain offering, mixed with oil, and its
libation:

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		the burnt offering of each Sabbath in its week, beside the continual
burnt offering and its libation.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		“And at the beginning of your months you shall bring forward a burnt
offering to YHWH: two bulls of the cattle and one ram, seven unblemished
one-year-old lambs,

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		with three tenths of fine flour, a grain offering, mixed with oil for
one bull and two tenths of fine flour mixed with oil for the one ram,

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		and one tenth of fine flour, a grain offering, mixed with oil for each
lamb, a burnt offering as a pleasant smell, an offering by fire to YHWH.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And their libations: half a hin will be for a bull and a third of a
hin for a ram and a fourth of a hin for a lamb—wine. This is the burnt
offering of each new month in its month for the months of the year.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And one goat for a sin offering to YHWH shall be done, beside the
continual burnt offering and its libation.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		“And in the first month on the fourteenth day of the month is a
Passover to YHWH.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And on the fifteenth day of this month is a holiday. For seven days
unleavened bread shall be eaten.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		On the first day is a holy assembly. You shall not do any act of work.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And you shall bring forward an offering by fire, a burnt offering to
YHWH. You shall have two bulls of the cattle and one ram and seven
unblemished one-year-old lambs.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And their grain offering shall be fine flour mixed with oil. You shall
do three tenths for a bull and two tenths for a ram.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And you shall do one tenth for each lamb, for the seven lambs.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And one goat for a sin offering to make atonement over you.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		You shall do these aside from the morning burnt offering that is for
the continual burnt offering.

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		You shall do food as a fire offering, a pleasant smell to YHWH, like
these daily for seven days. It shall be done beside the continual burnt
offering and its libation.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And on the seventh day you shall have a holy assembly. You shall not
do any act of work.

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		“And on the Day of Firstfruits, when you bring a new grain offering to
YHWH on your Feast of Weeks, you shall have a holy assembly. You shall
not do any act of work.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		And you shall bring forward a burnt offering for a plea-sant smell to
YHWH: two bulls of the cattle, one ram, seven one-year-old lambs

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		and their grain offering, fine flour mixed with oil, three tenths for
one bull, two tenths for one ram,

[image]\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		one tenth for each lamb, for the seven lambs,

[image]\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		one goat to make atonement over you.

[image]\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		You shall do it aside from the continual burnt offering and its grain
offering—they shall be unblemished for you—and their libations.

[image]\\
	}
}
{
}

