\Chapter{30}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		30

¹ And Moses said it to the children of Israel, according to everything
that YHWH commanded Moses.

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		TRIBES

² And Moses spoke to the heads of the tribes of the children of Israel,
saying, “This is the thing that YHWH commanded:

[image]

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		A man who will make a vow to YHWH or has sworn an oath to make a
restriction on himself shall not desecrate his word. He shall do it
according to everything that comes out of his mouth.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		“And a woman who will make a vow to YHWH and made a restriction in her
father’s house in her youth,

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		and her father hears her vow and her restriction that she made on
herself, and her father keeps quiet to her, then all her vows shall
stand, and every restriction that she made on herself shall stand.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		But if her father held her back on the day he heard all her vows and
her restrictions that she made on herself, it will not stand. And YHWH
will forgive her because her father held her back.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		“And if she will have a husband while her vows or the thing she let out
of her lips with which she restricted herself are on her,

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		and her husband hears and keeps quiet on the day he heard it, then her
vows will stand, and her restrictions that she made on herself will
stand.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		But if, on the day her husband hears it, he will hold her back and will
break her vow that is on her and what was let out of her lips by which
she restricted herself, then YHWH will forgive her.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		“And a widow’s or divorced woman’s vow, everything by which she has
restricted herself, shall stand regarding her.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		“And if she vowed or made a restriction on herself by an oath at her
husband’s house,

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		and her husband heard it and kept quiet to her—he did not hold her
back—then all her vows shall stand, and every restriction that she made
on herself shall stand.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		But if her husband broke them on the day he heard all that came out of
her lips for her vows and for restricting herself, it shall not stand.
Her husband had broken them, and YHWH will forgive her.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		Every vow and every oath of restriction to degrade oneself: her
husband shall make it stand, and her husband shall break it.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And if her husband will keep quiet in regard to her from that day to
the next, then he has made all her vows and all her restrictions that
are on her stand. He has made them stand because he kept quiet to her on
the day he heard it.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And if he will break them after he has heard them, then he shall bear
her crime.”

[image]\\
	}
}
{
}

\Verse{17}
{
	\hOther{}
}
{
	\eOther{
		These are the laws that YHWH commanded Moses between a man and his
wife, between a father and his daughter in her youth at her father’s
house.

[image]\\
	}
}
{
}

