\Chapter{33}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		These are the travels of the children of Israel who went out from the
land of Egypt by their armies by the hand of Moses and Aaron.

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		And Moses wrote their stops for their travels by YHWH’s word, and these
are their travels and their stops.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And they traveled from Rameses in the first month on the fifteenth day
of the first month. On the day after the Passover, the children of
Israel went out with a high hand before the eyes of all Egypt.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And the Egyptians were burying those whom YHWH had struck among them:
every firstborn. And YHWH had made judgments on their gods.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And the children of Israel traveled from Rameses and camped in Succoth.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And they traveled from Succoth and camped in Etham, which is at the
edge of the wilderness.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And they traveled from Etham and turned back toward Pi-hahiroth, which
is in front of Baal-Zephon: and they camped in front of Migdol.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And they traveled from before Pi-hahiroth and passed through the sea to
the wilderness. And they went three days’ journey in the wilderness of
Etham and camped in Marah.

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And they traveled from Marah and came to Elim. And in Elim were twelve
springs of water and seventy palm trees. And they camped there.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And they traveled from Elim and camped by the Red Sea.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And they traveled from the Red Sea and camped in the wilderness of
Sin.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And they traveled from the wilderness of Sin and camped in Dophkah.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And they traveled from Dophkah and camped in Alush.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And they traveled from Alush and camped at Rephidim. And there was no
water there for the people to drink.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And they traveled from Rephidim and camped in the wilderness of Sinai.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And they traveled from the wilderness of Sinai and camped at Kibroth
Hattaavah.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And they traveled from Kibroth Hattaavah and camped at Hazeroth.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And they traveled from Hazeroth and camped in Rithmah.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And they traveled from Rithmah and camped at Rimmon-parez.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And they traveled from Rimmon-parez and camped in Libnah.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And they traveled from Libnah and camped at Rissah.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And they traveled from Rissah and camped in Kehelathah.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		And they traveled from Kehelathah and camped at Mount Shapher.

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		And they traveled from Mount Shapher and camped in Haradah.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And they traveled from Haradah and camped in Makheloth.

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		And they traveled from Makheloth and camped at Tahath.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		And they traveled from Tahath and camped at Tarah.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		And they traveled from Tarah and camped in Mithkah.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		And they went from Mithkah and camped in Hashmonah.

[image]\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		And they traveled from Hashmonah and camped at Moseroth.

[image]\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		And they traveled from Moseroth and camped in Bene-jaakan.

[image]\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		And they traveled from Bene-jaakan and camped at Hor-haggidgad.

[image]\\
	}
}
{
}

\Verse{33}
{
	\hP{}
}
{
	\eP{
		And they went from Hor-haggidgad and camped in Jotbathah.

[image]\\
	}
}
{
}

\Verse{34}
{
	\hP{}
}
{
	\eP{
		And they traveled from Jotbathah and camped at Ebronah.

[image]\\
	}
}
{
}

\Verse{35}
{
	\hP{}
}
{
	\eP{
		And they traveled from Ebronah and camped at Ezion-geber.

[image]\\
	}
}
{
}

\Verse{36}
{
	\hP{}
}
{
	\eP{
		And they traveled from Ezion-geber and camped in the wilderness of
Zin. That is Kadesh.

[image]\\
	}
}
{
}

\Verse{37}
{
	\hP{}
}
{
	\eP{
		And they traveled from Kadesh and camped in Mount Hor, at the edge of
the land of Edom.

[image]\\
	}
}
{
}

\Verse{38}
{
	\hP{}
}
{
	\eP{
		And Aaron, the priest, went up into Mount Hor at the word of YHWH and
died there in the fortieth year after the children of Israel came out of
the land of Egypt, in the fifth month, on the first day of the month.

[image]\\
	}
}
{
}

\Verse{39}
{
	\hP{}
}
{
	\eP{
		And Aaron was a hundred twenty-three years old when he died in Mount
Hor.

[image]\\
	}
}
{
}

\Verse{40}
{
	\hP{}
}
{
	\eP{
		And the Canaanite, the king of Arad, who lived in the Negeb in the
land of Canaan, heard of the coming of the children of Israel.

[image]\\
	}
}
{
}

\Verse{41}
{
	\hP{}
}
{
	\eP{
		And they traveled from Mount Hor and camped in Zalmonah.

[image]\\
	}
}
{
}

\Verse{42}
{
	\hP{}
}
{
	\eP{
		And they traveled from Zalmonah and camped in Punon.

[image]\\
	}
}
{
}

\Verse{43}
{
	\hP{}
}
{
	\eP{
		And they traveled from Punon and camped in Oboth.

[image]\\
	}
}
{
}

\Verse{44}
{
	\hP{}
}
{
	\eP{
		And they traveled from Oboth and camped in Iyye-abarim, in the border
of Moab.

[image]\\
	}
}
{
}

\Verse{45}
{
	\hP{}
}
{
	\eP{
		And they traveled from Iyyim and camped in Dibon-gad.

[image]\\
	}
}
{
}

\Verse{46}
{
	\hP{}
}
{
	\eP{
		And they traveled from Dibon-gad and camped in Almon-diblathaim.

[image]\\
	}
}
{
}

\Verse{47}
{
	\hP{}
}
{
	\eP{
		And they traveled from Almon-diblathaim and camped in the mountains of
Abarim in front of Nebo.

[image]\\
	}
}
{
}

\Verse{48}
{
	\hP{}
}
{
	\eP{
		And they traveled from the mountains of Abarim and camped in the
plains of Moab by the Jordan toward Jericho.

[image]\\
	}
}
{
}

\Verse{49}
{
	\hP{}
}
{
	\eP{
		And they camped by the Jordan from Beth-jeshimoth to Abel-shittim in
the plains of Moab.

[image]\\
	}
}
{
}

\Verse{50}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses in the plains of Moab by the Jordan toward
Jericho, saying,

[image]\\
	}
}
{
}

\Verse{51}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel, and you shall say to them: When you
cross the Jordan to the land of Canaan,

[image]\\
	}
}
{
}

\Verse{52}
{
	\hP{}
}
{
	\eP{
		you shall dispossess all the residents of the land in front of you,
and destroy all their carved figures, and you shall destroy all their
molten images and demolish all their high places.

[image]\\
	}
}
{
}

\Verse{53}
{
	\hP{}
}
{
	\eP{
		And you shall take possession of the land and live in it, because I’ve
given the land to you to possess it.

[image]\\
	}
}
{
}

\Verse{54}
{
	\hP{}
}
{
	\eP{
		And you shall give legacies of the land by lot, by your families: for
the large you shall make its legacy larger, and for the small you shall
make its legacy smaller. Wherever the lot indicates for it shall belong
to it. You shall give legacies to the tribes of your fathers.

[image]\\
	}
}
{
}

\Verse{55}
{
	\hP{}
}
{
	\eP{
		And if you don’t dispossess the residents of the land in front of you,
then those whom you leave of them will become sticks in your eyes and
thorns in your sides, and they’ll afflict you on the land in which
you’re living.

[image]\\
	}
}
{
}

\Verse{56}
{
	\hP{}
}
{
	\eP{
		And it will be that, as I meant to do to them, I’ll do to you!”

[image]\\
	}
}
{
}

