\Chapter{34}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		34

¹ And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Command the children of Israel, and you shall say to them: When you
come to the land of Canaan, this is the land that will fall to you as a
legacy, the land of Canaan by its borders:

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And the southern side for you shall be from the wilderness of Zin next
to Edom, and the southern border for you shall be from the edge of the
Dead Sea to the east.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And the border for you shall turn from the south to the ascent of
Akrabim and will pass to Zin, and its extent shall be from the south to
Kadesh-barnea, and it shall go out to Hazar-addar and pass to Azmon.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And the border shall turn from Azmon to the Wadi of Egypt, and its
extent shall be to the sea.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And the western border: and the big sea shall be a border for you. This
shall be the western border for you.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And this shall be the northern border for you: you shall mark from the
big sea to Mount Hor,

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		from Mount Hor you shall mark to the entrance of Hamath, and the
border’s extent shall be to Zedad,

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		and the border shall go out to Ziphron, and its extent shall be to
Hazar-enan. This shall be the northern border for you.

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And you shall mark for the border to the east from Hazar-enan to
Shepham,

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		and the border shall go down from Shepham to Riblah at the east of
Ain, and the border shall go down and rub on the shoulder of the Sea of
Kinneret on the east,

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		and the border shall go down to the Jordan, and its extent will be to
the Dead Sea. This shall be the land for you by its borders all around.”

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And Moses commanded the children of Israel, saying, “This is the land
that you shall give as legacies by lot, which YHWH commanded to give to
the nine tribes and the half of a tribe.”

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		Because the tribe of the children of the Reubenites by their fathers’
house and the tribe of the children of the Gadites by their fathers’
house had taken and half of the tribe of Manasseh had taken their
legacy.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		The two tribes and the half of a tribe had taken their legacy from
across the Jordan toward Jericho on the east side—to the east.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		“These are the names of the people who will give the land as legacies
to you: Eleazar, the priest, and Joshua son of Nun;

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		and you shall take one chieftain for each tribe to give the land as
legacies.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And these are the people’s names: For the tribe of Judah, Caleb son of
Jephunneh.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And for the tribe of the children of Simeon, Samuel son of Ammihud.

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		For the tribe of Benjamin, Elidad son of Chislon.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And for the tribe of the children of Dan, a chieftain, Bukki son of
Jogli.

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		For the children of Joseph: for the tribe of the children of Manasseh,
a chieftain, Hanniel son of Ephod;

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		and for the tribe of the children of Ephraim, a chieftain, Kemuel son
of Shiphtan.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And for the tribe of the children of Zebulun, a chieftain, Elizaphan
son of Parnach.

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		And for the tribe of the children of Issachar, a chieftain, Paltiel
son of Azzan.

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		And for the tribe of the children of Asher, a chieftain, Ahihud son of
Shelomi.

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		And for the tribe of the children of Naphtali, a chieftain, Pedahel
son of Ammihud.”

[image]\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		These are the ones whom YHWH commanded to give the children of Israel
legacies in the land of Canaan.

[image]\\
	}
}
{
}

