\Chapter{35}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		35

¹ And YHWH spoke to Moses in the plains of Moab by the Jordan toward
Jericho, saying,

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Command the children of Israel that, from the legacy of their
possession, they shall give the Levites cities in which to live, and you
shall give the Levites surrounding land for the cities all around them.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And the cities shall be theirs to live in, and their surrounding lands
shall be for their cattle and for their property and for their animals.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And the surrounding lands of the cities that you shall give to the
Levites: from the city wall outward, a thousand cubits all around.

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And you shall measure outside the city: on the eastern side two
thousand in cubits, and on the southern side two thousand in cubits, and
on the western side two thousand in cubits, and on the northern side two
thousand in cubits, and the city in the middle. This shall be the
surrounding lands of the cities for them.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And the cities that you shall give to the Levites: six cities of refuge
that you shall give for the manslayer to flee there, and you shall give
in addition to them forty-two cities.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		All the cities that you shall give to the Levites: forty-eight cities,
them and their surrounding lands.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And the cities that you shall give from the possession of the children
of Israel: from the larger you shall give more, and from the smaller you
shall give fewer. Each shall give some of his cities to the Levites
according to his legacy that they will give.”

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel, and you shall say to them: When you
cross the Jordan to the land of Canaan,

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		you shall establish cities; they shall be cities of refuge for you,
and a manslayer who strikes a life by mistake shall flee there.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And you shall have the cities for refuge from an avenger so the
manslayer will not die until he stands in front of the congregation for
judgment.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And the cities that you shall give: You shall have six cities of
refuge.

[image]\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		You shall put three of the cities across the Jordan, and you shall put
three of the cities in the land of Canaan. They shall be cities of
refuge.

[image]\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		“These six cities shall be for refuge for the children of Israel and
for the alien and for the visitor among them, for anyone who strikes a
life by mistake to flee there.

[image]\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		But if he struck him with an iron item so that he died, he is a
murderer. The murderer shall be put to death.

[image]\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And if he struck him with a stone in the hand by which one could die,
so that he died, he is a murderer. The murderer shall be put to death.

[image]\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		Or if he struck him with a wooden object in the hand by which one
could die, so that he died, he is a murderer. The murderer shall be put
to death.

[image]\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		The blood avenger, he shall kill the murderer. When he comes upon him,
he shall kill him.

[image]\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And if he pushed him in hatred or threw something on him through
scheming so that he died,

[image]\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		or if he struck him with his hand in enmity so that he died, the one
who struck shall be put to death. He is a murderer. The blood avenger
shall kill the murderer when he comes upon him.

[image]\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		But if by chance, not in enmity, he pushed him or threw any object on
him not through scheming,

[image]\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		or with any stone by which one could die, without seeing, so that he
dropped it on him so that he died, and he was not an enemy to him and
was not seeking to harm him,

[image]\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		then the congregation shall judge between the one who struck and the
blood avenger on the basis of these judgments.

[image]\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And the congregation shall rescue the manslayer from the blood
avenger’s hand, and the congregation shall bring him back to his city of
refuge to which he fled, and he shall live in it until the death of the
high priest whom one anointed with the holy oil.

[image]\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		But if the murderer will go out of the border of his city of refuge to
which he will flee,

[image]\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		and the blood avenger will find him outside of the border of his city
of refuge, and the blood avenger will murder the murderer, he does not
have blood,

[image]\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		because he shall live in his city of refuge until the high priest’s
death, and after the high priest’s death the murderer shall go back to
the land of his possession.

[image]\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		“And these shall become a law of judgment for you through your
generations in all your homes.

[image]\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		Anyone who strikes a life, the murderer shall be murdered by the mouth
of witnesses. And one witness shall not testify against a person so as
to die.

[image]\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		And you shall not take a ransom for a murderer’s life, because he did
wrong so as to die, but he shall be put to death.

[image]\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		And you shall not take a ransom to flee to his city of refuge, to go
back to live in the land until the priest’s death.

[image]\\
	}
}
{
}

\Verse{33}
{
	\hP{}
}
{
	\eP{
		So you shall not pollute the land in which you are. Because blood: it
will pollute the land, and the land will not have expiation for blood
that is spilled in it except by the blood of the one who spilled it!

[image]\\
	}
}
{
}

\Verse{34}
{
	\hP{}
}
{
	\eP{
		And you shall not make the land impure in which you are living, in
which I tent, because I, YHWH, tent among the children of Israel.”

[image]\\
	}
}
{
}

