\Chapter{36}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		36

¹ And the heads of the fathers of the family of the children of Gilead
son of Machir son of Manasseh, from the families of the children of
Joseph, came forward and spoke in front of Moses and in front of the
chieftains, heads of fathers of the children of Israel.

[image]\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		And they said, “YHWH commanded my lord to give the land as legacy by
lot to the children of Israel, and my lord was commanded by YHWH to give
the legacy of Zelophehad, our brother, to his daughters.

[image]\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		If they will become wives to one of the sons of the tribes of the
children of Israel, then their legacy will be subtracted from our
fathers’ legacy and added onto the legacy of the tribe to whom they will
belong, and it will be subtracted from our legacy by the lot.

[image]\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And if the children of Israel will have the jubilee, then their legacy
will be added onto the legacy of the tribe to whom they will belong, and
their legacy will be subtracted from the legacy of our fathers’ tribe.”

[image]\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And Moses commanded the children of Israel by YHWH’s word, saying, “The
children of Joseph speak right.

[image]\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		This is the thing that YHWH has commanded Zelophehad’s daughters,
saying: They shall become wives for any in whose eyes it is good,
except: they shall become wives to the family of their father’s tribe.

[image]\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		So a legacy of the children of Israel will not turn from tribe to
tribe, but the children of Israel shall each cling to the legacy of his
fathers’ tribe.

[image]\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And any daughter who inherits a legacy from the tribes of the children
of Israel shall become a wife to someone from a family of her father’s
tribe, so that the children of Israel will each inherit his fathers’
legacy,

[image]\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		and a legacy will not turn from a tribe to another tribe, but the
tribes of the children of Israel shall each cling to its legacy.”

[image]\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		As YHWH commanded Moses, so Zelophehad’s daughters did.

[image]\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And Mahlah, Tirzah, and Hoglah and Milcah and Noah, Zelophehad’s
daughters, became wives to their uncles’ sons.

[image]\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		They became wives within the families of the children of Manasseh son
of Joseph, and their legacy was on the tribe of their father’s family.

[image]\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		These are the commandments and the judgments that YHWH commanded by
Moses’ hand to the children of Israel in the plains of Moab by the
Jordan toward Jericho.

[image]\\
	}
}
{
}

