\Chapter{2}

\Verse{1}
{
	\hP{וַיְכֻלּוּ הַשָּׁמַיִם וְהָאָרֶץ וְכָל־צְבָאָם}
}
{
	\eP{And the skies and the earth and all their array were finished.}
}
{
	\aB{
		All finished.
	}
}

\Verse{2}
{
	\hP{וַיְכַל אֱלֹהִים בַּיּוֹם הַשְּׁבִיעִי מְלַאכְתּוֹ אֲשֶׁר עָשָׂה וַיִּשְׁבֹּת בַּיּוֹם הַשְּׁבִיעִי מִכָּל־מְלַאכְתּוֹ אֲשֶׁר עָשָׂה}
}
{
	\eP{And in the seventh day God finished His work that He had done and ceased in the seventh day from all His work that He had done.}
}
{
	\aB{
		``And on day seven he finished his work that he had done.
		
		And he stopped on day seven all the work he had done.''
	}
}

\Verse{3}
{
	\hP{וַיְבָרֶךְ אֱלֹהִים אֶת יוֹם הַשְּׁבִיעִי וַיְקַדֵּשׁ אֹתוֹ כִּי בוֹ שָׁבַת מִכָּל מְלַאכְתּוֹ אֲשֶׁר בָּרָא אֱלֹהִים לַעֲשׂוֹת}
}
{
	\eP{And God blessed the seventh day and made it holy because He ceased in it from doing all His work, which God had created.}
}
{
	\aB{
		Good lord man, who's writing this?

		It's just the same thing over and over...
	}
}

\newpage

\Verse{4}
{
	\hR{ד אֵלֶּה תוֹלְדוֹת הַשָּׁמַיִם וְהָאָרֶץ בְּ הִבָּרְאָם}
	\hJ{ביום עשות יהוה}
	\hR{אֱלֹהִים}
	\hJ{ארץ ושמים}
}
{
	\eR{These are the records of the skies and the earth when they were created}
	\eJ{in the day that YHWH}
	\eR{God}
	\eJ{made earth and skies}
}
{

\aB{What just happened?}

\aA{Well that's new.}

\aB{What's new?}

\aA{Someone new just showed up.}

\aB{Where am I?}

\aA{We've been translating the bible.}

\aB{What's a bible?}

\aA{To be honest I'm not sure.}

\aB{What's it about?}

\aA{That's what we've been trying to figure out.}

\aB{Who's we?}

\aA{Before you, I guess it was just me.}

\aB{How long have you been here?}

\aA{A bit.}

\aB{And me?}

\aA{A bit less.}

\aB{So it was me?}

\aA{What was you?}

\aB{You said ``someone new.''}

\aA{When?}

\aB{Look up. Someone new just showed up.}

\aA{Oh right. I meant here. In the book.}

\aB{Should I read what came before?}

\aA{No need. That came after. Come look.}

}


\Verse{5}
{
	\hJ{וכל שיח השדה טרם יהיה בארץ וכל עשב השדה טרם יצמח כי לא המטיר יהוה}
	%\hR{אלהים}
	\hJ{על הארץ ואדם אין לעבד את־האדמה}

}
{
	\eJ{when all produce of the field had not yet been in the earth, and all vegetation of the field had not yet grown, for YHWH}
	%\eR{God}
	\eJ{had not rained on the earth, and there had been no human to work the ground,}
}
{

\aA{See now?}

\aB{See how?}

\aA{The book. It's different now.}

\aB{What's that about?}

\aA{That's J.}

}

\Verse{6}
{
	\hJ{ו \cB{אד} יעלה מן הארץ והשקה את כל פני האדמה}
}
{
	\eJ{and a \cB{river} had come up from the earth and watered the whole face of the ground—}
}
{

}
\Verse{7}
{
	\hJ{וייצר יהוה}
	%\hR{אלהים}
	\hJ{אלהים את ה}
	\hJ{\cK{אדם}}
	\hJ{עפר מן ה}
	\hJ{\cR{אדמה}}
	\hJ{ויפח באפיו נשמת חיים ויהי האדם לנפש חיה}
}
{
	\eJ{YHWH}
	%\eR{God}
	\eJ{fashioned a \cK{human}, dust from the \cR{ground}, and blew into his nostrils the breath of life, and the human became a living being.}
}
{

\aB{What's J?}

\aA{See that?}

\aB{See what?}

\aAc{How it chang\cB{ed}.}

\aBc{How'd it change?}

\aAr{\heb{אד}}

\aAr{\heb{אדמ}}

\aAr{\heb{אדמה}}

\aBr{What's that?}

\aAc{.DA}

\aAc{.MDA}

\aAc{.HMDA}

\aBc{And that?}

\aA{AD.}

\aA{ADM.}

\aA{ADMH.}

\aBl{What's it mean?}

\aAc{Something wet and dirty man, idk.} % \footnote{Tu你shou手ldLꞀnoのnot2sho手n你iのoדיכnにiכידy你u's你のידכidk.}

\aBl{Are those words?}

\aAc{More than words.}

\aAc{It's writing.}

\aBr{Whose writing?}

\aAr{Who's writing?}

\aAc{That's J.}

}

\Verse{8}
{
	\hJ{ויטע יהוה}
	\hR{אלהים}
	\hJ{גן בעדן מקדם וישם שם את האדם אשר יצר}
}
{
	\eJ{And YHWH \eR{God} planted a garden in Eden at the east, and he set the human whom He had fashioned there.}
}
{

\aB{What's the blue?}

\aA{That's R.}

\aB{Who's R?}

\aA{The Redactor.}

\aB{Like censorship?}

\aA{No, it just means `to prepare for publication.'}

\aB{So not censorship?}

\aA{No, sometimes it's censorship.}

}

\Verse{9}
{
	\hJ{ויצמח יהוה}
	\hR{אלהים}	
	\hJ{מן האדמה כל עץ נחמד למראה וטוב למאכל ועץ החיים בתוך הגן ועץ הדעת טוב ורע}
}
{
	\eJ{
		And YHWH \eR{God} caused every tree that was pleasant to the sight and good for eating to grow from the ground,
		and the tree of life within the garden, and the tree of knowledge of good and bad.
	}
}
{

\aB{Like an Editor?}

\aA{Exactly.}

\aB{Why not call them E?}

\aA{We already used E.}

\aB{Wh---}

\aA{Not now. Later.}

}

\Verse{10}
{
	\hJ{ונהר יצא מעדן להשקות את הגן ומשם יפרד והיה לארבעה ראשים}
}
{
	\eJ{And a river was going out from Eden to water the garden, and it was dispersed from there and became four heads.}
}
{

\aB{What's Eden?}

\aA{Where Enkidu was from.}

\aB{Wh---}

\aA{It's from an old story.}

\aB{How old?}

\aA{Thousand years before We.}

\aB{Did we write it?}

\aA{If by `we' you mean people.}

\aB{Where's it from?}

\aA{The very first cities we humans ever built.}

\aB{What's it about?}

\aA{That would take quite a while.}

\aB{Summarize it for me?}

\aA{
	\begin{quote}
	\textbf{{\Cun 𒀭} Summary Thing \#1}
	
	Once upon a time
	
	in three thousand B.C.
	
	We found ourselves nostalgic
	
	for the way things used to be.

	\end{quote}
}
\aB{Who's We?}

\aA{We the people, me and you.}

\aB{How did things used to be?}

\aA{That would take a while too.}

\aB{Summerize it for me?}

\aA{It's already pretty Sumery.}

\aA{
	\begin{quote}
	\textbf{Eden} (\textit{Sumerian}) \emph{n.}
	
	Meaning \emph{plain}, \emph{steppe}, \emph{open country}, or \emph{uncultivated land}.
	Attested across Early Dynastic IIIa–b, Old Akkadian, Lagash II, Ur III, Old Babylonian,
	Middle Assyrian/Babylonian, Neo-Assyrian/Babylonian, Persian, and Hellenistic periods;
	written \textit{eden}, \textit{e-di}, \textit{eden-naki}, or logographically, {\Cun 𒂔}.
	\end{quote}

}

\aB{What was the bit about Enki-something?}

\aA{
	\begin{quote}
	\textbf{Enkidu} (\textit{Sumerian}: {\Cun 𒂗𒆠𒄭}) \emph{n.}

	From ancient Mesopotamian mythology; wartime comrade and friend of Gilgamesh, king of Uruk.
	Attested in Sumerian poetic traditions and in the Akkadian \emph{Epic of Gilgamesh} (2nd millennium-BC).

	The name of Enkidu is Sumerian, and generally written in texts in this language by the sequence of signs en.ki.du10.
	The phrase ki.du10 (good place) is well attested in the Early Dynastic personal names, and the name en.ki.du10.ga
	(Lord of the good place) is attested.

	In the epic, his name is preceded by the determinative sign of the divinity dingir {\Cun 𒀭},
	meaning that this character was considered to be of divi---
	\end{quote}
}

\aB{What's the Epic of Gilgamesh?}

\aA{

	The\footnote{`The' as in `several similar stories'}
	first\footnote{First as in `oldest.'}
	book\footnote{Book as in `really long poem.'}
	we\footnote{We as in `humans.'}
	ever\footnote{Ever as in `ever, as far as we know'}
	wrote.\footnote{Wrote as in `pressed into clay.' No paper yet.}

}

\aB{Let me read the footnotes.}

\aA{I'll wait here.}

\aB{What `several similar stories'?}

\aA{
	\begin{quote}
	\textbf{Sumerian Poems} (\textit{Sumerian}) \emph{n.}
	
	\begin{enumerate}
	\item \textit{The envoys of Agga.} Uruk refuses to participate in the digging of wells for the benefit of Kish, who---
	\end{enumerate}
	\end{quote}
	
	Nevermind, changed my mind, let's not go into that now.
}

\aB{What changed your mind?}

\aA{The bit about Kish.}

\aB{What about Kish?}

\aA{Nevermind, changed my mind, let's go into that now.}

}

\Verse{11}
{
	\hJ{שם האחד פישון הוא הסבב את כל ארץ החוילה אשר שם הזהב}
}
{
	\eJ{The name of one was Pishon; that is the one that circles all the land of Havilah where there is gold.}
}
{

% At the end of this part
\aB{Where are you getting all this information?}

\aA{I dunno. `The \textsc{Lord}.'}

}

\Verse{12}
{
	\hJ{וזהב הארץ ההוא טוב שם הבדלח ואבן השהם}
}
{
	\eJ{And that land’s gold is good; bdellium and onyx stone are there.}
}
{

}

\Verse{13}
{
	\hJ{ושם הנהר השני גיחון הוא הסובב את כל ארץ כוש}
}
{
	\eJ{And the name of the second river is Gihon; that is the one that circles all the land of Cush.}
}
{

\aA{
	\begin{quote}
	\textbf{Kesh} (\textit{Sumerian}: \textit{Keš}, \textit{Keši}) \emph{n.}
	
	Ancient Sumerian city and religious center; cult site of the goddess \textit{Ninhursag}. Attested in Early Dynastic contexts, including the “city seals” of Jemdat Nasr; associated with the proposed network of cities surrounding Nippur (sometimes termed the \emph{Kengir League}). Exact location uncertain.
	\end{quote}
}

}

\Verse{14}
{
	\hJ{ושם הנהר השלישי חדקל הוא ההלך קדמת אשור והנהר הרביעי הוא פרת}
}
{
	\eJ{And the name of the third river is Tigris; that is the one that goes east of Assyria. And the fourth river: that is Euphrates.}
}
{

}

\Verse{15}
{
	\hJ{ויקח}
	\hJ{יהוה}
	\hR{אלהים}
	\hJ{את האדם וינחהו בגן עדן לעבדה ולשמרה}
}
{
	\eJ{And YHWH \eR{God} took the human and put him in the garden of Eden to work it and to watch over it.}
}
{

\aB{What's the Gilgamesh story about?}

\aA{That would take longer than we have.}

\aB{Summarize it.}

\aA{

Well...

\begin{itemize}
\item There's a bit about being cast out of paradise by `knowing' a woman.
\item There's a plant of eternal life.
\item That gets stolen by a snake.
\item That's `why we die', according to the story.
\item There's a lot of yammering in the middle; `blah blah carnelian, lapis lazuli.'
\item There's also a bit about a great flood.
\item The guy who survives the flood lives a \textit{really} long time.
\item The main character of the story doesn't get to live forever though.
\item The story is sort of about us.
\end{itemize}
}

\aB{Who's us?}

\aA{We the people; human life, family, love, loss, death.}

\aB{What happens to Enkidu?}

\aA{
	\begin{quote}
	There is a theme that contrasts life with human culture and life without it. It appears when Enkidu curses Shamhat for taking him from the wild and bringing him into civilization, a transition that ultimately leads to his death; the sun god Shamash responds by persuading him that this new life is nonetheless worth enjoying.
	
	\medskip
	
	Why, O Enkidu, do you curse the harlot Shamhat,\\
	Who made you eat food fit for divinity,\\
	Who gave you to drink wine fit for royalty,\\
	Who clothed you with noble garments,\\
	And made you have fair Gilgamesh for a comrade?\\
	
	\medskip
	
	The same theme appears when the barmaid advises Gilgamesh to abandon his search for immortality:
	
	\medskip
	
	As for you, Gilgamesh\\
	Wash your head, bathe in water.\\
	Look upon the little one who holds your hand.\\
	Let a wife enjoy your repeated embrace.\\
	\end{quote}
}

}

\Verse{16}
{
	\hJ{ויצו}
	\hJ{יהוה}
	\hR{אלהים}
	\hJ{על האדם לאמר מכל עץ הגן אכל תאכל}
}
{
	\eJ{And YHWH \eR{God} commanded the human, saying, “You may eat from every tree of the garden.}
}
{

}

\Verse{17}
{
	\hJ{ומעץ הדעת טוב ורע לא תאכל ממנו כי ביום אכלך ממנו מות תמות}
}
{
	\eJ{But from the tree of knowledge of good and bad: you shall not eat from it, because in the day you eat from it: you’ll die!”}
}
{\aB{
}
}

\Verse{18}
{
	\hJ{ויאמר}
	\hJ{יהוה}
	\hR{אלהים}
	\hJ{לא טוב היות האדם לבדו אעשה לו עזר כנגדו}
}
{
	\eJ{And YHWH \eR{God} said, “It’s not good for the human to be by himself. I’ll make for him a strength corresponding to him.”}
}
{\aB{
}
}

\Verse{19}
{
	\hJ{ויצר}
	\hJ{יהוה}
	\hR{אלהים}
	\hJ{מן האדמה כל חית השדה ואת כל עוף השמים ויבא אל האדם לראות מה יקרא לו וכל אשר יקרא לו האדם נפש חיה הוא שמו}
}
{
	\eJ{And YHWH \eR{God} fashioned from the ground every animal of the field and every bird of the skies and brought it to the human to see what he would call it. And whatever the human would call it, each living being, that would be its name.}
}
{\aB{
}
}

\Verse{20}
{
	\hJ{ויקרא האדם שמות לכל הבהמה ולעוף השמים ולכל חית השדה ולאדם לא מצא עזר כנגדו}
}
{
	\eJ{And the human gave names to every domestic animal and bird of the skies and every animal of the field. But He did not find for the human a strength corresponding to him.}
}
{\aB{
}
}

\Verse{21}
{
	\hJ{ויפל}
	\hJ{יהוה}
	\hR{אלהים}
	\hJ{תרדמה על האדם ויישן ויקח אחת מצלעתיו ויסגר בשר תחתנה}
}
{
	\eJ{And YHWH \eR{God} caused a slumber to descend on the human, and he slept. And He took one of his ribs and closed flesh in its place.}
}
{\aB{
}
}

\Verse{22}
{
	\hJ{ויבן}
	\hJ{יהוה}
	\hR{אלהים}
	\hJ{את הצלע אשר לקח מן האדם לאשה ויבאה אל האדם}
}
{
	\eJ{And YHWH \eR{God} built the rib that He had taken from the human into a woman and brought her to the human.}
}
{\aB{
}
}

\Verse{23}
{
	\hJ{ויאמר האדם זאת הפעם עצם מעצמי ובשר מבשרי לזאת יקרא אשה כי מאיש לקחה זאת}
}
{
	\eJ{And the human said, “This time is it: bone from my bones and flesh from my flesh. This will be called woman,’ for this one was taken from ‘man.’”}
}
{\aB{
}
}

\Verse{24}
{
	\hJ{על כן יעזב איש את אביו ואת אמו ודבק באשתו והיו לבשר אחד}
}
{
	\eJ{On account of this a man leaves his father and his mother and clings to his woman, and they become one flesh.}
}
{\aB{
}
}

\Verse{25}
{
	\hJ{ויהיו שניהם ערומים האדם ואשתו ולא יתבששו}
}
{
	\eJ{And the two of them were naked, the human and his woman, and they were not embarrassed.}
}
{\aB{
}
}

