\Chapter{6}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Command Aaron and his sons, saying: This is the instruction for the
burnt offering. It is the one that goes up on its place of burning on
the altar all night until morning, and the altar’s fire shall be kept
burning through it.\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And the priest shall wear his linen garment and shall wear linen
drawers on his flesh. And he shall lift the ashes to which the fire will
consume the burnt offering on the altar, and he shall set them beside
the altar.\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And he shall take off his clothes and wear other clothes, and he shall
take the ashes outside the camp, to a pure place.\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And the fire on the altar shall be kept burning through it. It shall
not go out. And the priest shall burn wood on it morning by morning, and
he shall arrange the burnt offering on it, and he shall burn the fat of
the peace offerings to smoke on it.\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		Fire always shall be kept burning on the altar. It shall not go out.\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		“And this is the instruction for the grain offering. The sons of Aaron
shall bring it forward in front of YHWH to the front of the altar.\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And he shall lift some of it in his fist, some of the fine flour of the
grain offering and some of its oil and all of the frankincense that is
on the grain offering, and he shall burn a representative portion of it
to smoke at the altar as a pleasant smell to YHWH.\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And Aaron and his sons shall eat the remainder of it. It shall be eaten
as unleavened bread, in a holy place. They shall eat it in the courtyard
of the Tent of Meeting.\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		It shall not be baked with leaven. I have given it as their portion
from my offerings by fire. It is the holy of holies, like the sin
offering and like the guilt offering.\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		Every male among the sons of Aaron shall eat it—an eternal law through
your generations—from YHWH’s offerings by fire. Anything that will touch
them will become holy.”\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		“This is the offering of Aaron and his sons that they shall bring to
YHWH in the day of his being anointed: a tenth of an ephah of fine flour
as a continual grain offering, half of it in the morning and half of it
in the evening.\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		It shall be made on a griddle in oil. You shall bring it well mixed.
You shall offer it as cakes of a grain offering of pieces, a pleasant
smell to YHWH.\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And the anointed priest in his place from among his sons shall do it,
an eternal law, for YHWH: it shall be burned to smoke entirely.\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And every grain offering of a priest shall be done entirely. It shall
not be eaten.”\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		“Speak to Aaron and to his sons, saying: This is the instruction for
the sin offering. In the place where the burnt offering will be
slaughtered, the sin offering shall be slaughtered, in front of YHWH. It
is the holy of holies.\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		The priest who makes it a sin offering shall eat it. It shall be eaten
in a holy place, in the courtyard of the Tent of Meeting.\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		Anything that will touch the meat of it will become holy. And if some
of its blood will spatter on clothing, you shall wash the thing on which
it will spatter in a holy place.\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And a clay container in which it will be boiled shall be broken. And
if it was boiled in a brass container then it shall be scoured and
rinsed with water.\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		Every male among the priests shall eat it. It is the holy of holies.\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		And every sin offering some of whose blood will be brought to the Tent
of Meeting for atoning in the Holy shall not be eaten. It shall be
burned in fire.\\
	}
}
{
}

