\Chapter{13}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		13

¹ And YHWH spoke to Moses and to Aaron, saying,\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“When a person will have a swelling or a rash or a bright spot in his
flesh’s skin, and it becomes an affliction of leprosy in his flesh’s
skin, and he will be brought to Aaron, the priest, or to one of his
sons, the priests,\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		and the priest will see the affliction in the flesh’s skin, and hair in
the affliction will have turned white, and the affliction’s appearance
is deeper than his flesh’s skin, it is an affliction of leprosy. And
when the priest will see it he shall identify him as impure.\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And if it is a white bright spot in his flesh’s skin, and its
appearance is not deeper than the skin, and its hair has not turned
white, then the priest shall shut in the one with the affliction seven
days.\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And the priest shall see him on the seventh day; and, here, in his eyes
the affliction will have stayed the same—the affliction has not spread
in the skin—then the priest shall shut him in seven days a second time.\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And the priest shall see him on the seventh day a second time; and,
here, the affliction has become dim, and the affliction has not spread
in the skin, then the priest shall identify him as pure. It is a rash.
And he shall wash his clothes and be pure.\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		But if the rash has spread in the skin after his being seen by the
priest for pronouncing him pure, and he is seen a second time by the
priest,\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		and the priest sees, and, here, the rash has spread in the skin, then
the priest shall identify him as impure. It is leprosy.\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		“When an affliction of leprosy will be in a human, and he will be
brought to the priest,\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		and the priest will see; and, here, a white swelling will be in the
skin, and it will have turned hair white, and some vital flesh will be
in the swelling,\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		it is chronic leprosy in his flesh’s skin, and the priest shall
identify him as impure. He shall not shut him in, because he is impure.\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And if the leprosy will develop in the skin, and the leprosy will
cover all the skin of the one with the affliction from his head to his
feet, to wherever it is within sight of the priest’s eyes,\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		and the priest will see, and, here, the leprosy has covered all his
flesh, then he shall identify the one with the affliction as pure. All
of him has turned white. He is pure.\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And on the day that vital flesh will appear in him he will be impure.\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And the priest will see the vital flesh and shall identify him as
impure. The vital flesh: it is impure. It is leprosy.\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		Or when the vital flesh will go back and turn to white, and he will
come to the priest,\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		and the priest will see him, and, here, the affliction has turned to
white, then the priest shall identify the affliction as pure. He is
pure.\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		“And when flesh will have a boil in it, in its skin, and will be
healed,\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		and in place of the boil there will be a white swelling or a reddish
white bright spot, and he will be seen by the priest,\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		and the priest will see, and, here, its appearance is lower than the
skin, and its hair has turned white, then the priest shall identify him
as impure. It is an affliction of leprosy. It has developed in the boil.\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And if the priest will see it, and, here, there is not white hair in
it, and it is not lower than the skin, and it has become dim, then the
priest shall shut him in seven days.\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And if it will spread in the skin, then the priest shall identify him
as impure. It is an affliction.\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		And if the bright spot will have stayed the same in its place—it has
not spread—it is the scar of the boil, and the priest shall identify him
as pure.\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		“Or when flesh will have a burn from a fire in its skin, and the vital
part of the burn is a bright spot of reddish white or white,\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		and the priest will see it, and, here, hair has turned white in the
bright spot, and its appearance is lower than the skin, it is leprosy.
It has developed in the burn. And the priest shall identify him as
impure. It is an affliction of leprosy.\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		And if the priest will see it, and, here, there is not white hair in
the bright spot, and it is not lower than the skin, and it has become
dim, then the priest shall shut him in seven days.\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		And the priest shall see him on the seventh day. If it will spread in
the skin, then the priest shall identify him as impure. It is an
affliction of leprosy.\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		And if the bright spot will have stayed the same in its place—it has
not spread in the skin—and it has become dim, it is the swelling of the
burn, and the priest shall identify him as pure, because it is the scar
of the burn.\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		“And when a man or woman will have an affliction in the head or beard,\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		and the priest will see the affliction, and, here, its appearance is
deeper than the skin, and there is thin yellow hair in it, then the
priest shall identify him as impure. It is a scab. It is leprosy of the
head or the beard.\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		And when the priest will see the affliction of the scab, and, here,
its appearance is not deeper than the skin, and there is not black hair
in it, then the priest shall shut in the affliction of the scab seven
days.\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		And the priest shall see the affliction on the seventh day. And, here,
the scab has not spread, and there is not yellow hair in it, and the
scab’s appearance is not deeper than the skin.\\
	}
}
{
}

\Verse{33}
{
	\hP{}
}
{
	\eP{
		Then he shall shave himself, and he shall not shave the scab. And the
priest shall shut in the one with the scab seven days a second time.\\
	}
}
{
}

\Verse{34}
{
	\hP{}
}
{
	\eP{
		And the priest shall see the scab on the seventh day. And, here, the
scab has not spread in the skin, and its appearance is not deeper than
the skin. Then the priest shall identify him as pure. And he shall wash
his clothes, and he shall be pure.\\
	}
}
{
}

\Verse{35}
{
	\hP{}
}
{
	\eP{
		But if the scab has spread in the skin, after his purification,\\
	}
}
{
}

\Verse{36}
{
	\hP{}
}
{
	\eP{
		and the priest will see him, and, here, the scab has spread in the
skin, the priest shall not inspect for the yellow hair. He is impure.\\
	}
}
{
}

\Verse{37}
{
	\hP{}
}
{
	\eP{
		And if, in his eyes, the scab has stayed the same, and black hair has
developed in it, the scab has been healed. He is pure. And the priest
shall identify him as pure.\\
	}
}
{
}

\Verse{38}
{
	\hP{}
}
{
	\eP{
		“And when a man or woman will have bright spots in the skin of their
flesh, white bright spots,\\
	}
}
{
}

\Verse{39}
{
	\hP{}
}
{
	\eP{
		and the priest will see, and, here, bright spots in the skin of their
flesh are dim white, it is a tetter. It has developed in the skin. He is
pure.\\
	}
}
{
}

\Verse{40}
{
	\hP{}
}
{
	\eP{
		“And when a man’s head will become hairless, he is bald. He is pure.\\
	}
}
{
}

\Verse{41}
{
	\hP{}
}
{
	\eP{
		And if his head will become hairless from the corner of his face, he
has a bald forehead. He is pure.\\
	}
}
{
}

\Verse{42}
{
	\hP{}
}
{
	\eP{
		And when there will be in the bald head or in the bald forehead a
reddish white affliction, it is leprosy developing in his bald head or
in his bald forehead.\\
	}
}
{
}

\Verse{43}
{
	\hP{}
}
{
	\eP{
		And the priest will see it, and, here, the affliction’s swelling is
reddish white in his bald head or in his bald forehead, like the
appearance of leprosy of skin of flesh,\\
	}
}
{
}

\Verse{44}
{
	\hP{}
}
{
	\eP{
		he is a leprous man. He is impure. The priest shall identify him as
impure. His affliction is in his head.\\
	}
}
{
}

\Verse{45}
{
	\hP{}
}
{
	\eP{
		And the leper in whom is the affliction: his clothes shall be torn,
and the hair of his head shall be loosed, and he shall cover over his
mustache. And he shall call, ‘Impure! Impure!’\\
	}
}
{
}

\Verse{46}
{
	\hP{}
}
{
	\eP{
		All the days that the affliction is in him he will be impure. He is
impure. He shall live separate. His home is outside of the camp.\\
	}
}
{
}

\Verse{47}
{
	\hP{}
}
{
	\eP{
		“And when clothing will have an affliction of leprosy in it—in
clothing of wool or in clothing of linen,\\
	}
}
{
}

\Verse{48}
{
	\hP{}
}
{
	\eP{
		either in the warp or in the woof of the linen or of the wool, or in
leather or in anything made of leather:\\
	}
}
{
}

\Verse{49}
{
	\hP{}
}
{
	\eP{
		if the affliction will be greenish or reddish in the clothing or in
the leather or in the warp or in the woof or in any item of leather, it
is an affliction of leprosy—and it will be shown to the priest,\\
	}
}
{
}

\Verse{50}
{
	\hP{}
}
{
	\eP{
		and the priest will see the affliction, and he shall shut in the thing
with the affliction seven days.\\
	}
}
{
}

\Verse{51}
{
	\hP{}
}
{
	\eP{
		And he shall see the affliction on the seventh day: if the affliction
has spread in the clothing or in the warp or in the woof or in the
leather, or any work into which the leather will be made, the affliction
is malignant leprosy. It is impure.\\
	}
}
{
}

\Verse{52}
{
	\hP{}
}
{
	\eP{
		And he shall burn the clothing or the warp or the woof in the wool or
in the linen or any item of leather in which the affliction will be,
because it is malignant leprosy. It shall be burned in fire.\\
	}
}
{
}

\Verse{53}
{
	\hP{}
}
{
	\eP{
		And if the priest will look, and, here, the affliction has not spread
in the clothing or in the warp or in the woof or any item of leather,\\
	}
}
{
}

\Verse{54}
{
	\hP{}
}
{
	\eP{
		then the priest shall command, and they shall wash the thing in which
the affliction is, and he shall shut it in seven days a second time.\\
	}
}
{
}

\Verse{55}
{
	\hP{}
}
{
	\eP{
		And the priest shall see the affliction after it will be washed, and,
here, the affliction has not changed its appearance, and the affliction
will not have spread, it is impure. You shall burn it in fire. It is a
deterioration, in its ‘bald head’ or in its ‘forehead.’\\
	}
}
{
}

\Verse{56}
{
	\hP{}
}
{
	\eP{
		If the priest will see, and, here, the affliction has become dim after
it was washed, then he shall rip it from the clothing or from the
leather or from the warp or from the woof.\\
	}
}
{
}

\Verse{57}
{
	\hP{}
}
{
	\eP{
		And if it will appear again in the clothing or in the warp or in the
woof or in any item of leather, it is developing. You shall burn it, the
thing in which the affliction is, in fire.\\
	}
}
{
}

\Verse{58}
{
	\hP{}
}
{
	\eP{
		And the clothing or the warp or the woof or any item of leather that
you will wash: if the affliction will turn away from them, then it shall
be washed a second time, and it will be pure.\\
	}
}
{
}

\Verse{59}
{
	\hP{}
}
{
	\eP{
		“This is the instruction for the affliction of leprosy of clothing of
wool or linen or warp or woof or any item of leather, to identify it as
pure or to identify it as impure.”\\
	}
}
{
}

