\Chapter{18}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		18

¹ And YHWH spoke to Moses, saying,\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel, and you shall say to them: I am YHWH,
your God.\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		You shall shall not do like what is done in the land of Egypt, in which
you lived; and you shall not do like what is done in the land of Canaan,
to which I’m bringing you; and you shall not go by their laws.\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		You shall do my judgments, and you shall observe my laws, to go by
them. I am YHWH, your God.\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And you shall observe my laws and my judgments, which, when a human
will do them, he’ll live through them! I am YHWH.\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		“Any man, to any close relative of his: you shall not come close to
expose nudity. I am YHWH.\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		You shall not expose your father’s nudity and your mother’s nudity. She
is your mother. You shall not expose her nudity.\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		You shall not expose your father’s wife’s nudity. It is your father’s
nudity.\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		Your sister’s nudity—your father’s daughter or your mother’s daughter,
born home or born outside—you shall not expose their nudity.\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		The nudity of your son’s daughter or your daughter’s daughter—you
shall not expose their nudity, because they are your nudity.\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		The nudity of your father’s wife’s daughter, born of your father: she
is your sister; you shall not expose her nudity.\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		You shall not expose your father’s sister’s nudity. She is your
father’s close relative.\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		You shall not expose your mother’s sister’s nudity. She is your
mother’s close relative.\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		You shall not expose your father’s brother’s nudity: you shall not
come close to his wife. She is your aunt.\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		You shall not expose your daughter-in-law’s nudity. She is your son’s
wife. You shall not expose her nudity.\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		You shall not expose your brother’s wife’s nudity. It is your
brother’s nudity.\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		You shall not expose the nudity of a woman and her daughter. You shall
not take her son’s daughter or her daughter’s daughter to expose her
nudity. They are close relatives. It is perversion.\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And you shall not take a woman to her sister to rival, to expose her
nudity along with her in her lifetime.\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And you shall not come close to a woman during her menstrual impurity
to expose her nudity.\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And you shall not give your intercourse of seed to your fellow’s wife,
to become impure by it.\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And you shall not give any of your seed for passing to the Molech, and
you shall not desecrate your God’s name. I am YHWH.\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And you shall not lie with a male like lying with a woman. It is an
offensive thing.\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		And you shall not give your intercourse with any animal, to become
impure by it. And a woman shall not stand in front of an animal to mate
with it. It is an aberration.\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		“You shall not become impure by all of these, because the nations that
I am putting out from in front of you became impure by all of these,\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		and the land became impure, and I reckoned its sin on it, and the land
vomited out its residents.\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		But you: you shall observe my laws and my judgments and not do any of
all these offensive things, the citizen and the alien who resides among
you—\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		because the people of the land who were before you did all of these
offensive things, and the land became impure—\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		so the land will not vomit you out for your making it impure as it
vomited out the nation that was before you.\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		Because anyone who will do any of these offensive things: the persons
who do will be cut off from among their people.\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		And you shall keep my charge: not to do any of the abominable customs
that were done before you; and you will not become impure by them. I am
YHWH, your God.”\\
	}
}
{
}

