\Chapter{19}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Speak to all the congregation of the children of Israel, and you shall
say to them: You shall be holy, because I, YHWH, your God, am holy.\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		“You shall each fear his mother and his father, and you shall observe
my Sabbaths. I am YHWH, your God.\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		“Do not turn to idols, and you shall not make molten gods for
yourselves. I am YHWH, your God.\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		“And when you will make a peace-offering sacrifice to YHWH, you shall
sacrifice it so that it will be accepted for you.\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		It shall be eaten on the day of your sacrifice and on the next day; and
what is left until the third day shall be burned in fire.\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And if it will be eaten on the third day it is a repugnant thing. It
shall not be acceptable.\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And anyone who eats it shall bear his crime, because he desecrated
YHWH’s holy thing, and that person will be cut off from his people.\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And when you reap your land’s harvest, you shall not finish harvesting
your field’s corner, and you shall not gather your harvest’s gleaning.\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And you shall not strip your vineyard, and you shall not collect the
vineyard’s fallen fruit. You shall leave them for the poor and for the
alien. I am YHWH, your God.\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		“You shall not steal, and you shall not lie, and you shall not act
false, each against his fellow.\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And you shall not swear by my name falsely, so that you would
desecrate your God’s name. I am YHWH.\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		“You shall not exploit your neighbor, and you shall not rob. An
employee’s wages shall not stay through the night with you until
morning.\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		You shall not curse a deaf person, and you shall not place a stumbling
block in front of a blind person. And you shall fear your God. I am
YHWH.\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		“You shall not do an injustice in judgment. You shall not be partial
to a weak person, and you shall not favor a big person. You shall judge
your fellow with justice.\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		You shall not go with slander among your people. You shall not stand
by at your neighbor’s blood. I am YHWH.\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		“You shall not hate your brother in your heart. You shall criticize
your fellow, so you shall not bear sin over him.\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		You shall not take revenge, and you shall not keep on at the children
of your people. And you shall love your neighbor as yourself. I am YHWH.\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		“You shall observe my laws. Your animal: you shall not mate two kinds.
Your field: you shall not seed two kinds. And a garment of two kinds,
sha‘atnez: it shall not go on you.\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		“And when a man will lie with a woman—an intercourse of seed—and she
is a maid designated to a man, and she has not been redeemed, or freedom
has not been given to her, there will be a reparation. They shall not be
put to death, because she was not freed.\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And he shall bring his guilt offering to YHWH, to the entrance of the
Tent of Meeting, a ram for a guilt offering.\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And the priest shall atone over him with the ram for the guilt
offering in front of YHWH over his sin that he committed, and it will be
forgiven for him from his sin that he committed.\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		“And when you will come to the land, and you will plant any tree for
eating, you shall leave its top with its fruit uncircumcised. It shall
be uncircumcised for three years for you. It shall not be eaten.\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		And in the fourth year all of its fruit shall be holy, tributes for
YHWH.\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And in the fifth year you shall eat its fruit, to increase its produce
for you. I am YHWH, your God.\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		“You shall not eat with the blood. You shall not practice divination,
and you shall not practice soothsaying.\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		You shall not trim your head’s edge, and you shall not destroy your
beard’s edge.\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		You shall not put a cut in your flesh for a person, and you shall not
put an inscription of a tattoo in you. I am YHWH.\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		“Do not desecrate your daughter to make her a prostitute, so the land
will not go to prostitution, and the land will fill with perversion.\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		You shall observe my Sabbaths and fear my holy place. I am YHWH.\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		“Do not turn to ghosts, and do not seek spirits of acquaintances, to
become impure by them. I am YHWH, your God.\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		“You shall get up in front of an aged person, and you shall show
respect in front of an elderly person. And you shall fear your God. I am
YHWH.\\
	}
}
{
}

\Verse{33}
{
	\hP{}
}
{
	\eP{
		“And if an alien will reside with you in your land, you shall not
persecute him.\\
	}
}
{
}

\Verse{34}
{
	\hP{}
}
{
	\eP{
		The alien who resides with you shall be to you like a citizen of
yours, and you shall love him as yourself, because you were aliens in
the land of Egypt. I am YHWH, your God.\\
	}
}
{
}

\Verse{35}
{
	\hP{}
}
{
	\eP{
		“You shall not do an injustice in judgment, in measurement, in weight,
and in quantity.\\
	}
}
{
}

\Verse{36}
{
	\hP{}
}
{
	\eP{
		You shall have just scales, just weights, a just ephah, and a just
hin. I am YHWH, your God, who brought you out from the land of Egypt.\\
	}
}
{
}

\Verse{37}
{
	\hP{}
}
{
	\eP{
		“And you shall observe all my laws and all my judgments and do them. I
am YHWH.”\\
	}
}
{
}

