\Chapter{20}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		20

¹ And YHWH spoke to Moses, saying,\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“And to the children of Israel you shall say: Any man from the children
of Israel and from the alien who resides in Israel who will give any of
his seed to the Molech shall be put to death. The people of the land
shall batter him with stone.\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And I shall set my face against that man, and I shall cut him off from
among his people because he gave any of his seed for the Molech so as to
make my holy place impure and to desecrate my holy name.\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And if the people of the land will hide their eyes from that man when
he gives any of his seed for the Molech, not to put him to death,\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		then I shall set my face at that man and at his family, and I shall cut
off him and all who whore after him, to whore after the Molech, from
among their people.\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And the person who will turn to ghosts and to spirits of acquaintances
to whore after them: I shall set my face against that person and cut him
off from among his people.\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		“And you shall make yourselves holy, and you shall be holy, because I
am YHWH, your God.\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And you shall observe my laws and do them. I am YHWH, who makes you
holy.\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		“Because any man who will curse his father and his mother shall be put
to death. He has cursed his father and his mother: his blood is on him!\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		“And a man who will commit adultery with a man’s wife—who will commit
adultery with his neighbor’s wife!—shall be put to death: the adulterer
and the adulteress.\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And a man who will lie with his father’s wife, he has exposed his
father’s nudity: the two of them shall be put to death. Their blood is
on them.\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And a man who will lie with his daughter-in-law: the two of them shall
be put to death. They have done an aberration. Their blood is on them.\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And a man who will lie with a male like lying with a woman: the two of
them have done an offensive thing. They shall be put to death. Their
blood is on them.\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And a man who will take a woman and her mother: it is a perversion.
You shall burn him and them in fire, so there will not be perversion
among you.\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And a man who will have his intercourse with an animal shall be put to
death. And you shall kill the animal.\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And a woman who will go up to any animal to mate with it: you shall
kill the woman and the animal. They shall be put to death. Their blood
is on them.\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And a man who will take his sister, his father’s daughter or his
mother’s daughter, and see her nudity, and she will see his nudity, it
is shame; and they will be cut off in the eyes of the children of their
people. He has exposed his sister’s nudity. He shall bear his crime.\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And a man who will lie with a menstruating woman and will expose her
nudity: he has uncovered her source, and she has exposed the source of
her blood. And the two of them will be cut off from among their people.\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And you shall not expose the nudity of your mother’s sister or your
father’s sister, because one has thus uncovered his close relative. They
shall bear their crime.\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And a man who will lie with his aunt: he has exposed his uncle’s
nudity. They shall bear their sin. They shall die childless.\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And a man who will take his brother’s wife: it is an impurity. He has
exposed his brother’s nudity. They will be childless.\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		“And you shall observe all my laws and all my judgments and do them,
and the land to which I am bringing you to live in it will not vomit you
out.\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		And you shall not go by the laws of the nation that I am ejecting from
in front of you, because they have done all of these, and I am disgusted
with them.\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		And I have said to you: You shall possess their land, and I shall give
it to you to possess it, a land flowing with milk and honey. I am YHWH,
your God, who has distinguished you from the peoples,\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		and you shall distinguish between the pure animal and the impure, and
between the impure bird and the pure, and you shall not make yourselves
detestable by an animal or by a bird or by anything that creeps on the
ground that I have distinguished as impure for you.\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		And you shall be holy to me because I, YHWH, am holy, and I have
distinguished you from the peoples to be mine.\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		“And a man or woman: if there will be among them a ghost or a spirit
of an acquaintance, they shall be put to death. They shall batter them
with stone. Their blood is on them.”\\
	}
}
{
}

