\Chapter{23}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		23

¹ And YHWH spoke to Moses, saying,\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel, and you shall say to them: YHWH’s
appointed times, which you shall call holy assemblies—these are my
appointed times:\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		Six days work shall be done, and in the seventh day is a Sabbath, a
ceasing, a holy assembly. You shall not do any work. It is a Sabbath to
YHWH in all your homes.\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		“These are YHWH’s appointed times, holy assemblies that you shall
proclaim at their appointed time:\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		In the first month, on the fourteenth of the month, ‘between the two
evenings,’ is YHWH’s Passover.\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And on the fifteenth day of this month is YHWH’s Festival of Unleavened
Bread. You shall eat unleavened bread seven days.\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		On the first day you shall have a holy assembly. You shall not do any
act of work.\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And you shall bring forward an offering by fire to YHWH for seven days.
On the seventh day you shall have a holy assembly. You shall not do any
act of work.”\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel, and you shall say to them: When you
will come to the land that I am giving to you and you reap its harvest,
you shall bring the first sheaf of your harvest to the priest,\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		and he shall elevate the sheaf in front of YHWH for acceptance for
you. The priest shall elevate it on the day after the Sabbath.\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		And on the day of your elevating the sheaf, you shall do an
unblemished lamb in its first year as a burnt offering to YHWH,\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		and its grain offering shall be two-tenths of a measure of fine flour
mixed with oil, an offering by fire to YHWH, a pleasant smell, and its
libation shall be wine, a fourth of a hin.\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And you shall not eat bread or parched or fresh grain until that very
day, until you have brought your God’s offering. It is an eternal law
through your generations in all your homes.\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And you shall count from the day after the Sabbath, from the day of
your bringing the sheaf for an elevation offering, seven Sabbaths. They
shall be complete.\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		You shall count until the day after the seventh Sabbath: fifty days.
And you shall bring forward a new grain offering to YHWH.\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		From your homes you shall bring bread for an elevation offering: two
of them. They shall be two-tenths of a measure of fine flour, baked with
leaven, firstfruits to YHWH.\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And you shall bring forward with the bread seven lambs, unblemished
one-year-olds, and one bull of the cattle and two rams. They shall be a
burnt offering to YHWH, with their grain offering and their libations,
an offering by fire, a pleasant smell to YHWH.\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And you shall do one goat as a sin offering and two one-year-old lambs
as a peace-offering sacrifice.\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And the priest shall elevate them with the bread of firstfruits, an
elevation offering in front of YHWH with the two sheep. They shall be a
holy thing to YHWH: for the priest.\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And you shall proclaim on that very day: you shall have a holy
assembly. You shall not do any act of work: an eternal law in all your
homes through your generations.\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And when you reap your land’s harvest, you shall not finish your
field’s corner when you harvest, and you shall not gather your harvest’s
gleaning. You shall leave them for the poor and for the alien. I am
YHWH, your God.”\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel, saying: In the seventh month, on the
first of the month you shall have a ceasing, a commemoration with
horn-blasting, a holy assembly.\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		You shall not do any act of work. And you shall bring forward an
offering by fire to YHWH.”\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		“Just: On the tenth of this seventh month, it is the Day of Atonement.
You shall have a holy assembly, and you shall degrade yourselves. And
you shall bring forward an offering by fire to YHWH.\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		And you shall not do any work on this very day, because it is a day of
atonement, to atone for you in front of YHWH, your God.\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		Because any person who will not be degraded on this very day will be
cut off from his people.\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		And any person who will do any work in this very day: I shall destroy
that person from among his people.\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		You shall not do any work: an eternal law through your generations in
all your homes.\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		It is a Sabbath, a ceasing, for you, and you shall degrade yourselves:
on the ninth of the month in the evening, from evening to evening, you
shall keep your Sabbath.”\\
	}
}
{
}

\Verse{33}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,\\
	}
}
{
}

\Verse{34}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel, saying: On the fifteenth day of this
seventh month is the Festival of Booths, seven days, for YHWH.\\
	}
}
{
}

\Verse{35}
{
	\hP{}
}
{
	\eP{
		On the first day is a holy assembly. You shall not do any act of work.\\
	}
}
{
}

\Verse{36}
{
	\hP{}
}
{
	\eP{
		For seven days you shall bring forward an offering by fire to YHWH. On
the eighth day you shall have a holy assembly, and you shall bring
forward an offering by fire to YHWH. It is a convocation. You shall not
do any act of work.\\
	}
}
{
}

\Verse{37}
{
	\hP{}
}
{
	\eP{
		“These are YHWH’s appointed times, which you shall call holy
assemblies, to bring forward an offering by fire to YHWH: burnt offering
and grain offering, sacrifice and libations, each day’s thing on its
day,\\
	}
}
{
}

\Verse{38}
{
	\hP{}
}
{
	\eP{
		aside from YHWH’s Sabbaths and aside from your gifts and aside from
all of your vows and aside from all of your contributions that you will
give to YHWH.\\
	}
}
{
}

\Verse{39}
{
	\hP{}
}
{
	\eP{
		“Just: On the fifteenth day of the seventh month when you gather the
land’s produce, you shall celebrate YHWH’s holiday seven days. On the
first day is a ceasing, and on the eighth day is a ceasing.\\
	}
}
{
}

\Verse{40}
{
	\hP{}
}
{
	\eP{
		And on the first day you shall take fruit of appealing trees, branches
of palms, boughs of thick trees, and willows of a wadi, and you shall be
happy in front of YHWH, your God, seven days.\\
	}
}
{
}

\Verse{41}
{
	\hP{}
}
{
	\eP{
		And you shall celebrate it, a holiday to YHWH, seven days in the year,
an eternal law through your generations; you shall celebrate it in the
seventh month.\\
	}
}
{
}

\Verse{42}
{
	\hP{}
}
{
	\eP{
		You shall live in booths seven days. Every citizen in Israel shall
live in booths,\\
	}
}
{
}

\Verse{43}
{
	\hP{}
}
{
	\eP{
		so your generations will know that I had the children of Israel live
in booths when I brought them out from the land of Egypt. I am YHWH,
your God.”\\
	}
}
{
}

\Verse{44}
{
	\hP{}
}
{
	\eP{
		And Moses spoke YHWH’s appointed times to the children of Israel.\\
	}
}
{
}

