\Chapter{25}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses in Mount Sinai, saying,\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel. And you shall say to them: When you
will come to the land that I am giving to you, then the land shall have
a Sabbath for YHWH.\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		Six years you shall seed your field, and six years you shall prune your
vineyard, and you shall gather its produce.\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And in the seventh year the land shall have a Sabbath, a ceasing, a
Sabbath for YHWH: you shall not seed your field, and you shall not prune
your vineyard,\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		you shall not reap your harvest’s free growth, and you shall not cut
off your untrimmed grapes. The land shall have a year of ceasing.\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And the land’s Sabbath shall be yours for food: for you and for your
servant and for your maid and for your employee and for your visitor who
are residing with you\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		and for your domestic animal and for the wild animal that are in your
land shall be all of its produce to eat.\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		“And you shall count seven Sabbaths of years: seven years, seven times.
And the days of the seven Sabbaths of years shall be for you forty-nine
years.\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And you shall pass a blasting horn in the seventh month on the tenth of
the month: on the Day of Atonement you shall have the horn pass through
all your land.\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And you shall consecrate the year that makes fifty years and proclaim
liberty in the land, to all its inhabitants. It shall be a jubilee for
you. And you shall go back, each to his possession; and you shall go
back, each to his family.\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		It, the year that makes fifty years, shall be a jubilee for you. You
shall not seed, and you shall not harvest its free growths, and you
shall not cut off its untrimmed fruits,\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		because it is a jubilee; it shall be a holy thing to you. You shall
eat its produce from the field.\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		In this jubilee year you shall go back, each to his possession.\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And when you will make a sale to your fellow or buy from your fellow’s
hand: each of you, do not persecute his brother.\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		You shall buy from your fellow by the number of years after the
jubilee. He shall sell to you by the number of years of yields—\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		corresponding to a greater amount of the years, you shall make its
price greater; and corresponding to a smaller amount of the years, you
shall make its price smaller—because it is a number of yields that he is
selling to you.\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And you shall not persecute—each of you—his brother, but you shall
fear your God, because I am YHWH, your God.\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		“And you shall do my laws and observe my judgments and do them, so you
will live on the land in security.\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And the land will give its fruit, and you will eat to the full, and
you will live in security on it.\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And if you will say, ‘What shall we eat in the seventh year? Here, we
won’t seed and won’t gather our produce,’\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		I shall command my blessing for you in the sixth year, and it will
make the produce for the three years.\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And you will seed the eighth year and eat from the old produce until
the ninth year; you will eat the old until its produce comes.\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		But the land shall not be sold permanently, because the land is mine,
because you are aliens and visitors with me!\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		So in all the land in your possession you shall give a redemption for
the land.\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		When your brother will be low so that he will sell any of his
possession, then his redeemer who is the closest relative to him shall
come and redeem his brother’s sale.

25:25,35,39. when your brother will be low. Meaning: when your fellow
Israelite will be so poor that he has difficulty holding on to his land.
It has long been noted that the three times that this phrase occurs in
this chapter reflect three stages of increasing hardship. In the first,
the person has to sell his land. In the second, he has both lost his
land and is without money. And in the third, he himself is sold (or
sells himself) into servitude. And at each stage, the man’s fellow
Israelite is commanded to help him. If he has to sell his land, one must
redeem it for him and then give it back to him in the jubilee year. If
he is without money, one must lend him money without any charge or
interest. And if he is sold, one must not treat him as a slave.

Here the units of law convey the specific requirements while the
arrangement conveys the basic principle, namely, that as one’s brother’s
need increases, so does one’s responsibility to help him. Further, one
must thus help one’s fellow as a matter of law. The chapter never speaks
of charity, nor does it appeal to one’s feelings of compassion or
generosity. An unfortunate Israelite need not feel degraded to be poor
nor ashamed to be pitied. Economic suffering is rather treated as a
reality of life, which one is required by law to remedy. The poor man
thus can know that his brother is helping him because the system
requires brothers to help one another and that, if the shoe were on the
other foot, he would do the same for his brother. This is not to say
that the text denies or discourages feelings of compassion, but only
that the fulfillment of the law is not made dependent upon the presence
or absence of such feelings.\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		And when a man will not have a redeemer, but his hand has come to
attain it and he has found enough for his redemption,\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		then he shall figure the years of his sale and pay back what is left
over to the man to whom he sold it, and he shall go back to his
possession.\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		And if his hand has not found enough to pay it back to him, then his
sale shall be in the hand of the one who bought it until the jubilee
year, and it shall come out in the jubilee, and he shall go back to his
possession.\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		“And when a man will sell a home in a walled city, then its redemption
shall be until the end of the year of its sale. Its redemption shall be
for days.\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		And if it will not be redeemed by the completion of a full year for
it, then the house that is in a city that has a wall shall be
established permanently for the one who bought it, through his
generations. It shall not come out in the jubilee.\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		“As for houses of the villages that do not have a wall around them: it
shall be figured along with the land’s field. It shall have redemption,
and it shall come out in the jubilee.\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		“As for the Levites’ cities, the houses in the cities of their
possession: the Levites shall have eternal redemption.\\
	}
}
{
}

\Verse{33}
{
	\hP{}
}
{
	\eP{
		And that which one from the Levites will redeem: it shall come out, a
sale of a house and of a city of his possession, in the jubilee, because
that—the houses of the Levites’ cities—is their possession among the
children of Israel.\\
	}
}
{
}

\Verse{34}
{
	\hP{}
}
{
	\eP{
		But a field of their cities’ surrounding land shall not be sold,
because it is an eternal possession for them.\\
	}
}
{
}

\Verse{35}
{
	\hP{}
}
{
	\eP{
		“And when your brother will be low so that his hand is slipping with
you, then you shall take hold of him—an alien and a visitor—and he shall
live with you.\\
	}
}
{
}

\Verse{36}
{
	\hP{}
}
{
	\eP{
		Do not take interest or a charge from him; but you shall fear your
God, and your brother will live with you.\\
	}
}
{
}

\Verse{37}
{
	\hP{}
}
{
	\eP{
		You shall not give him your money for interest, and you shall not give
him your food for a charge.\\
	}
}
{
}

\Verse{38}
{
	\hP{}
}
{
	\eP{
		I am YHWH, your God, who brought you out from the land of Egypt to
give you the land of Canaan, to be God to you.\\
	}
}
{
}

\Verse{39}
{
	\hP{}
}
{
	\eP{
		“And when your brother will be low with you so that he is sold to you,
you shall not have him work a slave’s work.\\
	}
}
{
}

\Verse{40}
{
	\hP{}
}
{
	\eP{
		He shall be like an employee, like a visitor, with you. He shall work
with you until the jubilee year.\\
	}
}
{
}

\Verse{41}
{
	\hP{}
}
{
	\eP{
		And he shall go out from you, he and his children with him, and go
back to his family, and he shall go back to his fathers’ possession.\\
	}
}
{
}

\Verse{42}
{
	\hP{}
}
{
	\eP{
		Because they are my servants, whom I brought out from the land of
Egypt; they shall not be sold like the sale of a slave.\\
	}
}
{
}

\Verse{43}
{
	\hP{}
}
{
	\eP{
		You shall not dominate him with harshness, but you shall fear your
God.\\
	}
}
{
}

\Verse{44}
{
	\hP{}
}
{
	\eP{
		“And your slave and your maid that you will have: from the nations
that are around you, you shall buy a slave or a maid from them.\\
	}
}
{
}

\Verse{45}
{
	\hP{}
}
{
	\eP{
		And also from the children of the visitors who reside with you—you
shall buy from them and from their families that are with you—to whom
they gave birth in your land. And they shall become a possession for
you.\\
	}
}
{
}

\Verse{46}
{
	\hP{}
}
{
	\eP{
		And you shall make them a legacy for your children after you to
inherit as a possession. You may have them work forever, but as for your
brothers, the children of Israel—a man toward his brother—you shall not
dominate him with harshness.\\
	}
}
{
}

\Verse{47}
{
	\hP{}
}
{
	\eP{
		“And if the hand of an alien and visitor with you will attain it, and
your brother is low with him and is sold to the alien and visitor with
you or to an offshoot of an alien’s family,\\
	}
}
{
}

\Verse{48}
{
	\hP{}
}
{
	\eP{
		after he is sold he shall have redemption. One of his brothers shall
redeem him,\\
	}
}
{
}

\Verse{49}
{
	\hP{}
}
{
	\eP{
		or his uncle or his uncle’s son shall redeem him, or some close
relative of his from his family shall redeem him; or if his hand can
attain it then he can redeem himself.\\
	}
}
{
}

\Verse{50}
{
	\hP{}
}
{
	\eP{
		And he shall figure with the one who buys him: from the year he was
sold to him to the jubilee year; and the price of his sale shall be by
the number of years. It shall be with him like the days of an employee:\\
	}
}
{
}

\Verse{51}
{
	\hP{}
}
{
	\eP{
		If there are still a great number of years, he shall pay back his
redemption according to them from his purchase price.\\
	}
}
{
}

\Verse{52}
{
	\hP{}
}
{
	\eP{
		And if a small amount of years remain until the jubilee year, then he
shall figure it for him. He shall pay back his redemption according to
his years.\\
	}
}
{
}

\Verse{53}
{
	\hP{}
}
{
	\eP{
		He shall be with him like a year-by-year employee. He shall not
dominate him with harshness before your eyes.\\
	}
}
{
}

\Verse{54}
{
	\hP{}
}
{
	\eP{
		And if he will not be redeemed by these, then he shall go out in the
jubilee year, he and his children with him.\\
	}
}
{
}

\Verse{55}
{
	\hP{}
}
{
	\eP{
		Because the children of Israel are servants to me. They are my
servants, whom I brought out from the land of Egypt. I am YHWH, your
God.\\
	}
}
{
}

