\Chapter{2}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		2

¹ And a man from the house of Levi went and took a daughter of Levi.\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		And the woman became pregnant and gave birth to a son. And she saw him,
that he was good, and she concealed him for three months.\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		And she was not able to conceal him anymore, and she took an ark made
of bulrushes for him and smeared it with bitumen and with pitch and put
the boy in it and put it in the reeds by the bank of the Nile.\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		And his sister stood still at a distance to know what would be done to
him.\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		And the Pharaoh’s daughter went down to bathe at the Nile, and her
girls were going alongside the Nile, and she saw the ark among the reeds
and sent her maid, and she took it.\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And she opened it and saw him, the child: and here was a boy crying,
and she had compassion on him, and she said, “This is one of the
Hebrews’ children.”\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		And his sister said to Pharaoh’s daughter, “Shall I go and call a
nursing woman from the Hebrews for you, and she’ll nurse the child for
you?”\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		And Pharaoh’s daughter said to her, “Go.” And the girl went and called
the child’s mother.\\
	}
}
{
}

\Verse{9}
{
	\hJ{}
}
{
	\eJ{
		And Pharaoh’s daughter said to her, “Take this child and nurse him for
me, and I’ll give your pay.” And the woman took the boy and nursed him.\\
	}
}
{
}

\Verse{10}
{
	\hJ{}
}
{
	\eJ{
		And the boy grew older, and she brought him to Pharaoh’ daughter, and
he became her son. And she called his name Moses, and she said, “Because
I drew him from the water.”\\
	}
}
{
}

\Verse{11}
{
	\hJ{}
}
{
	\eJ{
		And it was in those days, and Moses grew older, and he went out to his
brothers and saw their burdens, and he saw an Egyptian man striking a
Hebrew man, one of his brothers.\\
	}
}
{
}

\Verse{12}
{
	\hJ{}
}
{
	\eJ{
		And he turned this way and that way and saw that there was no man, and
he struck the Egyptian and hid him in the sand.\\
	}
}
{
}

\Verse{13}
{
	\hJ{}
}
{
	\eJ{
		And he went out on the second day, and here were two Hebrew men
fighting. And he said to the one who was in the wrong, “Why do you
strike your companion?”\\
	}
}
{
}

\Verse{14}
{
	\hJ{}
}
{
	\eJ{
		And he said, “Who made you a commander and judge over us? Are you
saying you’d kill me—the way you killed the Egyptian?!”

And Moses was afraid and said, “The thing is known for sure.”\\
	}
}
{
}

\Verse{15}
{
	\hJ{}
}
{
	\eJ{
		And Pharaoh heard this thing and sought to kill Moses, and Moses fled
from Pharaoh’s presence and lived in the land of Midian.

And he sat by a well.\\
	}
}
{
}

\Verse{16}
{
	\hJ{}
}
{
	\eJ{
		And a priest of Midian had seven daughters, and they came and drew
water and filled the troughs to water their father’s flock,\\
	}
}
{
}

\Verse{17}
{
	\hJ{}
}
{
	\eJ{
		and the shepherds came and drove them away. And Moses got up and saved
them and watered their flock.\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		And they came to Reuel, their father, and he said, “Why were you so
quick to come today?”\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		And they said, “An Egyptian man rescued us from the shepherds’ hand,
and he drew water for us and watered the flock, too.”\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		And he said to his daughters, “And where is he? Why is this that
you’ve left the man? Call him, and let him eat bread.”\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		And Moses was content to live with the man. And he gave Zipporah, his
daughter, to Moses,\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		and she gave birth to a son, and he called his name Gershom,
“because,” he said, “I was an alien in a foreign land.”\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		And it was after those many days, and the king of Egypt died.

And the children of Israel groaned from the work, and they cried out,
and their wail went up to God from the work.\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		And God heard their moaning, and God remembered His covenant with
Abraham, with Isaac, and with Jacob.

2:23–24. groan, cry, wail, moan. Four different words are used in the
Hebrew to describe their crying. This conveys that their agony is
intense, continuous, and pervasive.\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And God saw the children of Israel. And God knew!\\
	}
}
{
}

