\Chapter{3}

\Verse{1}
{
	\hE{}
}
{
	\eE{
		3

¹ And Moses had been shepherding the flock of Jethro, his father-in-law,
priest of Midian. And he drove the flock at the far side of the
wilderness, and he came to the Mountain of God, to Horeb.\\
	}
}
{
}

\Verse{2}
{
	\hE{}
}
{
	\eE{
		And an angel of YHWH appeared to him in a fire’s flame from inside a
bush. And he looked, and here: the bush was burning in the fire, and the
bush was not consumed!\\
	}
}
{
}

\Verse{3}
{
	\hE{}
}
{
	\eE{
		And Moses said, “Let me turn and see this great sight. Why doesn’t the
bush burn?”\\
	}
}
{
}

\Verse{4}
{
	\hE{}
}
{
	\eE{
		And YHWH saw that he turned to see. And God called to him from inside
the bush, and He said, “Moses, Moses.”

And he said, “I’m here.”\\
	}
}
{
}

\Verse{5}
{
	\hE{}
}
{
	\eE{
		And He said, “Don’t come close here. Take off your shoes from your
feet, because the place on which you’re standing: it’s holy ground.”\\
	}
}
{
}

\Verse{6}
{
	\hE{}
}
{
	\eE{
		And He said, “I’m your father’s God, Abraham’s God, Isaac’s God, and
Jacob’s God.” And Moses hid his face, because he was afraid of looking
at God.\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said, “I’ve seen the degradation of my people who are in
Egypt, and I’ve heard their wail on account of their taskmasters,
because I know their pains.\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		And I’ve come down to rescue them from Egypt’s hand and to bring them
up from that land to a good and widespread land, to a land flowing with
milk and honey, to the place of the Canaanite and the Hittite and the
Amorite and the Perizzite and the Hivite and the Jebusite.\\
	}
}
{
}

\Verse{9}
{
	\hE{}
}
{
	\eE{
		“And now, here, the cry of the children of Israel has come to me, and
also I’ve seen the oppression that Egypt is causing them.\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		And now go, and I’ll send you to Pharaoh, and bring out my people, the
children of Israel, from Egypt.”\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		And Moses said to God, “Who am I that I should go to Pharaoh and that
I should bring out the children of Israel from Egypt?”

3:11–12. “Who am I?” “Because I’ll be with you.” Some say that Moses’
first response shows his extreme humility. But in that case, God’s
answer is strange: “Because I’ll be with you” is not an answer to the
question “Who am I?” Rather, as in the case of the exchange with Abraham
over Sodom and Gomorrah, God apparently answers what is in the person’s
heart rather than what he says with his mouth. “Because I shall be with
you” is a response to someone who is saying in his heart: “I’m afraid.”
Moses has just been told that he must do this. Now God assures him that
“I’ll be with you.”\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		And He said, “Because I’ll be with you. And this is the sign for you
that I have sent you. When you bring out the people from Egypt you shall
serve God on this mountain.”\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		And Moses said to God, “Here, I’m coming to the children of Israel,
and I’ll say to them, ‘Your fathers’ God sent me to you.’ And they’ll
say to me, ‘What is His name?’ What shall I say to them?”\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		And God said to Moses, “I am who I am.” And He said, “You shall say
this to the children of Israel: ‘I Am’ has sent me to you.”\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		And God said further to Moses, “You shall say this to the children of
Israel: YHWH, your fathers’ God, Abraham’s God, Isaac’s God, and Jacob’s
God has sent me to you. This is my name forever, and this is how I am to
be remembered for generation after generation.\\
	}
}
{
}

\Verse{16}
{
	\hJ{}
}
{
	\eJ{
		“Go and gather Israel’s elders and say to them, ‘YHWH, your fathers’
God, has appeared to me—the God of Abraham, Isaac, and Jacob—saying: I
have taken account of you and what has been done to you in Egypt,\\
	}
}
{
}

\Verse{17}
{
	\hJ{}
}
{
	\eJ{
		and I say I shall bring you up from the degradation of Egypt to the
land of the Canaanite and the Hittite and the Amorite and the Perizzite
and the Hivite and the Jebusite, to a land flowing with milk and honey.\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		And they’ll listen to your voice, and you’ll come, you and Israel’s
elders, to the king of Egypt, and you’ll say to him, ‘YHWH, God of the
Hebrews, has communicated with us. And now, let us go on a trip of three
days in the wilderness so we may sacrifice to YHWH, our God.’\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		And I know that the king of Egypt won’t allow you to go, and not by a
strong hand,\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		and I’ll put out my hand and strike Egypt with all my wonders that
I’ll do among them, and after that he’ll let you go.\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		And I’ll put this people’s favor in Egypt’s eyes; and it will be, when
you go, you won’t go empty-handed.\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		And each woman will ask for silver articles and gold articles and
clothes from her neighbor and from anyone staying in her house, and
you’ll put them on your sons and on your daughters, and you’ll despoil
Egypt.”\\
	}
}
{
}

