\Chapter{4}

\Verse{1}
{
	\hE{}
}
{
	\eE{
		4

¹ And Moses answered, and he said, “And here, they won’t believe me and
won’t listen to my voice, because they’ll say, ‘YHWH hasn’t appeared to
you!’”\\
	}
}
{
}

\Verse{2}
{
	\hE{}
}
{
	\eE{
		And YHWH said to him, “What’s this in your hand?”

And he said, “A staff.”\\
	}
}
{
}

\Verse{3}
{
	\hE{}
}
{
	\eE{
		And He said, “Throw it to the ground.”

And he threw it to the ground. And it became a snake! And Moses fled
from it.\\
	}
}
{
}

\Verse{4}
{
	\hE{}
}
{
	\eE{
		And YHWH said to Moses, “Put out your hand and take hold of its tail.”

And he put out his hand and held onto it, and it became a staff in his
hand.\\
	}
}
{
}

\Verse{5}
{
	\hE{}
}
{
	\eE{
		“So that they will believe that YHWH, their fathers’ God, Abraham’s
God, Isaac’s God, and Jacob’s God, has appeared to you!”\\
	}
}
{
}

\Verse{6}
{
	\hE{}
}
{
	\eE{
		And YHWH said to him further, “Bring your hand into your bosom.”

And he brought his hand into his bosom. And he brought it out; and,
here, his hand was leprous like snow!\\
	}
}
{
}

\Verse{7}
{
	\hE{}
}
{
	\eE{
		And He said, “Put your hand back to your bosom.”

And he put his hand back to his bosom. And he brought it out from his
bosom; and, here, it had gone back like its flesh.\\
	}
}
{
}

\Verse{8}
{
	\hE{}
}
{
	\eE{
		“And it will be, if they won’t believe you and won’t listen to the
voice of the first sign, then they’ll believe the voice of the latter
one.\\
	}
}
{
}

\Verse{9}
{
	\hE{}
}
{
	\eE{
		And it will be, if they also won’t believe in these two signs and won’t
listen to your voice, then you’ll take some of the water of the Nile and
spill it on the dry ground. And it will be water that you’ll take from
the Nile, and it will become blood on the dry ground.”\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		And Moses said to YHWH, “Please, my Lord, I’m not a man of words.
Neither yesterday nor the day before—nor since you spoke to your
servant! Because I’m heavy of mouth and heavy of tongue.”\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		And YHWH said to him, “Who set a mouth for humans? Or who will set a
mute or deaf or seeing or blind? Is it not I, YHWH?\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		And now go, and I’ll be with your mouth, and I’ll instruct you what
you shall speak.”\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		And he said, “Please, my Lord, send by the hand you’ll send.”\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		And YHWH’s anger flared at Moses, and He said, “Isn’t Aaron your
Levite brother? I knew that he will speak! And also here he is, coming
out toward you! And he’ll see you and be happy in his heart.\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		And you’ll speak to him and set the words in his mouth, and I, I shall
be with your mouth and with his mouth, and I shall instruct you what you
shall do.\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		And he will speak for you to the people. And it will be: he will
become a mouth for you, and you will become a god for him!\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		And you shall take this staff in your hand, by which you’ll do the
signs.”\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		And Moses went.

And he went back to Jether, his father-in-law, and said to him, “Let me
go so I may go back to my brothers who are in Egypt and see if they’re
still living.”

And Jethro said to Moses, “Go in peace.”\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said to Moses in Midian, “Go. Go back to Egypt, because all
the people who sought your life have died.”\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		And Moses took his wife and his sons and rode them on an ass, and he
went back to the land of Egypt. And Moses took the staff of God in his
hand.\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		And YHWH said to Moses, “When you’re going to go back to Egypt, see
all the wonders that I’ve set in your hand, and you shall do them in
front of Pharaoh. And I: I’ll strengthen his heart, and he won’t let the
people go.\\
	}
}
{
}

\Verse{22}
{
	\hE{}
}
{
	\eE{
		And you shall say to Pharaoh, ‘YHWH said this: My child, my firstborn,
is Israel.\\
	}
}
{
}

\Verse{23}
{
	\hE{}
}
{
	\eE{
		And I’ve said to you: Let my child go and serve me. And should you
refuse to let it go, here: I’m killing your child, your firstborn!’”\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		And he was on the way, at a lodging place, and YHWH met him, and he
asked to kill him.\\
	}
}
{
}

\Verse{25}
{
	\hJ{}
}
{
	\eJ{
		And Zipporah took a flint and cut her son’s foreskin and touched his
feet, and she said, “Because you’re a bridegroom of blood to me.”\\
	}
}
{
}

\Verse{26}
{
	\hJ{}
}
{
	\eJ{
		And he held back from Him. Then she said, “A bridegroom of blood for
circumcisions.”\\
	}
}
{
}

\Verse{27}
{
	\hE{}
}
{
	\eE{
		And YHWH said to Aaron, “Go toward Moses, to the wilderness.” And he
went, and he met him in the Mountain of God, and he kissed him.\\
	}
}
{
}

\Verse{28}
{
	\hE{}
}
{
	\eE{
		And Moses told Aaron all YHWH’s words that He had sent him and all the
signs that He had commanded him.\\
	}
}
{
}

\Verse{29}
{
	\hE{}
}
{
	\eE{
		And Moses went, and Aaron, and they gathered all the elders of the
children of Israel,\\
	}
}
{
}

\Verse{30}
{
	\hE{}
}
{
	\eE{
		and Aaron spoke all the words that YHWH had spoken to Moses. And he
did the signs before the people’s eyes.\\
	}
}
{
}

\Verse{31}
{
	\hE{}
}
{
	\eE{
		And the people believed, and they heard that YHWH had taken account of
the children of Israel and that He had seen their degradation. And they
knelt and bowed.\\
	}
}
{
}

