\Chapter{5}

\Verse{1}
{
	\hRJE{}
}
{
	\eRJE{
		5

¹ And after that Moses and Aaron came and said to Pharaoh, “YHWH, God of
Israel, said this: ‘Let my people go, so they will celebrate a festival
for me in the wilderness.’”\\
	}
}
{
}

\Verse{2}
{
	\hOther{}
}
{
	\eOther{
		And Pharaoh said, “Who is YHWH that I should listen to His voice, to
let Israel go?! I don’t know YHWH, and also I won’t let Israel go.”\\
	}
}
{
}

\Verse{3}
{
	\hOther{}
}
{
	\eOther{
		And they said, “The God of the Hebrews has communicated with us. Let us
go on a trip of three days in the wilderness so we may sacrifice to
YHWH, our God, or else He’ll strike us with an epidemic or with the
sword.”\\
	}
}
{
}

\Verse{4}
{
	\hOther{}
}
{
	\eOther{
		And the king of Egypt said to them, “Why, Moses and Aaron, do you turn
the people loose from its work? Go to your burdens!”\\
	}
}
{
}

\Verse{5}
{
	\hOther{}
}
{
	\eOther{
		And Pharaoh said, “Here, the people of the land are now many, and
you’ve made them cease from their burdens.”\\
	}
}
{
}

\Verse{6}
{
	\hOther{}
}
{
	\eOther{
		And Pharaoh commanded the taskmasters among the people and its officers
in that day, saying,\\
	}
}
{
}

\Verse{7}
{
	\hOther{}
}
{
	\eOther{
		“You shall not continue to give straw to the people to make bricks as
yesterday and the day before. They shall go and collect straw for
themselves.\\
	}
}
{
}

\Verse{8}
{
	\hOther{}
}
{
	\eOther{
		And you shall impose on them the quota of the bricks that they were
making yesterday and the day before. You shall not subtract from it.
Because they’re lazy. On account of this they’re crying, saying, ‘Let us
go and sacrifice to our God.’\\
	}
}
{
}

\Verse{9}
{
	\hOther{}
}
{
	\eOther{
		Let the work be heavy on the people, and let them do it, and let them
not pay attention to words that are a lie!”\\
	}
}
{
}

\Verse{10}
{
	\hOther{}
}
{
	\eOther{
		And the people’s taskmasters and its officers went out and said to the
people, saying, “Pharaoh said this: ‘I am not giving you straw.\\
	}
}
{
}

\Verse{11}
{
	\hOther{}
}
{
	\eOther{
		You, go, take straw for yourselves from wherever you’ll find it,
because not a thing is subtracted from your work.’”\\
	}
}
{
}

\Verse{12}
{
	\hOther{}
}
{
	\eOther{
		And the people scattered through all the land of Egypt to collect
stubble for straw.\\
	}
}
{
}

\Verse{13}
{
	\hOther{}
}
{
	\eOther{
		And the taskmasters were prodding, saying, “Finish your work, the
day’s thing in that very day, as when there was the straw.”\\
	}
}
{
}

\Verse{14}
{
	\hOther{}
}
{
	\eOther{
		And the officers of the children of Israel whom Pharaoh’s taskmasters
had set over them were beaten—saying, “Why haven’t you finished your
requirement to make brick like the day before yesterday, also yesterday,
also today?”\\
	}
}
{
}

\Verse{15}
{
	\hOther{}
}
{
	\eOther{
		And the officers of the children of Israel came and cried to Pharaoh,
saying, “Why do you do a thing like this to your servants?\\
	}
}
{
}

\Verse{16}
{
	\hOther{}
}
{
	\eOther{
		Straw isn’t given to your servants, and they say to us: Make bricks.
And here, your servants are beaten, and it’s your people’s sin.”\\
	}
}
{
}

\Verse{17}
{
	\hOther{}
}
{
	\eOther{
		And he said, “You’re lazy, lazy! On account of this you’re saying,
‘Let us go and sacrifice to YHWH.’\\
	}
}
{
}

\Verse{18}
{
	\hOther{}
}
{
	\eOther{
		And now go, work! And straw will not be given to you, and you shall
give the quota of bricks!”\\
	}
}
{
}

\Verse{19}
{
	\hOther{}
}
{
	\eOther{
		And the officers of the children of Israel saw themselves in a bad
state—saying, “You shall not subtract from your bricks, the day’s thing
in that very day.”\\
	}
}
{
}

\Verse{20}
{
	\hOther{}
}
{
	\eOther{
		And they met Moses and Aaron, standing opposite them when they came
out from Pharaoh,\\
	}
}
{
}

\Verse{21}
{
	\hOther{}
}
{
	\eOther{
		and they said to them, “May YHWH look on you and judge, that you’ve
made our smell odious in Pharaoh’s eyes and in his servants’ eyes, to
give a sword in their hand to kill us!”\\
	}
}
{
}

\Verse{22}
{
	\hOther{}
}
{
	\eOther{
		And Moses went back to YHWH and said, “My Lord, why have you done bad
to this people? Why did you send me here?\\
	}
}
{
}

\Verse{23}
{
	\hOther{}
}
{
	\eOther{
		And since I came to Pharaoh to speak in your name he has done bad to
this people, and you haven’t rescued your people!”\\
	}
}
{
}

