\Chapter{8}

\Verse{1}
{
	\hRJE{}
}
{
	\eRJE{
		8

¹ And YHWH said to Moses, “Say to Aaron, ‘Reach out your hand with your
staff over the rivers, over the canals, and over the pools, and bring up
the frogs on the land of Egypt.’”\\
	}
}
{
}

\Verse{2}
{
	\hRJE{}
}
{
	\eRJE{
		And Aaron reached out his hand over Egypt’s waters, and the frogs came
up and covered the land of Egypt.\\
	}
}
{
}

\Verse{3}
{
	\hRJE{}
}
{
	\eRJE{
		And the magicians did so with their charms. And they brought up the
frogs on the land of Egypt.\\
	}
}
{
}

\Verse{4}
{
	\hRJE{}
}
{
	\eRJE{
		And Pharaoh called Moses and Aaron and said, “Pray to YHWH that He will
take away the frogs from me and from my people so I may let the people
go, and they’ll sacrifice to YHWH.”\\
	}
}
{
}

\Verse{5}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses said to Pharaoh, “Be honored over me as to when I’ll pray for
you and for your servants and for your people to cut off the frogs from
you and from your houses—they’ll be left only in the river.”\\
	}
}
{
}

\Verse{6}
{
	\hRJE{}
}
{
	\eRJE{
		And he said, “As of tomorrow.”

And he said, “According to your word: so that you’ll know that there’s
none like YHWH, our God.\\
	}
}
{
}

\Verse{7}
{
	\hRJE{}
}
{
	\eRJE{
		And the frogs will turn away from you and from your houses and from
your servants and from your people—they’ll be left only in the river.”\\
	}
}
{
}

\Verse{8}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses and Aaron went out from Pharaoh. And Moses cried to YHWH over
the matter of the frogs that he had set upon Pharaoh.\\
	}
}
{
}

\Verse{9}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH did according to Moses’ word, and the frogs died from the
houses, from the yards, and from the fields.\\
	}
}
{
}

\Verse{10}
{
	\hRJE{}
}
{
	\eRJE{
		And they piled them up, heaps and heaps, and the land smelled.\\
	}
}
{
}

\Verse{11}
{
	\hRJE{}
}
{
	\eRJE{
		And Pharaoh saw that there was a break, and he made his heart heavy,
and he did not listen to them—as YHWH had spoken.\\
	}
}
{
}

\Verse{12}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH said to Moses, “Say to Aaron, ‘Reach out your staff and
strike the dust of the earth, and it will become lice in all the land of
Egypt.’”\\
	}
}
{
}

\Verse{13}
{
	\hRJE{}
}
{
	\eRJE{
		And they did so, and Aaron reached out his hand with his staff and
struck the dust of the earth, and the lice were in the humans and in the
animals. All the dust of the earth was lice in all the land of Egypt.\\
	}
}
{
}

\Verse{14}
{
	\hRJE{}
}
{
	\eRJE{
		And the magicians did so with their charms, to bring out the lice, and
they were not able. And the lice were in the humans and in the animals.\\
	}
}
{
}

\Verse{15}
{
	\hRJE{}
}
{
	\eRJE{
		And the magicians said to Pharaoh, “It’s the finger of God!” And
Pharaoh’s heart was strong, and he did not listen to them—as YHWH had
spoken.\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Moses, “Get up early in the morning and stand up in
front of Pharaoh. Here, he’s going out to the water. And you’ll say to
him, ‘YHWH said this: Let my people go so they may serve me.\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		Because if you’re not letting my people go, here, I’m causing an
insect swarm to be let go on you and on your servants and on your people
and on your houses. And the houses of Egypt will be filled with the
insect swarm, and also the ground that they’re on.\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And I shall distinguish in that day the land of Goshen, on which my
people is standing, for no insect swarm to be there, so that you will
know that I, YHWH, am within the land.\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And I shall set a distinction between my people and your people. This
sign will be tomorrow.’”\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		And YHWH did so. And a heavy insect swarm came to Pharaoh’s house and
his servants’ house, and in all the land of Egypt the land was corrupted
because of the insect swarm.\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		And Pharaoh called Moses and Aaron. And he said, “Go. Sacrifice to
your God in the land.”\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		And Moses said, “It’s not right to do so, because we’ll be sacrificing
to YHWH, our God, an offensive thing to Egypt. Here, we’ll be
sacrificing an offensive thing to Egypt before their eyes; and will they
not stone us?!\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		We’ll go on a trip of three days in the wilderness, and we’ll
sacrifice to YHWH, our God, whatever He’ll say to us.”\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		And Pharaoh said, “I’ll let you go, and you’ll sacrifice to YHWH, your
God, in the wilderness. Only you shall not go far. Pray for me.”\\
	}
}
{
}

\Verse{25}
{
	\hJ{}
}
{
	\eJ{
		And Moses said, “Here, I’m going out from you, and I’ll pray to YHWH,
and the insect swarm will turn away from Pharaoh and from his servants
and from his people tomorrow. Only let Pharaoh not continue to toy so as
not to let the people go to sacrifice to YHWH.”\\
	}
}
{
}

\Verse{26}
{
	\hJ{}
}
{
	\eJ{
		And Moses went out from Pharaoh, and he prayed to YHWH.\\
	}
}
{
}

\Verse{27}
{
	\hJ{}
}
{
	\eJ{
		And YHWH did according to Moses’ word, and the insect swarm turned
away from Pharaoh and from his servants and from his people. Not one was
left.\\
	}
}
{
}

\Verse{28}
{
	\hJ{}
}
{
	\eJ{
		And Pharaoh made his heart heavy this time as well, and he did not let
the people go.\\
	}
}
{
}

