\Chapter{10}

\Verse{1}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH said to Moses, “Come to Pharaoh, because I have made his heart
and his servants’ heart heavy for the purpose of my setting these signs
of mine among them\\
	}
}
{
}

\Verse{2}
{
	\hRJE{}
}
{
	\eRJE{
		and for the purpose that you will tell in the ears of your son and your
son’s son about how I abused Egypt and about my signs that I set among
them, and you will know that I am YHWH.”\\
	}
}
{
}

\Verse{3}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses and Aaron came to Pharaoh and said to him, “YHWH, God of the
Hebrews, said this: ‘How long do you refuse to be humbled in front of
me? Let my people go, so they may serve me.\\
	}
}
{
}

\Verse{4}
{
	\hRJE{}
}
{
	\eRJE{
		Because if you refuse to let my people go, here, I’m bringing a locust
swarm in your border tomorrow,\\
	}
}
{
}

\Verse{5}
{
	\hRJE{}
}
{
	\eRJE{
		and it will cover the eye of the land, and one won’t be able to see the
land! And it will eat the remains of what has survived that is left to
you from the hail, and it will eat every tree that is growing for you
from the field.\\
	}
}
{
}

\Verse{6}
{
	\hRJE{}
}
{
	\eRJE{
		And they’ll fill your houses and the houses of all your servants and
the houses of all Egypt, which your fathers and your fathers’ fathers
did not see, from the day they were on the land until this day’.” And he
turned and went out from Pharaoh.\\
	}
}
{
}

\Verse{7}
{
	\hRJE{}
}
{
	\eRJE{
		And Pharaoh’s servants said to him, “How long will this be a trap for
us? Let the people go, so they may serve YHWH, their God. Don’t you know
yet that Egypt has perished?!”\\
	}
}
{
}

\Verse{8}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses and Aaron were brought back to Pharaoh. And he said to them,
“Go. Serve YHWH, your God. Who are the ones who are going?”\\
	}
}
{
}

\Verse{9}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses said, “We’ll go with our young and with our old, we’ll go
with our sons and with our daughters, with our sheep and with our oxen,
because we have a festival of YHWH.”\\
	}
}
{
}

\Verse{10}
{
	\hRJE{}
}
{
	\eRJE{
		And he said to them, “YHWH would be with you like that, when I would
let you and your infants go, see, because bad is in front of your faces.\\
	}
}
{
}

\Verse{11}
{
	\hRJE{}
}
{
	\eRJE{
		It is not like that. Go—the men!—and serve YHWH, because that is what
you’re asking.” And he drove them out from Pharaoh’s face.\\
	}
}
{
}

\Verse{12}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH said to Moses, “Reach out your hand at the land of Egypt for
the locust, and it will come up on the land of Egypt and eat all the
land’s vegetation, everything that the hail has left.”\\
	}
}
{
}

\Verse{13}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses reached out his staff at the land of Egypt, and YHWH drove
an east wind through the land all that day and all the night. It was the
morning: and the east wind had carried the locust swarm.\\
	}
}
{
}

\Verse{14}
{
	\hRJE{}
}
{
	\eRJE{
		And the locust swarm came up over all the land of Egypt and lingered
in all of Egypt’s border, very heavy: before it there was no such locust
swarm like it, and after it there will not be such.\\
	}
}
{
}

\Verse{15}
{
	\hRJE{}
}
{
	\eRJE{
		And it covered the eye of all the land, and the land was dark; and it
ate all the land’s vegetation and the fruit of every tree that the hail
had left, and not any plant was left, in the tree and in the field’s
vegetation, in all the land of Egypt.\\
	}
}
{
}

\Verse{16}
{
	\hRJE{}
}
{
	\eRJE{
		And Pharaoh hurried to call Moses and Aaron, and he said, “I’ve sinned
against YHWH, your God, and against you.\\
	}
}
{
}

\Verse{17}
{
	\hRJE{}
}
{
	\eRJE{
		And now, bear my sin just this one time and pray to YHWH, your God,
that He’ll turn just this death away from me.”\\
	}
}
{
}

\Verse{18}
{
	\hRJE{}
}
{
	\eRJE{
		And he went out from Pharaoh and prayed to YHWH,\\
	}
}
{
}

\Verse{19}
{
	\hRJE{}
}
{
	\eRJE{
		and YHWH turned back a very strong west wind, and it picked up the
locust swarm and blew it to the Red Sea. Not one locust was left in all
of Egypt’s border.\\
	}
}
{
}

\Verse{20}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH strengthened Pharaoh’s heart, and he did not let the children
of Israel go.\\
	}
}
{
}

\Verse{21}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH said to Moses, “Reach out your hand at the skies, and let
there be darkness on the land of Egypt, and one will feel darkness.”\\
	}
}
{
}

\Verse{22}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses reached out his hand at the skies, and there was dismal
darkness in all the land of Egypt—three days.\\
	}
}
{
}

\Verse{23}
{
	\hRJE{}
}
{
	\eRJE{
		Each man did not see his brother, and each man did not get up from
under it—three days. And for all the children of Israel there was light
in their homes.\\
	}
}
{
}

\Verse{24}
{
	\hRJE{}
}
{
	\eRJE{
		And Pharaoh called Moses, and he said, “Go. Serve YHWH. Only your
sheep and your oxen will stay put. Your infants will go with you as
well.”\\
	}
}
{
}

\Verse{25}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses said, “You shall put sacrifices and offerings in our hand as
well, so we’ll do them for YHWH, our God.\\
	}
}
{
}

\Verse{26}
{
	\hRJE{}
}
{
	\eRJE{
		And our livestock will go with us as well. Not a hoof will be left.
Because we’ll take from it to serve YHWH, our God, and we won’t know how
we’ll serve YHWH until we come there.”\\
	}
}
{
}

\Verse{27}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH strengthened Pharaoh’s heart, and he was not willing to let
them go.\\
	}
}
{
}

\Verse{28}
{
	\hRJE{}
}
{
	\eRJE{
		And Pharaoh said to him, “Go away from me! Watch yourself! Don’t
continue to see my face. Because in the day you see my face you’ll die!”

10:28,29; 11:6. continue. The word—Hebrew root ysp, meaning to do again,
add, continue—occurs three times in succession, a final reminder of
Joseph (yôsp), whom the oppressing Pharaohs did not know.\\
	}
}
{
}

\Verse{29}
{
	\hRJE{}
}
{
	\eRJE{
		And Moses said, “So you’ve spoken: I won’t continue to see your face
anymore.”\\
	}
}
{
}

