\Chapter{12}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		12

¹ And YHWH said to Moses and to Aaron in the land of Egypt, saying,\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“This month is the beginning of months for you. It is first of the
months of the year for you.\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		Speak to all of the congregation of Israel, saying: On the tenth of
this month, let them each take a lamb for the fathers’ houses, a lamb
per house.\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And if the household will be too few for a lamb, then he and his
neighbor who is close to his house will take it according to the count
of persons; you shall count each person according to what he eats for
the lamb.\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		You shall have an unblemished, male, year-old lamb; you shall take it
from the sheep or from the goats.\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And it will be for you to watch over until the fourteenth day of this
month. And all the community of the congregation of Israel will
slaughter it ‘between the two evenings.’\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		And they will take some of the blood and place it on the two doorposts
and on the lintel on the houses in which they will eat it.\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And they will eat the meat in this night; they will eat it fire-roasted
and with unleavened bread on bitter herbs.\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		Do not eat any of it raw or cooked in water, but fire-roasted: its head
with its legs and with its innards.\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And do not leave any of it until morning; and you shall burn what is
left of it until morning in fire.\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And you shall eat it like this: your hips clothed, your shoes on your
feet, and your staff in your hand; and you shall eat it in haste. It is
YHWH’s Passover.\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		“And I shall pass through the land of Egypt in this night, and I shall
strike every firstborn in the land of Egypt, from human to animal, and I
shall make judgments on all the gods of Egypt. I am YHWH.\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And the blood will be as a sign for you on the houses in which you
are, and I shall see the blood, and I shall halt at you, and there won’t
be a plague among you as a destroyer when I strike in the land of Egypt.

12:13,23,27. halt. Hebrew psa does not mean “to pass
over.” That wording has led people to images of the deity floating over
houses. The verb means “to halt” or “to walk in a halting manner”; it
can refer to limping (2 Sam 4:4). The noun form pissa
means a cripple (2 Sam 9:13). Admittedly, this verb occurs in Isaiah in
a verse that pictures God defending Jerusalem “like birds flying”
(31:5). Still, “halting” fits with the context here in Exodus,
especially in 12:23, where it suggests a conception of the deity moving
along through Egypt, spotting the blood on the doorposts, and coming to
an abrupt stop. God “halts on the threshold” and does not allow the
destroying force to enter the house. “Passing over” the threshold does
not really fit with this picture of blocking or preventing the
destroyer.

12:13,23. destroyer. The Hebrew pun conveys the message: the Israelites
are to slaughter (root ) the lamb so as to keep out the destroyer
(root ).\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		“And this day will become a commemoration for you, and you shall
celebrate it, a festival to YHWH; you shall celebrate it through your
generations, an eternal law:\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		Seven days you shall eat unleavened bread. Indeed, on the first day
you shall make leaven cease from your houses. Because anyone who eats
leavened bread: that person will be cut off from Israel—from the first
day to the seventh day.\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And you will have a holy assembly on the first day and a holy assembly
on the seventh day. Not any work will be done on them. Just what will be
eaten by each person: that alone will be done for you.\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And you shall observe the unleavened bread, because in this very day I
brought out your masses from the land of Egypt, and you shall observe
this day through your generations, an eternal law.\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		In the first month, on the fourteenth day of the month, in the
evening, you shall eat unleavened bread, until the twenty-first day of
the month, in the evening.\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		Seven days leaven shall not be found in your houses, because anyone
who eats something leavened: that person will be cut off from the
congregation of Israel, whether the alien or the citizen of the land.\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		You shall not eat anything leavened; in all your homes you shall eat
unleavened bread.”\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		And Moses called all Israel’s elders, and he said to them, “Pull out
and take a sheep for your families and slaughter the Passover.\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		And you’ll take a bunch of hyssop and dip in the blood that is in a
basin and touch some of the blood that is in the basin to the lintel and
to the two doorposts. And you shall not go out, each one, from his
house’s entrance until morning.\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		And YHWH will pass to strike Egypt, and He’ll see the blood on the
lintel and on the two doorposts, and YHWH will halt at the entrance and
will not allow the destroyer to come to your houses to strike.\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		And you shall observe this thing as a law for you and your children
forever.\\
	}
}
{
}

\Verse{25}
{
	\hJ{}
}
{
	\eJ{
		And it will be, when you will come to the land that YHWH will give to
you as He has spoken, that you shall observe this service.\\
	}
}
{
}

\Verse{26}
{
	\hJ{}
}
{
	\eJ{
		And it will be, when your children will say to you, ‘What is this
service to you?’\\
	}
}
{
}

\Verse{27}
{
	\hJ{}
}
{
	\eJ{
		that you shall say, ‘It is the Passover sacrifice to YHWH, because He
halted at the houses of the children of Israel in Egypt when He struck
Egypt, and He saved our houses.’”

And the people knelt and bowed.\\
	}
}
{
}

\Verse{28}
{
	\hR{}
}
{
	\eR{
		And the children of Israel went and did as YHWH had commanded Moses
and Aaron. They did so.\\
	}
}
{
}

\Verse{29}
{
	\hRJE{}
}
{
	\eRJE{
		And it was in the middle of the night, and YHWH struck every firstborn
in the land of Egypt, from the firstborn of Pharaoh who was sitting on
his throne to the firstborn of the prisoner who was in the prison house
and every firstborn of an animal.\\
	}
}
{
}

\Verse{30}
{
	\hRJE{}
}
{
	\eRJE{
		And Pharaoh got up at night, he and all his servants and all Egypt,
and there was a big cry in Egypt, because there was not a house in which
there was not one dead.\\
	}
}
{
}

\Verse{31}
{
	\hRJE{}
}
{
	\eRJE{
		And he called Moses and Aaron at night, and he said, “Get up. Go out
from among my people, both you and the children of Israel, and go, serve
YHWH as you spoke.\\
	}
}
{
}

\Verse{32}
{
	\hRJE{}
}
{
	\eRJE{
		Take your sheep also, your oxen also, as you spoke, and go. And you’ll
bless me as well!”\\
	}
}
{
}

\Verse{33}
{
	\hRJE{}
}
{
	\eRJE{
		And Egypt was forceful on the people to hurry to let them go from the
land, because they said, “We’re all dead!”\\
	}
}
{
}

\Verse{34}
{
	\hRJE{}
}
{
	\eRJE{
		And the people carried off its dough before it leavened, their bowls
being wrapped in their garments on their shoulder.\\
	}
}
{
}

\Verse{35}
{
	\hRJE{}
}
{
	\eRJE{
		And the children of Israel had done according to Moses’ word, and they
asked items of silver and items of gold and garments from Egypt.\\
	}
}
{
}

\Verse{36}
{
	\hRJE{}
}
{
	\eRJE{
		And YHWH had put the people’s favor in the Egyptians’ eyes, and they
lent to them, and they despoiled Egypt.\\
	}
}
{
}

\Verse{37}
{
	\hP{}
}
{
	\eP{
		And the children of Israel traveled from Rameses to Succoth, about six
hundred thousand on foot—men, apart from infants.\\
	}
}
{
}

\Verse{38}
{
	\hP{}
}
{
	\eP{
		And also a great mixture had gone up with them, and sheep and oxen, a
very heavy livestock.\\
	}
}
{
}

\Verse{39}
{
	\hP{}
}
{
	\eP{
		And they baked the dough that they brought out of Egypt: cakes of
unleavened bread, because it had not leavened, because they were driven
from Egypt and were not able to delay, and they also had not made
provisions for themselves.\\
	}
}
{
}

\Verse{40}
{
	\hP{}
}
{
	\eP{
		And the duration of the children of Israel that they lived in Egypt
was thirty years and four hundred years.\\
	}
}
{
}

\Verse{41}
{
	\hP{}
}
{
	\eP{
		And it was at the end of thirty years and four hundred years, and it
was in that very day: all of YHWH’s masses went out from the land of
Egypt.\\
	}
}
{
}

\Verse{42}
{
	\hP{}
}
{
	\eP{
		It is a night to be observed for YHWH for bringing them out from the
land of Egypt. It is this night, to be observed for YHWH for all the
children of Israel through their generations.\\
	}
}
{
}

\Verse{43}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Moses and Aaron, “This is the law of the Passover:
any foreigner shall not eat from it.\\
	}
}
{
}

\Verse{44}
{
	\hP{}
}
{
	\eP{
		And every slave of a man, purchased with money: you shall circumcise
him; then he shall eat from it.\\
	}
}
{
}

\Verse{45}
{
	\hP{}
}
{
	\eP{
		A visitor and an employee shall not eat from it.\\
	}
}
{
}

\Verse{46}
{
	\hP{}
}
{
	\eP{
		It shall be eaten in one house; you shall not take any of the meat
from the house outside. And you shall not break a bone from it.\\
	}
}
{
}

\Verse{47}
{
	\hP{}
}
{
	\eP{
		All of the congregation of Israel shall do it.\\
	}
}
{
}

\Verse{48}
{
	\hP{}
}
{
	\eP{
		And if an alien will reside with you and will make a Passover to YHWH,
let him be circumcised, every male, and then he may come forward to do
it, and he will be like a citizen of the land, but everyone who is
uncircumcised shall not eat from it.\\
	}
}
{
}

\Verse{49}
{
	\hP{}
}
{
	\eP{
		There shall be one instruction for the citizen and for the alien who
resides among you.”\\
	}
}
{
}

\Verse{50}
{
	\hP{}
}
{
	\eP{
		And all the children of Israel did as YHWH had commanded Moses and
Aaron. They did so.\\
	}
}
{
}

\Verse{51}
{
	\hP{}
}
{
	\eP{
		And it was in this very day: YHWH brought out the children of Israel
from the land of Egypt by their masses.\\
	}
}
{
}

