\Chapter{14}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		14

¹ And YHWH spoke to Moses, saying,\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		“Speak to the children of Israel that they should go back and camp in
front of Pi-Hahiroth, between Migdol and the sea, in front of
Baal-Zephon. You shall camp facing it, by the sea.\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And Pharaoh will say about the children of Israel: ‘They’re muddled in
the land! The wilderness has closed them in.’\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And I’ll strengthen Pharaoh’s heart, and he’ll pursue them, and I’ll be
glorified against Pharaoh and against all of his army, and Egypt will
know that I am YHWH.” And they did so.\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		And it was told to the king of Egypt that the people had fled, and the
heart of Pharaoh and his servants was changed toward the people. And
they said, “What is this that we’ve done, that we let Israel go from
serving us?!”\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And he hitched his chariot and took his people with him.\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		And he took six hundred chosen chariots—and all the chariotry of
Egypt—and officers over all of it.\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And YHWH strengthened the heart of Pharaoh, king of Egypt, and he
pursued the children of Israel. And the children of Israel were going
out with a high hand.\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And Egypt pursued them, and they caught up to them, camping by the
sea—every chariot horse of Pharaoh and his horsemen and his army—at
Pi-Hahiroth, in front of Baal-Zephon.\\
	}
}
{
}

\Verse{10}
{
	\hJ{}
}
{
	\eJ{
		And Pharaoh came close! And the children of Israel raised their eyes,
and here was Egypt coming after them, and they were very afraid. And the
children of Israel cried out to YHWH.\\
	}
}
{
}

\Verse{11}
{
	\hJ{}
}
{
	\eJ{
		And they said to Moses, “Was it because of an absence—none!—of graves
in Egypt that you took us to die in the wilderness?! What is this that
you’ve done to us to bring us out of Egypt?\\
	}
}
{
}

\Verse{12}
{
	\hJ{}
}
{
	\eJ{
		Isn’t this the thing that we spoke to you in Egypt, saying: Stop from
us! And let’s serve Egypt. Because serving Egypt is better for us than
our dying in the wilderness!”\\
	}
}
{
}

\Verse{13}
{
	\hJ{}
}
{
	\eJ{
		And Moses said to the people, “Don’t be afraid. Stand still and see
YHWH’s salvation that He’ll do for you today. For, as you’ve seen Egypt
today, you’ll never see them again, ever.\\
	}
}
{
}

\Verse{14}
{
	\hJ{}
}
{
	\eJ{
		YHWH will fight for you, and you’ll keep quiet!”\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Moses, “Why do you cry out to me? Speak to the
children of Israel that they should move!\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And you, lift your staff and reach your hand out over the sea—and
split it! And the children of Israel will come through the sea on the
dry ground.\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And I, here, I’m strengthening Egypt’s heart, and they’ll come after
them, and I’ll be glorified against Pharaoh and against all of his army,
against his chariots and against his horsemen.\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And Egypt will know that I am YHWH when I’m glorified against Pharaoh,
against his chariots and against his horsemen.”\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		And the angel of God who was going in front of the camp of Israel
moved and went behind them, and the column of cloud went from in front
of them and stood behind them.\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		And it came between the camp of Egypt and the camp of Israel. And
there was the cloud and darkness [for the Egyptians], while it [the
column of fire] lit the night [for the Israelites], and one did not come
near the other all night.\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		And Moses reached his hand out over the sea, and YHWH drove back the
sea with a strong east wind all night and turned the sea into dry
ground, and the sea was split.\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And the children of Israel came through the sea on the dry ground. And
the water was a wall to them at their right and at their left.\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		And Egypt pursued and came after them, every horse of Pharaoh, his
chariots and his horsemen, through the sea.\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		And it was in the morning watch, and YHWH gazed at Egypt’s camp
through a column of fire and cloud and threw Egypt’s camp into tumult,\\
	}
}
{
}

\Verse{25}
{
	\hJ{}
}
{
	\eJ{
		and He turned its chariots’ wheel so that it drove it with heaviness.

And Egypt said, “Let me flee from Israel, because YHWH is fighting for
them against Egypt!”\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Moses, “Reach your hand out over the sea, and the
water will go back over Egypt, over his chariots and over his horsemen.”\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		And Moses reached his hand out over the sea, and the sea went back to
its strong flow toward morning, and Egypt was fleeing toward it. And
YHWH tossed the Egyptians into the sea.\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		And the waters went back and covered the chariots and the horsemen—all
of Pharaoh’s army who were coming after them in the sea. Not even one of
them was left.\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		And the children of Israel had gone on the dry ground through the sea,
and the water had been a wall to them at their right and at their left.\\
	}
}
{
}

\Verse{30}
{
	\hR{}
}
{
	\eR{
		And YHWH saved Israel from Egypt’s hand that day. And Israel saw Egypt
dead on the seashore,\\
	}
}
{
}

\Verse{31}
{
	\hR{}
}
{
	\eR{
		and Israel saw the big hand that YHWH had used against Egypt, and the
people feared YHWH, and they trusted in YHWH and in Moses His servant.\\
	}
}
{
}

