\Chapter{15}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		15

¹ Then Moses and the children of Israel sang this song to YHWH. And they
said, saying:

Let me sing to YHWH, for He triumphed! Horse and its rider He cast in
the sea.\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		My strength and song are Yah, and He became a salvation for me. This
is my God, and I’ll praise Him, my father’s God, and I’ll hail Him.\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		YHWH is a warrior. YHWH is His name.\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		Pharaoh’s chariots and his army He plunged in the sea and the choice
of his troops drowned in the Red Sea.\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		The deeps covered them. They sank in the depths like a stone.\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		Your right hand, YHWH, awesome in power, your right hand, YHWH,
crushed the foe.\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		And in your triumph’s greatness you threw down your adversaries. You
let go your fury: it consumed them like straw.\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		And by wind from your nostrils water was massed, surf piled up like a
heap, the deeps congealed in the heart of the sea.\\
	}
}
{
}

\Verse{9}
{
	\hJ{}
}
{
	\eJ{
		The enemy said, “I’ll pursue! I’ll catch up! I’ll divide spoil! My
soul will be sated! I’ll unsheathe my sword! My hand will deprive them!”\\
	}
}
{
}

\Verse{10}
{
	\hJ{}
}
{
	\eJ{
		You blew with your wind. Sea covered them. They sank like lead in the
awesome water.\\
	}
}
{
}

\Verse{11}
{
	\hJ{}
}
{
	\eJ{
		Who is like you among the gods, YHWH! Who is like you: awesome in
holiness! fearsome with splendors! making miracles!\\
	}
}
{
}

\Verse{12}
{
	\hJ{}
}
{
	\eJ{
		You reached your right hand: earth swallowed them.\\
	}
}
{
}

\Verse{13}
{
	\hJ{}
}
{
	\eJ{
		You led, in your kindness, the people you redeemed; you ushered, in
your strength, to your holy abode.\\
	}
}
{
}

\Verse{14}
{
	\hJ{}
}
{
	\eJ{
		Peoples heard—they shuddered. Shaking seized Philistia’s residents.\\
	}
}
{
}

\Verse{15}
{
	\hJ{}
}
{
	\eJ{
		Then Edom’s chiefs were terrified. Moab’s chieftains: trembling
seized them. All Canaan’s residents melted.\\
	}
}
{
}

\Verse{16}
{
	\hJ{}
}
{
	\eJ{
		Terror and fear came over them. At the power of your arm they’re
silent like stone. ’Til your people passed, YHWH, ’til the people you
created passed.\\
	}
}
{
}

\Verse{17}
{
	\hJ{}
}
{
	\eJ{
		You’ll bring them and plant them in your legacy’s mountain, your
throne’s platform, that you made, YHWH; a holy place, Lord, that your
hands reared.\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		YHWH will reign forever and ever!\\
	}
}
{
}

\Verse{19}
{
	\hR{}
}
{
	\eR{
		Because Pharaoh’s horses with his chariots and with his horsemen came
in the sea, and YHWH brought back the water of the sea over them, and
the children of Israel had gone on the dry ground through the sea.\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		And Miriam, the prophetess, Aaron’s sister, took a drum in her hand,
and all the women went out behind her with drums and with dances.\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		And Miriam sang to them:

Sing to YHWH for He triumphed!

Horse and its rider He cast in the sea.\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		And Moses had Israel travel from the Red Sea, and they went out to the
wilderness of Shur. And they went three days in the wilderness. And they
did not find water.\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		And they came to Marah, and they were not able to drink water from
Marah because it was bitter. On account of this he called its name
Marah.\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		And the people complained at Moses, saying, “What shall we drink?”\\
	}
}
{
}

\Verse{25}
{
	\hE{}
}
{
	\eE{
		And he cried to YHWH, and YHWH showed him a tree, and he threw it into
the water, and the water sweetened.

He set law and judgment for them there, and He tested them there.\\
	}
}
{
}

\Verse{26}
{
	\hE{}
}
{
	\eE{
		And He said, “If you’ll listen to the voice of YHWH, your God, and
you’ll do what is right in His eyes and turn your ear to His
commandments and observe all His laws, I won’t set on you any of the
sickness that I set on Egypt, because I, YHWH, am your healer.”\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		And they came to Elim. And twelve springs of water and seventy palm
trees were there. And they camped there by the water.\\
	}
}
{
}

