\Chapter{16}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		16

¹ And they traveled from Elim, and all of the congregation of the
children of Israel came to the wilderness of Sîn, which is between Elim
and Sinai, on the fifteenth day of the second month after their exodus
from the land of Egypt.\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		And all of the congregation of the children of Israel complained at
Moses and at Aaron in the wilderness.\\
	}
}
{
}

\Verse{3}
{
	\hP{}
}
{
	\eP{
		And the children of Israel said to them, “Who would make it so that we
had died by YHWH’s hand in the land of Egypt, when we sat by a pot of
meat, when we ate bread to the full! Because you brought us out to this
wilderness to kill this whole community with starvation!”\\
	}
}
{
}

\Verse{4}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Moses, “Here, I’m raining bread from the skies for
you, and let the people go out and gather the daily ration in its day in
order that I can test them: will they go by my instruction or not.\\
	}
}
{
}

\Verse{5}
{
	\hP{}
}
{
	\eP{
		And it will be that on the sixth day they’ll prepare what they bring
in, and it will be twice as much as they’ll gather on regular days.”\\
	}
}
{
}

\Verse{6}
{
	\hP{}
}
{
	\eP{
		And Moses and Aaron said to all the children of Israel, “At evening
you’ll know that YHWH brought you out from the land of Egypt,\\
	}
}
{
}

\Verse{7}
{
	\hP{}
}
{
	\eP{
		and in the morning you’ll see YHWH’s glory, because He has heard your
complaints about YHWH. And what are we, that you complain at us?!”\\
	}
}
{
}

\Verse{8}
{
	\hP{}
}
{
	\eP{
		And Moses said, “When YHWH gives you meat to eat in the evening and
bread to the full in the morning, because YHWH has heard your complaints
that you’re making at Him! And what are we? Your complaints are not at
us but at YHWH!”\\
	}
}
{
}

\Verse{9}
{
	\hP{}
}
{
	\eP{
		And Moses said to Aaron, “Say to all of the congregation of the
children of Israel, ‘Come close in front of YHWH, because He has heard
your complaints.’”\\
	}
}
{
}

\Verse{10}
{
	\hP{}
}
{
	\eP{
		And it was as Aaron was speaking to all of the congregation of the
children of Israel: and they turned to the wilderness, and here was
YHWH’s glory appearing in a cloud.\\
	}
}
{
}

\Verse{11}
{
	\hP{}
}
{
	\eP{
		And YHWH spoke to Moses, saying,\\
	}
}
{
}

\Verse{12}
{
	\hP{}
}
{
	\eP{
		“I’ve heard the complaints of the children of Israel. Speak to them,
saying, ‘Between the two evenings you shall eat meat, and in the morning
you shall be filled with bread, and you will know that I am YHWH, your
God.’”\\
	}
}
{
}

\Verse{13}
{
	\hP{}
}
{
	\eP{
		And it was in the evening, and quail went up and covered the camp. And
in the morning there was a layer of dew around the camp.\\
	}
}
{
}

\Verse{14}
{
	\hP{}
}
{
	\eP{
		And the layer of dew went up, and here, on the face of the wilderness:
scaly thin, thin as frost on the ground.\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And the children of Israel saw, and each said to his brother, “What is
it?”—because they did not know what it was.

And Moses said to them, “That is the bread that YHWH has given you for
food.\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		This is the thing that YHWH has commanded: Collect some of it, each
according to what he eats; you shall take an omer per head, the number
of your persons, each for whoever is in his tent.”\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And the children of Israel did so. And they collected—the one who took
the most and the one who took the least.\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And they measured by the omer, and the one who took the most had not
exceeded, and the one who took the least had not fallen short. Each had
collected according to what he eats.\\
	}
}
{
}

\Verse{19}
{
	\hP{}
}
{
	\eP{
		And Moses said to them, “Let no one leave any of it over until
morning.”\\
	}
}
{
}

\Verse{20}
{
	\hP{}
}
{
	\eP{
		And they did not listen to Moses, and people left some of it over
until morning, and it yielded worms and stank. And Moses was angry at
them.\\
	}
}
{
}

\Verse{21}
{
	\hP{}
}
{
	\eP{
		And they collected it morning by morning, each by what he eats, and
when the sun was hot it melted.\\
	}
}
{
}

\Verse{22}
{
	\hP{}
}
{
	\eP{
		And it was: on the sixth day they collected double bread, two times
the omer for each one, and all the chiefs of the congregation came and
told Moses.\\
	}
}
{
}

\Verse{23}
{
	\hP{}
}
{
	\eP{
		And he said to them, “That is what YHWH spoke. Tomorrow is a ceasing,
a holy Sabbath to YHWH. Bake what you’ll bake, and cook what you’ll
cook, and leave what is left over for keeping until the morning.”\\
	}
}
{
}

\Verse{24}
{
	\hP{}
}
{
	\eP{
		And they left it until the morning, as Moses had commanded, and it did
not stink, and there was not a worm in it.\\
	}
}
{
}

\Verse{25}
{
	\hP{}
}
{
	\eP{
		And Moses said, “Eat it today, because today is a Sabbath to YHWH.
Today you won’t find it in the field.\\
	}
}
{
}

\Verse{26}
{
	\hP{}
}
{
	\eP{
		Six days you shall collect it. And on the seventh day is a Sabbath;
there will not be any in it.”\\
	}
}
{
}

\Verse{27}
{
	\hP{}
}
{
	\eP{
		And it was: on the seventh day some of the people went out to collect,
and they did not find any.\\
	}
}
{
}

\Verse{28}
{
	\hP{}
}
{
	\eP{
		And YHWH said to Moses, “How long do you refuse to observe my
commandments and my instructions?\\
	}
}
{
}

\Verse{29}
{
	\hP{}
}
{
	\eP{
		See that YHWH has given you the Sabbath. On account of this He is
giving you two days’ bread on the sixth day. Stay, each in his place.
Let no man go out from his place in the seventh day.”\\
	}
}
{
}

\Verse{30}
{
	\hP{}
}
{
	\eP{
		And the people ceased in the seventh day.\\
	}
}
{
}

\Verse{31}
{
	\hP{}
}
{
	\eP{
		And the house of Israel called its name “manna.” And it was like a
coriander seed, white, and its taste was like a wafer in honey.\\
	}
}
{
}

\Verse{32}
{
	\hP{}
}
{
	\eP{
		And Moses said, “This is the thing that YHWH has commanded: ‘an
omer-ful of it is for watching over through your generations so that
they will see the bread that I fed you in the wilderness when I brought
you out from the land of Egypt.’”\\
	}
}
{
}

\Verse{33}
{
	\hP{}
}
{
	\eP{
		And Moses said to Aaron, “Take one jar and place an omer-ful of manna
there and lay it in front of YHWH for watching over through your
generations,”\\
	}
}
{
}

\Verse{34}
{
	\hP{}
}
{
	\eP{
		as YHWH had commanded Moses. And Aaron laid it in front of the
Testimony for watching over.\\
	}
}
{
}

\Verse{35}
{
	\hP{}
}
{
	\eP{
		And the children of Israel ate the manna forty years until they came
to settled land. They ate the manna until they came to the edge of the
land of Canaan.\\
	}
}
{
}

\Verse{36}
{
	\hP{}
}
{
	\eP{
		(And an omer is a tenth of an ephah.)\\
	}
}
{
}

