\Chapter{19}

\Verse{1}
{
	\hP{}
}
{
	\eP{
		19

¹ In the third month after the exodus of the children of Israel from the
land of Egypt, on this day, they came to the wilderness of Sinai.\\
	}
}
{
}

\Verse{2}
{
	\hP{}
}
{
	\eP{
		And they traveled from Rephidim and came to the wilderness of Sinai and
camped in the wilderness. And Israel camped there opposite the mountain.\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		And Moses had gone up to God. And YHWH called to him from the mountain,
saying, “This is what you shall say to the house of Jacob and tell to
the children of Israel:\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		‘You’ve seen what I did to Egypt, and I carried you on eagles’ wings
and brought you to me.\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		And now, if you’ll listen to my voice and observe my covenant, then
you’ll be a treasure to me out of all the peoples, because all the earth
is mine.\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And you’ll be a kingdom of priests and a holy nation to me.’ These are
the words that you shall speak to the children of Israel.”\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		And Moses came and called the people’s elders and set before them all
these words that YHWH had commanded him.\\
	}
}
{
}

\Verse{8}
{
	\hE{}
}
{
	\eE{
		And all the people responded together, and they said, “We’ll do
everything that YHWH has spoken.” And Moses brought back the people’s
words to YHWH.\\
	}
}
{
}

\Verse{9}
{
	\hE{}
}
{
	\eE{
		And YHWH said to Moses, “Here, I am coming to you in a mass of cloud
for the purpose that the people will hear when I am speaking with you,
and they will believe in you as well forever.” And Moses told the
people’s words to YHWH.\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		And YHWH said to Moses, “Go to the people and consecrate them today
and tomorrow; and they shall wash their clothes\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		and be ready for the third day, because on the third day YHWH will
come down on Mount Sinai before the eyes of all the people.\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		And you shall limit the people all around, saying, ‘Watch yourselves
about going up in the mountain and touching its edge. Anyone who touches
the mountain shall be put to death.\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		A hand shall not touch him, but he shall be stoned or shot. Whether
animal or man, he will not live.’ At the blowing of the horn they shall
go up the mountain.”\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		And Moses went down from the mountain to the people. And he
consecrated the people, and they washed their clothes.\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		And he said to the people, “Be ready for three days. Don’t come close
to a woman.”\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		And it was on the third day, when it was morning, and it was: thunders
and lightning and a heavy cloud on the mountain, and a sound of a horn,
very strong. And the entire people that was in the camp trembled.\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		And Moses brought out the people toward God from the camp, and they
stood up at the bottom of the mountain.\\
	}
}
{
}

\Verse{18}
{
	\hE{}
}
{
	\eE{
		And Mount Sinai was all smoke because YHWH came down on it in fire,
and its smoke went up like the smoke of a furnace, and the whole
mountain trembled greatly.\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		And the sound of the horn was getting much stronger. Moses would
speak, and God would answer him in a voice.\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		And YHWH came down on Mount Sinai, at the top of the mountain, and
YHWH called to Moses at the top of the mountain, and Moses went up.\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said to Moses, “Go down. Warn the people in case they break
through to YHWH, to see, and many of them fall.\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		And also let the priests who approach YHWH consecrate themselves, or
else YHWH will break out against them.”\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		And Moses said to YHWH, “The people is not able to go up to Mount
Sinai, because you warned us, saying, ‘Limit the mountain and consecrate
it.’”\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said to him, “Go. Go down. Then you’ll come up, you and Aaron
with you. And let the priests and the people not break through to come
up to YHWH, or else He’ll break out against them.”\\
	}
}
{
}

\Verse{25}
{
	\hJ{}
}
{
	\eJ{
		And Moses went down to the people, and he said it to them.\\
	}
}
{
}

