\Chapter{20}

\Verse{1}
{
	\hE{}
}
{
	\eE{
		20

¹ And God spoke all these words, saying:\\
	}
}
{
}

\Verse{2}
{
	\hE{}
}
{
	\eE{
		I am YHWH, your God, who brought you out from the land of Egypt, from a
house of slaves.\\
	}
}
{
}

\Verse{3}
{
	\hE{}
}
{
	\eE{
		You shall not have other gods before my face.\\
	}
}
{
}

\Verse{4}
{
	\hE{}
}
{
	\eE{
		You shall not make a statue or any form that is in the skies above or
that is in the earth below or that is in the water below the earth.\\
	}
}
{
}

\Verse{5}
{
	\hE{}
}
{
	\eE{
		You shall not bow to them, and you shall not serve them. Because I,
YHWH, your God, am a jealous God, counting parents’ crime on children,
on the third generation, and on the fourth generation of those who hate
me,\\
	}
}
{
}

\Verse{6}
{
	\hE{}
}
{
	\eE{
		but practicing kindness to thousands for those who love me and for
those who observe my commandments.\\
	}
}
{
}

\Verse{7}
{
	\hE{}
}
{
	\eE{
		You shall not bring up the name of YHWH, your God, for a falsehood,
because YHWH will not make one innocent who will bring up His name for a
falsehood.\\
	}
}
{
}

\Verse{8}
{
	\hE{}
}
{
	\eE{
		Remember the Sabbath day, to make it holy.\\
	}
}
{
}

\Verse{9}
{
	\hE{}
}
{
	\eE{
		Six days you shall labor and do all your work,\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		and the seventh day is a Sabbath to YHWH, your God. You shall not do
any work: you and your son and your daughter, your servant and your maid
and your animal and your alien who is in your gates.\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		Because for six days YHWH made the skies and the earth, the sea, and
everything that is in them, and He rested on the seventh day. On account
of this, YHWH blessed the Sabbath day and made it holy.\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		Honor your father and your mother, so that your days will be extended
on the land that YHWH, your God, is giving you.\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		You shall not murder.

You shall not commit adultery.

You shall not steal.

You shall not testify against your neighbor as a lying witness.\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		You shall not covet your neighbor’s house. You shall not covet your
neighbor’s wife or his servant or his maid or his ox or his ass or
anything that your neighbor has.\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		And all the people were seeing the thunders and the flashes and the
sound of the horn and the mountain smoking. And the people saw, and they
moved and stood at a distance,\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		and they said to Moses, “You speak with us so we may listen, but let
God not speak with us or else we’ll die.”\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		And Moses said to the people, “Don’t be afraid, because God is coming
for the purpose of testing you and for the purpose that his fear will be
on your faces so that you won’t sin.”\\
	}
}
{
}

\Verse{18}
{
	\hE{}
}
{
	\eE{
		And the people stood at a distance, and Moses went over to the nimbus
where God was.\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		And YHWH said to Moses, “You shall say this to the children of
Israel: You have seen that I have spoken with you from the skies.\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		You shall not make gods of silver with me, and you shall not make gods
of gold for yourselves.\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		You shall make an altar of earth for me, and you shall sacrifice on it
your burnt offerings and your peace offerings, your sheep and your oxen.
In every place where I’ll have my name commemorated I’ll come to you,
and I’ll bless you.\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		And if you’ll make an altar of stones for me, you shall not make them
cut. When you have elevated your sword over it, then you have desecrated
it.\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		And you shall not go up by stairs on my altar, so that your nudity
will not be exposed over it.”\\
	}
}
{
}

\Verse{24}
{
	\hJ{}
}
{
	\eJ{
	}
}
{
}

\Verse{26}
{
	\hJ{}
}
{
	\eJ{
	}
}
{
}

