\Chapter{22}

\Verse{1}
{
	\hE{}
}
{
	\eE{
		22

¹“If the thief will be found while breaking in and will be struck, and
he dies, there is no blood for him.\\
	}
}
{
}

\Verse{2}
{
	\hE{}
}
{
	\eE{
		If the sun has risen on him there is blood for him. He shall pay. If he
does not have it, then he shall be sold for his theft.

22.2. If the sun has risen on him there is blood for him. If the theft
was in the daytime—which is less frightening and when escape, help, and
witnesses are more possible—then one is legally responsible if one kills
the thief.\\
	}
}
{
}

\Verse{3}
{
	\hE{}
}
{
	\eE{
		If the theft will be found in his hand—from ox to ass to sheep—alive,
he shall pay two.\\
	}
}
{
}

\Verse{4}
{
	\hE{}
}
{
	\eE{
		“If a man will have a field or a vineyard grazed, and he will let his
beast go and graze in another person’s field, he shall pay the best of
his field and the best of his vineyard.\\
	}
}
{
}

\Verse{5}
{
	\hE{}
}
{
	\eE{
		“If fire will break out and find thorns and stacked grain or standing
grain or a field is consumed, the one who set the blaze shall pay.\\
	}
}
{
}

\Verse{6}
{
	\hE{}
}
{
	\eE{
		“If a man will give his neighbor money or items to watch, and it will
be stolen from the man’s house, if the thief will be found he shall pay
two.\\
	}
}
{
}

\Verse{7}
{
	\hE{}
}
{
	\eE{
		If the thief will not be found, then the owner of the house shall be
brought near to God: that he has not put out his hand into his
neighbor’s property.\\
	}
}
{
}

\Verse{8}
{
	\hE{}
}
{
	\eE{
		“Over every case of an offense, over an ox, over an ass, over a sheep,
over clothing, over every loss about which one will say that ‘This is
it,’ the word of the two of them shall come to God. The one whom God
will implicate shall pay two to his neighbor.\\
	}
}
{
}

\Verse{9}
{
	\hE{}
}
{
	\eE{
		“If a man will give an ass or an ox or a sheep or any animal to his
neighbor to watch, and it dies or is injured or is seized—no one seeing—\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		an oath of YHWH shall be between the two of them: that he has not put
out his hand into his neighbor’s property; and its owner shall take it,
and he shall not pay.\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		And if it will be stolen from him, he shall pay its owner.\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		If it will be torn, he shall bring it in witness; he shall not pay for
the torn one.\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		And if a man will ask it of his neighbor, and it is injured or dies,
its owner not being with it, he shall pay.\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		If its owner is with it, he shall not pay. If it was hired, he has its
hire coming to him.\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		“And if a man will deceive a virgin who is not betrothed, and he lies
with her, he shall espouse her by a bride-price to him as a wife.\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		If her father will refuse to give her to him, he shall weigh out money
corresponding to the bride-price of virgins.\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		“You shall not let a witch live.\\
	}
}
{
}

\Verse{18}
{
	\hE{}
}
{
	\eE{
		“Anyone who lies with an animal shall be put to death.\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		“One who sacrifices to gods shall be completely destroyed—except to
YHWH alone.\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		“And you shall not persecute an alien, and you shall not oppress him,
because you were aliens in the land of Egypt.\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		“You shall not degrade any widow or orphan.\\
	}
}
{
}

\Verse{22}
{
	\hE{}
}
{
	\eE{
		If you will degrade them, when they will cry out to me I’ll hear their
cry,\\
	}
}
{
}

\Verse{23}
{
	\hE{}
}
{
	\eE{
		and my anger will flare, and I’ll kill you with a sword, and your
wives will be widows and your children orphans!\\
	}
}
{
}

\Verse{24}
{
	\hE{}
}
{
	\eE{
		“If you will lend money to my people, to the poor who is with you, you
shall not be like a creditor to him; you shall not impose interest on
him.\\
	}
}
{
}

\Verse{25}
{
	\hE{}
}
{
	\eE{
		If you take your neighbor’s clothing as security, you shall give it
back to him by the sunset,\\
	}
}
{
}

\Verse{26}
{
	\hE{}
}
{
	\eE{
		because it is his only apparel; it is his clothing for his skin. In
what will he sleep? And it will be, when he will cry out to me, that I
shall listen, because I am gracious.\\
	}
}
{
}

\Verse{27}
{
	\hE{}
}
{
	\eE{
		“You shall not blaspheme God, and you shall not curse a chieftain
among your people.\\
	}
}
{
}

\Verse{28}
{
	\hE{}
}
{
	\eE{
		“You shall not delay your fulfillment and your flowing.

“You shall give me the firstborn of your sons.\\
	}
}
{
}

\Verse{29}
{
	\hE{}
}
{
	\eE{
		“You shall do this to your ox and to your sheep: Seven days it will be
with its mother. On the eighth day you shall give it to me.\\
	}
}
{
}

\Verse{30}
{
	\hE{}
}
{
	\eE{
		“And you shall be holy people to me.

“And you shall not eat meat in the field that is torn. You shall throw
it to the dog.\\
	}
}
{
}

