\Chapter{24}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		24

¹ And He said to Moses, “Come up to YHWH: you and Aaron, Nadab and Abihu,
and seventy of Israel’s elders, and bow from a distance.\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		And Moses will come over alone to YHWH, and they shall not come over,
and the people shall not come up with him.”\\
	}
}
{
}

\Verse{3}
{
	\hE{}
}
{
	\eE{
		And Moses came and told the people all of YHWH’s words and all the
judgments. And all the people answered, one voice, and they said, “We’ll
do all the things that YHWH has spoken.”\\
	}
}
{
}

\Verse{4}
{
	\hE{}
}
{
	\eE{
		And Moses wrote all of YHWH’s words. And he got up early in the morning
and built an altar below the mountain and twelve pillars for twelve
tribes of Israel.\\
	}
}
{
}

\Verse{5}
{
	\hE{}
}
{
	\eE{
		And he sent young men of the children of Israel, and they made burnt
offerings, and they made peace-offering sacrifices to YHWH: bulls.\\
	}
}
{
}

\Verse{6}
{
	\hE{}
}
{
	\eE{
		And Moses took half of the blood and set it in basins and threw half of
the blood on the altar.\\
	}
}
{
}

\Verse{7}
{
	\hE{}
}
{
	\eE{
		And he took the scroll of the covenant and read in the people’s ears.
And they said, “We’ll do everything that YHWH has spoken, and we’ll
listen.”\\
	}
}
{
}

\Verse{8}
{
	\hE{}
}
{
	\eE{
		And Moses took the blood and threw it on the people, and he said, “Here
is the blood of the covenant that YHWH has made with you regarding all
these things.”\\
	}
}
{
}

\Verse{9}
{
	\hE{}
}
{
	\eE{
		And Moses and Aaron, Nadab and Abihu, and seventy of Israel’s elders
went up.\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		And they saw the God of Israel. And below His feet it was like a
structure of sapphire brick and like the essence of the skies for
clarity.

24:10–11. And they saw God. … And they envisioned God. Some have taken
this to mean that they literally, physically see God. But, as Ibn Ezra
properly observed, the verb for “they saw” (Hebrew r’h) is also used to
refer to seeing in a vision, as when Isaiah says, “I saw the Lord
sitting on a throne” (Isa 6:1). This meaning of “they saw” here is
confirmed by the parallel use in v. 11 of the word “envisioned” (Hebrew
zh), which regularly means to have a vision (as, for example in
Isa 1:1). Also, this is consistent with the idea that no one ever sees
the actual form of God except Moses on a single occasion. This idea is
understood throughout the Tanak, without exception. (On the distinction
between vision and regular experience, see The Hidden Face of God, pp.
17–18, 62–63.)\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		And He did not put out His hand to the chiefs of the children of
Israel. And they envisioned God. And they ate and drank.\\
	}
}
{
}

\Verse{12}
{
	\hE{}
}
{
	\eE{
		And YHWH said to Moses, “Come up to me, to the mountain, and be there,
and I’ll give you stone tablets and the instruction and the commandment
that I’ve written to instruct them.”\\
	}
}
{
}

\Verse{13}
{
	\hE{}
}
{
	\eE{
		And Moses and Joshua, his attendant, got up, and Moses went up to the
Mountain of God.\\
	}
}
{
}

\Verse{14}
{
	\hE{}
}
{
	\eE{
		And he said to the elders, “Sit for us here until we’ll come back to
you. And here, Aaron and Hur are with you. Let whoever has any matters
go over to them.”\\
	}
}
{
}

\Verse{15}
{
	\hP{}
}
{
	\eP{
		And Moses went up to the mountain. And the cloud covered the mountain.\\
	}
}
{
}

\Verse{16}
{
	\hP{}
}
{
	\eP{
		And YHWH’s glory settled on Mount Sinai, and the cloud covered it six
days. And He called to Moses on the seventh day from inside the cloud.\\
	}
}
{
}

\Verse{17}
{
	\hP{}
}
{
	\eP{
		And the appearance of YHWH’s glory was like a consuming fire in the
mountaintop before the eyes of the children of Israel.\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And Moses came inside the cloud and went up into the mountain. And
Moses was in the mountain forty days and forty nights.\\
	}
}
{
}

