\Chapter{28}

\Verse{1}
{
	\hOther{}
}
{
	\eOther{
		28

¹“And you, bring Aaron, your brother, forward to you, and his sons with
him, from among the children of Israel, for him to function as a priest
for me: Aaron, Nadab and Abihu, Eleazar and Ithamar, Aaron’s sons.\\
	}
}
{
}

\Verse{2}
{
	\hOther{}
}
{
	\eOther{
		And you shall make holy clothes for Aaron, your brother, for glory and
for beauty.\\
	}
}
{
}

\Verse{3}
{
	\hOther{}
}
{
	\eOther{
		And you shall speak to all the wise of heart whom I have filled with a
spirit of wisdom, that they shall make Aaron’s clothes, to sanctify him
for him to function as a priest for me.\\
	}
}
{
}

\Verse{4}
{
	\hOther{}
}
{
	\eOther{
		And these are the clothes that they shall make: breastplate and ephod
and robe and patterned coat, a headdress and a sash. And they shall make
holy clothes for Aaron, your brother, and for his sons, for him to
function as a priest for me.\\
	}
}
{
}

\Verse{5}
{
	\hOther{}
}
{
	\eOther{
		And they shall take the gold and the blue and the purple and the
scarlet and the linen.\\
	}
}
{
}

\Verse{6}
{
	\hOther{}
}
{
	\eOther{
		“And they shall make the ephod: gold, blue, and purple, scarlet, and
woven linen, designer’s work.\\
	}
}
{
}

\Verse{7}
{
	\hOther{}
}
{
	\eOther{
		It shall have two connected shoulder-pieces at its two ends, and it
will be connected.\\
	}
}
{
}

\Verse{8}
{
	\hOther{}
}
{
	\eOther{
		And the ephod’s designed belt that is on it shall be like its work and
be a part of it: gold, blue, and purple, and scarlet and woven linen.\\
	}
}
{
}

\Verse{9}
{
	\hOther{}
}
{
	\eOther{
		And you shall take two onyx stones and inscribe the names of the
children of Israel on them:\\
	}
}
{
}

\Verse{10}
{
	\hOther{}
}
{
	\eOther{
		six of their names on one stone and the names of the remaining six on
the second stone, according to their birth orders.\\
	}
}
{
}

\Verse{11}
{
	\hOther{}
}
{
	\eOther{
		By a stone engraver’s work you shall inscribe the two stones with
signet inscriptions according to the names of the children of Israel.
You shall make them surrounded by settings of gold.\\
	}
}
{
}

\Verse{12}
{
	\hOther{}
}
{
	\eOther{
		And you shall set the two stones on the ephod’s shoulder-pieces,
commemorative stones for the children of Israel, and Aaron shall carry
their names in front of YHWH on his two shoulders as a commemoration.\\
	}
}
{
}

\Verse{13}
{
	\hOther{}
}
{
	\eOther{
		“And you shall make settings of gold\\
	}
}
{
}

\Verse{14}
{
	\hOther{}
}
{
	\eOther{
		and two chains of pure gold. You shall make them twisted, rope work,
and put the rope chains on the settings.\\
	}
}
{
}

\Verse{15}
{
	\hOther{}
}
{
	\eOther{
		“And you shall make a breastplate of judgment, designer’s work. You
shall make it like the work of the ephod. You shall make it gold, blue,
and purple and scarlet and woven linen.\\
	}
}
{
}

\Verse{16}
{
	\hOther{}
}
{
	\eOther{
		It shall be square when doubled, its length a span and its width a
span.\\
	}
}
{
}

\Verse{2}
{
	\hOther{}
}
{
	\eOther{
		And you shall put a mounting of stones in it: four rows of stone. A
row of a carnelian, a topaz, and an emerald: the one row.\\
	}
}
{
}

\Verse{18}
{
	\hOther{}
}
{
	\eOther{
		And the second row: a ruby, a sapphire, and a diamond.\\
	}
}
{
}

\Verse{19}
{
	\hOther{}
}
{
	\eOther{
		And the third row: a jacinth, an agate, and an amethyst.\\
	}
}
{
}

\Verse{20}
{
	\hOther{}
}
{
	\eOther{
		And the fourth row: a beryl and an onyx and a jasper. They shall be
set in gold in their mountings.\\
	}
}
{
}

\Verse{21}
{
	\hOther{}
}
{
	\eOther{
		And the stones shall be with the names of the children of Israel,
twelve with their names; they shall be signet engravings, each with its
name, for twelve tribes.\\
	}
}
{
}

\Verse{22}
{
	\hOther{}
}
{
	\eOther{
		And you shall make twisted chains, rope work, of pure gold, on the
breastplate.\\
	}
}
{
}

\Verse{23}
{
	\hOther{}
}
{
	\eOther{
		And you shall make two rings of gold on the breastplate and put the
two rings on the two ends of the breastplate\\
	}
}
{
}

\Verse{24}
{
	\hOther{}
}
{
	\eOther{
		and put the two ropes of gold on the two rings at the ends of the
breastplate.\\
	}
}
{
}

\Verse{25}
{
	\hOther{}
}
{
	\eOther{
		And you shall put the two ends of the two ropes on the two settings,
and you shall put them on the ephod’s shoulder-pieces opposite the front
of it.\\
	}
}
{
}

\Verse{26}
{
	\hOther{}
}
{
	\eOther{
		And you shall make two rings of gold and set them on the breastplate’s
two ends on its side that is adjacent to the ephod, inward.\\
	}
}
{
}

\Verse{27}
{
	\hOther{}
}
{
	\eOther{
		And you shall make two rings of gold and put them on the ephod’s two
shoulder-pieces below, opposite the front of it, by its connection,
above the ephod’s designed belt.\\
	}
}
{
}

\Verse{28}
{
	\hOther{}
}
{
	\eOther{
		And they shall attach the breastplate from its rings to the ephod’s
rings with a blue string so it will be on the ephod’s designed belt and
the breastplate will not be detached from the ephod.\\
	}
}
{
}

\Verse{29}
{
	\hOther{}
}
{
	\eOther{
		And Aaron shall carry the names of the children of Israel in the
breastplate of judgment on his heart when he comes into the Holy, as a
commemorative in front of YHWH always.\\
	}
}
{
}

\Verse{30}
{
	\hOther{}
}
{
	\eOther{
		And you shall put the Urim and Tummim in the breastplate of judgment,
and they shall be on Aaron’s heart when he comes in front of YHWH, and
Aaron shall carry the judgment of the children of Israel on his heart in
front of YHWH always.\\
	}
}
{
}

\Verse{31}
{
	\hOther{}
}
{
	\eOther{
		“And you shall make the robe of the ephod all of blue.\\
	}
}
{
}

\Verse{32}
{
	\hOther{}
}
{
	\eOther{
		And its head-opening shall be within it. It shall have a binding for
its opening all around, weaver’s work. It shall be like the opening of a
coat of mail for him; it will not be torn.\\
	}
}
{
}

\Verse{33}
{
	\hOther{}
}
{
	\eOther{
		And you shall make on its skirts pomegranates of blue and purple and
scarlet, on its skirts all around, and bells of gold within them all
around:\\
	}
}
{
}

\Verse{34}
{
	\hOther{}
}
{
	\eOther{
		a golden bell and a pomegranate, a golden bell and a pomegranate, on
the robe’s skirts all around.\\
	}
}
{
}

\Verse{35}
{
	\hOther{}
}
{
	\eOther{
		And it shall be on Aaron for ministering: and the sound of it will be
heard when he comes to the Holy in front of YHWH and when he goes out,
so he will not die.\\
	}
}
{
}

\Verse{36}
{
	\hOther{}
}
{
	\eOther{
		“And you shall make a plate of pure gold and make signet inscriptions
on it: ‘Holiness to YHWH.’\\
	}
}
{
}

\Verse{37}
{
	\hOther{}
}
{
	\eOther{
		And you shall set it on a blue string, and it shall be on the
headdress. It shall be opposite the front of the headdress.\\
	}
}
{
}

\Verse{38}
{
	\hOther{}
}
{
	\eOther{
		And it shall be on Aaron’s forehead, and Aaron shall bear the crime of
the holy things that the children of Israel will sanctify, for all their
holy gifts. And it shall be on his forehead always for acceptance for
them in front of YHWH.

28:38,43. bear a crime. This difficult expression is thought to have a
range of meanings. In these passages it conveys that the priests bear an
enormous responsibility on account of their closeness to the holy.
Coming close to the holy objects or to the altar, they risk violation of
the sacred if they act incorrectly. The seriousness of this matter will
become manifest when two of Aaron’s sons violate the holy and die
(Leviticus 10). After the destruction of the first Temple in Jerusalem
and the loss of the ark, tablets, Tabernacle, and Urim and Tummim, much
of the feeling for the sacred must have been lost. And since the
destruction of the second Temple, our sense of the sacred has diminished
even more. So it has become ever harder to comprehend this aspect of the
biblical world and to appreciate the power and awe that were associated
with sacred objects, sacred places, and the priesthood.\\
	}
}
{
}

\Verse{39}
{
	\hOther{}
}
{
	\eOther{
		And you shall weave the coat in a pattern of linen and make a
headdress of linen. And you shall make a sash, embroiderer’s work,\\
	}
}
{
}

\Verse{40}
{
	\hOther{}
}
{
	\eOther{
		and you shall make coats for Aaron’s sons, and you shall make sashes
for them, and you shall make hats for them—for glory and for beauty.\\
	}
}
{
}

\Verse{41}
{
	\hOther{}
}
{
	\eOther{
		And you shall dress them—Aaron, your brother, and his sons with
him—and you shall anoint them and fill their hand and sanctify them, and
they shall function as priests for me.\\
	}
}
{
}

\Verse{42}
{
	\hOther{}
}
{
	\eOther{
		And make shorts of linen for them, to cover naked flesh; they shall be
from hips to thighs.\\
	}
}
{
}

\Verse{43}
{
	\hOther{}
}
{
	\eOther{
		And they shall be on Aaron and on his sons when they come to the Tent
of Meeting or when they come close to the altar to minister in the Holy,
so they will not bear a crime and die. It is an eternal law for him and
for his seed after him.\\
	}
}
{
}

