\Chapter{31}

\Verse{1}
{
	\hOther{}
}
{
	\eOther{
		31

¹ And YHWH spoke to Moses, saying,\\
	}
}
{
}

\Verse{2}
{
	\hOther{}
}
{
	\eOther{
		“See, I’ve called by name Bezalel, son of Uri, son of Hur, of the tribe
of Judah.\\
	}
}
{
}

\Verse{3}
{
	\hOther{}
}
{
	\eOther{
		And I’ve filled him with the spirit of God in wisdom and in
understanding and in knowledge and in every kind of work,\\
	}
}
{
}

\Verse{4}
{
	\hOther{}
}
{
	\eOther{
		to form conceptions to make in gold and in silver and in bronze\\
	}
}
{
}

\Verse{5}
{
	\hOther{}
}
{
	\eOther{
		and in cutting stone for setting and in cutting wood—for making things
in every kind of work.\\
	}
}
{
}

\Verse{6}
{
	\hOther{}
}
{
	\eOther{
		And I: here, I’ve put Oholiab, son of Ahisamach, of the tribe of Dan,
with him. And in the heart of every wise-hearted person I’ve put wisdom.
And they’ll make everything that I’ve commanded you:\\
	}
}
{
}

\Verse{7}
{
	\hOther{}
}
{
	\eOther{
		the Tent of Meeting and the Ark of the Testimony and the atonement dais
that is on it and all the equipment of the tent\\
	}
}
{
}

\Verse{8}
{
	\hOther{}
}
{
	\eOther{
		and the table and its equipment and the pure menorah and all its
equipment and the incense altar\\
	}
}
{
}

\Verse{9}
{
	\hOther{}
}
{
	\eOther{
		and the burnt offering altar and all its equipment and the basin and
its stand\\
	}
}
{
}

\Verse{10}
{
	\hOther{}
}
{
	\eOther{
		and the fabric clothes and the holy clothes for Aaron, the priest, and
his sons’ clothes for functioning as priests\\
	}
}
{
}

\Verse{11}
{
	\hOther{}
}
{
	\eOther{
		and the anointing oil and the incense of fragrances for the Holy.
According to everything that I’ve commanded you, they shall do.”\\
	}
}
{
}

\Verse{12}
{
	\hOther{}
}
{
	\eOther{
		And YHWH said to Moses, saying,\\
	}
}
{
}

\Verse{13}
{
	\hOther{}
}
{
	\eOther{
		“And you, speak to the children of Israel, saying, ‘Just: you shall
observe my Sabbaths, because it is a sign between me and you through
your generations: to know that I, YHWH, make you holy.\\
	}
}
{
}

\Verse{14}
{
	\hOther{}
}
{
	\eOther{
		And you shall observe the Sabbath, because it is a holy thing to you.
One who desecrates it shall be put to death. Because anyone who does
work in it: that person will be cut off from among his people.

31:14,15. put to death. The extreme punishment of execution for
violation of the Sabbath must be understood in the context of the
singular importance of the Sabbath: as sign of the covenant and as
imitatio Dei—see the previous comment. Also, as I discussed in my
comments on Genesis 1, the special place of the Sabbath in the creation
of the universe marks it as having cosmic significance as well as
historical significance. Combining the cosmic with history, it sets the
history of human events that begins with Genesis 1 in the context of the
very nature of the universe. And it makes time holy. Thus this long list
of holy objects concludes with this reminder that periods of time are
holy as well. The Sabbath is thus so phenomenally important that a
violation of the Sabbath bears an extraordinary punishment.\\
	}
}
{
}

\Verse{15}
{
	\hOther{}
}
{
	\eOther{
		Six days work shall be done, and in the seventh day is a Sabbath, a
ceasing, a holy thing to YHWH. Anyone who does work in the Sabbath day
shall be put to death.\\
	}
}
{
}

\Verse{16}
{
	\hOther{}
}
{
	\eOther{
		And the children of Israel shall observe the Sabbath, to make the
Sabbath through their generations, an eternal covenant.\\
	}
}
{
}

\Verse{17}
{
	\hOther{}
}
{
	\eOther{
		Between me and the children of Israel it is a sign forever, because
for six days YHWH made the skies and the earth, and in the seventh day
He ceased and was refreshed.’”\\
	}
}
{
}

\Verse{18}
{
	\hP{}
}
{
	\eP{
		And when He finished speaking with him in Mount Sinai, He gave the two
tablets of the Testimony to Moses, tablets of stone, written by the
finger of God.\\
	}
}
{
}

