\Chapter{32}

\Verse{1}
{
	\hE{}
}
{
	\eE{
		32

¹ And the people saw that Moses was delaying to come down from the
mountain, and the people assembled at Aaron and said to him, “Get up.
Make gods for us who will go in front of us, because this Moses, the man
who brought us up from the land of Egypt: we don’t know what has become
of him!”\\
	}
}
{
}

\Verse{2}
{
	\hE{}
}
{
	\eE{
		And Aaron said to them, “Take off the gold rings that are in your
wives’, your sons’, and your daughters’ ears, and bring them to me.”\\
	}
}
{
}

\Verse{3}
{
	\hE{}
}
{
	\eE{
		And all the people took off the gold rings that were in their ears and
brought them to Aaron.\\
	}
}
{
}

\Verse{4}
{
	\hE{}
}
{
	\eE{
		And he took them from their hand and fashioned it with a stylus and
made it a molten calf.

And they said, “These are your gods, Israel, who brought you up from the
land of Egypt!”\\
	}
}
{
}

\Verse{5}
{
	\hE{}
}
{
	\eE{
		And Aaron saw, and he built an altar in front of it, and Aaron called,
and he said, “A festival to YHWH tomorrow!”\\
	}
}
{
}

\Verse{6}
{
	\hE{}
}
{
	\eE{
		And they got up early the next day, and they made burnt offerings and
brought over peace offerings, and the people sat down to eat and drink,
and they got up to fool around.\\
	}
}
{
}

\Verse{7}
{
	\hJ{}
}
{
	\eJ{
		And YHWH spoke to Moses: “Go. Go down. Because your people, whom you
brought up from the land of Egypt, has corrupted.\\
	}
}
{
}

\Verse{8}
{
	\hJ{}
}
{
	\eJ{
		They’ve turned quickly from the way that I commanded them. They’ve made
themselves a molten calf, and they’ve bowed to it and sacrificed to it
and said, ‘These are your gods, Israel, who brought you up from the land
of Egypt!’”\\
	}
}
{
}

\Verse{9}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said to Moses, “I’ve seen this people; and, here, it’s a
hard-necked people.\\
	}
}
{
}

\Verse{10}
{
	\hJ{}
}
{
	\eJ{
		And now, leave off from me, and my anger will flare at them, and I’ll
finish them, and I’ll make you into a big nation!”\\
	}
}
{
}

\Verse{11}
{
	\hJ{}
}
{
	\eJ{
		And Moses conciliated in front of YHWH, his God, and said, “Why, YHWH,
should your anger flare at your people whom you brought out from the
land of Egypt with big power and with a strong hand?\\
	}
}
{
}

\Verse{12}
{
	\hJ{}
}
{
	\eJ{
		Why should Egypt say, saying, ‘He brought them out for bad, to kill
them in the mountains, and to finish them from on the face of the
earth’? Turn back from your flaring anger, and relent about the bad to
your people.\\
	}
}
{
}

\Verse{13}
{
	\hJ{}
}
{
	\eJ{
		Remember Abraham, Isaac, and Israel, your servants, that you swore to
them by yourself, and you spoke to them: ‘I’ll multiply your seed like
the stars of the skies, and I’ll give to your seed all this land that
I’ve said, and they’ll possess it forever.’”\\
	}
}
{
}

\Verse{14}
{
	\hJ{}
}
{
	\eJ{
		And YHWH relented about the bad that He had spoken, to do to His
people.\\
	}
}
{
}

\Verse{15}
{
	\hE{}
}
{
	\eE{
		And Moses turned and went down from the mountain. And the two tablets
of witness were in his hand, tablets written from their two sides: from
this side and from this side they were written.\\
	}
}
{
}

\Verse{16}
{
	\hE{}
}
{
	\eE{
		And the tablets: they were God’s doing. And the writing: it was God’s
writing, inscribed on the tablets.\\
	}
}
{
}

\Verse{17}
{
	\hE{}
}
{
	\eE{
		And Joshua heard the sound of the people in its shouting, and he said
to Moses, “A sound of war is in the camp.”\\
	}
}
{
}

\Verse{18}
{
	\hE{}
}
{
	\eE{
		And he said, “It’s not a sound of singing of victory, and it’s not a
sound of singing of defeat. It’s just the sound of singing I hear!”\\
	}
}
{
}

\Verse{19}
{
	\hE{}
}
{
	\eE{
		And it was when he came close to the camp, and he saw the calf and
dancing: and Moses’ anger flared, and he threw the tablets from his
hands and shattered them below the mountain.\\
	}
}
{
}

\Verse{20}
{
	\hE{}
}
{
	\eE{
		And he took the calf that they had made, and he burned it in fire and
ground it until it was thin, and he scattered it on the face of the
water, and he made the children of Israel drink!\\
	}
}
{
}

\Verse{21}
{
	\hE{}
}
{
	\eE{
		And Moses said to Aaron, “What did this people do to you, that you’ve
brought a big sin on it?!”\\
	}
}
{
}

\Verse{22}
{
	\hE{}
}
{
	\eE{
		And Aaron said, “Let my lord’s anger not flare. You know the people,
that it’s in a bad state.\\
	}
}
{
}

\Verse{23}
{
	\hE{}
}
{
	\eE{
		And they said to me, ‘Make gods for us who will go in front of us,
because this Moses, the man who brought us up from the land of Egypt: we
don’t know what has become of him!’\\
	}
}
{
}

\Verse{24}
{
	\hE{}
}
{
	\eE{
		And I said to them, ‘Whoever has gold: take it off.’ And they gave it
to me, and I threw it into the fire, and this calf came out!”\\
	}
}
{
}

\Verse{25}
{
	\hE{}
}
{
	\eE{
		And Moses saw the people, that it was turned loose, because Aaron had
turned it loose—to denigration among their adversaries!\\
	}
}
{
}

\Verse{26}
{
	\hE{}
}
{
	\eE{
		And Moses stood in the gate of the camp and said, “Whoever is for
YHWH: to me!” And all the children of Levi were gathered to him.\\
	}
}
{
}

\Verse{27}
{
	\hE{}
}
{
	\eE{
		And he said to them, “YHWH, God of Israel, said this: ‘Set, each man,
his sword on his thigh; cross over and come back from gate to gate in
the camp; and kill, each man, his brother and, each man, his neighbor
and, each man, his relative.’”\\
	}
}
{
}

\Verse{28}
{
	\hE{}
}
{
	\eE{
		And the children of Levi did according to Moses’ word, and about three
thousand men fell from the people in that day.\\
	}
}
{
}

\Verse{29}
{
	\hE{}
}
{
	\eE{
		And Moses said, “Fill your hand to YHWH today—because each man was at
his son and at his brother—and to put a blessing on you today.”\\
	}
}
{
}

\Verse{30}
{
	\hJ{}
}
{
	\eJ{
		And it was on the next day, and Moses said to the people, “You’ve
committed a big sin. And now I’ll go up to YHWH. Perhaps I may make
atonement for your sin.”\\
	}
}
{
}

\Verse{31}
{
	\hJ{}
}
{
	\eJ{
		And Moses went back to YHWH and said, “Please, this people has
committed a big sin and made gods of gold for themselves.\\
	}
}
{
}

\Verse{32}
{
	\hJ{}
}
{
	\eJ{
		And now, if you will bear their sin—and if not, wipe me out from your
scroll that you’ve written.”\\
	}
}
{
}

\Verse{33}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said to Moses, “The one who has sinned against me, I’ll wipe
him out from my scroll.

32:33–34. The one who has sinned against me, I’ll wipe him out.... And
now, go. Moses’ gesture is both selfless and audacious at the same time.
He takes a great risk to himself for the sake of winning forgiveness for
his people, but at the same time he is speaking more boldly to God than
he has dared to do before—and he is ascribing much importance to himself
in assuming that “wipe me out of your scroll” carries enough weight to
affect a divine decision. But God’s answer seems to brush aside Moses’
gesture, as if to say, “Don’t tell me whom to write in my scroll. I’ll
do whatever I’ll do. Now, go.”\\
	}
}
{
}

\Verse{34}
{
	\hJ{}
}
{
	\eJ{
		And now, go. Lead the people to where I spoke to you. Here, my angel
will go ahead of you. And, in the day that I take account, I’ll account
their sin on them.”\\
	}
}
{
}

\Verse{35}
{
	\hJ{}
}
{
	\eJ{
		And YHWH struck the people because they had made the calf, which Aaron
had made.\\
	}
}
{
}

