\Chapter{33}

\Verse{1}
{
	\hJ{}
}
{
	\eJ{
		33

¹ And YHWH spoke to Moses: “Go. Go up from here, you and the people whom
you brought up from the land of Egypt, to the land that I swore to
Abraham, to Isaac, and to Jacob, saying, ‘I’ll give it to your seed.’\\
	}
}
{
}

\Verse{2}
{
	\hJ{}
}
{
	\eJ{
		And I’ll send an angel ahead of you—and I’ll drive out the Canaanite,
the Amorite, and the Hittite and the Perizzite and the Hivite and the
Jebusite—\\
	}
}
{
}

\Verse{3}
{
	\hJ{}
}
{
	\eJ{
		to a land flowing with milk and honey, because I won’t go up among you,
because you’re a hard-necked people, or else I’ll finish you on the
way.”\\
	}
}
{
}

\Verse{4}
{
	\hJ{}
}
{
	\eJ{
		And the people heard this bad thing, and they mourned, and not a man
put his jewelry on him.\\
	}
}
{
}

\Verse{5}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said to Moses, “Say to the children of Israel: ‘You’re a
hard-necked people. If I would go up among you for one moment, I would
finish you! And now, put your jewelry down from on you, so I may know
what I’ll do with you.’”\\
	}
}
{
}

\Verse{6}
{
	\hJ{}
}
{
	\eJ{
		And the children of Israel divested their jewelry from Mount Horeb.\\
	}
}
{
}

\Verse{7}
{
	\hE{}
}
{
	\eE{
		And Moses would take the tent and pitch it outside of the camp, going
far from the camp, and he called it the Tent of Meeting. And it would
be: everyone seeking YHWH would go out to the Tent of Meeting, which was
outside of the camp.\\
	}
}
{
}

\Verse{8}
{
	\hE{}
}
{
	\eE{
		And it would be, when Moses would go out to the Tent, all the people
would get up, and they would stand up, each one at the entrance of his
tent, and they would look after Moses until he came to the Tent.\\
	}
}
{
}

\Verse{9}
{
	\hE{}
}
{
	\eE{
		And it would be, when Moses came to the Tent, the column of cloud would
come down, and it would stand at the entrance of the Tent, and He would
speak with Moses.\\
	}
}
{
}

\Verse{10}
{
	\hE{}
}
{
	\eE{
		And all the people would see the column of cloud standing at the
entrance of the Tent, and all the people would get up and bow, each at
the entrance of his tent.\\
	}
}
{
}

\Verse{11}
{
	\hE{}
}
{
	\eE{
		And YHWH would speak to Moses face-to-face, the way a man speaks to
his fellow man. And he would come back to the camp. And his attendant,
Joshua, son of Nun, a young man, would not depart from inside the Tent.\\
	}
}
{
}

\Verse{12}
{
	\hJ{}
}
{
	\eJ{
		And Moses said to YHWH, “See, you say to me, ‘Bring this people up,’
and you haven’t made known to me whom you will send with me. And you’ve
said, ‘I’ve known you by name,’ and also ‘You’ve found favor in my
eyes.’\\
	}
}
{
}

\Verse{13}
{
	\hJ{}
}
{
	\eJ{
		And now, if I’ve found favor in your eyes, make your way known to me,
so I may know you, so that I’ll find favor in your eyes. And see that
this nation is your people.”\\
	}
}
{
}

\Verse{14}
{
	\hJ{}
}
{
	\eJ{
		And He said, “My face will go, and I’ll let you rest.”\\
	}
}
{
}

\Verse{15}
{
	\hJ{}
}
{
	\eJ{
		And he said to Him, “If your face isn’t going, don’t take us up from
here.\\
	}
}
{
}

\Verse{16}
{
	\hJ{}
}
{
	\eJ{
		And by what then will it be known that I’ve found favor in your eyes,
I and your people? Is it not by your going with us? And we’ll be
distinguished, I and your people, from every people that is on the face
of the earth.”\\
	}
}
{
}

\Verse{17}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said to Moses, “I’ll do this thing that you’ve spoken as
well, because you’ve found favor in my eyes, and I’ve known you by
name.”\\
	}
}
{
}

\Verse{18}
{
	\hJ{}
}
{
	\eJ{
		And he said, “Show me your glory!”\\
	}
}
{
}

\Verse{19}
{
	\hJ{}
}
{
	\eJ{
		And He said, “I shall have all my good pass in front of you, and I
shall invoke the name YHWH in front of you. And I shall show grace to
whomever I shall show grace, and I shall show mercy to whomever I shall
show mercy.”\\
	}
}
{
}

\Verse{20}
{
	\hJ{}
}
{
	\eJ{
		And He said, “You won’t be able to see my face, because a human will
not see me and live.”\\
	}
}
{
}

\Verse{21}
{
	\hJ{}
}
{
	\eJ{
		And YHWH said, “Here is a place with me, and you’ll stand up on a
rock;\\
	}
}
{
}

\Verse{22}
{
	\hJ{}
}
{
	\eJ{
		and it will be, when my glory passes, that I’ll set you in a cleft of
the rock, and I’ll cover my hand over you until I’ve passed,\\
	}
}
{
}

\Verse{23}
{
	\hJ{}
}
{
	\eJ{
		and I’ll turn my hand away, and you’ll see my back, but my face won’t
be seen.”\\
	}
}
{
}

